### 2019-05-12 draft.tex
Add files via upload

% \documenclass: mandatorio, indica o tipo/formato de documento
% \documentclass[12pt,a4paper]{abntex2}
\documentclass[12pt,a4paper,ruledheader]{report}
\usepackage[inner=2.0cm,outer=2.0cm,top=3.0cm,bottom=2.0cm]{geometry}
\usepackage{enumerate}
%\usepackage{chngcntr}
\usepackage[toc]{appendix}
\usepackage{pdflscape}
%\usepackage{rotating}
\usepackage[portuguese,brazilian,english]{babel}
%\usepackage[portuguese,brazil,brazilian]{babel}
%\usepackage[utf8]{inputenc} %comentar para luatex
\usepackage[utf8]{luainputenc} %comentar para pdftex
\usepackage{lmodern}
\usepackage[T1]{fontenc}
% \usepackage{ae}
\usepackage{fontspec}
%\usepackage{lxfonts}
\usepackage{nomencl}
%\makenomenclature
%\renewcommand{\rmdefault}{lmss}
%\renewcommand{\rmdefault}{ptm}
\renewcommand{\sfdefault}{lmss}
%\renewcommand{\sfdefault}{ptm}
%\renewcommand{\ttdefault}{ptm} 
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{mathrsfs}
\usepackage{amssymb}
\usepackage{bm}
% melhoras na justificação
\usepackage{microtype}
\usepackage{setspace}
\usepackage{float}
\onehalfspacing
\usepackage{units}
\usepackage{parskip}
\usepackage{stmaryrd}
\usepackage{appendix}
\usepackage{epigraph}
%angulos em graus
%\usepackage{gensymb}
%símbolo de grau (não funciona com package gensymb
%um dos dois tem de ser comentado)
\newcommand{\degree}{\ensuremath{^\circ}}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{pdfpages} 
\usepackage{color}
\setlength{\parindent}{1.25cm}
%\setlength{\parskip}{0.2cm}
%\setlength\parindent{0pt}
%\setmarks{chapter}
\usepackage{listofsymbols}
\usepackage{fancyhdr}
% \usepackage{titlesec}
% \usepackage{ifthen}
% \usepackage{calc}
% \usepackage{abntex2abrev}
% \usepackage{setspace}
\usepackage{url}
\usepackage{cite}
% \usepackage[english,hyperpageref]{backref}
% Paginas com as citações na bibl
% \usepackage[num]{abntex2cite}
%\setlength{\headheight}{15.2pt}
\usepackage[breaklinks=true]{hyperref}
% \makeatletter
\hypersetup{
  colorlinks=true,    % false: boxed links; true: colored links
  linkcolor=blue,     % color of internal links
  citecolor=blue,     % color of links to bibliography
  filecolor=magenta,  % color of file links
  urlcolor=blue,
  bookmarksdepth=4
  pdftitle={Thesis}, 
  pdfauthor={Sabrina Tigik Ferr\~ao},
  pdfsubject={Thesis},
  pdfkeywords={plasma}{plasma kinetic theory}{collisions}
  {quasilinear theory}{weak turbulence theory} 
}
% \makeatother
\usepackage{cleveref}
\def\calE{{\cal E}}
\def\calL{{\cal L}}
\def\bk{{\bf k}}
\def\bq{{\bf q}}
\def\bv{{\bf v}}
\def\bu{{\bf u}}
\usepackage{makeidx}
%\maketitle
\makeindex
\definecolor{teal}{rgb}{0.0, 0.5, 0.5}
\definecolor{darkcyan}{rgb}{0.0, 0.55, 0.55}
\definecolor{darkblue}{rgb}{0.34,0.49,0.6}
\definecolor{darkgrayishcyan}{rgb}{0.275,0.38,0.35}
\definecolor{aurometalsaurus}{rgb}{0.43, 0.5, 0.5}
\definecolor{arsenic}{rgb}{0.23, 0.27, 0.29}
\definecolor{skobeloff}{rgb}{0.0, 0.48, 0.45}
\definecolor{skyblue}{rgb}{0.53, 0.81, 0.92}
\definecolor{raspberry}{rgb}{0.89, 0.04, 0.36}
\definecolor{amaranth}{rgb}{0.9, 0.17, 0.31}
\definecolor{softred}{rgb}{0.92,0.345,0.46}
\definecolor{darkelectricblue}{rgb}{0.33, 0.41, 0.47}
\definecolor{slategray}{rgb}{0.44, 0.5, 0.56}
\definecolor{cadet}{rgb}{0.33, 0.41, 0.47}
\definecolor{lapislazuli}{rgb}{0.15, 0.38, 0.61}
\definecolor{airforceblue}{rgb}{0.36, 0.54, 0.66}
\definecolor{cerulean}{rgb}{0.0, 0.48, 0.65}
\definecolor{chromeyellow}{rgb}{1.0, 0.65, 0.0}
\definecolor{deepsaffron}{rgb}{1.0, 0.6, 0.2}
\definecolor{fulvous}{rgb}{0.86, 0.52, 0.0}
\definecolor{pumpkin}{rgb}{1.0, 0.46, 0.09}
\definecolor{lilac}{rgb}{0.78, 0.64, 0.78}

\begin{document}
\frenchspacing 
\input{pagtit}
\pagenumbering{gobble}
%\input{folhadeaprovacao}
%\input{ty}
%\input{epi}
%\input{resumo}
%\input{param}{\pagestyle{empty}}
%\pagenumbering{none}
\begin{abstract}
  The weak turbulence theory has been an important theoretical tool
  for the study of nonlinear kinetic instabilities in plasmas. For
  a long time, this theory treated exclusively of the study of
  oscillatory processes and its influence in the plasma dynamics. The
  long-lasting timescale of nonlinear processes, however, suggests
  that collisional processes might have some effect in the late plasma
  dynamics, acting alongside nonlinear collective effects. In a recent
  work [P. H. Yoon et al., Phys. Rev. E 93:033203 (2016)], collisional
% LFZ180220: Coloquei espaço entre a vírgula e "Phys. Rev. E". E coloquei
% vírgula após "incorporated", na linha que segue.
  effects and collective processes were systematically incorporated,
  starting from first principles, in the weak turbulence theory equations,
  considering electrostatic oscillations. The outcome of this innovative
% LFZ180220: Mudei "outcomes" para "outcome", uma vez que o verbo está como
% "was".
% Sabrina: não seria melhor manter o "outcomes" e trocar "was" por "were"?
% É que tem mais de um resultado... Ou será que dá pra considerar esses
% dois itens como um resultado global?
  approach was a formal mathematical expression for the collisional
  damping rate for Langmuir and ion-sound waves, and the discovery of a
  new fundamental  process of emission of electrostatic fluctuations, in
  the ion-sound and Langmuir frequency range, caused by binary interactions
  of particles,
% LFZ180220: Não fica melhor "caused by binary interactions of particles",
% em lugar de "caused by particle scattering"? Se não achares adequado tens
% que voltar à forma anterior.
% Sabrina: Acho que pode ser. Na verdade meio que copiei parte dessa frase
% do artigo. Acho que o Peter quis dar ênfase ao fato de a mudança na forma
% da função de distribuição ser causada por espalhamento. Mas concordo que
% aqui pode causar certa confusão por causa do efeito de espalhamento das
% ondas. Então concordo, já fiz a mudança.
  named \emph{electrostatic bremsstrahlung}. In the present study we
  introduce the first numerical analysis of these two new equations and
  discuss the relevance of these numerical results in the solar physics scope.
  %The first work concerns the collisional damping equation, where we compare
  The first work to be discussed concerns the collisional damping equation, 
  and in it we compare
% LFZ180220: Fiz uma proposta de mmudança na frase. OK?
% Sabrina: OK
  the results of numerical integration of the rigorous expression with the
  damping rate calculated with the widely applied \emph{Spitzer formula}.
  % Besides that, the insignificance of the collisional damping rate gets
  % LFZ180220: Aqui também, proposta de mudança na frase. Entre outras coisas,
% estou propondo inversão das frases. OK?
% (verifiquei que essa nova ordem está de acordo com o que estava no resumo,
% abaixo)
% Sabrina: ah sim, a ideia de inserir essa frase veio quando eu estava
% escrevendo o resumo já, aí só acrescentei aqui, mas no lugar errado,
% pelo visto
  We show that the Spitzer approximation highly over-estimates the intensity
  of collisional attenuation of plasma waves. 
  The lack of relevance of the collisional damping rate gets further 
  % proven 
  demonstrated when we compare it with the collisionless (Landau) damping rate. 
  In the second work to be discussed, we analyze
  the so-far ignored electrostatic bremsstrahlung effect. We show that the
  presence of electrostatic bremsstrahlung emission modifies the Langmuir
  %spectrum, which in turn alters the shape of the initial Maxwellian electron
  %velocity distribution. 
  % LFZ180220: Proposta de mudança aqui. OK?
  % Sabrina: OK
  spectrum, which in turn alters the shape of the initial electron
  velocity distribution, assumed to be Maxwellian. 
  After a long time-evolution period (numerical
  integration), the system seems to arrive to a new quasi-steady state, in
  which the shape of the electron velocity distribution resembles the shape
  of a core-halo distribution function, i.e., composed by a Maxwellian core
  and a suprathermal tail. The outcomes of both analyses are unprecedented;
  the prospects and possibilities for further studies on this subject are
  promising.
  % Sabrina: não sei se preciso mencionar este trabalho aqui, mas coloquei
  % mesmo assim. Se achares denecessário, é só comentar o trecho a seguir:
  % LFZ180220: Acho que cabe sim mencionar esse trabalho. Mas proponho uma
  % mudança na frase. Acho exagerado dizer que "não tem nenhuma relação",
  % uma vez que o bremsstrahlung é um efeito colisional.
  % Sabrina: é, eu sei que alguma relação tem, só não sabia muito como
  % expressar isso sem me enrolar. Enfim, ficou muito boa a tua sugestão. 
  In the end, we also present an extra result, indirectly related to the
  main subject of this doctoral project, regarding the analysis of the
  complete set of electromagnetic weak turbulence equations, in the presence
  of a core-halo velocity distribution function. 
  %This work, however, was a
  %parallel research and does not have any relation with the main subject of
  %this doctoral working proposal.

  % Sabrina: o trecho abaixo foi removido do abstract para dar uma
  % "enxugada" no texto. Se achares necessário, recoloco.
  % To do so, we assume Maxwellian
  % velocity distribution for ions and electrons, and consider static ions
  % while the electrons evolve in time under the quasilinear velocity diffusion
  % process, which also includes spontaneous emission, collisional damping
  % and, of course, electrostatic bremsstrahlung in the wave kinetic equation.
  % For the particles we consider the quasilinear particle kinetic equation
  % added by the linearized Landau collision operator.
\end{abstract}
\newpage
\begin{otherlanguage}{brazilian}
  % \selectlanguage{portuguese}
  \begin{abstract}
    A teoria de turbulência fraca tem sido uma importante ferramenta
    teórica para o estudo de instabilidades cinéticas não lineares
    em plasmas. Por um longo tempo, esta teoria tratou exclusivamente
    do estudo de processos oscilatórios e de sua influência na dinâmica
    do plasma. Entretanto, a escala de tempo de longa duração dos
    processos não lineares, sugere que processos colisionais podem ter
    algum efeito na dinâmica do plasma, atuando em conjunto com os
    efeitos dos processos coletivos não-lineares. Em um trabalho recente
    [P. H. Yoon et al., Phys. Rev. E 93:033203 (2016)], efeitos colisionais
% LFZ180220: Coloquei espaço entre a vírgula e "Phys. Rev. E"
% Sabrina: OK
    e processos coletivos foram sistematicamente incorporados, partindo
    de primeiros princípios, nas equações da teoria de turbulência fraca,
    considerando oscilações eletrostáticas. O resultado dessa abordagem
% LFZ180220: Mudei para "O resultado", para combinar com "foi"
% Sabrina: Nossa, sério que eu errei isso aqui também? Geeente...
% Traduzi sem nem pensar a respeito, que vergonha.
    inovadora foi uma expressão matemática formal para a taxa de amortecimento
    colisional para ondas de Langmuir e íon-acústicas, e a descoberta de um
    novo processo fundamental de emissão de flutuações eletrostáticas, na
    faixa de frequência das ondas de Langmuir e das ondas íon-acústicas,
    %causado pelo espalhamento das partículas do plasma, nomeado como
% LFZ180220: Proponho mudança, compatível com a proposta no "abstract"
% Sabrina: OK
    causado por interações binárias entre partículas do plasma, nomeado como
    \emph{bremsstrahlung eletrostático}. Neste estudo, introduzimos as
    primeiras análises numéricas relativas a essas duas novas equações e
    discutimos a relevância desses resultados numéricos no contexto da física
    %solar. O primeiro trabalho se refere à nova equação para o amortecimento
    %colisional, no qual comparamos o resultado da integração numérica dessa
% LFZ180220: Proponho mudança similar àquela proposta no "abstract".
% Sabrina: OK
    solar. O primeiro trabalho a ser discutido se refere à nova equação para o 
    amortecimento colisional, e nele comparamos o resultado da integração
    numérica dessa
    expressão, com a largamente usada \emph{fórmula de Spitzer}. Com isso
    conseguimos mostrar que a aproximação de Spitzer super-estima em muito
    a intensidade da atenuação colisional das ondas de plasma. Além disso,
% LFZ180220: Aqui o ordenamento das frase já estava adequado, e de acordo com
% a mudança proposta no "abstract". So faço uma pequena mudança no texto. OK?
    %a insignificância da taxa de amortecimento colisional se comprova quando
% Sabrina: OK
    a falta de relevância da taxa de amortecimento colisional fica
    demonstrada quando
    a comparamos com a taxa de amortecimento não colisional (de Landau).
    No segundo trabalho, nós analizamos o até então ignorado efeito de
    \emph{bremsstrahlung} eletrostático. Nó mostramos que a presença da
    emissão de \emph{bremsstrahlung} eletrostático modifica o espectro
    das ondas de Langmuir que, por sua vez, altera a forma da função de
    %distribuição inicial dos elétrons, que é Maxwelliana. Após um longo
% LFZ180220: Mudança compatível com a mudança proposta no "abstract".
% Sabrina: OK
    distribuição inicial dos elétrons, suposta Maxwelliana. Após um longo
    tempo de evolução temporal (integração numérica), o sistema parece
    chegar a um novo estado quase-estacionário, no qual a forma da função
    de distribuição de velocidades dos elétrons lembra a forma de uma função
    de distribuição núcleo-halo, ou seja, composta por um núcleo Maxwelliano e
    uma cauda supratérmica. Os resultados de ambas análises são sem precedentes;
    as perspectivas e as possibilidades para novos estudos neste assunto são
    promissoras.
    % Sabrina: não sei se preciso mencionar este trabalho aqui, mas coloquei
    % mesmo assim. Se achares denecessário, é só comentar o trecho a seguir:
% LFZ180220: Mudança proposta similar à que foi proposta no "abstract":
    %No final é também apresentado um resultado extra, relativo à
% Sabrina: OK
    No final é também apresentado um resultado extra, indiretamente relacionado
    ao assunto principal desse projeto de trabalho de doutorado, relativo à
    análise do conjunto completo de equações eletromagnéticas da teoria de
    turbulência fraca, na presença de uma função de distribuição de velocidades
    núcleo-halo. 
    %Este trabalho, no entanto, não tem relação com o assunto
    %principal dessa proposta de trabalho de doutorado.
  \end{abstract}
\end{otherlanguage}
% \input{resumo}
\pagenumbering{roman}
\tableofcontents{\thispagestyle{empty}}
%\listoffigures{\thispagestyle{empty}}
\pagestyle{fancy}
\pagenumbering{arabic}
\fancyhf{}
\renewcommand{\headrulewidth}{0.5pt}
\lhead{\nouppercase{\it \leftmark}}
\rhead{\thepage}
\setcounter{page}{0}

% LFZ180216: O título não está aqui, mas pode ser discutido um pouco.
% A questão é que parece dar ênfase demais a processos colisionais. A gente
% estuda a evolução temporal do sistema, incluindo processos colisionais. Parece
% meio forte dizer que se estuda a evolução de processos colisionais, apenas.
% Por outro lado, se ficar assim, acho que deve ser "collisional processes"
% em lugar de "colisional process"
% Sabrina: Eu mudei um pouco o título pra incluir a teoria de turbulência
% fraca. Ficou meio grande, mas fazer o quê? Não tirei "plasmas
% astrofísicos" porque acho que dá uma vaga ideia de com que tipo de plasma
% estamos lidando. Eu acho melhor do que escrever "low density and fully
% ionized plasmas", o que deixaria o título maior ainda. Mas, se achares
% necessário, posso tirar a menção a plasmas astrofísicos e deixar sem nada
% que caracterize o plasma, ou colocar "low density and fully ionized plasmas".
% O que achares melhor.
% Sabrina 20/02: Sem comentários a respeito do título?
\chapter{Introduction}
\label{cha:intro}
In the context of the plasma kinetic theory, processes
involving waves and kinetic instabilities, the so-called\emph{
  collective processes}, are almost exclusively associated with
situations in which the effects of collisional dissipation can
be neglected, what happens when the studied phenomenon evolves
in a much shorter 
% LFZ180216: "much shorter" ?
% Sabrina: OK
time-scale than the collisional relaxation time
of the plasma in question \cite{akhi1967}. In such cases, the
plasma dynamics may be described by the Vlasov-Maxwell system, 
% LFZ180216: Acho que vai vírgula depois de "system"
% Sabrina: OK
a complex set of coupled equations whose solution invariably will
depend on some degree of approximation. In the presence of small
amplitude oscillations in a fully ionized plasma, we can make use
of perturbation theory in order to solve such complicated system
\cite{klimo}. From this method, one may obtain simpler approximations
like the linear theory and the quasilinear formalism, and also
more complex formulations, like the weak turbulence theory, which
takes into account low-order nonlinearities on the plasma dynamics.

With the lowest order of this chain of perturbative approximations,
the linear theory, it is possible to obtain the dispersion relations,
mathematical expressions that not only help us on identifying the
different oscillatory modes that may be excited in plasmas, but also
wholly characterizes these oscillations. 
% LFZ180216: Como está no plural, "dispersion relations", acho que a frase
% deve seguir como:
% "mathematical expressions that not only help us on identifying the
% different oscillatory modes that may be excited in plasmas, but also
% wholly characterize these oscillations."
% Sabrina: OK
Valuable information like
how these waves propagate and the frequencies that will resonate with
the plasma particles, resulting in damping or amplification of these
% LFZ180216: "of these"?
% Sabrina: OK
oscillations \cite{bitt,chen,gurnett2017}, are given by the dispersion
relations. This information, however, is static. 
% LFZ180216: "is static", ao invés de "it is static"? Acho que o sujeiro já
% é "This information", não precisa do "it".
% Sabrina: OK
There is no way to
know, based solely on the linear formulation, any further development
of the system, how these waves will evolve in time from a given initial
state, for instance. Thus, to clarify if these oscillations will grow
until their amplitudes become too large to be treated by a perturbative
method, or if they will rapidly increase and saturate, or if they will
be completely damped, or if they will decrease a little and then saturate, 
a certain degree of nonlinearity must be taken into account. That is the
purpose of the quasilinear approximation.
% LFZ180216: Sugestão:
% "Thus, to clarify if these oscillations will grow
% until their amplitudes become too large to be treated by a perturbative
% method, or if they will rapidly increase and saturate, 
% or if they will be completely damped,
% or if they will decrease a little and then saturate, 
% a certain degree of nonlinearity must be taken
% into account. That is the purpose of the quasilinear approximation."
% Sabrina: OK

In the quasilinear theory, low-order nonlinear terms are kept in
the equation for the time evolution of the velocity distribution
function. The velocity distribution will then evolve in time
through a process of diffusion in velocity space,
% LFZ180216: Acho que não está errado, mas me parece melhor "through a
% process of diffusion in velocity space,"
% Sabrina: OK
 in which the diffusion
coefficient depends on the spectral energy density of the waves.
The dispersion relation is formally given by the same expression
obtained under the linear theory, except that now it 
depends on a time-dependent velocity distribution function, 
% LFZ180216: Suggestion: depends on a time-dependent velocity
% distribution function,
% Sabrina: OK
which must vary in a much slower
time-scale than the period of the plasma oscillations. Under such
condition, the gradual changing on the velocity space shape slowly
modifies the wave spectrum, whose new form will then alter the
velocity distribution function and so on, until a new quasi-stationary
equilibrium state is attained \cite{gurnett2017}. However, depending
on the phenomenon being described this saturation state reached
under the quasilinear approximation might keep on evolving if higher
order nonlinearities are taken into account \cite{akhi2}. This kind
of nonlinear analysis is given by the \emph{weak turbulence theory},
which is the next step in this chain of perturbative approximations.

Mostly developed in the period between the late $1950$s and early
$1970$s \cite{Kadomtsev1965,Tsytovich1967,saggal,tsynlep,david,
  tsyitotp,akhi2,tsytotp,mel}, the weak turbulence theory has
become a valuable theoretical tool for the analysis of nonlinear
phenomena in plasmas since then, being applied in several studies
until nowadays \cite{Grognard1982,McClements87b,Hanssen1991,
  Edney2001,Kontar2001,Kontar2002,THD13}. Its complex formulation
is constituted by a set of coupled kinetic equations, which describe
the time evolution of the velocity distribution functions of the
plasma particles and the time evolution of the spectral intensities of
the plasma wave modes. The development of the weak turbulence theory
was resumed in a relatively recent series of papers, where the author,
starting from first principles, has extended the original formalism in
order to include new effects. In the initial work, it was considered
only the propagation of electrostatic oscillations, 
% LFZ180216: Em lugar do trecho acima, acho melhor dizer "it was considered
% only the propagation of electrostatic oscillations,"
% Isso porque a frase anterior falava que novos efeitos tinham sido
% incluidos ao formalismo, e dessa forma o "added" parece indicar que as
% oscilações eletrostáticas foram adicionadas, como novos efeitos, e não 
% é o caso.
% Sabrina: OK
taking into account the
effects of both wave-wave and wave-particle interactions \cite{Yoon00}.
Later, the formalism was expanded, and the effects of discrete particle,
% LFZ180216: "discrete particle effects"?
% Sabrina 20/02: acho que passei batido por esse antes...
related to spontaneous emission and spontaneous scattering processes
were included \cite{Yoon05a}. In a further extension, the effects of
the propagation of electromagnetic waves were incorporated into the
revised formulation \cite{Yoon06,Yoon2012b}.

The equations of this revised version of the weak turbulence theory
have been the subject of extensive studies involving nonlinear analysis
and two-dimensional numerical integration applied to the time evolution
of the Langmuir turbulence \cite{ZGPY08,Ziebell2012,YZGLW12,
  ZYGP14a,ZYGP14b} in a fully ionized and unmagnetized plasma, and in
other studies that also include the emission of electromagnetic waves
\cite{ZYSGP14c,ZYPGP15,ZPYGP16}. Some studies
using a one-dimensional approach have also been made 
\cite{ZiebellGY01,GaelzerZY02,GZVYR08}.
% LFZ180216: Nessa parte final da frase a ideia não era dizer "other studies
% that also include the emission of electromagnetic waves"?
%
% Sabrina: Pode ser. Acho, traduzi mal o texto do plano de pesquisa
% para o PDSE.
% LFZ180220: No plano para o PDSE havia uma frase mais ambígua do que essa que
% propus aqui. Dizia "estudo de processos de emissão envolvendo ondas de
% Langmuir". Nota que se diz "processos de emissão", sem especificar o tipo.
% E depois "envolvendo ondas de Langmuir". Não era apenas "emissão de ondas
% de Langmuir", como tinhas escrito na primeira versão. Poderíamos colocar
% a mesma frase do PDSE, mas acho que esta que diz "also include the emission
% of electromagnetic waves" também serve. A frase anterior fala em turbulência
% de Langmuir", e essa fala em "also include" outros efeitos. OK?
% Sabrina: OK
%
% LFZ180216: Outra coisa: Poderia haver aqui uma frase como "Some studies
% using a one-dimensional approach have also been made 
% \cite{ZiebellGY01,GaelzerZY02,GZVYR08}."
% Na verdade, essa referência GZVYR08, se aparecer aqui assim como sugiro, deve
% sair da frase anterior onde estão mmencionadas análises bi-dimensionais.
% Sabrina: Desculpa, mas não entendi bem como escrever essa parte, até porque
% tenho pouca familiaridade com esses trabalhos em 1D. Na verdade não tenho eles
% nem em  bibtex, nem em pdf. Mas se quiseres editar o texto para colocar eles
% e adicionar o bibtex no papers.bib, ficarei muito agradecida. Se eu for fazer
% isso, vai me tomar um tempo que infelizmente não tenho...
% LFZ180220: OK, vou fazer a mudança conforme estava proposto, e adicionar as
% referências.
% Sabrina: Obrigada!
The Langmuir turbulence is a by-product 
% LFZ180216: "by-product"?
% Sabrina: OK
of the instability generated when an energetic electron beam interacts with
a background plasma. The electron beam alters the electron velocity
distribution triggering the so-called \emph{bump-in-tail instability}.
Besides being recurrently used in textbooks as an illustrative example
of the quasilinear diffusion process \cite{akhi2,chen,gurnett2017}, the
bump-in-tail instability also has an essential role in the study of type
II and type III radio bursts \cite{Emslie1984,Hannah2009,ZVST11,Hannah2011,
  KK12,RR14,BNKR14}. In this context, the relevance of a more accurate
description of nonlinear kinetic instabilities in plasmas, represented
here by the beam-plasma interaction, becomes clear.

The next step towards a more complete description of weakly-turbulent
processes in plasmas is the inclusion of collisional effects in the
formalism. So far, the effects of binary collisions have been neglected
under the time-scale argument, mentioned in the first paragraph. This
assumption can be considered quite precise for the evolution of the
bump-in-tail instability under the quasilinear approximation. In such
regimen, the plasma quickly saturates in a quasi-equilibrium state and
the time evolution entirely ceases. However, when nonlinear processes
are considered in the dynamics, one cannot be sure if this argument
still holds. Basically, for the system to evolve inside the weak
turbulence theory limitations, the incident beam must be tenuous, and
the oscillations must have low amplitude (after all, the turbulence
ought to be weak). Under such conditions, the time evolution of the
system occurs in a time interval that is way longer than the oscillation
period of the plasma waves being studied. In fact, there are studies that
show that nonlinear effects keep acting in the system in a time-scale that
goes far beyond than the saturation time of the quasilinear instability,
to the extent that an asymptotic analysis of the new quasi-equilibrium
state of the turbulent process becomes relevant \cite{Yoon2012c,ZYGP14a,
  ZYGP14b,ZYSGP14c,ZYPGP15}.

The hypothesis about the probable relevance of binary
collisions in the nonlinear dynamics of the beam-plasma
interaction was numerically tested in \cite{Tigik2016a}.
In this work a linearized form of the Landau collision
integral was added into the particle kinetic equation
and the complete self-consistent set of electrostatic
weak turbulence equations was numerically integrated in
two-dimensions. It was shown that collisions indeed do
affect the plasma dynamics in a time-scale that is very
close to the time-scale of action of nonlinear effects.
Beyond the purely theoretical conjecture, combining
collective processes and collisional effects have some
important applications in solar physics. In the solar
hard X-ray analysis, for instance, the interpretation
models that employ quasilinear/nonlinear oscillatory
instabilities with some kind of collisional dissipation
(collisional damping for the waves, binary collisions for
the particles) are usually empirically adapted merely by
adding an \emph{ad hoc} expression into the particles and wave
kinetic equations to fit the observed data \cite{PK95,
  Kohl1998,Veronig05,Brown2006,Kontar2011,KKDSSK11}, yet,
there is no rigorous theory to compare or support such
models. Moreover, though the formalism in \cite{Tigik2016a}
makes use of the full Landau collision integral in the
particle kinetic equation, it does not take into account
collisional damping effects in the wave equation, which is
widely used in these empirical models. The point is: until
that moment, there was not a proper theoretical tool to deal
with the combination of collective processes and collisional
interaction.

In a recent paper \cite{YZKS16}, it was presented the first rigorous
theory that, starting from first principles, incorporates collisional
effects into the already well established weak turbulence formalism.
The authors used 
% LFZ180216: Acho que podes escrever "The authors used ..." e mais abaixo na
% frase "they also kept ...", ou então "The authors use ..., they also keep".
% Como está misturas dois tempos verbais na mesma frase.
% Sabrina: OK, corrigi para "used"
the same standard weak turbulence perturbative method
but, instead of keeping only the collective eigenmodes in the linear
and nonlinear wave-particle interactions, they also kept the effects
of the non-collective fluctuations emitted by thermal particles. The
outcome is a complete first principles nonlinear description of the
propagation of electrostatic oscillations in the presence of both wave
and particle collisional dissipation, and a hitherto unknown process.
This new effect depicts the emission of electrostatic radiation in the
eigenmode frequency range, which is caused by particle scattering. 
Since this is a form of braking radiation, 
% LFZ180216: "braking radiation"?
% Sabrina: OK
the authors named it as
\emph{electrostatic bremsstrahlung}.

Considering the context presented above, the working proposal of
this PhD Thesis is to put forward the first numerical analysis of
the new weak turbulence theory for collisional plasmas \cite{YZKS16}
and explore its applications in the solar physics scope. In
\Cref{cha:kin-theo} and \Cref{cha:weak-turb}, we make a brief review
of the basic plasma kinetic theory equations and the weak turbulence
theory, respectively. In \Cref{noneigenmode}, we introduce the
new generalization of the weak turbulence theory, which takes into
account the contribution of noneigenmode fluctuations during the
derivation of the particle and wave kinetic equations, resulting
in three new terms. In \Cref{main}, we contextualize the present
work regarding the theory discussed in the previous chapter and
present the results obtained so far by appending the two papers
published in this subject. In \Cref{cha:final}, we summarize the
results and discuss the perspectives of the present research.
Then, we propose a schedule for the remaining period 
% LFZ180216: "for the remaining period"?
% Sabrina: OK
until the thesis
defense. In the end we have three appendices. \Cref{appA} shows
an improved approximation for the second order susceptibility of
the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
presents a discussion about the asymptotic equilibrium state of the
Langmuir waves spectrum, considering a combination of a inverse
power-law kappa distribution and a Maxwellian distribution, in the
presence and in the absence of the electrostatic bremsstrahlung.
% LFZ180216: Tenho a impressão que essa última frase dá uma impressão errada.
% Se bem me lembro, é suposta a presença de uma distribuição do tipo
% "inverse power-law", mas na hora de calcular o bremsstrahlung se usa uma
% Maxwelliana. Sugiro uma frase mais ambígua, que não entra em detalhes, mas
% não diz que o bremsstrahlung foi calculado com a "Kappa". Por exemplo,
% "presents a discussion about the asymptotic equilibrium state of the
% Langmuir waves spectrum, considering a combination of a inverse power-law 
% kappa distribution and a Maxwellian distribution, in the presence and in the
% absence of the electrostatic bremsstrahlung."
% Sabrina: OK
The discussion in \Cref{appB} is
related with the article appended in \Cref{appC}, which is a
parallel research and is only slightly related with the main
subject of this work, that is the study of the combined action
of collective and collisional processes in weakly turbulent
plasmas, in the presence of electrostatic oscillations.

\chapter{Kinetic theory}
\label{cha:kin-theo}
The kinetic theory is the most fundamental description of the
plasma dynamics. Based on the concepts and methods of statistical
mechanics, together with the Maxwell equations, it provides a
formal self-consistent evolution of the plasma processes. This
formalism takes into account the variations of the velocity
distribution function $f({\bf r},{\bf v},t)$ in the phase-space
for each particle species. Statistically, this means that the
product between the distribution function and the volume element
in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
represents the probability of finding a particle of species
$\alpha$ in a volume element $d^3r$ around ${\bf r}$ and in a
velocity volume element $d^3v$ around ${\bf v}$, at the instant
$t$ \cite{klimo,klimon}.
% LFZ180216: Acho que deve ser "instant $t$" (ou seja, $t$ em itálico).
% Sabrina: OK

As mentioned before, in the absence of collisions, the plasma
dynamics is given by the Vlasov-Maxwell system, which is composed
by the Vlasov movement equation
\begin{equation}
  \label{eq:vlasov}
  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
  +\frac{q_{\alpha}}{m_{\alpha}}
  \left({\bf E}({\bf r},t)+\frac{1}{c}{\bf v}\times {\bf B}({\bf r},t) \right)
  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0,
\end{equation}
where the fields are described by the Maxwell equations
\begin{eqnarray}
  \label{max1}
  {\bf \nabla \cdot E}&=& 4\pi\rho\\
  \label{max2}
  {\bf \nabla \cdot B}&=& 0\\
  \label{max3}
    {\bf \nabla \times E}&=& -\frac{1}{c}
   \frac{\partial \bf B}{\partial t}\\
  \label{max4}
    {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t},
\end{eqnarray}
here given in cgs units, as commonly used in the
plasma physics literature.

In a statistical description, the charge density $\rho$
and the current density ${\bf J}$ depend on the velocity
distribution function
\begin{eqnarray}
  \label{qdensity}
    \rho({\bf r},t)
  &=&\sum_{\alpha}q_{\alpha}\int_v
    f_{\alpha}({\bf r},{\bf v},t)d^3v\\
\label{jdensity}
  {\bf J}({\bf r},t)
  &=&\sum_{\alpha}q_{\alpha}\int_v{\bf v}
  f_{\alpha}({\bf r},{\bf v},t) d^3v,
\end{eqnarray}
where $\alpha$ accounts for all charged species that constitute
the plasma. In a fully ionized hydrogen plasma, $\alpha=i$ for
ions and $\alpha=e$ for electrons.

Together, the expressions \eqref{eq:vlasov}, \eqref{max1},
\eqref{max2}, \eqref{max3}, \eqref{max4}, \eqref{qdensity}
and \eqref{jdensity} form a closed self-consistent set
of coupled nonlinear equations, which is responsible for the
description of a myriad of oscillatory processes that may
occur in plasmas and how they affect (and are affected by) the
velocity distribution function, in the absence of collisions.
The solution of such complicated system  will invariably depend
on some degree of approximation.

Considering the extensive variety of nonlinear processes that
might occur in a plasma, the appropriate way to deal with these
equations will depend on intrinsic characteristics of the plasma
and the nature of the phenomenon under consideration. For low
amplitude oscillations in a fully ionized plasma, one may employ
perturbation theory in order to solve the Vlasov equation
\cite{klimo}.

\subsection{Low amplitude electrostatic oscillations}
We are interested in the presence of high-frequency electrostatic
waves propagating in a homogeneous, fully ionized and unmagnetized
plasma, which is initially in equilibrium. Under such conditions,
we may consider ${\bf B=0}$. Thus, the Vlasov equation takes the
following form
\begin{equation}
  \label{vlasov-elec}
  \frac{\partial f_\alpha}{\partial t}+{\bf v \cdot \nabla}f_\alpha
+\frac{q_{\alpha}}{m_\alpha}\ {\bf E}\ {\bf\cdot \nabla_v}f_\alpha=0,
\end{equation}
where the electric field is given by
\begin{equation}
{\bf \nabla \cdot E}  = 4\pi\ \sum_\alpha q_\alpha 
\int_v  f_\alpha({\bf r},{\bf v},t) d^3v.
\label{leidegauss}
\end{equation}

Assuming low amplitude oscillations, we may approximate these equations
by introducing a small first order perturbation into the initial velocity
distribution function and, assuming ${\bf E}_0=0$, we introduce a small
first order electric field :
\begin{eqnarray}
  \label{fpert}
  f_{\alpha}({\bf r}, {\bf v},t)&=&f_{\alpha0}({\bf v})
	    +f_{\alpha1}({\bf r}, {\bf v},t),\\
  {\bf E}({\bf r},t)&=&{\bf E}_1({\bf r},t).
\label{Epert}
\end{eqnarray}

Until this point, the linear, quasilinear and nonlinear formulations
are identical. For a further evaluation we must decide if substitute
Eqs. \eqref{fpert} and \eqref{Epert} in Eq. \eqref{vlasov-elec} as they
are and then eliminate all nonlinear terms in the Vlasov equation. Or if
we take the average of Eqs. \eqref{fpert} and \eqref{Epert} and use the
averaged quantities to keep some degree of nonlinearity in the movement
equation. The subsequent deduction for each case was carefully detailed
and discussed in Chapters 2 and 3 of Ref. \cite{Tigik2015}. Therefore,
in order to maintain the focus on the objectives of the present work, we
% LFZ180216: Ao invés da frase acima, que tal a seguinte:
% "in order to maintain the focus on the objectives of the present work, we" ?
% Sabrina: OK
reproduce in the next chapter only a brief review of the deduction of
the weak turbulence theory equations.

\chapter{Weak turbulence theory}
\label{cha:weak-turb}
The weak turbulence theory is what we may call a ``borderline approach''
because, despite the fact that it deals with some more intense
instabilities, we must assure that these fluctuations are still inside
the weak turbulence limit, i.e., if the turbulence is weak enough to be
treated by a perturbative method. Such boundary is defined by a comparison
between the averaged kinetic energy of the particles per volume unity
$\calE_{kin}=\bar n m<v^2>/2$, and the energy density $\calE_f$, which
is associated with the fluctuations of the perturbative electric field.
Thus, by ``weak turbulence'' we mean
\begin{equation}
  \label{eq:weak}
  \calE_f \ll \calE_{kin},
\end{equation}
that is,
% LFZ180216: Não fica melhor com vírgula depois de "that is"?
% Sabrina: OK
the energy density of the fluctuations must be much smaller
% LFZ180216: Ou simplesmente "much smaller"?
% Sabrina: OK
than the kinetic energy density of the particles. This condition is
related to the slow wave-growing assumption \cite{david}, which is
central for the further development of nonlinear kinetic equations,
as will be discussed further.

The following discussion is a reduced version of the
comprehensive demonstration presented in Section 3.2 of
Ref. \cite{Tigik2015}. We also use the same notation and
logic sequence. Any deviation from \cite{Tigik2015} will
be explained in a footnote.

\section{Nonlinear kinetic equations}
\label{sec:kin-gen-eq}
Let us consider the propagation of electrostatic oscillations
in a homogeneous, unmagnetized and fully ionized plasma. Thus,
in the absence of collisions, the movement equation is given
by the electrostatic Vlasov equation
\begin{equation}
  \label{vlasov-nl}
  \frac{\partial f_a({\bf r}, {\bf v},t)}{\partial t}
+{\bf v \cdot \nabla}f_a({\bf r}, {\bf v},t)
+\frac{e_a}{m_a}{\bf E}({\bf r},t){\bf \cdot}
\frac{\partial f_a({\bf r},{\bf v},t)}{\partial \bf v}=0,
\end{equation}
where the electric field is given by
\begin{equation}
   {\bf \nabla \cdot E}({\bf r},t)
   =4\pi \hat n \sum_a e_a\int d^3 v f_a({\bf r}, {\bf v},t). 
\end{equation}
In the above equations, $f_a$ is the velocity distribution function,
where the subscript ``$a$'' is the kind of particle: $a=i$ for ions
and $a=e$ for electrons. For an overall neutral plasma, the number
density of
% LFZ180216: Sugestão "the number density of"
% Sabrina: OK
the ions and the electrons is the same $\hat n = \hat n_e = \hat n_i$.

Proceeding under the perturbative approach, we assume small
fluctuations and write the velocity distribution function
and the electric field as a sum of an equilibrium zero-order
term and a small first-order fluctuation
\begin{equation}
  \label{pert-nl}
  \begin{split}
      f_a({\bf r}, {\bf v},t)&=F_a({\bf v})+\delta f_a({\bf r}, {\bf v},t)\\
  {\bf E}({\bf r},t)&=\delta {\bf E}({\bf r},t),
  \end{split}
\end{equation}
where the zero-order electric field is assumed to be zero and
$F_a$ is the equilibrium velocity distribution.

Substituting \eqref{pert-nl} in \eqref{vlasov-nl} we obtain
\begin{equation} 
  \frac{\partial F_a}{\partial t}-\frac{e_a}{m_a}\
  \delta {\bf E \cdot} \frac{\partial F_a}{\partial \bf v}
+\frac{\partial\ \delta f_a}{\partial t}+{\bf v \cdot \nabla} \delta f_a
  +\frac{e_a}{m_a}\ \delta {\bf E \cdot}
  \frac{\partial\ \delta f_a}{\partial \bf v}=0.
\label{turb_ave_vlasov}
\end{equation}

Taking the average\footnote{For more details see subsection 3.1.1
  of Ref. \cite{Tigik2015}.} of Eq. \eqref{turb_ave_vlasov}, we
obtain a kinetic equation for the time evolution of the equilibrium
velocity distribution function
\begin{equation}
\frac{\partial F_a}{\partial t}
=-\frac{e_a}{m_a}\left< \delta {\bf E \cdot}
\frac{\partial\ \delta f_a}{\partial \bf v}\right>.
\label{form_par}
\end{equation}

Subtracting \eqref{form_par} from \eqref{turb_ave_vlasov} we obtain
an equation for the fluctuations
\begin{equation}
\frac{\partial\ \delta f_a}{\partial t}+{\bf v \cdot \nabla} \delta f_a
+\frac{e_a}{m_a}\ \delta {\bf E \cdot} \frac{\partial F_a}{\partial t}
+\frac{e_a}{m_a}\left[\delta {\bf E \cdot} \frac{\partial\ \delta f_a}{\partial \bf v}
-\left< \delta {\bf E \cdot}
\frac{\partial\ \delta f_a}{\partial \bf v}\right>\right]=0.
\label{flut}
\end{equation}

It is interesting to mention that at this stage, Eqs. \eqref{form_par}
and \eqref{flut} are precisely the same as those leading to the
quasilinear approximation.
% LFZ180216: Sugiro "are precisely the same as those leading to the
% quasilinear approximation."
% Sabrina: OK
Thus, at this point, one must choose whether the quasilinear approach
is enough or if a nonlinear formulation is necessary. In the first case
all terms proportional to $\delta {\bf E} \delta f_a$ are neglected in
the equation for the fluctuations\footnote{See subsection 3.1.2 of
  \cite{Tigik2015}.}. We shall keep these terms and proceed with the
nonlinear approach.

Now we assume the fluctuations may be decomposed in terms of the
Fourier-Laplace transformation over the fast time-scale of the
fluctuations, while amplitudes of the spectra vary in a slow
time-scale
\begin{equation}
\begin{split}
  \delta f_a({\bf r}, {\bf v},t)
  &=\int d^3k \int_L d \omega\
  \delta f^a_{{\bf k}, \omega}({\bf v}, t)e^{i({\bf k \cdot r}-\omega t)},\\
  \delta f^a_{{\bf k}, \omega}({\bf v}, t)
  &=\frac{1}{(2 \pi)^4} \int d^3 r \int_0^{\infty} dt\
  \delta f_a({\bf r}, {\bf v},t) e^{-i({\bf k \cdot r} - \omega t)},\\
  \delta {\bf E}({\bf r},t)
  &=\int d^3 k \int_L d \omega\ \delta {\bf E}_{{\bf k},\omega}(t)
  e^{i({\bf k \cdot r}-\omega t)},\\
  \delta {\bf E}_{{\bf k},\omega}(t)
  &=\frac{1}{(2 \pi)^4}\int d^3 r \int_0^{\infty} dt\
  \delta {\bf E}({\bf r},t) e^{-i({\bf k \cdot r} - \omega t)},
\end{split}
\end{equation}
% LFZ180216: Na última equação o denominador deve ser (2\pi)^4 ao invés de
% 2\pi^4, não?
% Sabrina: OK
where the integration path is taken along $L$, stretching from
$\omega = -\infty +i\sigma$ to $\omega=\infty+i\sigma$, in which
$\sigma >0$ and $\sigma \rightarrow 0$. We should emphasize that
we assume slow and adiabatic time-dependence for the spectral
amplitudes $\delta f^a_{{\bf k},\omega}({\bf v},t)$ and
$\delta {\bf E}(t)_{{\bf k}, \omega}$ in the above transformation.

The Fourier-Laplace transformation of nonlinear terms, where we
have the product of two functions, is given by the convolution
of these functions
\begin{equation}
\begin{split}
\frac{1}{(2\pi)^4}\int d^3r \int dt\ \delta f_a({\bf r}, {\bf v},t)\
\delta {\bf E}({\bf r},t)\ e^{-i({\bf k \cdot r}-\omega t)}
&=\int d^3 k' \int d \omega '\ \delta f^a_{{\bf k'}, \omega '}\
\delta {\bf E}_{{\bf k-k'},\omega-\omega '}\\
&=\int d^3 k' \int d \omega '\ \delta f^a_{{\bf k-k'}, \omega-\omega '}\
\delta {\bf E}_{{\bf k'},\omega '}.
\end{split}
\label{conv}
\end{equation}

Applying these transformations to the Vlasov-Maxwell system, we
obtain a set of hierarchic equations composed by the formal
particle kinetic equation \cite{Yoon00}
\begin{equation}
\frac{\partial F_a}{\partial t}=-\frac{e_a}{m_a}\frac{\partial}{\partial {\bf v}}
{\bf \cdot}\int d^3k \int d\omega \int d^3k'\int d\omega '\
\left<\delta{\bf E}_{{\bf k'},\omega '}\ \delta f^a_{{\bf k},\omega}\right>
e^{i({\bf k+k'}){\bf \cdot r}-i(\omega+\omega ')t};
\label{eq-cin-par}
\end{equation}
the equation of the fluctuating distribution evolution
\begin{equation}
\begin{split}
  \left(\omega-{\bf k \cdot v}
    +i\frac{\partial}{\partial t}\right)\delta f^a_{{\bf k},\omega}
  &=-i \frac{e_a}{m_a} \delta {\bf E}_{{\bf k},\omega}{\bf \cdot}
  \frac{\partial F_a}{\partial \bf v}
  -i\frac{e_a}{m_a}\frac{\partial}{\partial \bf v}
  {\bf \cdot} \int d^3k' \int d\omega '\\
  \times \bigr[\delta {\bf E}_{{\bf k'},\omega '}
  \delta f^a&_{{\bf k-k'},\omega-\omega '}
    -\left<\delta {\bf E}_{{\bf k'},\omega '}
    \delta f^a_{{\bf k-k'},\omega-\omega '}\right>\bigr];
\end{split}
\label{ev-par-per}
\end{equation}
and the differential form of the Gauss law for the electric field fluctuations
% and the Poisson equation for the electric field fluctuations
% LFZ180216: Aqui há um ponto que às vêzes me incomoda. O uso desse nome é
% frequente, o Peter costuma usá-lo, e "no embalo" eu uso muitas vêzes também.
% Mas a rigor a equação de Poisson é uma equação com o Laplaciano do potencial,
% não com a divergẽncia do campo (essa seria a lei de Gauss). É de se pensar
% se mantemos o costume, ou se vale a pena mudar ...
% (se mexer aqui tem que mudar mais adiante também)
% Sabrina: Pode ser assim?
% LFZ180220: Pode ser, com a mudança mais abaixo acompanhando.
\begin{equation}
   {\bf k \cdot}\delta{\bf E}_{{\bf k},\omega}=-4\pi \hat n i
   \sum_a e_a\int d^3v\ \delta f^a_{{\bf k}, \omega}.
\label{poisson-flut}
\end{equation}

The bracketed terms in Eqs. \eqref{eq-cin-par} and \eqref{ev-par-per}
represent the ensemble averages over the phases of the perturbation. One
may notice that the above set of equations is not closed, since the solution
for $\delta f^a_{{\bf k},\omega}$ requires knowing the two-body correlation
$\left<\delta f^a_{{\bf k},\omega}\delta f^a_{{\bf k'},\omega '}\right>$,
which depends on the tertiary correlation $\left<\delta f^a_{{\bf k},\omega}
  \delta f^a_{{\bf k'},\omega '}\delta f^a_{{\bf k''},\omega ''}\right>$, and
so on.

On the left-hand side of  Eq. \eqref{eq-cin-par} we have retained the
slow adiabatic derivative $i(\partial/\partial t)$. To deal with
that we employ two-step approximation \cite{Yoon00} and redefine
the angular frequency $\omega \rightarrow \omega+i \partial/\partial t$.
Then the equation for the
% LFZ180216: "the perturbed"?
% Sabrina: OK
perturbed distribution may be iteratively
solved up to third order in electric field.  The solution is then
inserted into Eq. \eqref{poisson-flut}
% the perturbed Poisson equation
% LFZ180216: Se o nome Poisson foi mudado anteriormente, deve ser mudado aqui
% também.
% Sabrina: coloquei o número da equação no lugar. Pode ser?
% LFZ180220: OK
and,  under the assumption that there are random phases associated with
the fluctuations, we take the appropriated ensembles averages. This
procedure results in the nonlinear spectral balance equation.
And is at this point, according to the two-time approximation, the
slow time derivative is reintroduced \cite{YZKS16}. This procedure
results in the nonlinear spectral balance equation\footnote{Equation
  \eqref{nlebe} is not in the same form that appears in Refs.
  \cite{Yoon00,Tigik2015}. The reason for this choice (see Eq. 2.59
  of Ref. \cite{YZKS16}), will become clear in the next chapter.}
\begin{eqnarray}
  &&\frac{i}{2}\frac{\partial \epsilon({\bf k},\omega)}{\partial \omega}
  \frac{\partial \left<\delta E^2\right>_{{\bf k},\omega}}{\partial t}
  +\mbox{Re}\,\epsilon({\bf k},\omega)\left<\delta E^2 \right>_{{\bf k},\omega}
+i\mbox{Im}\,\epsilon({\bf k},\omega)\left<\delta E^2 \right>_{{\bf k},\omega}
  \nonumber\\
  &&\qquad \qquad \qquad -\frac{2}{\pi}\frac{1}{k^2\epsilon^*({\bf k},\omega)}
     \sum_ae_a^2\int d{\bf v}\,\delta(\omega-{\bf k\cdot v})F_a({\bf v})
  \nonumber\\
  &&=-2\int d{\bf k'} \int d\omega '\
  \biggl\{ \left[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},
    \omega-\omega ')\right]^2
  \biggl[\frac{\left<\delta E^2\right>_{{\bf k-k'},\omega-\omega '}}
       {\epsilon({\bf k'},\omega ')}
  \nonumber\\
  &&+\frac{\left<\delta E^2\right>_{{\bf k'},\omega '}}
  {\epsilon({\bf k-k'},\omega-\omega ')}\biggr]
     -\bar \chi^{(3)}({\bf k'},\omega|-{\bf k'},-\omega '|{\bf k},\omega)
      \left<\delta E^2\right>_{{\bf k'},\omega'}\biggr\}
  \left<\delta E^2\right>_{{\bf k},\omega}\nonumber\\
  &&+2\int d{\bf k'} \int d\omega '
  \frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
{\epsilon^*({\bf k},\omega)}
\left<\delta E^2\right>_{{\bf k'},\omega '}
     \left<\delta E^2\right>_{{\bf k-k'},\omega-\omega '}
  \label{nlebe}\\
&&-\frac{4}{\pi}\int d{\bf k '} \int d\omega '\
\frac{1}{k^2|\epsilon({\bf k'},\omega ')|^2}
\biggl[ \frac{[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')]^2}
{\epsilon({\bf k-k'},\omega-\omega ')}
    \left<\delta E^2 \right>_{{\bf k},\omega}
  \nonumber\\
&&-\frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
{\epsilon^*({\bf k},\omega)}
\left<\delta E^2 \right>_{{\bf k-k'},\omega-\omega '}\biggr]
\sum_ae_a^2\int d{\bf v}\, \delta(\omega '-{\bf k \cdot v})F_a({\bf v})
  \nonumber\\
&&-\frac{4}{\pi}\int d{\bf k '} \int d\omega '\
\frac{1}{|{\bf k - k'}|^2|\epsilon({\bf k-k'},\omega-\omega ')^2}
\biggl[ \frac{[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')]^2}
{\epsilon({\bf k'},\omega ')}\left<\delta E^2 \right>_{{\bf k},\omega}
  \nonumber\\
&&-\frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
{\epsilon^*({\bf k},\omega)}
\left<\delta E^2 \right>_{{\bf k'},\omega '}\biggr]
\sum_ae_a^2\int d{\bf v}\, \delta(\omega-\omega '-{\bf (k-k')\cdot v})F_a({\bf v})
\nonumber
\end{eqnarray}
where on the left-hand side we have the expressions that correspond
to the linear equation and on the right-hand side are the nonlinear
expressions. The term
\begin{equation} 
\epsilon({\bf k},\omega)=1+\sum_a\chi_a({\bf k},\omega)
\end{equation}
is the linear dielectric response function.

In the above equations, $\sum_a \chi_a({\bf k},\omega)$
is the linear dielectric susceptibility,
$\sum_a \chi_a^{(2)}({\bf k}_1,\omega_1|{\bf k}_2,\omega_2)$ is the
second order nonlinear dielectric susceptibility and
$\sum_a \bar \chi_a^{(3)}({\bf k}_1,\omega_1|{\bf k}_2,\omega_2|{\bf k}_3,\omega_3)$
is the partial third-order nonlinear dielectric susceptibility.
For particles of species $a$, the dielectric susceptibilities
are respectively given by
\begin{equation}
\chi_a({\bf k},\omega)=-\frac{4\pi e_a\hat n_a}{k^2}
\int d^3v\ {\bf k \cdot g}_{{\bf k},\omega}F_a,
\end{equation}
\begin{equation}
\begin{split}
\chi_a^{(2)}({\bf k_1},\omega_1|{\bf k_2},\omega_2)
&=-\frac{1}{2}\frac{4\pi ie_a\hat n_a}{k_1k_2|{\bf k_1}+{\bf k_2}|}\\
\times\int d^3v\ {\bf g}_{{\bf k_1}+{\bf k_2}, \omega_1+\omega_2}
\bigl[{\bf k_1}&({\bf k_2}{\bf \cdot g}_{{\bf k_2},\omega_2})
 +{\bf k_2}({\bf k_1}{\bf \cdot g}_{{\bf k_1},\omega_1})\bigr]F_a,
\end{split}
\end{equation}
\begin{equation}
\begin{split}
  \bar \chi_a^{(3)}({\bf k_1},\omega_1|{\bf k_2},\omega_3|{\bf k_3},\omega_3)
  &=-\frac{1}{2}\frac{4\pi i e_a\hat n_a}{k_1k_2k_3|{\bf k_1}+{\bf k_2}+{\bf k_3}|}\\
  \times\int d^3v\
  ({\bf g}_{{\bf k_1}+{\bf k_2}+{\bf k_3}, \omega_1+\omega_2+\omega_3}{\bf \cdot k_1})
  {\bf g}&_{{\bf k_2}+{\bf k_3},\omega_2+\omega_3}{\bf \cdot}
  \bigl[{ \bf k_2}({\bf k_3}{\bf \cdot g}_{{\bf k_3},\omega_3})
  +{\bf k_3}({\bf k_2}{\bf \cdot g}_{{\bf k_2},\omega_2})\bigr]F_a,
\end{split}
\end{equation}
where ${\bf g}_{{\bf k},\omega}$ is a differential operator:
\begin{equation}
\label{op-dif}
  {\bf g}_{{\bf k},\omega}\equiv-\frac{e_a}{m_a}\
   \frac{1}{\omega-{\bf k \cdot v}+i0}\ \frac{\partial}{\partial \bf v}.
\end{equation}

Equation \eqref{nlebe} is a general expression. The usual
approach in plasma kinetic theory is to assume $|\mbox{Im}\
\epsilon({\bf k},\omega)|\ll|\mbox{Re}\ \epsilon({\bf k},\omega)|$.
Then, the imaginary part of \eqref{nlebe} leads to the wave kinetic
equation, while the real part leads to the wave dispersion equation,
whose solutions are the wave dispersion relations.

For the generalized particle kinetic equation is used a similar
procedure. In this work, however, we use only the quasilinear
approximation for the particle kinetic equation. Therefore, the
nonlinear particle equation will be omitted here\footnote{The
generalized form can be seen at Refs. \cite{Yoon00,Tigik2015}}.
Then, in the quasilinear approximation, the particle kinetic equation
is given by the following expression\footnote{\Cref{part}
  is not in the same form that it appears in Refs. \cite{Yoon00,Tigik2015}.
  The reason for this choice, which is based in Ref. \cite{YZKS16},
  will become clear in the next chapter.} \cite{YZKS16}
\begin{equation}
  \begin{split}
  \frac{\partial F_a}{\partial t}&=\frac{\pi e_a^2}{m_a^2}
  \int d{\bf k}\, \int d\omega\,
  \left( \frac{\bf k}{k}\cdot \frac{\partial}{\partial {\bf v}}\right)
  \delta(\omega -{\bf k \cdot v})\\
  &\times\left[\mbox{Im} \frac{m_a \epsilon({\bf k},\omega)}
    {2\pi^3k \left|\epsilon ({\bf k},\omega) \right|^2 } F_a
  +\left<\delta E^2\right>_{{\bf k},\omega}
\left( \frac{\bf k}{k}\frac{\partial F_a}{\partial \bf v} \right)  \right].
  \end{split}
\label{part}
\end{equation}

\subsection{Wave kinetic equation for linear eigenmodes}
Following the standard weak turbulence theory procedure, we assume
slow wave amplification, which means that
% LFZ180216: "means that"?
% Sabrina: OK
the wave growing process
does not affect the plasma dynamics. Hence, the normal modes
of oscillation are determined only by the linear response of
the plasma, while the interactions among waves and particles
are, in general, described by the nonlinear wave and particle
kinetic equations. Thus, we have a theory that depicts nonlinear
interactions between linear eigenmodes. The dispersion relations
for linear normal modes are given by the solutions of the real
part of the first term in Eq. \eqref{nlebe}
\begin{equation}
  0=\mbox{Re}\ \epsilon({\bf k},\omega)\left<\delta E^2 \right>_{{\bf k},\omega}.
  \label{real-lin}
\end{equation}

Let us assume $\omega=\omega^{\alpha}_{{\bf k},\omega}$ is the solution
of the above expression. Once the dispersion relation has been calculated,
we may write the spectral wave amplitude as follows
\begin{equation}
\left<\delta E^2\right>_{{\bf k},\omega}
=\sum_{\alpha}\bigl[I^{+\alpha}_{\bf k} \delta(\omega-\omega_{\bf k}^{\alpha})
  +I^{-\alpha}_{\bf k} \delta(\omega+\omega_{\bf k}^{\alpha})\bigr],
\label{wave-dens}
\end{equation}
where the $\pm$ signs represent the propagation direction
of their respective normal modes, denoted by $\alpha$. The
eigenmodes will be given by the oscillation modes that satisfy
the following condition
\begin{equation}
\label{eigenmode}
\epsilon({\bf k,\pm\, \omega_{{\bf k},\omega}^\alpha}) \approx 0.
\end{equation}

In an unmagnetized plasma, there are two possible electrostatic
eigenmodes: the  Langmuir $(\alpha= L)$ and ion-sound $(\alpha=S)$
waves. Therefore, after careful considerations and extensive
algebraic manipulations, the following kinetic equation for these
waves is obtained\footnote{\Cref{wave-lin} is not in the same form
  that it appears in Refs. \cite{Yoon00,Tigik2015}. The reason for this
  choice, which is based in Ref. \cite{YZKS16}, will become clear in
  the next chapter.}\cite{Yoon00,Yoon05a}
\begin{equation}
\begin{split}
  \frac{\partial I^{\alpha}_{\bf k}}{\partial t}
    =&-\frac{2 \mbox{Im}\ \epsilon({\bf k}, \sigma \omega_{\bf k}^{\alpha})}
    {\epsilon '({\bf k},\sigma \omega_{\bf k}^{\alpha})}I^{\alpha}_{\bf k}
    +\sum_{a=e,i}\frac{4e^2}{k^2[\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)]^2}
    \int d{\bf v}\, \delta(\sigma\omega_{\bf k}^\alpha-{\bf k \cdot v})
    f_a({\bf v})\\
    -&\sum_{\alpha,\beta}\ \sum_{\sigma '=\pm 1}
    \int d{\bf k '}\ A_{\alpha,\beta}({\bf k,k'})
    I_{\bf k'}^{\beta}\ I_{\bf k}^{\alpha}
    -\sum_{a=e,i}\frac{16 e_a^2}{\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}
    \sum_{\sigma '=\pm 1}\sum_{\beta=L,S}\\
    \times&\int d{\bf v}\int d{\bf k '}\,
    \frac{|\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^{\beta}|{\bf k-k'},
      \sigma \omega_{\bf k}^\alpha-\sigma '\omega_{\bf k'}^{\beta})|^2}
    {|{\bf k-k'}|^2|\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha
      -\sigma '\omega_{\bf k'}^{\beta})|^2}\\
    \times& \left[ \frac{I_{\bf k}^{\sigma \alpha}}
      {\epsilon({\bf k '},\sigma '\omega_{\bf k'}^\beta)}
    -\frac{I_{\bf k'}^{\sigma '\beta}}
    {\epsilon '({\bf k },\sigma \omega_{\bf k}^\alpha)}\right]
   \delta[\sigma \omega_{\bf k}^\alpha-\sigma '\omega_{\bf k'}^\beta
  -({\bf k-k'}){\bf \cdot v}] f_a({\bf v})\\
    -&4\pi \sum_{\alpha,\beta,\gamma}\ \sum_{\sigma ''= \pm 1}\int d{\bf k '}\
    \frac{|\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^\beta|{\bf k-k'},
      \sigma ''\omega_{\bf k-k'}^\gamma)|^2}
       {\epsilon '({\bf k},\sigma \omega_{\bf k}^{\alpha})}\\
       \times& \biggl(\frac{I_{\bf k-k'}^{\gamma}\ I_{\bf k}^{\alpha}}
       {\epsilon '({\bf k'},\sigma ' \omega_{\bf k'}^{\beta})}
       +\frac{I_{\bf k'}^{\beta}\ I_{\bf k}^{\alpha}}
       {\epsilon '({\bf k-k'},\sigma ''\omega_{\bf k-k'}^{\gamma})}
       -\frac{I_{k'}^{\beta}\ I_{\bf k-k'}^{\gamma}}
       {\epsilon '({\bf k},\sigma \omega_{\bf k}^{\alpha})}\biggr)
       \delta\bigl(\sigma \omega_{\bf k}^{\alpha}-\sigma ' \omega_{\bf k'}^{\beta}
       -\sigma '' \omega_{\bf k-k'}^{\gamma}\bigr),
       \label{wave-lin}
\end{split}
\end{equation}
where the coefficient $A_{\alpha,\beta}({\bf k,k'})$ is given by
\begin{equation}
\begin{split}
  &A_{\alpha,\beta}({\bf k,k'})
  =\frac{4}{\epsilon '({\bf k},\sigma \omega_{\bf k}^{\alpha})}
  \mbox{Im}\biggl(2\bigl[\chi^{(2)}({\bf k'},\sigma ' \omega_{\bf k'}^{\beta}|
    {\bf k-k'},\sigma \omega_{k}^{\alpha}-\sigma ' \omega_{\bf k'}^{\beta})\bigr]^2\\
    \times&{\cal P}\frac{1}{\epsilon({\bf k-k'},\sigma \omega_{\bf k}^{\alpha}
        -\sigma ' \omega_{\bf k'}^{\beta})}
       -\bar \chi^{(3)}({\bf k'},\sigma ' \omega_{\bf k'}^{\beta}|-{\bf k'},
       -\sigma ' \omega_{\bf k'}^{\beta}|{\bf k},
       \sigma \omega{\bf k}^{\alpha})\biggr),
       \label{coef-esp}
\end{split}
\end{equation}
and $\mathcal{P}$ is the principal value of the integral where
the coefficient belongs. In both expressions the following
short-hand notation has been used
\begin{equation}
\epsilon '({\bf k},\sigma \omega_{\bf k}^{\alpha})
=\frac{\partial \mbox{Re}\ \epsilon ({\bf k},\sigma \omega_{\bf k}^{\alpha})}
{\partial \sigma \omega_{\bf k}^{\alpha}}.
\end{equation}

On the right hand side of \eqref{wave-lin}, in the first two terms
we have the quasilinear wave-particle interaction, responsible for
the induced and spontaneous emission processes. The third and fourth
terms are nonlinear wave-particle interactions accounting for the
induced and spontaneous scattering processes. The last term is the
nonlinear wave-wave interaction describing the induced and spontaneous
three wave-decay processes.

\section{Weak turbulence equations for Langmuir and ion-sound waves}
The further evaluation of Eq. \eqref{wave-lin} demands a careful
analysis of the resonance conditions for each process and will not
be addressed here\footnote{A comprehensive description of this
  process can be seen in subsection 3.2.3 and section 3.3 of
  \cite{Tigik2015}.}. In the following equations we show the complete
wave kinetic equation for both $(L)$ and $(S)$ waves, in which the term
describing the effects of spontaneous emission is already included.

For $(L)$ waves we have:
\begin{displaymath}
\frac{\partial}{\partial t}\frac{I_{\bf k}^{\sigma L}}{\mu_{\bf k}^L}
=\mu_{\bf k}^L\,\frac{\omega_{pe}^2}{k^2}\int d^3v\;
\delta(\sigma\omega_{\bf k}^L-{\bf k}\cdot{\bf v})
\biggl(\hat{n}\,e^2\,F_e({\bf v})+\pi\,(\sigma\omega_{\bf k}^L)\,
\;{\bf k}\cdot\frac{\partial F_e({\bf v})}{\partial{\bf v}}
\,\frac{I_{\bf k}^{\sigma L}}{\mu_{\bf k}^L}\biggr)
\end{displaymath}
\begin{displaymath}
-\,\pi\sigma\mu_{\bf k}^L\,\omega_{\bf k}^L
\,\frac{e^2}{2T_e^2}\sum_{\sigma ',\sigma ''}\int d^3 k'\;
\frac{\mu_{{\bf k}'}^L\,\mu_{{\bf k}-{\bf k}'}^S
\,({\bf k}\cdot{\bf k}')^2}{k^2\,k'^2\,|{\bf k}-{\bf k}'|^2}
\biggl(\sigma '\omega_{{\bf k}'}^L\,
\frac{I_{{\bf k}-{\bf k}'}^{\sigma ''S}}{\mu_{{\bf k}-{\bf k}'}^S}
\frac{I_{\bf k}^{\sigma L}}{\mu_{\bf k}^L}
\end{displaymath}
\begin{equation}
+\,\sigma ''\omega_{{\bf k}-{\bf k}'}^L
\,\frac{I_{{\bf k}'}^{\sigma 'L}}{\mu_{{\bf k}'}^L}
\frac{I_{\bf k}^{\sigma L}}{\mu_{\bf k}^L}
-\sigma\omega_{\bf k}^L\,\frac{I_{{\bf k}'}^{\sigma 'L}}
{\mu_{{\bf k}'}^L}\frac{I_{{\bf k}-{\bf k}'}^{\sigma ''S}}
{\mu_{{\bf k}-{\bf k}'}^S}\biggr)
\;\delta(\sigma\omega_{\bf k}^L-\sigma '\omega_{{\bf k}'}^L
-\sigma ''\omega_{{\bf k}-{\bf k}'}^S)
\label{L,1}
\end{equation}
\begin{displaymath}
+\,\sigma\omega_{\bf k}^L\,\frac{e^2}{m_e^2\,\omega_{pe}^2}
\sum_{\sigma '}\int d^3 k'\int d^3v\;
\frac{\mu_{\bf k}^L\,\mu_{{\bf k}'}^L\,
({\bf k}\cdot{\bf k}')^2}{k^2\,k'^2}\;\delta[\sigma\omega_{\bf k}^L
-\sigma '\omega_{{\bf k}'}^L-({\bf k}-{\bf k}')\cdot{\bf v}]
\end{displaymath}
\begin{displaymath}
\times\,\biggl[\frac{\hat{n}\,e^2}{\omega_{pe}^2}
\,\biggl(\sigma\omega_{\bf k}^L\,\frac{I_{{\bf k}'}^{\sigma 'L}}
{\mu_{{\bf k}'}^L}
-\sigma '\omega_{{\bf k}'}^L\,
\frac{I_{\bf k}^{\sigma L}}{\mu_{\bf k}^L}
\biggr)\,[F_e({\bf v})+F_i({\bf v})]
+\pi\,\frac{m_e}{m_i}\,\frac{I_{{\bf k}'}^{\sigma 'L}}{\mu_{{\bf k}'}^L}
\frac{I_{\bf k}^{\sigma L}}{\mu_{\bf k}^L}\;({\bf k}-{\bf k}')
\cdot\frac{\partial F_i({\bf v})}{\partial{\bf v}}\biggr].
\end{displaymath}

In the first line on the right-hand side of \eqref{L,1}, one may recognize
the quasilinear resonance condition $\delta(\sigma\omega_{\bf k}^L
-{\bf k}\cdot{\bf v})$, which is responsible for the spontaneous
emission process and the induced emission process, respectively.
In the second and third lines we have the three wave-decay process,
which can be recognized by the wave-wave resonance condition 
$\delta(\sigma\omega_{\bf k}^L-\sigma '\omega_{{\bf k}'}^L
-\sigma ''\omega_{{\bf k}-{\bf k}'}^S)$ at the end of the third line.
Inside the parenthesis, the first two terms depicts the induced
wave-decay process, and the third term describes the spontaneous
wave-decay process. In the last two lines we have the equations
for the induced and spontaneous scattering processes. At the end
of the fourth line is the nonlinear wave-particle resonance
condition $\delta[\sigma\omega_{\bf k}^L-\sigma '\omega_{{\bf k}'}^L
-({\bf k}-{\bf k}')\cdot{\bf v}]$  and, in the last line, are the
terms of spontaneous and induced scattering, respectively.

For $(S)$ waves we have the same effects, in the same order:
\begin{displaymath}
\frac{\partial}{\partial t}\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}
=\mu_{\bf k}^S\,\frac{\omega_{pe}^2}{k^2}
\int d^3v\;\delta(\sigma\omega_{\bf k}^S-{\bf k}\cdot{\bf v})
\biggl[\hat{n}\,e^2\,[F_e({\bf v})+F_i({\bf v})]
\end{displaymath}
\begin{displaymath}
+\,\pi\,(\sigma\omega_{\bf k}^L)\,\biggl({\bf k}\cdot
\frac{\partial F_e({\bf v})}{\partial{\bf v}}
+\frac{m_e}{m_i}\;{\bf k}\cdot
\frac{\partial F_i({\bf v})}{\partial{\bf v}}\biggr)
\,\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}\biggr]
\end{displaymath}
\begin{displaymath}
-\,\pi\sigma\omega_{\bf k}^L\,\frac{e^2}{4T_e^2}
\sum_{\sigma ',\sigma ''}\int d^3k'\;
\frac{\mu_{\bf k}^S\,\mu_{{\bf k}'}^L\,\mu_{{\bf k}-{\bf k}'}^L
\,[{\bf k}'\cdot({\bf k}-{\bf k}')]^2}{k^2\,k'^2\,|{\bf k}-{\bf k}'|^2}
\biggl(\sigma '\omega_{{\bf k}'}^L\,
\frac{I_{{\bf k}-{\bf k}'}^{\sigma ''L}}{\mu_{{\bf k}-{\bf k}'}^L}
\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}
\end{displaymath}
\begin{equation}
+\,\sigma ''\omega_{{\bf k}-{\bf k}'}^L
\,\frac{I_{{\bf k}'}^{\sigma 'L}}{\mu_{{\bf k}'}^L}
\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}
-\sigma\omega_{\bf k}^L\,
\frac{I_{{\bf k}'}^{\sigma 'L}}{\mu_{{\bf k}'}^L}
\frac{I_{{\bf k}-{\bf k}'}^{\sigma ''L}}
{\mu_{{\bf k}-{\bf k}'}^L}\biggr)
\;\delta(\sigma\omega_{\bf k}^S-\sigma '\omega_{{\bf k}'}^L
-\sigma ''\omega_{{\bf k}-{\bf k}'}^L)
\label{S,1}
\end{equation}
\begin{displaymath}
+\,\sigma\omega_{\bf k}^L\,\frac{e^2}{m_e^2\,\omega_{pe}^2}
\sum_{\sigma '}\int d^3k'\int d^3v\;
\frac{\mu_{\bf k}^S\,\mu_{{\bf k}'}^S\,
({\bf k}\cdot{\bf k}')^2}{k^4\,k'^4\,\lambda_{De}^4}
\;\delta[\sigma\omega_{\bf k}^S-\sigma '\omega_{{\bf k}'}^S
-({\bf k}-{\bf k}')\cdot{\bf v}]
\end{displaymath}
\begin{displaymath}
\times\,\biggl[\frac{\hat{n}\,e^2}{\omega_{pe}^2}
\,W_{{\bf k},{\bf k}'}\,\biggl(\sigma\omega_{\bf k}^L\,
\frac{I_{{\bf k}'}^{\sigma 'S}}{\mu_{{\bf k}'}^S}
-\sigma '\omega_{{\bf k}'}^L\,
\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}\biggr)
\;[F_e({\bf v})+F_i({\bf v})]
\end{displaymath}
\begin{displaymath}
+\,\pi\,\frac{m_e}{m_i}\biggl(W_{{\bf k},{\bf k}'}
+\sigma\,\sigma '\,\frac{k'}{k}\biggr)
\,\frac{I_{{\bf k}'}^{\sigma 'S}}{\mu_{{\bf k}'}^S}
\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}\;({\bf k}-{\bf k}')
\cdot\frac{\partial F_i({\bf v})}{\partial{\bf v}}\biggr].
\end{displaymath}
In the scattering term we have
\begin{equation}
  \label{W}
W_{{\bf k},{\bf k}'}=\biggl(1+\frac{1}{\xi^2}\biggr)^2
\frac{1}{|{\bf k}-{\bf k}'|^4\,\lambda_{De}^4\,
|\epsilon_\parallel({\bf k}-{\bf k}',
\sigma\omega_{\bf k}^S-\sigma '\omega_{{\bf k}'}^S)|^2},
\end{equation}
where
\begin{equation}
  \label{eps-par}
\epsilon_\parallel({\bf k}-{\bf k}',
\sigma\omega_{\bf k}^S-\sigma '\omega_{{\bf k}'}^S)
=1+\frac{2\,({\bf k}\cdot{\bf k}'-\sigma\,\sigma\,k\,k')}
{|{\bf k}-{\bf k}'|^2\,(k-\sigma\,\sigma '\,k')^2\,\lambda_{De}^2}
\end{equation}
\begin{displaymath}
+\,i\,\biggl(\frac{\pi}{2}\frac{m_e}{m_i}\biggr)^{1/2}
\biggl[\exp\biggl(-\frac{m_e}{m_i}\frac{\xi}{2}\biggr)
+\biggl(\frac{m_i}{m_e}\frac{T_e^3}{T_i^3}\biggr)^{1/2}
\exp\biggl(-\frac{T_e}{T_i}\frac{\xi}{2}\biggr)\biggr],
\end{displaymath}
with
\begin{equation}
  \label{xi}
\xi=\frac{(\sigma\,k-\sigma ' k')^2}{|{\bf k}-{\bf k}'|^2}.
\end{equation}

Though Eq. \eqref{S,1} depicts the full wave kinetic equation for
ion-sound waves, the scattering term has always been neglected and
will not be considered in this work as well. The reason for that is
that the scattering of ion-sound waves caused by other ion-sound
waves evolves in a very slow time-scale. Indeed, we are interested
in describing collisional processes, which act in a long evolution
time. However, one must take one step at a time, and we do not
discard including ion-sound scattering in future analysis.

% LFZ180216: Nas aplicações esse termo de espalhamento tem sido sempre
% desprezado. Há algum comentário a esse respeito em algum lugar? Suponho que
% haja nos trabalhos anexados, mas talvez seja bom dizer algo a respeito
% aqui, não?
% Sabrina: Acrescentei. Que tu achas?
% LFZ180220: Acho que ficou bom. Só mudei uma ou duas palavras. Achei que
% as duas frase finais podem ser unidas. OK?
% Sabrina: OK

The particle kinetic equation is given by
\begin{equation}
\begin{split}
\frac{\partial F_a({\bf v})}{\partial t}&=\frac{\pi e_a^2}{m_a^2}
\sum_\sigma\sum_{\alpha=L,S}\int d^3k\ \biggl(\frac{\bf k}{k}
\cdot\frac{\partial}{\partial{\bf v}}\biggr)\ \mu_{\bf k}^\alpha
\delta(\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v})\\
&\times\biggl(\frac{m_a}{4\pi^2}\frac{\sigma\omega_{\bf k}^L}{k}
F_a({\bf v})+\frac{I_{\bf k}^{\sigma\alpha}}{\mu_{\bf k}^\alpha}
\frac{\bf k}{k}\cdot\frac{\partial F_a({\bf v})}{\partial{\bf v}}\biggr),
\end{split}
\label{Fa,1}
\end{equation}
where $a=i$ for ions and $a=e$ for electrons, and $\alpha=L,S$.

The following definitions were used to write the above equations
\begin{displaymath}
\frac{1}{\epsilon '_\parallel({\bf k},\sigma\omega_{\bf k}^L)}
=\frac{\sigma\mu_{\bf k}^L\,\omega_{\bf k}^L}{2},\qquad
\frac{1}{\epsilon '_\parallel({\bf k},\sigma\omega_{\bf k}^S)}
=\frac{\sigma\mu_{\bf k}^S\,\omega_{\bf k}^L}{2},\qquad
\end{displaymath}
\begin{displaymath}
\mu_{\bf k}^L=1,\qquad
\mu_{\bf k}^S=|k|^3\lambda_{De}^3\biggl(\frac{m_e}{m_i}\biggr)^{1/2}
\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2}.
\end{displaymath}

\chapter{Weak turbulence for collisional plasmas}
\label{noneigenmode}
In \Cref{cha:weak-turb} we made a brief review of the standard weak
turbulence theory procedure. Such procedure takes into account only
the contributions from the linear eigenmodes. The basic premise of this
conventional approach claims that only frequencies $\omega=\omega_{\bf k}$
that satisfy the dispersion relations are considered significant, even if
the general electrostatic fluctuations $\left<\delta E^2\right>_{{\bf k},\omega}$
are characterized by all ${\bf k}$ and $\omega$. Therefore, the fluctuations
whose $\omega \ne \omega_{\bf k}$, which characterize the noneigenmodes,
are ignored. In Ref. \cite{YZKS16} the authors present a generalization
of this customary approach, where, besides the traditional inclusion of
the normal modes, it is also taken into account the contribution from the
noneigenmode fluctuations. The result is a generalized expression for the
spectral energy density of the waves, with some remarkable consequences
for the wave and particle kinetic equations.

The generalized spectral energy density, which contains the noneigenmode
contribution, is the central factor of this new kinetic turbulence theory
for collisional plasmas. When
% LFZ180216: Será que precisa essa vírgula depois de "When"?
% Sabrina: definitivamente não. 
 it is substituted in the nonlinear terms of
the nonlinear spectral balance equation, two new terms appear in the wave
kinetic equation. The first term is a rigorous expression for the collisional
damping rate of plasma waves. The second term is a hitherto unknown process
of electrostatic radiation emission, in the eigenmode frequency range, due to
particle scattering. This underlying electrostatic form of braking radiation
% LFZ180216: "braking radiation" ?
% Sabrina: OK
was then called \emph{electrostatic bremsstrahlung} \cite{YZKS16}. For the
particle kinetic equation, the application of this generalized expression is
responsible for the arising of the Balescu-Lenard collision integral, without
any \emph{ad hoc} addition.

In this chapter, we provide a basic outline of the elaborated demonstration
imparted by the authors of \cite{YZKS16}. We start by showing how the
noneigenmodes contribution is included in the spectral energy density of the
waves. Then we show that the inclusion of the noneigenmodes does not affect
the quasilinear wave kinetic equation. In the next two subsections, we
exhibit, without entering in details, the effects of the new contribution
to the particle kinetic equation and the nonlinear particle kinetic equation.

\section{Inclusion of noneigenmodes}
Let us start considering the linear part of the spectral balance equation,
which corresponds to the left-hand side of Eq. \eqref{nlebe}
\begin{equation}
  \label{lin}
  \begin{split}
  \frac{1}{2}\frac{\partial \,\mbox{Re}\,\epsilon({\bf k},\omega)}{\partial \omega}
  \frac{\partial \left< \delta E^2 \right>_{{\bf k},\omega}}{\partial t}
  +&\,\mbox{Re}\,\epsilon({\bf k},\omega)
  \left< \delta E^2 \right>_{{\bf k},\omega}
  +i\, \mbox{Im}\,\epsilon({\bf k},\omega)
  \left< \delta E^2 \right>_{{\bf k},\omega}\\
  =&\frac{2}{\pi}\frac{1}{k^2\epsilon^{*}({\bf k},\omega)}
  \sum_a e^2_a\, \int d{\bf v}\,\delta(\omega-{\bf k \cdot v})f_a({\bf v}),
\end{split}
\end{equation}
where dielectric constant is given by
\begin{equation}
  \label{dielec}
  \epsilon({\bf k},\omega)=\sum_a \frac{4\pi e^2_a}{m_ak^2}\int d{\bf v}\,
  \frac{{\bf k \cdot}\partial f_a/\partial{\bf v}}{\omega-{\bf k \cdot v}+i0}.
\end{equation}

Then, taking the real part of \eqref{lin}, we have
\begin{equation}
  \label{real}
  \mbox{Re}\, \epsilon({\bf k},\omega)\left[
  \left\langle \delta E^2 \right\rangle_{{\bf k},\omega}
  -\frac{2}{\pi}\frac{1}{k^2|\epsilon({\bf k},\omega)|^2}
  \sum_a e_a^2 \int d{\bf v}\, \delta(\omega-{\bf k \cdot v})
  f_a({\bf v})\right]=0.
\end{equation}

In the above equation we have two possibilities to the wave-number
frequency space. If one is interested in the region of $({\bf k},\omega)$
in which $|\epsilon({\bf k},\omega)|^2\ne 0$, then the left- and right-hand
sides of \eqref{real} may be balanced by writing
\begin{equation}
  \label{balance}
  \left\langle \delta E^2 \right\rangle_{{\bf k},\omega}
  =\left\langle \delta E^2 \right\rangle_{{\bf k},\omega}^0,
\end{equation}
where
\begin{equation}
  \label{field-fluc}
  \left\langle \delta E^2 \right\rangle_{{\bf k},\omega}^0
  \equiv \frac{2}{\pi}\frac{1}{k^2|\epsilon({\bf k},\omega)|^2}
  \sum_a e_a^2 \int d{\bf v}\, \delta(\omega-{\bf k \cdot v})
  f_a({\bf v}).
\end{equation}

It is clear that the solution of \eqref{balance} depends on the denominator
$|\epsilon({\bf k},\omega)|^2$ not being zero. For eigenmodes, however,
$\epsilon({\bf k},\omega_{\bf k}^\alpha)=0$, meaning the denominator remains
nonzero only if $\omega \ne \omega_{\bf k}^\alpha$, i.e., if $\omega$ does
not satisfy the dispersion relation. Hence, the electric field fluctuation
$\left< \delta E^2 \right>_{{\bf k},\omega}^0$ must represent noneigenmodes
contribution. As exposed in \Cref{sec:kin-gen-eq} the standard theory is
concerned only with the normal oscillation modes, which are the solutions
of the dispersion relations, calculated in the vicinity of the zeros of
$\mbox{Re}\,\epsilon({\bf k},\omega)$.

Therefore, we have two distinct situations. In the first case,
when collective modes are not important, the electric field energy
can be expressed by Eq. \eqref{balance} with the electric field fluctuation
$\left< \delta E^2 \right>_{{\bf k},\omega}^0$ given by \eqref{field-fluc},
and the standard situation, in which collective modes are important,
then the wave electric field is determined by
\begin{equation}
  \label{collective}
  \begin{split}
  \left< \delta E^2 \right>_{{\bf k},\omega}
  -\left< \delta E^2 \right>_{{\bf k},\omega}^0
  &=\sum_{\sigma=\pm 1}\sum_{\alpha=L,S}
    I_{\bf k}^{\sigma \alpha}\delta(\omega-\sigma \omega_{\bf k}^\alpha)\\
  \mbox{Re}\, \epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)&=0.
\end{split}
\end{equation}

The theory that we are 
% LFZ180216: "The theory that we are ..."?
% Sabrina: OK
analyzing is a generalization of the standard weak
turbulence theory, in which both the eigenmode and noneigenmode are
included by defining the following quantity
\begin{equation}
  \label{Psi}
  \Psi_{{\bf k},\omega}\equiv\left< \delta E^2 \right>_{{\bf k},\omega}
  -\left< \delta E^2 \right>_{{\bf k},\omega}^0.
\end{equation}

Thus, the function $\Psi_{{\bf k},\omega}$ becomes the total eigenfunction
of Eq. \eqref{real}:
\begin{equation}
  \label{total}
  \mbox{Re}\, \epsilon({\bf k},\omega)\Psi_{{\bf k}, \omega}=0,
\end{equation}
where $\Psi_{{\bf k},\omega}$ can be expressed as
\begin{equation}
  \label{Psi-eigen}
  \Psi_{{\bf k},\omega}=\sum_{\sigma=\pm 1}\sum_{\alpha=L,S}
  I_{\bf k}^{\sigma \alpha}\delta(\omega-\sigma \omega_{\bf k}^\alpha),
\end{equation}
with the eigenvalue $\sigma \omega_{\bf k}^\alpha$ satisfying
\begin{equation}
  \mbox{Re}\, \epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)=0.
\end{equation}

This procedure encompasses these two situations by taking into account
the collective modes that satisfy the eigenmode condition, and the
non eigenmode contribution by generalizing Eq. \eqref{wave-dens},
as follows
\begin{equation}
  \label{gen-dens}
  \left< \delta E^2 \right>_{{\bf k},\omega}
  =\left< \delta E^2 \right>_{{\bf k},\omega}^0
  +\sum_{\sigma=\pm 1}\sum_{\alpha=L,S}
  I_{\bf k}^{\sigma \alpha}\delta(\omega-\sigma \omega_{\bf k}^\alpha).
\end{equation}

\subsection{Absence of noneigenmode contribution to quasilinear wave
  kinetic equation}
Let us start by including the noneigenmode term in the quasilinear
wave kinetic equation. Substituting Eq. \eqref{gen-dens} in the
imaginary part of Eq. \eqref{lin}, we have
\begin{equation}
  \begin{split}
 &\frac{\partial\, \mbox{Re}\,\epsilon({\bf k},\omega)}{\partial \omega}
  \frac{\partial \left< \delta E^2 \right>_{{\bf k},\omega}^0}{\partial t}
  + 2\, \mbox{Im}\,\epsilon({\bf k},\omega)
  \left< \delta E^2 \right>_{{\bf k},\omega}^0+\sum_{\sigma=\pm 1}\sum_\alpha\biggl[
    \frac{\partial \mbox{Re}\, \epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)}
    {\partial(\sigma\omega_{\bf k}^\alpha)}
    \frac{\partial I_{\bf k}^{\sigma \alpha}}{\partial t}\\
  &+2\,\mbox{Im}\,\epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)
    I_{\bf k}^{\sigma \alpha}\biggr]\delta(\omega-\sigma\omega_{\bf k}^\alpha)
=\mbox{Im}\,\frac{4}{\pi k^2\epsilon^{*}({\bf k},\omega)}
  \sum_a e^2_a\, \int d{\bf v}\,\delta(\omega-{\bf k \cdot v})f_a({\bf v}).
\end{split}
\end{equation}

Making use of
\begin{equation}
  \label{principal}
  \begin{split}
    \frac{1}{\epsilon({\bf k},\omega)}
    &=\mathcal{P}  \frac{1}{\epsilon({\bf k},\omega)}
    -\sum_{\sigma=\pm 1}\sum_{\alpha=L,S}
    \frac{i\pi \delta(\omega-\sigma\omega_{\bf k}^\alpha)}{\epsilon '({\bf k},\omega)}\\
    \frac{1}{\epsilon^*({\bf k},\omega)}
    &=\mathcal{P}\frac{1}{\epsilon^*({\bf k},\omega)}
    +\sum_{\sigma=\pm 1}\sum_{\alpha=L,S}
    \frac{i\pi \delta(\omega-\sigma\omega_{\bf k}^\alpha)}{\epsilon '({\bf k},\omega)},
  \end{split}
\end{equation}
where
\begin{displaymath}
  \epsilon '({\bf k},\omega)=\partial\,
  \mbox{Re}\, \epsilon({\bf k},\omega)/\partial \omega,
\end{displaymath}
we obtain
\begin{equation}
  \label{noneigenmode-ql}
  \begin{split}
 \epsilon '({\bf k},\omega)
  &\frac{\partial \left< \delta E^2 \right>_{{\bf k},\omega}^0}{\partial t}
  + \mbox{Im}\,\frac{4}{\pi k^2\epsilon^*({\bf k},\omega)}
  \sum_ae_a^2 \int d{\bf v}\, \delta(\omega-{\bf k \cdot v})f_a({\bf v})\\
  &+\sum_{\sigma=\pm 1}\sum_\alpha\left[
    \epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)
    \frac{\partial I_{\bf k}^{\sigma \alpha}}{\partial t}
    +2\,\mbox{Im}\,\epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)
    I_{\bf k}^{\sigma \alpha}\right]\delta(\omega-\sigma\omega_{\bf k}^\alpha)\\
  &=\mbox{Im}\,\mathcal{P} \frac{4}{\pi k^2\epsilon^{*}({\bf k},\omega)}
  \sum_a e^2_a\, \int d{\bf v}\,\delta(\omega-{\bf k \cdot v})f_a({\bf v})\\
  & +\sum_{\sigma=\pm 1}\sum_\alpha
  \frac{4\delta(\omega-{\bf k \cdot v})}
  {k^2\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}
  \sum_a e^2_a\, \int d{\bf v}\,\delta(\omega-{\bf k \cdot v})f_a({\bf v}).
\end{split}
\end{equation}

According to the definition \eqref{field-fluc}, the argument
of the dielectric constant excludes the eigenmodes. Hence, the
second term on the left-hand side of Eq. \eqref{noneigenmode-ql}
is implicitly taken with the principal value, which means it
cancels out the first term of the right-hand side. Thus, by assuming
$\partial \left< \delta E^2 \right>_{{\bf k},\omega}^0/\partial t=0$,
and removing the common factor $\sum_{\sigma=\pm 1}\sum_\alpha
\delta(\omega-\sigma\omega_{\bf k}^\alpha)$, we are left with
\begin{equation}
  \label{eigenmode-ql}
  \begin{split}
    \epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)
    \frac{\partial I_{\bf k}^{\sigma \alpha}}{\partial t}
    +2\,\mbox{Im}\,\epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)
    I_{\bf k}^{\sigma \alpha}
  =\frac{4}{k^2\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}
  \sum_a e^2_a\, \int d{\bf v}\,\delta(\omega-{\bf k \cdot v})f_a({\bf v}).
\end{split}
\end{equation}
And, rearranging Eq. \eqref{eigenmode-ql}, we obtain
\begin{equation}
  \begin{split}
\label{eigenmode-ql2}
    \frac{\partial I_{\bf k}^{\sigma \alpha}}{\partial t}
    =-\frac{2\,\mbox{Im}\,\epsilon({\bf k},\sigma\omega_{\bf k}^\alpha)}
    {\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}I_{\bf k}^{\sigma \alpha}
  +\frac{4}{k^2[\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)]^2}
  \sum_a e^2_a\, \int d{\bf v}\,\delta(\omega-{\bf k \cdot v})f_a({\bf v}),
\end{split}
\end{equation}
that is equivalent to the first term of Eq. \eqref{wave-lin},
plus the term of spontaneous emission, which is absent in
\eqref{wave-lin}, but has the exact same form of the second
right-hand term in Eq. \eqref{eigenmode-ql2} (see Eq. 3.8 of
 Ref. \cite{YZKS16}). These two processes are determined by
 linear wave-particle resonance conditions
 $\sigma \omega_{\bf k}^\alpha-{\bf k\cdot v}=0$.
So we may conclude that noneigenmodes do not alter the
quasilinear wave kinetic equation.

\subsection{Noneigenmode contribution to particle kinetic equation}
For the particle kinetic equation, however, the outcome is different.
In this case, the inclusion of noneigenmode field fluctuations leads to
the rigorous Balescu-Lenard collision integral, resulting in the merge
of two essential formulations of the plasma kinetic theory, without any
\emph{ad hoc} addition. The procedure starts by inserting the generalized wave
electric field intensity, given by Eq. \eqref{gen-dens}, in Eq. \eqref{part}
\begin{equation}
  \begin{split}
  \frac{\partial f_a}{\partial t}&=\frac{\pi e_a^2}{m_a^2}
  \int d{\bf k}\, \int d\omega\,
  \left( \frac{\bf k}{k}\cdot \frac{\partial}{\partial {\bf v}}\right)
  \delta(\omega -{\bf k \cdot v})
  \biggl[\mbox{Im}\, \mathcal{P} \frac{m_a}
    {2\pi^3k\, \epsilon^*({\bf k},\omega)} f_a({\bf v})\\
    &+\frac{2}{\pi k^2|\epsilon({\bf k},\omega)|^2}
    \sum_b e_b^2\int d{\bf v'} \delta(\omega-{\bf k\cdot v'})
    f_b({\bf v '})\left( \frac{\bf k}{k}\cdot
    \frac{\partial f_a({\bf v})}{\partial {\bf v}}\right)\\
  &+\sum_\sigma\sum_\alpha\frac{\pi m_a\,\delta(\omega-\sigma\omega_{\bf k}^\alpha)}
      {2\pi^3 k\, \epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}f_a({\bf v})
      +\sum_\sigma\sum_\alpha I_{\bf k}^{\sigma \alpha}\,
      \delta(\omega-\sigma\omega_{\bf k}^\alpha)
      \left( \frac{\bf k}{k}\cdot
      \frac{\partial f_a({\bf v})}{\partial {\bf v}}\right)\biggr].
  \end{split}
\label{part-eig}
\end{equation}

Proceeding with the $\omega$ integration, we redefine the velocity
distribution function by taking the ambient density factor out
\begin{equation}
  \label{Fa}
f_a({\bf v})= \hat n F_a({\bf v}), \quad \int d^3v\ F_a({\bf v})=1,
\end{equation}
% LFZ180216: Talvez seja desnecessário o espaçamento extra antes do d^3v. O
% espaço parece tão grande ...
% Sabrina: OK
and, making explicit use of the definition for
$\mbox{Im}\,\epsilon({\bf k},\omega)$:
\begin{displaymath}
  \mbox{Im}\epsilon({\bf k},\omega)
  =-\pi \sum_\alpha \frac{4\hat n \pi e_a^2}{m_a k^2} \int d{\bf v}\,
  {\bf k \cdot}\frac{\partial F_a}{\partial {\bf v}}\delta(\omega-{\bf k\cdot v}),
\end{displaymath}
we obtain the following form of the generalized particle kinetic
equation including both the eigenmode and noneigenmode contributions
\cite{YZKS16}
\begin{equation}
\begin{split}
  \frac{\partial F_a({\bf v})}{\partial t}
  &=\sum_b\frac{2e_a^2e_b^2n_b}{m_a}\frac{\partial }{\partial v_i}
  \int d{\bf k}\ \int d{\bf v'}
  \frac{k_ik_j}{k^4}\frac{\delta({\bf k \cdot v - k \cdot v'})}
    {|\epsilon({\bf k, k\cdot v})|^2}\\
  &\times \left(\frac{\partial }{\partial v_j} -\frac{m_a}{m_b}
    \frac{\partial }{\partial v'_j}\right)
  F_a({\bf v})F_b({\bf v'})\\
  &+\frac{\pi e_a^2}{m_a^2}\sum_\sigma\sum_{\alpha=L,S}
  \int d{\bf k} \biggl(\frac{\bf k}{k}
\cdot\frac{\partial}{\partial{\bf v}}\biggr)
\delta(\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v})\\
&\times\biggl(\frac{m_a}{2\pi^2k\epsilon '({\bf k},\sigma\omega_{\bf k}^L)}
F_a({\bf v})+I_{\bf k}^{\sigma\alpha}
\frac{\bf k}{k}\cdot\frac{\partial F_a({\bf v})}{\partial{\bf v}}\biggr),
\end{split}
\label{Fa-gen}
\end{equation}
where the first term on the right-hand side is the contribution
of the noneigenmode inclusion in the particle kinetic equation
and, as mentioned before, corresponds to
% LFZ180216: Que tal "and corresponds to", em lugar de "it is"?
% Sabrina: OK
the Balescu-Lenard collision integral.
The other term is the usual quasilinear particle equation, which
contains the velocity friction term, related with the spontaneous
emission process, and the velocity space diffusion term.

In Eq. \eqref{Fa-gen}, the linear response $|\epsilon({\bf k},
{\bf k\cdot v})|^2$ in the denominator of the Balescu-Lenard
integral can be approximated under the assumption that the most
important contributions to the noneigenmode fluctuations is in
the region around $v=0$ , i.e., the region with the highest
concentration of particles in the velocity distribution function.
Therefore, we may treat these various angular frequency arguments
as if they have the basic form of ${\bf k \cdot v}\approx 0$ and
approximate the collision integral as
\begin{equation}
  \label{approx}
  \epsilon({\bf k},{\bf k \cdot v})\approx
  \epsilon({\bf k},0)=1+\sum_a \frac{2 \omega_{pa}^2}{k^2v_{T_a}^2}
  =1+\frac{2 \omega_{pe}^2}{k^2v_{Te}^2}\left( 1+\frac{T_e}{T_i} \right),
\end{equation}
where $\omega_{pe}=\sqrt{4 \pi n_e e^2/m_e}$ is the plasma frequency,
$v_{Te}= \sqrt{2T_e/m_e}$ is the electron thermal velocity, and $T_e$
and $T_i$ are the electron and ion temperature, respectively. This
leads to
\begin{equation}
\begin{split}
  \frac{\partial F_a({\bf v})}{\partial t}
  &=\sum_b\frac{2e_a^2e_b^2n_b}{m_a}\frac{\partial }{\partial v_i}
  \int d{\bf k}\ \int d{\bf v'}\,
  \frac{k_ik_j\lambda_{De}^4\delta({\bf k \cdot v - k \cdot v'})}
    {|1+T_e/T_i+k^2 \lambda_{De}^2|^2}\\
  &\times \left(\frac{\partial }{\partial v_j} -\frac{m_a}{m_b}
    \frac{\partial }{\partial v'_j}\right)
  F_a({\bf v})F_b({\bf v'})\\
  &+\frac{\pi e_a^2}{m_a^2}\sum_\sigma\sum_{\alpha=L,S}
  \int d{\bf k} \biggl(\frac{\bf k}{k}
\cdot\frac{\partial}{\partial{\bf v}}\biggr)
\delta(\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v})\\
&\times\biggl(\frac{m_a}{2\pi^2k\epsilon '({\bf k},\sigma\omega_{\bf k}^L)}
F_a({\bf v})+I_{\bf k}^{\sigma\alpha}
\frac{\bf k}{k}\cdot\frac{\partial F_a({\bf v})}{\partial{\bf v}}\biggr),
\end{split}
\label{Fa-gen-approx}
\end{equation}
where $\lambda_{De}=\sqrt{T_e/4\pi n_ee^2}$ is the Debye length.

The collision integral also has a further approximation where,
assuming $2[\omega_{pe}/kv_{Te}]^2\ll 1$, the linear response
function can be written as $\epsilon({\bf k},{\bf k \cdot v})
\approx 1$. In such case, the wave number range of noneigenmode
fluctuations must be restricted to the short wavelength regime,
$k^2\lambda_{De}^2\gg 1$. This approximation leads to the well
known Landau collision integral, which is the approximation used
in Refs. \cite{Tigik2016a,Tigik2017a}. A very detailed discussion
about the limits and assumptions of the weak coupling approximation,
which leads to the Landau collision integral,
% LFZ180216: Acho que vai uma vígula aqui, depois de "integral"
% Sabrina: OK
 can be seen in Chapter
4 of Ref. \cite{Tigik2015}.
In Ref. \cite{Tigik2015} the Balescu-Lenard collision integral was
obtained through the Klimontovich statistical formalism
\cite{klimo,klimon}, which is also the starting point for
the derivation of the weak turbulence theory \cite{YZKS16} and the
basis of the simplified approach presented in \Cref{sec:kin-gen-eq}.
The implementation depicted in Ref. \cite{Tigik2015} did not make
any mention about the connection of the eigenmode and noneigenmode
contributions to each term of the particle kinetic equation. However,
the final result was exactly the same, which means that
% LFZ180216: "means that"?
% Sabrina: OK
the real novelty
here are not the equations, but it is this eigenmode/noneigenmode
relationship with collective and collisional processes, respectively.
The truly innovative outcome regarding new equations and the inclusion
of noneigenmode fluctuations will appear in the wave dynamics, as will
become clear in the next subsection.

\subsection{Noneigenmode contribution to nonlinear wave
  kinetic equation}
For the nonlinear wave kinetic equation, the implementation
is far more extensive and complicated than the two previous
cases. Such complex series of steps is not well suited to a
Qualifying Exam text but to a PhD Thesis, where they can be
properly explained and then, well comprehended by the reader.
In this text, we provide a brief explanation of the method,
which is not very different from the quasilinear case, though
it is way more complex, and present some important remarks
regarding the inclusion of noneigenmodes in the nonlinear wave
equation. It is worth to mention again that the process of
inclusion of the noneigenmode contribution in the wave and the
particle kinetic equations can be seen in Ref. \cite{YZKS16}.

Now, let us consider all terms in Eq. \eqref{nlebe}. On the
left-hand side, we have the quasilinear equations that, as
discussed before, are not altered by the inclusion of the
noneigenmode fluctuations. Thus, we can call the left-hand
side as ``$NL$'', and work only with the nonlinear part, on
right-hand side of \eqref{nlebe}, and substitute the total
electric field fluctuation, given by Eq. \eqref{gen-dens},
in these terms. Moreover, we are interested in how the
noneigenmode contribution affects the emissions in the
eigenmode frequency range, i.e., $\omega=\sigma \omega_{\bf k}$.
Therefore, all the noneigenmode fluctuations $\left<\delta E^2
\right>_{{\bf k}, \omega}^0$, with superscript $0$ and subscript
${\bf k},\omega$ to be more specific, can be neglected at this
point since, by definition, they are excluded from the region
that satisfies the $\omega=\sigma\omega_{\bf k}$ condition.
The noneigenmode fluctuations with different arguments
($\left< \delta E^2\right>_{{\bf k'},\omega '}^0$ and
$\left< \delta E^2\right>_{{\bf k-k'},\omega-\omega '}^0$),
though, must be retained. After all these considerations,
we have a generalized form of Eq. \eqref{nlebe}:
\begin{align}
  \mbox{NL}
 =-&2\int d{\bf k'} \int d\omega '\
     \biggl\{ \left[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},
     \omega-\omega ')\right]^2
     \nonumber\\
  &\times\biggl[\frac{\left< \delta E^2 \right>_{{\bf k-k'},\omega-\omega '}^0
     +\sum_{\sigma ''}\sum_{\gamma} I_{\bf k -k'}^{\sigma '' \gamma}
     \delta(\omega-\omega ' -\sigma '' \omega_{\bf k -k'}^\gamma)}
     {\epsilon({\bf k'},\omega ')}
  \label{nlebe-gen}\\
  &+\frac{\left< \delta E^2 \right>_{{\bf k'},\omega '}^0
  +\sum_{\sigma '}\sum_{\beta}
  I_{\bf k'}^{\sigma ' \beta}\delta(\omega '-\sigma ' \omega_{\bf k'}^\beta)}
     {\epsilon({\bf k-k'},\omega-\omega ')}\biggr]
     -\bar \chi^{(3)}({\bf k'},\omega|-{\bf k'},-\omega '|{\bf k},\omega)
     \nonumber\\
     &\times\biggl[ \left< \delta E^2 \right>_{{\bf k'},\omega '}^0
	+\sum_{\sigma '}\sum_{\beta}I_{\bf k'}^{\sigma ' \beta}
	\delta(\omega '-\sigma ' \omega_{\bf k'}^\beta) \biggr]\biggr\}
	\sum_{\sigma}\sum_{\alpha}
  I_{\bf k}^{\sigma \alpha}\delta(\omega-\sigma \omega_{\bf k}^\alpha)
	\nonumber\\
  +&2\int d{\bf k'} \int d\omega '
  \frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
     {\epsilon^*({\bf k},\omega)}\biggl[ \left< \delta E^2 \right>_{{\bf k'},\omega '}^0
  +\sum_{\sigma '}\sum_{\beta}
     I_{\bf k'}^{\sigma ' \beta}\delta(\omega '-\sigma ' \omega_{\bf k'}^\beta) \biggr]
  \nonumber\\
  &\times \biggl[  \left< \delta E^2 \right>_{{\bf k-k'},\omega-\omega '}^0
     +\sum_{\sigma"}\sum_{\gamma} I_{\bf k -k'}^{\sigma" \gamma}
     \delta(\omega-\omega ' -\sigma" \omega_{\bf k -k'}^\gamma) \biggr]
     \nonumber\\
-&\frac{4}{\pi}\int d{\bf k '} \int d\omega '\
\frac{1}{k^2|\epsilon({\bf k'},\omega ')|^2}
\biggl\{ \frac{[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')]^2}
{\epsilon({\bf k-k'},\omega-\omega ')}\sum_{\sigma}\sum_{\alpha}
   I_{\bf k}^{\sigma \alpha}\delta(\omega-\sigma \omega_{\bf k}^\alpha)
   \nonumber\\
  &-\frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
   {\epsilon^*({\bf k},\omega)}
     \biggl[ \left< \delta E^2 \right>_{{\bf k-k'},\omega-\omega '}^0
     +\sum_{\sigma"}\sum_{\gamma}I_{\bf k -k'}^{\sigma" \gamma}
     \delta(\omega-\omega ' -\sigma" \omega_{\bf k -k'}^\gamma)\biggr]\biggr\}
    \nonumber
\end{align}
\begin{align}
  &\times\sum_ae_a^2\int d{\bf v}\, \delta(\omega '-{\bf k \cdot v})F_a({\bf v})
  \nonumber\\
-&\frac{4}{\pi}\int d{\bf k '} \int d\omega '\
\frac{1}{|{\bf k - k'}|^2|\epsilon({\bf k-k'},\omega-\omega ')^2}
\biggl\{ \frac{[\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')]^2}
   {\epsilon({\bf k'},\omega ')}\nonumber\\
  &\times\sum_{\sigma}\sum_{\alpha}
  I_{\bf k}^{\sigma \alpha}\delta(\omega-\sigma \omega_{\bf k}^\alpha)
-\frac{|\chi^{(2)}({\bf k'},\omega '|{\bf k-k'},\omega-\omega ')|^2}
{\epsilon^*({\bf k},\omega)}  \nonumber\\
&\times 
   \biggl[\left< \delta E^2 \right>_{{\bf k'},\omega '}^0
   +\sum_{\sigma '}\sum_{\beta}I_{\bf k'}^{\sigma ' \beta}
   \delta(\omega '-\sigma ' \omega_{\bf k'}^\beta)\biggr]\biggr\}
   \sum_a e_a^2\int d{\bf v}\,
   \delta(\omega-\omega '-{\bf (k-k')\cdot v})F_a({\bf v}).\nonumber
\end{align}

In the above equation, the noneigenmode fluctuations are represented
by the terms  $\left<\delta E^2 \right>_{{\bf k'}, \omega '}^0$, and
$\left< \delta E^2\right>_{{\bf k-k'},\omega-\omega '}^0$. It is important
to reinforce that if one is interested only in nonlinear terms related
to collective and spontaneous fluctuations in the eigenmode frequency
range, then all of these terms might be ignored. In such case, we are
back to the standard weak turbulence theory.

After an extensive algebraic manipulation that involves making explicit
use of definition \cref{field-fluc} in the noneigenmode field fluctuations,
carrying out the $\omega '$ integrations, then using Eq. \eqref{principal}
to decompose the denominators
$1/\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha-{\bf k'\cdot v})$
and $1/\epsilon^*({\bf k},\omega)$ into principal parts and imaginary terms,
and taking the imaginary part of the resulting equation, we finally obtain
the noneigenmode corrections to the nonlinear wave kinetic equation:
\begin{equation}
  \label{corr}
  \begin{split}
    \mbox{corr}&=-\sum_{\sigma '}\sum_\beta\sum_a \,8\pi e_a^2
    \int d{\bf k'}\int d{\bf v}\,
    \frac{|\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^\beta|{\bf k-k'},
      ({\bf k-k'}){\bf \cdot v})|^2}
    {|{\bf k-k'}|^2|\epsilon[{\bf k-k'},{\bf k-k'},({\bf k-k'}){\bf \cdot v}]|^2}\\
    &\times \left[ \frac{I_{\bf k}^{\sigma \alpha}}
      {\epsilon '({\bf k'},\sigma '\omega_{\bf k'}^\beta)}
      -\frac{I_{\bf k'}^{\sigma '\beta}}
	{\epsilon '({\bf k},\sigma \omega_{\bf k}^\alpha)}\right] 
    \delta[\sigma\omega_{\bf k}^\alpha-\sigma '\omega_{\bf k'}^\beta
    -({\bf k-k'}){\bf \cdot v}]f_a({\bf v})\\
    &-\sum_a \frac{4 e_a^2}{\pi}
    \int d{\bf k '}\int d{\bf v}\,\mbox{Im}\biggl[ \mathcal{P}\,
    \frac{2[\chi^{(2)}({\bf k'},{\bf k' \cdot v}|{\bf k-k'},
      \sigma\omega_{\bf k}^\alpha-{\bf k'\cdot v})]^2}
    {\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha-{\bf k'\cdot v})}\\
    &-\bar \chi^{(3)}({\bf k'},{\bf k' \cdot v}|{\bf -k'},{\bf -k'\cdot v}
    |{\bf k},\sigma\omega_{\bf k}^\alpha)\biggr]
    \frac{I_{\bf k}^{\sigma \alpha}}{k'^2|\epsilon({\bf k'},{\bf k'\cdot v})|^2}
    f_a({\bf v})\\
    &+\sum_a\sum_b \frac{24 e_a^2 e_b^2}{\pi}\int d{\bf k '}
    \int d{\bf v} \int d{\bf v'}\,
    \frac{|\chi^{(2)} \left[ {\bf k'},{\bf k' \cdot v'}|
     {\bf k-k'},({\bf k-k'}){\bf \cdot v} \right]|^2}{k'^2|{\bf k-k'}|^2
   |\epsilon({\bf k'},{\bf k'\cdot v'})|^2
 |\epsilon({\bf k-k'},({\bf k-k'}){\bf \cdot v})|^2}\\
    &\times \frac{\delta \left[ \sigma\omega_{\bf k}^\alpha-{\bf k \cdot v}
	+{\bf k' \cdot}({\bf v-v'})\right]}
    {\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}f_a({\bf v}) f_b({\bf v'}).
  \end{split}
\end{equation}

At this point, we have to define an approximation for the various response
functions with the angular frequency replaced by ${\bf k \cdot v}$,
appearing in the denominator of the correction terms. To do so, we must
remember that waves are not subjected to Debye screening, therefore we
cannot assume $k^2\lambda_{De}^2\gg 1$, that would lead to the same
approximation $\epsilon({\bf k},0) \approx 1 $, which reduces the
Balescu-Lenard collision integral to the Landau collision integral.
Instead, we make use of Eq. \eqref{approx}, $\epsilon({\bf k},{\bf k \cdot v})\approx
\epsilon({\bf k},0) = 1+(2 \omega_{pe}^2/k^2v_{Te}^2)\left( 1+T_e/T_i \right)$,
which is the same we applied to the collision integral in the previous
subsection. Thus, applying this approximation and then adding the
right-hand side of \eqref{corr} to the right-hand side of Eq.
\eqref{wave-lin}, we obtain a generalized wave kinetic equation,
which includes both the eigenmode and noneigenmode fluctuations:
\begin{eqnarray}
  \frac{\partial I^\alpha_{\bf k}}{\partial t}
    &=&-\frac{2 \mbox{Im}\ \epsilon({\bf k}, \sigma \omega_{\bf k}^\alpha)}
    {\epsilon '({\bf k},\sigma \omega_{\bf k}^\alpha)}I^\alpha_{\bf k}
    +\sum_a\frac{4e^2}{k^2[\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)]^2}
    \int d{\bf v}\, \delta(\sigma\omega_{\bf k}^\alpha-{\bf k \cdot v})f_a({\bf v})
	\nonumber\\
      &&-4\pi \sum_{\alpha,\beta,\gamma}\ \sum_{\sigma ',\sigma ''}\int d{\bf k '}\
    \frac{|\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^\beta|{\bf k-k'},
      \sigma ''\omega_{\bf k-k'}^\gamma)|^2}
    {\epsilon '({\bf k},\sigma \omega_{\bf k}^{\alpha})}
    \nonumber\\
      &&\times \biggl(\frac{I_{\bf k-k'}^{\gamma}\ I_{\bf k}^{\alpha}}
       {\epsilon '({\bf k'},\sigma ' \omega_{\bf k'}^{\beta})}
       +\frac{I_{\bf k'}^{\beta}\ I_{\bf k}^{\alpha}}
       {\epsilon '({\bf k-k'},\sigma ''\omega_{\bf k-k'}^{\gamma})}
       -\frac{I_{k'}^{\beta}\ I_{\bf k-k'}^{\gamma}}
       {\epsilon '({\bf k},\sigma \omega_{\bf k}^{\alpha})}\biggr)
       \delta\bigl(\sigma \omega_{\bf k}^{\alpha}-\sigma ' \omega_{\bf k'}^{\beta}
	 -\sigma '' \omega_{\bf k-k'}^{\gamma}\bigr)
    \nonumber\\
    &&-\sum_{\alpha,\beta}\ \sum_{\sigma '}
    \int d{\bf k '}\ A_{\alpha,\beta}({\bf k,k'})
    I_{\bf k'}^{\beta}\ I_{\bf k}^{\alpha}
       -\sum_a\,\frac{16 e_a^2}{\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}
       \sum_{\sigma '}\sum_{\beta}
    \nonumber\\
    &&\times\int d{\bf v}\int d{\bf k '}\,
    \frac{|\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^{\beta}|{\bf k-k'},
      \sigma \omega_{\bf k}^\alpha-\sigma '\omega_{\bf k'}^{\beta})|^2}
    {|{\bf k-k'}|^2|\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha
      -\sigma '\omega_{\bf k'}^{\beta})|^2}
    \nonumber\\
    &&\times \left[ \frac{I_{\bf k}^{\sigma \alpha}}
      {\epsilon({\bf k '},\sigma '\omega_{\bf k'}^\beta)}
    -\frac{I_{\bf k'}^{\sigma '\beta}}
    {\epsilon '({\bf k },\sigma \omega_{\bf k}^\alpha)}\right]
   \delta[\sigma \omega_{\bf k}^\alpha-\sigma '\omega_{\bf k'}^\beta
   -({\bf k-k'}){\bf \cdot v}] f_a({\bf v})
   \nonumber\\
    &&\textcolor{darkblue}{
       -\sum_a \,\frac{16 e_a^2}{\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)}
       \sum_{\sigma '}\sum_\beta\,
    \int d{\bf k'}\int d{\bf v}\,
       \frac{|{\bf k-k'}|^2 \lambda_{De}^4
       |\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^\beta|{\bf k-k'},0)|^2}
    {|1+T_e/T_i+|{\bf k-k'}|^2 \lambda_{De}^2|^2}}
    \nonumber\\
    &&\textcolor{darkblue}{\times \left[ \frac{I_{\bf k}^{\sigma \alpha}}
      {\epsilon '({\bf k'},\sigma '\omega_{\bf k'}^\beta)}
      -\frac{I_{\bf k'}^{\sigma '\beta}}
	{\epsilon '({\bf k},\sigma \omega_{\bf k}^\alpha)}\right] 
    \delta[\sigma\omega_{\bf k}^\alpha-\sigma '\omega_{\bf k'}^\beta
    -({\bf k-k'}){\bf \cdot v}]f_a({\bf v})}
	 \nonumber\\
      &&\textcolor{skobeloff}{-\sum_a \frac{8 e_a^2}{\pi}
	 \int d{\bf k '}\int d{\bf v}\,
	 \frac{k'^2\lambda_{De}^4}{|1+T_e/T_i+k'^2\lambda_{De}^2|^2}}
	 \nonumber\\
    &&\textcolor{skobeloff}{
     \times\mbox{Im}\biggl[ \mathcal{P}\,
    \frac{2[\chi^{(2)}({\bf k'},0|{\bf k-k'},\sigma\omega_{\bf k}^\alpha)]^2}
    {\epsilon({\bf k-k'},\sigma \omega_{\bf k}^\alpha)}
       -\bar \chi^{(3)}({\bf k'},0|{\bf -k'},0|{\bf k},\sigma\omega_{\bf k}^\alpha)\biggr]
       I_{\bf k}^{\sigma \alpha}f_a({\bf v})}
      \nonumber\\
 &&\textcolor{softred}{+\sum_a\sum_b
     \frac{48 e_a^2 e_b^2}{\pi[\epsilon '({\bf k},\sigma\omega_{\bf k}^\alpha)]^2}
     \int d{\bf k '} \int d{\bf v} \int d{\bf v'}\,
     \frac{k'^2|\chi^{(2)} \left( {\bf k'},0|{\bf k-k'},0 \right)|^2}
     {|1+T_e/T_i+k^2 \lambda_{De}^2|^2}}
    \nonumber\\
  &&\textcolor{softred}{\times \frac{|{\bf k-k'}|^2\lambda_{De}^8}
     {|1+T_e/T_i+|{\bf k-k'}|^2 \lambda_{De}^2|^2} 
     \delta \left[ \sigma\omega_{\bf k}^\alpha-{\bf k \cdot v}
	+{\bf k' \cdot}({\bf v-v'})\right] f_a({\bf v}) f_b({\bf v'})},
       \label{wave-gen}
\end{eqnarray}
where the coefficient $A_{\alpha,\beta}({\bf k},{\bf k'})$ is given by
Eq. \eqref{coef-esp}.

Above, looking at the first noneigenmode term,
(blue), one may notice the extreme similarity with its previous
term, which describes the spontaneous scattering process. In fact, this
term is nothing but a correction due to the noneigenmode fluctuations,
to the spontaneous scattering process. Such effect, though, it is not
relevant for this work and will not be analyzed here. However, we are
interested in the last two corrections, the \emph{collisional damping}
(in dark-green), and \emph{electrostatic bremsstrahlung} (in pink),
respectively. The final expressions for the three new contributions
to the wave kinetic equation are right below.

\subsubsection{Correction for the spontaneous scattering}
The blue term in Eq. \eqref{wave-gen}, which depicts the
correction for the spontaneous scattering term is:
\begin{equation}
  \label{corrLS}
  \begin{split}
     \frac{\partial I_{\bf k}^{\sigma L}}{\partial t}\biggr|_{\mbox{\tiny corr}}
    &= - 4\hat n e^2 \sum_{\sigma '}  \int d{\bf k'}\int d{\bf v}\,
       \frac{|{\bf k-k'}|^2 \lambda_{De}^4\,
       |\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^L|{\bf k-k'},0)|^2}
    {|1+T_e/T_i+|{\bf k-k'}|^2 \lambda_{De}^2|^2}\\
    &\times \sigma \omega_{\bf k}^L \left( \sigma '\omega_{\bf k'}^L I_{\bf k}^{\sigma L}
      -\sigma \omega_{\bf k}^L I_{\bf k'}^{\sigma 'L}\right) 
    \delta[\sigma\omega_{\bf k}^L-\sigma '\omega_{\bf k'}^L
    -({\bf k-k'}){\bf \cdot v}]\left[ F_e({\bf v}) +F_i({\bf v})\right],\\
     \frac{\partial I_{\bf k}^{\sigma S}}{\partial t}\biggr|_{\mbox{\tiny corr}}
     &= - 4\hat n e^2\mu_{\bf k}\mu_{\bf k'}
     \sigma \omega_{\bf k}^L \sum_{\sigma '}  \int d{\bf k'}\int d{\bf v}\,
       \frac{|{\bf k-k'}|^2 \lambda_{De}^4\,
       |\chi^{(2)}({\bf k'},\sigma '\omega_{\bf k'}^S|{\bf k-k'},0)|^2}
    {|1+T_e/T_i+|{\bf k-k'}|^2 \lambda_{De}^2|^2}\\
    &\times \left( \sigma '\omega_{\bf k'}^S I_{\bf k}^{\sigma S}
      -\sigma \omega_{\bf k}^S I_{\bf k'}^{\sigma 'S}\right)
    \delta[\sigma\omega_{\bf k}^S-\sigma '\omega_{\bf k'}^S
    -({\bf k-k'}){\bf \cdot v}]\left[ F_e({\bf v}) +F_i({\bf v})\right],
  \end{split}
\end{equation}
where $\mu_{\bf k}=|k|^3\lambda_{De}^3 \left(m_e/m_i\right)^{1/2}
\left( 1+3T_i/T_e \right)^{1/2}$.

After a careful analysis on the second order susceptibility, we have
the following expressions for $L$ and $S$ waves
\begin{equation}
  \begin{split}
    u_{k,k'}^{L\, (\mbox{\tiny corr})}
    &= - \frac{\hat n e^2}{m_e^2\omega_{pe}^4}\sigma \omega_{\bf k}^L
    \sum_{\sigma '}  \int d{\bf k'}\int d{\bf v}\,
       \frac{({\bf k-k'})^2}{k^2 k'^2|1+T_e/T_i+({\bf k-k'})^2 \lambda_{De}^2|^2}\\
    &\times  \left( \sigma '\omega_{\bf k'}^L I_{\bf k}^{\sigma L}
      -\sigma \omega_{\bf k}^L I_{\bf k'}^{\sigma 'L}\right) 
    \delta[\sigma\omega_{\bf k}^L-\sigma '\omega_{\bf k'}^L
    -({\bf k-k'}){\bf \cdot v}]\left[ F_e({\bf v}) +F_i({\bf v})\right],
  \end{split}
\end{equation}
\begin{equation}
  \begin{split}
    u_{k,k'}^{S\, (\mbox{\tiny corr})}
    &= - \frac{\hat n e^2}{m_e^2\omega_{pe}^4}\mu_{\bf k}\mu_{\bf k'}
    \sigma \omega_{\bf k}^L \sum_{\sigma '}  \int d{\bf k'}\int d{\bf v}\,
    \frac{1}{k^2 k'^2\lambda_{De}^4}
    \left(1-\frac{T_e}{T_i} \frac{\bf k \cdot k'}{k'^2} \right)^2
    \left[1+\frac{T_e}{T_i}+({\bf k-k'})^2 \lambda_{De}^2\right]^{-2}\\
    &\times  \left( \sigma '\omega_{\bf k'}^S I_{\bf k}^{\sigma S}
      -\sigma \omega_{\bf k}^S I_{\bf k'}^{\sigma 'S}\right) 
    \delta[\sigma\omega_{\bf k}^S-\sigma '\omega_{\bf k'}^S
    -({\bf k-k'}){\bf \cdot v}]\left[ F_e({\bf v}) +F_i({\bf v})\right].
  \end{split}
\end{equation}

The corrected expression for the spontaneous scattering of
$L$ and $S$ waves are 
\begin{equation}
  \label{corrL}
  \begin{split}
  u_{k,k'}^{L}&=\sigma\omega_{\bf k}^L\,\frac{\hat n e^4}{m_e^2\,\omega_{pe}^4}
\sum_{\sigma '}\int d{\bf k'}\int d{\bf v}\;
\frac{({\bf k}\cdot{\bf k}')^2}{k^2\,k'^2}\;\delta[\sigma\omega_{\bf k}^L
-\sigma '\omega_{{\bf k}'}^L-({\bf k}-{\bf k}')\cdot{\bf v}]\\
&\times\,\bigl(\sigma\omega_{\bf k}^L\,I_{{\bf k}'}^{\sigma 'L}
  -\sigma '\omega_{{\bf k}'}^L\, I_{\bf k}^{\sigma L}\bigr)
  \left[1\textcolor{darkblue}{
  + \frac{1}{|1+T_e/T_i+({\bf k-k'})^2 \lambda_{De}^2|^2}} \right]
  \,[F_e({\bf v})+F_i({\bf v})],
\end{split}
\end{equation}
\begin{equation}
  \label{corrS}
  \begin{split}
  u_{k,k'}^{S}&=\sigma\omega_{\bf k}^L\frac{\hat n e^4}{m_e^2\omega_{pe}^4}
  \frac{\mu_{\bf k}\mu_{{\bf k}'}}{k^2\lambda_{De}^4}\sum_{\sigma '}
  \int \frac{d{\bf k'}}{k'^2}
  \int d{\bf v}\,\delta[ \sigma\omega_{\bf k}^S-\sigma '\omega_{{\bf k}'}^S
  -({\bf k}-{\bf k}')\cdot{\bf v}]
  \left(\sigma\omega_{\bf k}^L\frac{I_{{\bf k}'}^{\sigma 'S}}{\mu_{{\bf k}'}}
  -\sigma '\omega_{{\bf k}'}^L\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}}\right)\\
&\times\left[\frac{({\bf k}\cdot{\bf k}')^2}{k^2k'^2}W_{{\bf k},{\bf k}'}
  \textcolor{darkblue}{
    +\frac{\left(1-\frac{T_e}{T_i} \frac{\bf k \cdot k'}{k'^2}\right)^2}
        {|1+T_e/T_i+({\bf k-k'})^2 \lambda_{De}^2|^2}}\right]
[F_e({\bf v})+F_i({\bf v})],
\end{split}
\end{equation}
where the blue term is the noneigenmode contribution.

\subsubsection{Collisional damping for $L$ and $S$ waves}
The collisional damping expression is given by the dark-green
term in Eq. \eqref{wave-gen}:
\begin{equation}
  \label{CD}
  \begin{split}
  \frac{\partial I_{\bf k}^{\sigma L}}{\partial t}\biggr|_{\mbox{\tiny coll}}
    &=-\sum_a \frac{4\hat n e_a^2}{\pi}\sigma \omega_{\bf k}^L
    \int d{\bf k '} \frac{k'^2\lambda_{De}^4}{|1+T_e/T_i+k'^2\lambda_{De}^2|^2}\\
    &\times \int d{\bf v}\,\mbox{Im}\biggl[ \mathcal{P}\,
    \frac{2[\chi^{(2)}({\bf k'},0|{\bf k-k'},\sigma\omega_{\bf k}^L)]^2}
    {\epsilon({\bf k-k'},\sigma \omega_{\bf k}^L)}
    -\bar \chi^{(3)}({\bf k'},0|{\bf -k'},0|{\bf k},\sigma\omega_{\bf k}^L)\biggr]
    F_a({\bf v})\,I_{\bf k}^{\sigma L},\\
   \frac{\partial I_{\bf k}^{\sigma S}}{\partial t}\biggr|_{\mbox{\tiny coll}}
    &=-\sum_a \frac{4\hat n e_a^2}{\pi}\sigma \mu_{\bf k} \omega_{\bf k}^L
    \int d{\bf k '} \frac{k'^2\lambda_{De}^4}{|1+T_e/T_i+k'^2\lambda_{De}^2|^2}\\
    &\times\int d{\bf v}\,\mbox{Im}\biggl[ \mathcal{P}\,
    \frac{2[\chi^{(2)}({\bf k'},0|{\bf k-k'},
      \sigma\omega_{\bf k}^S)]^2}
    {\epsilon({\bf k-k'},\sigma \omega_{\bf k}^S)}
    -\bar \chi^{(3)}({\bf k'},0|{\bf -k'},0|{\bf k},\sigma\omega_{\bf k}^S)\biggr]
    F_a({\bf v})\,I_{\bf k}^{\sigma S}.
  \end{split}
\end{equation}

With the appropriate approximations for the second order and partial
third order susceptibilities carefully analyzed \cite{YZKS16}, we 
% LFZ180216: "analyzed"?
% Sabrina: sim
obtain the following expressions for $L$ and $S$ waves
\begin{eqnarray}
  \label{gammaL}
\gamma_{\bf k}^{\sigma L\,(\mbox{\tiny coll})}
  &=& \sigma \omega_{\bf k}^L
\frac{4\hat{n}e^4\omega_{pe}^2}{T_e^2}\int d{\bf k}'
\frac{({\bf k}\cdot {\bf k'})^2\lambda_{De}^4}{k^2k'^4 
      |\epsilon({\bf k'},\sigma\omega_{\bf k}^L)|^2}\\
&&\times \left(1+\frac{T_e}{T_i}+({\bf k}-{\bf k'})^2\lambda_{De}^2\right)^{-2}
\int d{\bf v}\, {\bf k'}\cdot \frac{\partial F_e({\bf v})}{\partial {\bf v}}
\delta [\sigma\omega_{\bf k}^L-{\bf k'}\cdot{\bf v}]\nonumber\\
\gamma_{\bf k}^{\sigma S\, (\mbox{\tiny coll})}
  &=& \sigma \mu_{\bf k}\omega_{\bf k}^L
\frac{\hat{n}e^4\omega_{pe}^2}{T_e^2}\int d{\bf k}'
\frac{1}{k^2k'^4 |\epsilon({\bf k'},\sigma\omega_{\bf k}^S)|^2}\nonumber\\
&&\times \left(1+\frac{T_e}{T_i}+({\bf k}-{\bf k'})^2\lambda_{De}^2\right)^{-2}
   \left(1+\frac{2T_e}{T_i}\frac{{\bf k}\cdot{\bf k}'}{k^2}\right)
   \label{gammaS}\\
&&\times \int d{\bf v}\, {\bf k'}\cdot \frac{\partial}{\partial{\bf v}}
\left(F_e({\bf v})+\frac{m_e}{m_i}F_i({\bf v})\right)
\delta [\sigma\omega_{\bf k}^S-{\bf k'}\cdot{\bf v}].\nonumber
\end{eqnarray}

\subsubsection{Electrostatic bremsstrahlung for $L$ and $S$ waves}
The electrostatic bremsstrahlung equations are given by the pink term
in Eq. \eqref{wave-gen}:
\begin{equation}
\label{PkL,1}
  \begin{split}
    \frac{\partial I_{\bf k}^{\sigma L}}{\partial t}\biggr|_{\mbox{\tiny brem}}&=\sum_{a,b}
\frac{12n_ee_a^2e_b^2\omega_{pe}^2}{\pi}\int d{\bf k}'\int d{\bf v}\int d{\bf v}'
\,\frac{|\chi^{(2)}({\bf k}',0|{\bf k}-{\bf k}',0)|^2}{k'^2|{\bf k}-{\bf k}'|^2
|\epsilon({\bf k}',0)|^2|\epsilon({\bf k}-{\bf k}',0)|^2}\\
&\times\delta\left[\sigma\omega_{\bf k}^L-{\bf k}\cdot{\bf v}+{\bf k}'\cdot
  ({\bf v}-{\bf v}')\right]F_a({\bf v})F({\bf v}'),\\
\end{split}
\end{equation}
\begin{equation}
     \label{PkS,1}
  \begin{split}
 \frac{\partial}{\partial t}
\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}}\biggr|_{\mbox{\tiny brem}}&=\sum_{a,b}
\frac{12n_ee_a^2e_b^2\omega_{pe}^2}{\pi}
\int d{\bf k}'\int d{\bf v}\int d{\bf v}'
\,\frac{|\chi^{(2)}({\bf k}',0|{\bf k}-{\bf k}',0)|^2}{k'^2|{\bf k}-{\bf k}'|^2
|\epsilon({\bf k}',0)|^2|\epsilon({\bf k}-{\bf k}',0)|^2}\\
&\times\delta\left[\sigma\omega_{\bf k}^S-{\bf k}\cdot{\bf v}+{\bf k}'\cdot
  ({\bf v}-{\bf v}')\right]F_a({\bf v})F({\bf v}').
  \end{split}
\end{equation}

In Ref. \cite{YZKS16}, the following approximation for the
second order susceptibility of both $L$ and $S$ waves was
employed
\begin{equation}
  \label{sec-susc-brem}
  \chi^{(2)}({\bf k}',0|{\bf k}-{\bf k}',0)
  =-i \sum_a\frac{e_a}{T_a} \frac{\omega_{pa}^2}{k k' |{\bf k-k'}|}\frac{1}{v_{Ta}^2}
  =\frac{i e}{T_e}\frac{1}{v_{Te}^2}\left( 1-\frac{T_e^2}{T_i^2}
  \frac{\omega_{pe}^2}{k k' |{\bf k-k'}|}\right).
\end{equation}

In the present work, however, we have revisited the subject, and found
that an improved approximation could be employed for the $L$ waves. The
derivation of this alternative approach, where we basically make the
same assumption ${\bf k \cdot v}\approx 0$, ${\bf k'\cdot v'}\approx 0$
and ${\bf k' \cdot v}\approx 0$ but a few steps later, is detailed in
\Cref{appA}. For the $S$ waves we keep the original approximation. 
Then, after applying the respective approximation for the
second order susceptibility for the $L$ and $S$ waves, we have
\begin{equation}
  \label{PkL}
  \begin{split}
      P_{\bf k}^{\sigma L}
  &= \frac{3e^2}{4\pi^3}\frac{1}{(\omega_\bk^L)^2}
    \left(1-\frac{m_e}{m_i}\frac{T_e}{T_i}\right)^2\frac{v_e^4}{k^2}
    \int d{\bf k}'k'^2|{\bf k- k'}|^2\left(1+\frac{T_e}{T_i}
    +({\bf k}-{\bf k}')^2\lambda_D^2\right)^{-2}\\
  &\times\left(1+\frac{T_e}{T_i}
    +{k'}^2\lambda_D^2\right)^{-2} \int d{\bf v}\int d{\bf v}'\,
    \delta[\sigma \omega_{\bf k}^L-{\bf k \cdot v}
    +{\bf k'\cdot}({\bf v}-{\bf v}')]
    \sum_aF_a({\bf v})\sum_bF_b({\bf v}')
  \end{split}
\end{equation}
\begin{equation}
  \label{PkS}
  \begin{split}
      P_{\bf k}^{\sigma S}
  &= \mu_{\bf k}\frac{3e^2T_e}{16\pi^3m_e}
    \biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2\frac{1}{k^2\lambda_D^2}
    \int d{\bf k}'\left(1+\frac{T_e}{T_i}
    +({\bf k}-{\bf k}')^2\lambda_D^2\right)^{-2}\\
  & \times\left(1+\frac{T_e}{T_i}
    +{k'}^2\lambda_D^2\right)^{-2}\int d{\bf v}\int d{\bf v}'\,
    \delta[\sigma\omega_{\bf k}^S-{\bf k \cdot v}
    +{\bf k'\cdot}({\bf v}-{\bf v}')]
    \sum_a F_a({\bf v})\sum_b F_b({\bf v}').
  \end{split}
\end{equation}

\subsubsection{Generalized wave kinetic equation for $L$ and $S$ waves}
Adding Eqs. \eqref{gammaL} and \eqref{PkL} to Eq. \eqref{L,1},
and Eqs. \eqref{gammaS} and \eqref{PkS} to Eq. \eqref{S,1}, and
then substituting the spontaneous emission term of both equations
with their respective corrected expressions, \eqref{corrL} and
\eqref{corrS}, we obtain the following generalized wave kinetic
equations for $L$ and $S$ waves, respectively:
\begin{equation}
  \label{L-gen}
  \begin{split}
\frac{\partial I_{\bf k}^{\sigma L}}{\partial t}
&=\frac{\omega_{pe}^2}{k^2}\int d{\bf v}\;
\delta(\sigma\omega_{\bf k}^L-{\bf k}\cdot{\bf v})
\biggl(\hat{n}\,e^2\,F_e({\bf v})+\pi\,(\sigma\omega_{\bf k}^L)\,
\;{\bf k}\cdot\frac{\partial F_e({\bf v})}{\partial{\bf v}}
\,I_{\bf k}^{\sigma L}\biggr)\\
&-\,\pi\sigma\,\omega_{\bf k}^L
\,\frac{e^2}{2T_e^2}\sum_{\sigma ',\sigma ''}\int d{\bf k'}\;
\frac{\mu_{{\bf k}-{\bf k}'}^S
\,({\bf k}\cdot{\bf k}')^2}{k^2\,k'^2\,|{\bf k}-{\bf k}'|^2}
\biggl(\sigma '\omega_{{\bf k}'}^L\,
\frac{I_{{\bf k}-{\bf k}'}^{\sigma ''S}}{\mu_{{\bf k}-{\bf k}'}^S}
I_{\bf k}^{\sigma L}\\
&+\,\sigma ''\omega_{{\bf k}-{\bf k}'}^L
\,I_{{\bf k}'}^{\sigma 'L}\,I_{\bf k}^{\sigma L}
-\sigma\omega_{\bf k}^L I_{{\bf k}'}^{\sigma 'L}
\frac{I_{{\bf k}-{\bf k}'}^{\sigma ''S}}
{\mu_{{\bf k}-{\bf k}'}^S}\biggr)
\;\delta(\sigma\omega_{\bf k}^L-\sigma '\omega_{{\bf k}'}^L
-\sigma ''\omega_{{\bf k}-{\bf k}'}^S)\\
&+\,\sigma\omega_{\bf k}^L\,\frac{e^2}{m_e^2\,\omega_{pe}^2}
\sum_{\sigma '}\int d{\bf k'}\int d{\bf v}\;
\frac{({\bf k}\cdot{\bf k}')^2}{k^2\,k'^2}\;\delta[\sigma\omega_{\bf k}^L
-\sigma '\omega_{{\bf k}'}^L-({\bf k}-{\bf k}')\cdot{\bf v}]\\
&\times\biggl\{\frac{\hat{n}\,e^2}{\omega_{pe}^2}
\bigl(\sigma\omega_{\bf k}^LI_{{\bf k}'}^{\sigma 'L}
  -\sigma '\omega_{{\bf k}'}^L I_{\bf k}^{\sigma L}\bigr)
  \left[1+ \frac{1}{|1+T_e/T_i+({\bf k-k'})^2 \lambda_{De}^2|^2} \right]
[F_e({\bf v})+F_i({\bf v})]\\
&+\pi\,\frac{m_e}{m_i}\,I_{{\bf k}'}^{\sigma 'L}
I_{\bf k}^{\sigma L}\;({\bf k}-{\bf k}')
\cdot\frac{\partial F_i({\bf v})}{\partial{\bf v}}\biggr\}
+2 I_{\bf k}^{\sigma L} \gamma_{\bf k}^{\sigma L}+ P_{\bf k}^{\sigma L},
  \end{split}
\end{equation}
\begin{equation}
  \label{S-gen}
  \begin{split}
\frac{\partial}{\partial t}\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}
&=\mu_{\bf k}^S\,\frac{\omega_{pe}^2}{k^2}
\int d{\bf v}\;\delta(\sigma\omega_{\bf k}^S-{\bf k}\cdot{\bf v})
\biggl[\hat{n}\,e^2\,[F_e({\bf v})+F_i({\bf v})]\\
&+\,\pi\,(\sigma\omega_{\bf k}^L)\,\biggl({\bf k}\cdot
\frac{\partial F_e({\bf v})}{\partial{\bf v}}
+\frac{m_e}{m_i}\;{\bf k}\cdot
\frac{\partial F_i({\bf v})}{\partial{\bf v}}\biggr)
\,\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}\biggr]\\
&-\,\pi\sigma\omega_{\bf k}^L\,\frac{e^2}{4T_e^2}
\sum_{\sigma ',\sigma ''}\int d{\bf k'}\;
\frac{\mu_{\bf k}^S[{\bf k}'\cdot({\bf k}-{\bf k}')]^2}{k^2k'^2|{\bf k}-{\bf k}'|^2}
\biggl(\sigma '\omega_{{\bf k}'}^L\,
I_{{\bf k}-{\bf k}'}^{\sigma ''L}
\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}\\
&+\,\sigma ''\omega_{{\bf k}-{\bf k}'}^L
\,I_{{\bf k}'}^{\sigma 'L}\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}
-\sigma\omega_{\bf k}^LI_{{\bf k}'}^{\sigma 'L}
I_{{\bf k}-{\bf k}'}^{\sigma ''L}\biggr)
\delta(\sigma\omega_{\bf k}^S-\sigma '\omega_{{\bf k}'}^L
-\sigma ''\omega_{{\bf k}-{\bf k}'}^L)\\
&+\frac{e^2}{m_e^2\omega_{pe}^2}\frac{\mu_{\bf k}^S\mu_{{\bf k}'}^S}{\lambda_{De}^4}
\sigma\omega_{\bf k}^L\sum_{\sigma '}\int \frac{d{\bf k'}}{k^2k'^2}\int d{\bf v}\;
\delta[\sigma\omega_{\bf k}^S-\sigma '\omega_{{\bf k}'}^S
-({\bf k}-{\bf k}')\cdot{\bf v}]\\
&\times\,\biggl\{\biggl[\frac{\hat{n}\,e^2}{\omega_{pe}^2}
\frac{({\bf k}\cdot{\bf k}')^2}{k^2\,k'^2}W_{{\bf k},{\bf k}'}
+\frac{\left(1-\frac{T_e}{T_i} \frac{\bf k \cdot k'}{k'^2}\right)^2}
{|1+T_e/T_i+({\bf k-k'})^2 \lambda_{De}^2|^2}\biggr]\\
&\times\biggl(\sigma\omega_{\bf k}^L\,
\frac{I_{{\bf k}'}^{\sigma 'S}}{\mu_{{\bf k}'}^S}
-\sigma '\omega_{{\bf k}'}^L\,
\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}\biggr)
\,[F_e({\bf v})+F_i({\bf v})]\\
&+\frac{m_e}{m_i}\frac{\pi({\bf k}\cdot{\bf k}')^2}{k^2\,k'^2}
\biggl(W_{{\bf k},{\bf k}'}+\sigma\,\sigma '\frac{k'}{k}\biggr)
\,\frac{I_{{\bf k}'}^{\sigma 'S}}{\mu_{{\bf k}'}^S}
\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}^S}({\bf k}-{\bf k}')
\cdot\frac{\partial F_i({\bf v})}{\partial{\bf v}}\biggr\}
+2 I_{\bf k}^{\sigma S} \gamma_{\bf k}^{\sigma S}+ P_{\bf k}^{\sigma S},
\end{split}
\end{equation}
where the coefficient $W$ is given by Eq. \eqref{W}.

\chapter{Weakly turbulent processes in the presence of
  collisional interactions}
\label{main}
The generalization introduced in \cite{YZKS16} and summarized
in \Cref{noneigenmode}, is an innovative approach, in
which the contribution of the usually neglected noneigenmode
fluctuations is taken into account along with the well-known
eigenmodes contribution. The outcome of this new formulation
is a first principles theory that combines both collective
and non-collective processes, assuming the propagation of
electrostatic oscillations in unmagnetized plasmas, without
any \emph{ad hoc} addition. Such theory is the basis of the
present research, whose primary objective is performing
numerical analysis of the generalized weak turbulence
equations, and then investigate its applications on the
description and interpretation of space plasma phenomena.
More specifically, the solar plasma, where the results of
the first two analysis \cite{Tigik2016b,Tigik2017a} have
shown a promising perspective. In this chapter, we discuss
some important aspects regarding the work that has been
done until the moment and the employed methodology. Then,
we present the results in the form of appended papers, in
chronological order, in \Cref{coll-damp,sec:gen-supr}.

\section{Collisional damping rates for plasma waves}
\label{coll-damp}
In this first analysis, we have numerically integrated Eqs. \eqref{gammaL}
for $L$ waves, and \eqref{gammaS} for $S$ waves, considering Maxwellian
velocity distribution function for the particles, without including the
new effects in the time evolution subroutine. The main objective here
was to comprehend important aspects of this so-far unknown expression,
how it relates to other equivalent plasma processes and with the
heuristic Spitzer formula, for collisional damping. The main question
was: ``Are they equivalent?'', more specifically, ``Are their intensities,
at least, in the same order of magnitude?''. The answer was no. We found
out that the Spitzer formula overestimates the collisional damping effect
in several orders of magnitude in comparison with the new expression.
Further, the insignificance of the collisional damping became even more
evident when we compared its damping rate with the collisionless (Landau)
damping rate in the same figure.

The following paper is fairly self-sustained regarding the theory
and methods applied. All important equations are there, including
their normalized form and the normalization constants. Any doubt
related to the origin of the new equations are filled by
\Cref{noneigenmode}.

\includepdf[pages=2-6]{Tigik2016b.pdf}
\section{Generation of suprathermal electrons by collective processes
  in collisional plasmas}
\label{sec:gen-supr}
For the analysis of the electrostatic bremsstrahlung, the simple integration
of Eqs. \eqref{PkL} and \eqref{PkS}
was not very clarifying since we did not have any equivalent effect for
comparison. So we had to perform the time evolution of the system and analyze
the outcome. However, in order to put in evidence the action of the new effect,
is useful to start with the simplest possible situation. Therefore, instead of
using the complete set of nonlinear weak turbulence equations given by
Eqs. \eqref{L-gen} and \eqref{S-gen}, we restrict our analysis to the
quasilinear formalism, which includes single particle spontaneous emission
and wave-particle induced emission, and add the collisional damping and
electrostatic bremsstrahlung effects. The particle kinetic equation is
given by the usual quasilinear equation, where we included the Landau
collision integral (the same used in \cite{Tigik2016a}). After a long
evolution period, the system reaches a steady state where the electron
velocity distribution strongly resembles a core-halo distribution. An
interesting and surprising detail is that this suprathermal electron
population grows even in the presence of binary collisions. In the next
two subsections we provide some helpful information regarding the equations
and methods employed in \cite{Tigik2017a}.

Furthermore, an extra result is presented in \Cref{appB}, where
we compare the stationary state of the $L$ waves spectrum obtained
after the time evolution (using the results discussed in \cite{
  Tigik2016a}), with the asymptotic Langmuir spectrum generated by
a theoretical core-halo distribution, composed $95\%$ by a Maxwellian
core and $5\%$ by a kappa tail, in the presence and in the absence of
bremsstrahlung emission, for several values of the $\kappa$ index. It is
shown that the asymptotic spectra obtained in the case of distributions
with low $\kappa$ indexes are less affected by the electrostatic
bremsstrahlung emission than the spectra generated in the presence of
higher $\kappa$ indexes, and in the Maxwellian case. These findings
suggest that core-halo distributions may represent the asymptotic
equilibrium when the electrostatic bremsstrahlung is taken into account.

\subsection{Dimensionless equations}
In order to simplify the numerical analysis, it is convenient to write
the equations in terms of dimensionless variables. Thus, let us start
by some important definitions
\begin{align*}
  z\equiv \frac{\omega}{\omega_{pe}},
  & \quad \tau\equiv \omega_{pe}t, \quad
    {\bf q}\equiv \frac{{\bf k}v_e}{\omega_{pe}}, \quad
    {\bf u}\equiv \frac{\bf v}{v_e},\\
  \mu_{\bf q}^L
  = 1,&\quad\mu_{\bf q}^S = \frac{q^3}{2^{3/2}}
	\,\sqrt{\frac{m_e}{m_i}}\;\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},
\end{align*}
\begin{align*}
  \Phi_a({\bf u})=  v_e^3 F_a({\bf u}),& \quad
    \calE_{\bf q}^{\sigma\alpha}= \frac{(2\pi)^2 g}{m_ev_e^2}
    \frac{I_{\bf k}^{\sigma\alpha}}{\mu_{\bf k}^\alpha},\quad
    P_{\bf k}^\alpha=\frac{m_ev_e^2}{(2\pi)^2g}\omega_{pe}P_{\bf q}^\alpha,\\
\end{align*}
where $g=1/[2^{3/2}\,(4\pi)^2\,\hat{n}\,\lambda_{De}^3]$ is the
plasma parameter, $\lambda_{De}=T_e/(4\pi\hat{n}e^2)=v_e^2/(2\omega_{pe}^2)$,
$v_e=(2T_e/m_e)^{1/2}$ is the electron thermal velocity and $T_e$ is
electrons temperature.

In terms of the normalized variables and quantities, the equations
for $L$ and $S$ waves, including the contributions from non-eigenmode
fluctuations, become
\begin{equation}
  \begin{split}
    \frac{\partial\calE_{\bf q}^{\sigma L}}{\partial\tau}
  &=\mu_{\bf q}^L\,\frac{\pi}{q^2}\int d{\bf u}\;
    \delta(\sigma z_{\bf q}^L-{\bf q}\cdot{\bf u})\\
    &\times\biggl(g\,\Phi_e({\bf u})+(\sigma z_{\bf q}^L)
    {\bf q}\cdot\frac{\partial \Phi_e({\bf u})}{\partial{\bf u}}
    \calE_{\bf q}^{\sigma L}\biggr)
    +2\calE_{\bf q}^{\sigma L}\gamma_{\bf q}^{\sigma L}+P_{\bf q}^{\sigma L},
      \end{split}
 \label{EpsL}
\end{equation}
\begin{equation}
  \begin{split}
    \frac{\partial{\cal E}_{\bf q}^{\sigma S}}{\partial \tau}
  &=\mu_{\bf q}^S\,\frac{\pi}{q^2}
    \int d{\bf u}\;
    \delta(\sigma z_{\bf q}^S-{\bf q}\cdot{\bf u})
    \biggl[g[\Phi_e({\bf u})+\Phi_i({\bf u})]\\
    &+\,(\sigma z_{\bf q}^L)\,\biggl({\bf q}\cdot
    \frac{\partial \Phi_e({\bf u})}{\partial{\bf u}}
    +\frac{m_e}{m_i}\;{\bf q}\cdot
    \frac{\partial \Phi_i({\bf u})}{\partial{\bf u}}\biggr)
    \,\calE_{\bf q}^{\sigma S}\biggr]
    +2\calE_{\bf q}^{\sigma S}\gamma_{\bf q}^{\sigma S}+P_{\bf q}^{\sigma S},
\end{split}
 \label{EpsS}
\end{equation}
where, $\gamma_{\bf q}^{\sigma L}$ and $\gamma_{\bf q}^{\sigma S}$ describe
the collisional damping rate for $L$ and $S$ waves, respectively
\begin{equation}
  \label{GqL}
  \begin{split}
    \gamma_{\bf q}^{\sigma L}&=
    \frac{2gz_{\bf q}^L}{q^2}\int d{\bf q}'
    \frac{({\bf q}\cdot {\bf q'})^2}{{q'}^4
    |\epsilon({\bf q'},z_{\bf q}^L)|^2}
    \left(1+\frac{T_e}{T_i}
    +\frac{({\bf q}-{\bf q'})^2}{2}\right)^{-2}\\
  &\times\int d{\bf u}\,{\bf q'}\cdot
    \frac{\partial \Phi_e({\bf u})}{\partial {\bf u}}
    \delta(z_{\bf q}^L-{\bf q'}\cdot{\bf u}),
  \end{split}
\end{equation}
\begin{equation}
  \label{GqS}
  \begin{split}
    \gamma_{\bf q}^{\sigma S}
    &=\frac{2gz_{\bf q}^L}{q^2}
    \int\frac{d{\bf q}'}{{q'}^4|\epsilon({\bf q'},z_{\bf q}^S)|^2}
    \left(1+\frac{T_e}{T_i}+\frac{({\bf q}-{\bf q'})^2}{2}\right)^{-2}
    \left(1+\frac{2T_e}{T_i}\frac{{\bf q}\cdot{\bf q}'}{q^2}\right)\\
  &\times \int d{\bf u}\, {\bf q'}
    \cdot\frac{\partial}{\partial {\bf u}}
    \left(\Phi_e({\bf u})+\frac{m_e}{m_i}
    \Phi_i({\bf u})\right)\delta(z_{\bf q}^S
    -{\bf q'}\cdot{\bf u}),
  \end{split}
\end{equation}
and $P_{\bf q}^{\sigma L}$ and $P_{\bf q}^{\sigma S}$ terms depict the
normalized electrostatic bremsstrahlung equations, given by
\begin{equation}
  \begin{split}
    P_{\bf q}^{\sigma L}
  &= \frac{12e^2}{\pi^3}
    \frac{1}{q^2}\frac{1}{(z_{\bf q}^L)^2}
    \left(1-\frac{m_e}{m_i}\frac{T_e}{T_i}\right)^2
    \frac{\omega_{pe}^2}{v_e}
    \int d{\bf q'}\,q'^2|{\bf q-q'}|^2\\
  &\times \left[2\left(1+\frac{T_e}{T_i}\right)+q'^2\right]^{-2}
    \left[2\left(1+\frac{T_e}{T_i}\right) +|{\bf q-q'}|^2\right]^{-2}
    \label{PqL}\\
  &\times \int d{\bf u}\int d{\bf u'}
    \delta \left[ \sigma z_{\bf q}^L-{\bf q\cdot u}
    +{\bf q'}\cdot ({\bf u-u'})\right]
    \sum_a \Phi_a({\bf u})\sum_b \Phi_b({\bf u'}),
 \end{split}
\end{equation}
\begin{equation}
  \begin{split}
  P_{\bf q}^{\sigma S}
  &= \mu_{\bf q}\frac{3e^2T_e}{16\pi^3m_e}
    \biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2
    \frac{32}{q^2}\frac{\omega_{pe}^2}{v_e^3}\int d{\bf q}'\\
  &\times\left[2
    \left(1+\frac{T_e}{T_i}\right)+{q'}^2\right]^{-2}
    \left[2 \left(1+\frac{T_e}{T_i}\right)
    +({\bf q}-{\bf q}')^2\right]^{-2}
    \label{PqS}\\
  &\times\int d{\bf u}\int d{\bf u}'\,
    \delta[\sigma z_{\bf q}^L-{\bf q}'\bm{\cdot}{\bf u}'
    -({\bf q}-{\bf q}') \bm {\cdot}{\bf u}]
    \sum_a\Phi_a({\bf u})\sum_b\Phi_b({\bf u}').
  \end{split}
\end{equation}

The dimensionless form of the particle kinetic equation has the
following form
\begin{equation}
  \begin{split}
    \frac{\partial \Phi_a({\bf u})}{\partial \tau}
    &= \frac{e_a^2}{e^2}\frac{m_e^2}{m_a^2}
    \sum_\sigma\sum_{\alpha=L,S}\int d{\bf q}\;\biggl(\frac{\bf q}{q}
    \cdot\frac{\partial}{\partial{\bf u}}\biggr)\,\mu_{\bf q}^\alpha
    \;\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u})\\
    & \times\,\biggl(g\frac{m_a}{m_e}\frac{\sigma z_{\bf q}^L}{q}
    \,\Phi_a({\bf u})+\calE_{\bf q}^{\sigma\alpha}
    \;\frac{\bf q}{q}\cdot\frac{\partial \Phi_a({\bf u})}
    {\partial{\bf u}}\biggr)+\sum_b\theta_{ab}(\Phi_a,\Phi_b),
    \label{Feu-evol}
  \end{split}
\end{equation}
where $\theta_{ab}(\Phi_a,\Phi_b)$ is the linearized Landau
collision integral, given by
\begin{equation}
  \begin{split}
     \theta_{ab}(\Phi_a,\Phi_b) &= \Gamma_{ab}\left\{
     \frac{\partial}{\partial{\bf u}_a}\cdot
     \left(2\frac{m_a}{m_b}\Psi(u_{ab})
     \frac{{\bf u}_a}{u^3_a}\Phi_a\right)\right.\\
  &+\frac{\partial}{\partial{\bf u}_a}\cdot
     \left\{\left[\left(\Phi(u_{ab})
     -\frac{1}{2 u_{ab}^2}\Psi(u_{ab})\right)
     \frac{\partial^2u_a}{\partial{\bf u}_a
     \partial{\bf u}_a}\right]\cdot
     \frac{\partial \Phi_a}{\partial{\bf u}_a}\right\}
    \label{eq:coll-lin} \\
  &+\left. \frac{\partial}{\partial{\bf u}_a}\cdot
     \left[\left(\frac{1}{u_{ab}^2}\Psi(u_{ab})
     \frac{{\bf u}_a{\bf u}_a}{u_a^3}\right)\cdot
   \frac{\partial \Phi_a}{\partial{\bf u}_a}\right]\right\},
\end{split}
\end{equation}
where $u_{ab}\equiv u_a (v_{T_a}/v_{T_b})$, $u_a=v_a/v_{T_a}$,
with $v_{T_a}$ and $v_{T_b}$ representing the thermal velocity of
the particles of species $a$ and $b$, respectively. The quantity
$\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an auxiliary function \cite{
  Gaffey1976}, in which $\Phi(x) \equiv \frac{2}{\sqrt{\pi}}
\int_0^x e^{-t^2}dt$ is the error function and $\Phi'(x)=
\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative. The factor
$\Gamma_{ab}$ is given by $\Gamma_{ab}=2\pi g Z_b^2 \ln\Lambda $,
where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma
parameter, $\ln \Lambda$ is Coulomb logarithm, and $Z_{b=e,i}$ is
the ion and electrons charge number, with $Z_e=1$.
The dispersion relations for $L$ and $S$ waves in dimensionless
form are given by
\begin{eqnarray*}
  z_{\bf q}^L = \left(1+\frac{3}{2}q^2\right)^{1/2},
 \quad   z_{\bf q}^S = \frac{q\, A}{(1+q^2/2)^{1/2}}, \quad
    A= \frac{1}{\sqrt{2}} \left(\frac{m_e}{m_i}\right)^{1/2}
     \left(1+3\frac{T_i}{T_e}\right)^{1/2}.
\end{eqnarray*}

The above set of integro-differential equations was numerically solved in
2D wave-number space and 2D velocity space, respectively. For the wave kinetic
equations, it was used a fourth-order Runge-Kutta method and, for the partial
differential equation describing the electron dynamics, we employed the
splitting algorithm. In both cases we used fixed time step $\Delta \tau=0.1$.
The wave number space grid has been assumed with $71\times 71$ points in
$k_{\perp}$ and $k_{\parallel}$, with $0<k_{\perp}v_e/\omega_{pe}<0.6$ and
$0<k_{\parallel}v_e/\omega_{pe}<0.6$. In the velocity space, the grid
configuration was  $71\times 141$ for $v_{\perp}/v_e$ and $v_{\parallel}/v_e$,
with velocity range $0<v_{\perp}/v_e<16$ and $-16<v_{\parallel}/v_e<16$.

\includepdf[pages=-]{Tigik2017a.pdf}

\chapter{Final remarks}
\label{cha:final}
In this text, we have summarized the early results of the analysis of a new first
principles theory, depicted in \Cref{noneigenmode}, which combines collective
processes (eigenmodes) and collisional interactions (noneigenmodes), for Langmuir
and ion-sound waves, without any \emph{ad hoc} addition. The importance of this
formalism, became clear right in the first study, presented in \Cref{coll-damp},
where it was shown the collisional damping rate calculated with the heuristic
Spitzer formula, that is independent of the wave-number, is highly overestimated
when compared with the rigorous expression, which has to be integrated in the
wave-number space. The Spitzer approximation is largely applied to the modeling
and interpretation of several solar phenomena observed by space-probes \cite{
  VWK2000,Hannah2009,ZVST11,KRB12,KF13,RR14,Reid2015}, a fact that emphasizes
the necessity of the development of a mathematically rigorous theory able to
describe hybrid situations involving collective oscillations and collisional
interactions.

The second study, discussed in \Cref{sec:gen-supr}, was focused on the
consequences of taking into account the hitherto unknown effect of
electrostatic bremsstrahlung. The outcome of such analysis revealed an
underlying process, which takes the electron velocity distribution
out of its initial equilibrium state and transforms it into a new
quasi-equilibrium state that resembles a velocity distribution composed
by a Maxwellian core with a suprathermal tail. Such velocity distributions
are pervasively observed in space plasmas \cite{Parker1958a,Vasyliunas68,
  Coroniti1974,FABMG75,Lin1998,Horne2005,Clark2015,Padovani2015,deSoria2016,
  Padovani2017,Deca2017}. However, until these
days, despite several attempts of explanations based on different models,
no existing first principles approach is capable to self-consistently
describe its origin and evolution. Again, the relevance of this research
becomes evident. The ubiquity of inverse power-law velocity distribution
in space plasmas indicates the action of a fundamental physical process on
the plasma particles; this process may be the electrostatic bremsstrahlung.
For instance, the possibility of the formation of a suprathermal electron
distribution in a mildly collisional environment, as demonstrated in
\cite{Tigik2017a}, is in accordance with the velocity filtration model,
which rely on the existence of a high energy electron population in the
transition region, located between the chromosphere and the solar corona,
to explain the temperature inversion observed in the solar corona \cite{
  Scudder92a,Scudder92b,Anderson94,Scudder94,Scudder96,DS99,DS03,Teles15}.
Howsoever, the generality of the results of Ref. \cite{Tigik2017a} suggests
that collisional interactions involving charged particles enfold physical
processes that go beyond the Coulomb collisions effects, which might be
connected to some unexplained phenomena in plasma. Therefore, it is in
this context that the present doctoral working proposal is inserted.

The prospects of this research are promising. Besides including the
new effects on the time evolution of nonlinear beam-plasma interaction,
we are planning the inclusion of effects due to non-homogeneous
medium on the beam-plasma dynamics, and its implementation in the numerical
code. Furthermore, the results regarding
the electrostatic bremsstrahlung term deserve further research in order
to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
the electrostatic bremsstrahlung being the underlying effect behind the
generation of suprathermal velocity distributions, which are pervasively
observed in space plasmas. The objectives above are in accordance with
the research project approved for the ``Sandwich Doctorate Program'',
that is proposed to occur under the supervision of Dr. Peter Yoon in the
University of Maryland.

\section{Schedule}
\label{sec:schedule}
The expected schedule for the remaining period of this doctoral
research is detailed below:
\begin{itemize}
\item \textbf{March to July 2018:} inclusion the new effects on
  the time evolution of nonlinear beam-plasma interaction, and of
  implementation the code for the inclusion of non-homogeneous
  medium on the beam-plasma dynamics;
\item \textbf{August 2018 to February 2019:} internship period in
  the University of Maryland, working on the further development
  of the electrostatic bremsstrahlung hypothesis;
\item \textbf{March to August of 2019:} Thesis elaboration.
\end{itemize}

\begin{appendix}
\chapter{Improved approximation for the second order susceptibility}
\label{appA}
\setcounter{equation}{0}
\renewcommand{\theequation}{A\arabic{equation}}
Let us start with an analysis of the approximation of the second order
susceptibility used in \cite{YZKS16} for the bremsstrahlung equations.
The expressions for $L$ and $S$ waves, in the above cited paper, are
given by:
\begin{eqnarray}
\label{bremsst,L,1}
P_{\bf k}^{\sigma L} &=& \frac{3e^2T_e}{16\pi^3m_e}
\biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2\frac{1}{k^2\lambda_{De}^2}
\int d{\bf k}'\left(1+\frac{T_e}{T_i}
+{k'}^2\lambda_{De}^2\right)^{-2}\left(1+\frac{T_e}{T_i}
+({\bf k}-{\bf k}')^2\lambda_{De}^2\right)^{-2}
\nonumber\\
&& \times\int d{\bf v}\int d{\bf v}'\,
\delta[\sigma\omega_{\bf k}^L-{\bf k}\bm{\cdot}{\bf v}
+{\bf k}'\bm{\cdot}({\bf v}-{\bf v}')]
\sum_aF_a({\bf v})\sum_bF_b({\bf v}'),
\\
\label{bremsst,S,1}
P_{\bf k}^{\sigma S} &=& \mu_{\bf k}\frac{3e^2T_e}{16\pi^3m_e}
\biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2\frac{1}{k^2\lambda_{De}^2}
\int d{\bf k}'\left(1+\frac{T_e}{T_i}
+{k'}^2\lambda_{De}^2\right)^{-2}\left(1+\frac{T_e}{T_i}
+({\bf k}-{\bf k}')^2\lambda_{De}^2\right)^{-2}
\nonumber\\
&& \times\int d{\bf v}\int d{\bf v}'\,
\delta[\sigma\omega_{\bf k}^S-{\bf k}\bm{\cdot}{\bf v}
+{\bf k}'\bm{\cdot}({\bf v}-{\bf v}')]
\sum_aF_a({\bf v})\sum_bF_b({\bf v}').
\end{eqnarray}

Assuming that the most important contribution comes from the region
where ${\bf k}\cdot {\bf v}\simeq 0$, ${\bf k'}\cdot{\bf v'}\simeq 0$,
and ${\bf k'}\cdot {\bf v}\simeq 0$,
\begin{equation}
\begin{split}
\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\int d{\bf v''}\\
&\left[-\frac{T_a}{m_a}\frac{{\bf k'}\cdot({\bf k-k'})}
{(-{\bf k}\cdot{\bf v''}+i0)}
\frac{({\bf k-k'})\cdot{\bf v''}}
   {[-({\bf k-k'})\cdot{\bf v''}+i0]^2} \right.
   + \frac{1}{(-{\bf k}\cdot{\bf v''}+i0)}
\frac{({\bf k'}\cdot{\bf v''})(({\bf k-k'})\cdot{\bf v''})}
{(-({\bf k-k'})\cdot{\bf v''}+i0)}\\
& -\frac{T_a}{m_a} \frac{({\bf k-k'})\cdot {\bf k'}}{(-{\bf k}\cdot{\bf v''}+i0)}
\frac{{\bf k'}\cdot{\bf v''}}{(-{\bf k'}\cdot{\bf v''}+i0)^2} \left.
+ \frac{1}{(-{\bf k}\cdot{\bf v''}+i0)}\frac{(({\bf k-k'})\cdot{\bf v''})
({\bf k'}\cdot{\bf v''})}{(-{\bf k'}\cdot{\bf v''}+i0)}
\right] f_a({\bf v''})
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\int d{\bf v''}\\
&\times \left[-\frac{T_a}{m_a}
  \frac{{\bf k'}\cdot({\bf k-k'})}{(-{\bf k}\cdot{\bf v''}+i0)}
\frac{({\bf k-k'})\cdot{\bf v''}}
{(-({\bf k-k'})\cdot{\bf v''})
[-({\bf k-k'})\cdot{\bf v''}+i0]} \right.
 + \frac{1}{(-{\bf k}\cdot{\bf v''}+i0)}
\frac{({\bf k'}\cdot{\bf v''})(({\bf k-k'})\cdot{\bf v''})}
{[-({\bf k-k'})\cdot{\bf v''}+i0]}\\
&-\frac{T_a}{m_a} \frac{({\bf k-k'})\cdot {\bf k'}}
{(-{\bf k}\cdot{\bf v''}+i0)}
\frac{{\bf k'}\cdot{\bf v''}}
{(-{\bf k'}\cdot{\bf v''})(-{\bf k'}\cdot{\bf v''}+i0)}
\left. + \frac{1}{(-{\bf k}\cdot{\bf v''}+i0)}
\frac{(({\bf k-k'})\cdot{\bf v''})
({\bf k'}\cdot{\bf v''})}
{(-{\bf k'}\cdot{\bf v''}+i0)}
\right] f_a({\bf v''})
\end{split}
\end{equation}

Simplifying, and writing the coefficient in front of the expression in a
different way,
\begin{equation}
\begin{split}
\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}\\
&\times\int d{\bf v''}\,\left\{\frac{T_a}{m_a}
\frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
\left[\frac{1}{({\bf k-k'})\cdot{\bf v''}} 
+\frac{1}{({\bf k'})\cdot{\bf v''}}\right] 
+ \frac{\bf k'\cdot v''}{\bf k\cdot v''} 
+ \frac{({\bf k}-{\bf k'}){\bf \cdot v''}}{\bf k\cdot v''} 
\right\} F_a({\bf v''}) + i\,{\rm Im}\chi^{(2)}
\end{split}
\end{equation}
where we have used $f_a= \hat{n} F_a$.

\begin{equation}
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
\int d{\bf v''}\,\left[\frac{T_a}{m_a}
\frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
\frac{{\bf k}\cdot {\bf v''}}{({\bf k-k'})\cdot{\bf v''}}+1
\right] F_a({\bf v''}) 
\end{equation}
\begin{equation}
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
\int d{\bf v''}\,\left[\frac{T_a}{m_a}
\frac{{\bf k'}\cdot({\bf k-k'})}{({\bf k-k'})\cdot{\bf v''}}+1
\right] F_a({\bf v''}) 
\end{equation}

The term containing ${\bf v''}$ vanishes, for distribution function which
depends only on the absolute value of the velocity, like the Maxwellian 
distribution. Therefore,
\begin{equation}
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
\end{equation}

Defining $e_i=e$, $e_e=-e$ and assuming $n_e=n_i=\overline{n}$, we have
\begin{equation}
\begin{split}
\label{chi2,5}
\chi^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
&= \sum_a\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]\\
&\simeq  i e\frac{1}{k k'|{\bf k-k'}|}
\left(\frac{\omega_{pe}^2}{T_e v_{e}^2}-\frac{\omega_{pi}^2}{T_i v_{i}^2}\right)\\
&=i e\frac{\omega_{pe}^2}{k k'|{\bf k-k'}|}
\left(\frac{m_e}{T_e 2T_e}-\frac{m_e}{m_i}\frac{m_i}{T_i 2 T_i}\right)\\
&=i\frac{e}{T_e}\frac{\omega_{pe}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{e}^2}
\left(1-\frac{m_e}{m_i}\frac{2T_e^2}{m_e}\frac{m_i}{2T_i^2}\right)\\
&=i\frac{e}{T_e}\frac{\omega_{pe}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{e}^2}
\left(1-\frac{T_e^2}{T_i^2}\right).
\end{split}
\end{equation}

Finally we have the original approximation:
\begin{equation}
\chi^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
=i\frac{e}{2T_e}\frac{1}{k k'|{\bf k-k'}|\lambda_{De}^2}
\left(1-\frac{T_e^2}{T_i^2}\right).
\end{equation}

\section{Alternative approach}
From Eq.(4.24) in \cite{YZKS16} we have
\begin{eqnarray}
\label{Eq4.24}
&&
\sum_{a,b}\frac{48e_a^2e_b^2}{\pi}\frac{1}{[\epsilon'({\bf k},\sigma
\omega_{\bf k}^\alpha)]^2}\int d{\bf k'}\int d{\bf v}\int d{\bf v'}
\delta[\sigma\omega_{\bf k}^\alpha-{\bf k\cdot v}+{\bf k'}\cdot
({\bf v-v'})]\\
&&
\times \frac{|\chi^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot
{\bf v}]|^2}{k'^2|{\bf k-k'}|^2|\epsilon({\bf k'},{\bf k'\cdot v'})|^2|
\epsilon[{\bf k-k'},({\bf k-k'})\cdot {\bf v}]|^2}f_a({\bf v}f_b({\bf v'}),
\nonumber
\end{eqnarray}
which depends on the second-order susceptibility, defined as follows,
\begin{eqnarray}
\label{chi2,1}
\chi_a^{(2)} (q_1|q_2)=-\frac{4\pi i e_a}{k_1k_2|{\bf k_1}+{\bf k_2}|}
\int d{\bf v''}\, \alpha_a^{(2)}({\bf v''};q_1|q_2)f_a({\bf v''}),
\end{eqnarray}
with $\alpha_a^{(2)}$ given by,
\begin{eqnarray}
\label{alpha2}
\alpha_a^{(2)}({\bf v''};q_1|q_2)f_a({\bf v''})=\frac{1}{2}\left[
({\bf k_1}\cdot{\bf g}_{q_1+q_2}^a)({\bf k_2}\cdot g_{q_2}^a)
+({\bf k_2}\cdot{\bf g}_{q_1+q_2}^a)({\bf k_1}\cdot g_{q_1}^a)\right],
\end{eqnarray}
and $g_q^a$ given by,
\begin{eqnarray}
\label{goper}
g_{{\bf k},\omega}^a=-\frac{e_a}{m_a}\frac{1}{\omega-{\bf k}\cdot{\bf v''}+i0}
\frac{\partial}{\partial {\bf v''}}.
\end{eqnarray}

Notice that we used variable ${\bf v''}$, since ${\bf v}$ and ${\bf v'}$ 
already appear in Eq. \eqref{chi2,1}.

Therefore, using Eq. \eqref{alpha2} in Eq. \eqref{chi2,1},
\begin{equation}
\begin{split}
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
=&-\frac{4\pi ie_a}{k k'|{\bf k-k'}|}\frac{1}{2}\int d{\bf v''}\,\biggl[
({\bf k'}\cdot
{\bf g}_{{\bf k},{\bf k'}\cdot {\bf v'}+({\bf k-k'})\cdot {\bf v}}^a)
(({\bf k-k'})\cdot 
{\bf g}_{{\bf k-k'},({\bf k-k'})\cdot {\bf v}}^a)\\
&+(({\bf k-k'})\cdot
{\bf g}_{{\bf k},{\bf k'}\cdot {\bf v'}+({\bf k-k'})\cdot {\bf v}}^a)
({\bf k'}\cdot 
{\bf g}_{{\bf k'},{\bf k'}\cdot {\bf v'}}^a)
\biggr] f_a({\bf v''})
\end{split}
\end{equation}

By using Eq. \eqref{goper},
\begin{equation}
\begin{split}
\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\int d{\bf v''}\\
&\times\left\{[\frac{{\bf k'}\cdot \partial_{\bf v''}}
{[{\bf k'\cdot v'}+({\bf k-k'})\cdot{\bf v}-{\bf k}\cdot{\bf v''}+i0]}
\frac{({\bf k-k'})\cdot \partial_{\bf v''}}
{[({\bf k-k'})\cdot {\bf v}
-({\bf k-k'})\cdot{\bf v''}+i0]} \right.\\
&\left. + \frac{({\bf k-k'})\cdot \partial_{\bf v''}}
{[{\bf k'}\cdot {\bf v'}+({\bf k-k'})\cdot {\bf v}
-{\bf k}\cdot{\bf v''}+i0]}
\frac{{\bf k'}\cdot \partial_{\bf v''}}
{[{\bf k'\cdot v'}-{\bf k'}\cdot{\bf v''}+i0]}
\right\} f_a({\bf v''})
\end{split}
\end{equation}
\begin{equation}
\begin{split}
\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\int d{\bf v''}\\
&\times\left\{\frac{
{\bf k'}\cdot({\bf k-k'})}
{[{\bf k'\cdot v'}+({\bf k-k'})\cdot{\bf v}-{\bf k}\cdot{\bf v''}+i0]}
\frac{({\bf k-k'})\cdot \partial_{\bf v''}}
{[({\bf k-k'})\cdot {\bf v}
-({\bf k-k'})\cdot{\bf v''}+i0]^2} \right.\\
& + \frac{1}
{[{\bf k'\cdot v'}+({\bf k-k'})\cdot{\bf v}-{\bf k}\cdot{\bf v''}+i0]}
\frac{{\bf k'}\cdot \partial_{\bf v''}
({\bf k-k'})\cdot \partial_{\bf v''}}
{[({\bf k-k'})\cdot {\bf v}
-({\bf k-k'})\cdot{\bf v''}+i0]}\\
& + \frac{({\bf k-k'})\cdot {\bf k'}}
{[{\bf k'}\cdot {\bf v'}+({\bf k-k'})\cdot {\bf v}
-{\bf k}\cdot{\bf v''}+i0]}
\frac{{\bf k'}\cdot \partial_{\bf v''}}
{[{\bf k'\cdot v'}-{\bf k'}\cdot{\bf v''}+i0]^2}\\
&\left. + \frac{1}
{[{\bf k'}\cdot {\bf v'}+({\bf k-k'})\cdot {\bf v}
-{\bf k}\cdot{\bf v''}+i0]}
\frac{({\bf k-k'})\cdot \partial_{\bf v''}
{\bf k'}\cdot \partial_{\bf v''}}
{[{\bf k'\cdot v'}-{\bf k'}\cdot{\bf v''}+i0]}
\right\} f_a({\bf v''})
\end{split}
\end{equation}

Assuming a Maxwellian velocity distribution function
\begin{equation}
  \begin{split}
    \label{chi2,2}
    \chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|
    {\bf k-k'},({\bf k-k'})\cdot{\bf v}]
    =-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}
    \frac{m_a^2}{T_a^2}\int d{\bf v''}\\
    &\times\left\{-\frac{T_a}{m_a}\frac{ {\bf k'}
	\cdot({\bf k-k'})}{[{\bf k'\cdot v'}
	+({\bf k-k'})\cdot{\bf v}-{\bf k}\cdot{\bf v''}+i0]}
      \frac{({\bf k-k'})\cdot{\bf v''}}{[({\bf k-k'})
	\cdot {\bf v}-({\bf k-k'})\cdot{\bf v''}+i0]^2} \right.\\
    & + \frac{1}{[{\bf k'\cdot v'}+({\bf k-k'})\cdot{\bf v}
      -{\bf k}\cdot{\bf v''}+i0]}\frac{({\bf k'}\cdot{\bf v''})
      (({\bf k-k'})\cdot{\bf v''})}{[({\bf k-k'})\cdot {\bf v}
      -({\bf k-k'})\cdot{\bf v''}+i0]}\\
    & -\frac{T_a}{m_a} \frac{({\bf k-k'})\cdot {\bf k'}}
    {[{\bf k'}\cdot {\bf v'}+({\bf k-k'})\cdot {\bf v}
      -{\bf k}\cdot{\bf v''}+i0]} \frac{{\bf k'}\cdot{\bf v''}}
    {[{\bf k'\cdot v'}-{\bf k'}\cdot{\bf v''}+i0]^2}\\
    &\left. + \frac{1}{[{\bf k'}\cdot {\bf v'}+({\bf k-k'})
	\cdot {\bf v}-{\bf k}\cdot{\bf v''}+i0]}\frac{(({\bf k-k'})
	\cdot{\bf v''}) ({\bf k'}\cdot{\bf v''})}{[{\bf k'\cdot v'}
	-{\bf k'}\cdot{\bf v''}+i0]} \right\}f_a({\bf v''})
  \end{split}
\end{equation}

Here, instead of making the early assumption that
${\bf k} \cdot {\bf v}\simeq 0$, ${\bf k}' \cdot {\bf v}'\simeq 0$
and ${\bf k}'\cdot {\bf v} \simeq 0$, we take into account
the fact that Eq. \eqref{Eq4.24} contains a delta function:
\begin{equation}
{\bf k'\cdot v'}+({\bf k-k'})\cdot{\bf v}= \sigma\omega_{\bf k}^\alpha.
\end{equation}

With this small change we obtain a quite different expression than that obtained
at the same point in the previous approach:
\begin{equation}
\begin{split}
\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2} \int d{\bf v''}\\
&\times\left\{-\frac{T_a}{m_a}\frac{{\bf k'}\cdot({\bf k-k'})}
{[\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v''}+i0]}
\frac{({\bf k-k'})\cdot{\bf v''}}
{[\sigma\omega_{\bf k}^\alpha-{\bf k'}\cdot {\bf v'}
-({\bf k-k'})\cdot{\bf v''}+i0]^2} \right.\\
& + \frac{1}
{[\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v''}+i0]}
\frac{({\bf k'}\cdot{\bf v''})
(({\bf k-k'})\cdot{\bf v''})}
{[\sigma\omega_{\bf k}^\alpha-{\bf k'}\cdot {\bf v'}
-({\bf k-k'})\cdot{\bf v''}+i0]}\\
& -\frac{T_a}{m_a} \frac{({\bf k-k'})\cdot {\bf k'}}
{[\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v''}+i0]}
\frac{{\bf k'}\cdot{\bf v''}}
{[\sigma\omega_{\bf k}^\alpha- ({\bf k- k'})\cdot{\bf v'}
-{\bf k'}\cdot{\bf v''}+i0]^2}\\
&\left. + \frac{1}
{[\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v''}+i0]}
\frac{(({\bf k-k'})\cdot{\bf v''})
({\bf k'}\cdot{\bf v''})}
{[\sigma\omega_{\bf k}^\alpha- ({\bf k- k'})\cdot{\bf v'}
-{\bf k'}\cdot{\bf v''}+i0]}
\right\} f_a({\bf v''}).
\end{split}
\end{equation}

And it is just after the previous assumption that we assume that the most
important contribution comes from the region where
${\bf k}\cdot {\bf v}\simeq 0$, ${\bf k'}\cdot{\bf v'}\simeq 0$,
and ${\bf k'}\cdot {\bf v}\simeq 0$, then
\begin{equation}
\begin{split}
\label{chi2,2b}
\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\int d{\bf v''}\\
&\times \left\{-\frac{T_a}{m_a}\frac{{\bf k'}\cdot({\bf k-k'})}
{[\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v''}+i0]}
\frac{({\bf k-k'})\cdot{\bf v''}}
{[\sigma\omega_{\bf k}^\alpha
-({\bf k-k'})\cdot{\bf v''}+i0]^2} \right.\\
& + \frac{1}
{[\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v''}+i0]}
\frac{({\bf k'}\cdot{\bf v''})
(({\bf k-k'})\cdot{\bf v''})}
{[\sigma\omega_{\bf k}^\alpha-({\bf k-k'})\cdot{\bf v''}+i0]}\\
& -\frac{T_a}{m_a} \frac{({\bf k-k'})\cdot {\bf k'}}
{[\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v''}+i0]}
\frac{{\bf k'}\cdot{\bf v''}}
{[\sigma\omega_{\bf k}^\alpha-{\bf k'}\cdot{\bf v''}+i0]^2}\\
&\left. + \frac{1}
{[\sigma\omega_{\bf k}^\alpha-{\bf k}\cdot{\bf v''}+i0]}
\frac{(({\bf k-k'})\cdot{\bf v''})
({\bf k'}\cdot{\bf v''})}
{[\sigma\omega_{\bf k}^\alpha
-{\bf k'}\cdot{\bf v''}+i0]}
\right\} f_a({\bf v''})
\end{split}
\end{equation}

For $L$ waves, we can assume that the factor $\sigma\omega_{\bf k}^L$ is 
dominant on the denominators,
\begin{equation}
  \begin{split}
    \chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
    =-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\int d{\bf v''}\\
    &\times\left[-\frac{T_a}{m_a}[{\bf k'}\cdot({\bf k-k'})]
      \frac{({\bf k-k'})\cdot{\bf v''}}
      {(\sigma\omega_{\bf k}^L)^3}+ \frac{({\bf k'}\cdot{\bf v''})
        (({\bf k-k'})\cdot{\bf v''})}
      {(\sigma\omega_{\bf k}^L)^2} \right.\\
    &\left. -\frac{T_a}{m_a} [({\bf k-k'})\cdot {\bf k'}]
      \frac{{\bf k'}\cdot{\bf v''}}
      {(\sigma\omega_{\bf k}^L)^3}
      + \frac{(({\bf k-k'})\cdot{\bf v''})
        ({\bf k'}\cdot{\bf v''})}
      {(\sigma\omega_{\bf k}^L)^2}
    \right] f_a({\bf v''})
    \label{dom-freq}
  \end{split}
\end{equation}

Due its asymmetry, the terms which are linear in ${\bf v''}$ will vanish
when integrated, remaining
\begin{equation}
\begin{split}
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}
\int d{\bf v''}\,\left[2\frac{({\bf k'}\cdot{\bf v''})
(({\bf k-k'})\cdot{\bf v''})}
{(\sigma\omega_{\bf k}^L)^2} 
\right] f_a({\bf v''}).
\end{split}
\end{equation}

As an approximation, we write
\begin{equation}
\begin{split}
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
&=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}
2\frac{k'|{\bf k-k'}|}{(\sigma\omega_{\bf k}^L)^2} 
\int d{\bf v''}\,|{\bf v''}|^2 f_a({\bf v''})\\
&=-\frac{2\pi ie_a^3}{k m_a^2}\frac{m_a^2}{T_a^2}
\frac{2}{(\sigma\omega_{\bf k}^L)^2} \frac{2T_a}{m_a}\overline{n}\\
&=-i\frac{e_a}{m_a}\frac{\omega_{pa}^2}{k(\sigma\omega_{\bf k}^L)^2} 
\frac{m_a^2}{T_a^2}\frac{2T_a}{m_a}\nonumber
\end{split}
\end{equation}
which leads to
\begin{equation}
\label{chi2,3}
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq -i4\frac{e_a}{m_a}\frac{\omega_{pa}^2}{(\omega_{\bf k}^L)^2} 
\frac{1}{kv_{a}^2}
\end{equation}

Defining $e_i=e$ and $e_e=-e$, and assuming $n_e=n_i=\overline{n}$, we have
\begin{equation}
\chi^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
= \sum_a
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\end{equation}
\begin{equation}
\begin{split}
\sum_a
\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq & -4i\frac{e}{k(\omega_{\bf k}^L)^2}
\left(\frac{\omega_{pe}^2}{m_ev_e^2}-\frac{\omega_{pi}^2}{m_iv_i^2}\right)\\
=& -4i\frac{e}{k(\omega_{\bf k}^L)^2}
\left(\frac{\omega_{pe}^2}{m_ev_e^2}-\frac{(m_e/m_i)\omega_{pe}^2}{m_iv_i^2}\right)\\
=& -4ie\frac{\omega_{pe}^2}{k(\omega_{\bf k}^L)^2}\frac{1}{m_ev_e^2}
\left(1-\frac{m_e^2}{m_i^2}\frac{v_e^2}{v_i^2}\right)\\
=& -4ie\frac{\omega_{pe}^2}{k(\omega_{\bf k}^L)^2}\frac{m_e}{m_e2T_e}
\left(1-\frac{m_e^2}{m_i^2}\frac{2T_e}{m_e}\frac{m_i}{2T_i}\right)\\
=&-i\frac{2e}{T_e}\frac{\omega_{pe}^2}{k(\omega_{\bf k}^L)^2}
\left(1-\frac{m_e}{m_i}\frac{T_e}{T_i}\right)
\end{split}
\end{equation}
\begin{equation}
\label{chi2,4}
\chi^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
\simeq i\frac{2e}{T_e}\frac{\omega_{pe}^2}{k(\omega_{\bf k}^L)^2}
\left(1-\frac{m_e}{m_i}\frac{T_e}{T_i}\right)
\end{equation}

Since this approximation assumes the dominant frequency range on the
denominators is given by the dispersion relation of Langmuir waves
(see Eq. \eqref{dom-freq}), which are high frequency oscillations
near the electron plasma frequency, it is not suitable for use on
the bremsstrahlung expression for $S$ waves.

\chapter{Asymptotic equilibrium}
\label{appB}
The results presented in Ref. \cite{Tigik2017a} suggest that in the presence
of electrostatic bremsstrahlung emission, the wave-particle system evolves to
a state of asymptotic equilibrium, in which the velocity distribution resembles
the ubiquitous core-halo velocity distribution. To test this assumption, we
search for the steady state solution of the kinetic equation for Langmuir waves,
taking into account the effects of collisional damping and electrostatic
bremsstrahlung, in addition to the spontaneous and induced emission processes,
\begin{equation}
  \frac{\partial {\cal E}_{\bf q}^{\sigma L}}
  {\partial \tau}
  =\mu_{\bf q}^L\frac{\pi}{q^2}
  \int d{\bf u}\;\delta(\sigma
  z_{\bf q}^L-{\bf q}\cdot{\bf u})\biggl(g\,\Phi_e({\bf u})
  +\sigma z_{\bf q}^L\,{\cal E}_{\bf q}^{\sigma L}
  \,{\bf q}\cdot\frac{\partial \Phi_e}{\partial{\bf u}}\biggr)
  +P_{\bf q}^{\sigma L}+2\gamma_{\bf q}^{\sigma L}\calE_{\bf q}^{\sigma L}\approx 0,
  \label{asymp}
\end{equation}

For use in this asymptotic equation, let us assume isotropic distributions for
ions and electrons, which are the summation of Maxwellian and $\kappa_\beta$
distributions. In terms of dimensionless variables,
\begin{equation}
\label{fbeta}
f_{\beta}({\bf u})= \left(1-\frac{n_{\kappa\beta}}{n_e}\right)
\frac{1}{\pi^{3/2} u_{\beta}^3}\exp\left(-\frac{u^2}{u_\beta^2}\right)
+\frac{n_{\kappa\beta}}{n_e}\frac{1}{\pi^{3/2} \kappa_\beta^{3/2}
u_{\beta,\kappa}^3}
\frac{\Gamma(\kappa_\beta+1)}{\Gamma(\kappa_\beta-1/2)}
\left(1+\frac{u^2}{\kappa_\beta u_{\beta,\kappa}^2}
\right)^{-(\kappa_\beta+1)}~.
\end{equation}
where
\begin{equation}
u_{\beta,\kappa}= \frac{v_{\beta,\kappa}}{v_e},\quad
u_\beta=\frac{v_\beta}{v_e},\quad
u_{\beta,\kappa}^2= \frac{\kappa_\beta-3/2}{\kappa_\beta} u_\beta^2.
\end{equation}

The equilibrium is obtained setting expression \eqref{asymp}
equal to zero, leading to
\begin{equation}
{\cal E}_{\bf q}^{\sigma L}=
\frac{g}{2(z_{\bf q}^L)^2}
\frac{\left(1-\frac{n_{\kappa e}}{n_e}\right)I_M^{eL}+\frac{n_\kappa}{n_e}I_1^{eL}
+\frac{1}{\mu_{\bf q}^L g}\frac{q^2}{\pi}
P_q^{\sigma L}}
{\left(1-\frac{n_{\kappa e}}{n_e}\right)I_M^{eL}
+\frac{u_e^2}{u_{e,\kappa}^2}\frac{(\kappa_e+1)}{\kappa_e}
\frac{n_{\kappa e}}{n_e}I_2^{eL}
-\frac{1}{\mu_{\bf q}^L}\frac{q^2}{\pi}
\frac{1}{(\sigma z_q^L)^2}
\gamma_{\bf q}^{\sigma L(coll)}},
\end{equation}
where
\begin{equation}
  I_M^{\beta\alpha}= \int d^3u\; \Phi_{\beta,M}(u)
\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u}),
\end{equation}
\begin{equation}
  I_1^{\beta\alpha}= \int d^3u\; \Phi_{\beta,\kappa}(u)
  \delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u}),
\end{equation}
\begin{equation}
I_2^{\beta\alpha}= \int d^3u\;
\left(1+\frac{u^2}{\kappa_\beta u_{\beta,\kappa}^2}\right)^{-1}
\Phi_{\beta,\kappa}(u)\delta(\sigma z_{\bf q}^\alpha-{\bf q}\cdot{\bf u}).
\end{equation}

The integrals $I_M^{\beta\alpha}$, $I_1^{\beta\alpha}$ and 
$I_2^{\beta\alpha}$ can be evaluated analytically, resulting in
\begin{eqnarray}
\label{IM,I1,I2}
&&I_M^{\beta\alpha}= \frac{1}{\pi^{1/2} u_{\beta}}
\frac{1}{q}\exp\left(-\frac{(z_q^\alpha/q)^2}{u_{\beta}^2}\right),\\
&&I_1^{\beta\alpha}= \frac{1}{\pi^{1/2} \kappa_\beta^{1/2} u_{\beta,\kappa}}
\frac{\Gamma(\kappa_\beta)}{\Gamma(\kappa_\beta-1/2)}
\frac{1}{q}\left(1+\frac{(z_q^\alpha/q)^2}{\kappa_\beta u_{\beta,\kappa}^2}
\right)^{-\kappa_\beta},\nonumber\\
&&I_2^{\beta\alpha}= \frac{1}{\pi^{1/2} \kappa_\beta^{1/2} u_{\beta,\kappa}}
\frac{\Gamma(\kappa_\beta)}{\Gamma(\kappa_\beta-1/2)}
\frac{\kappa_\beta}{\kappa_\beta+1}
\frac{1}{q}\left(1+\frac{(z_q^\alpha/q)^2}{\kappa_\beta u_{\beta,\kappa}^2}
\right)^{-(\kappa_\beta+1)}\nonumber.
 \end{eqnarray}

Using the expressions given by the equations \eqref{IM,I1,I2}, the
numerator of the expression for the asymptotic wave spectrum becomes
\begin{eqnarray*}
  \left(1-\frac{n_{\kappa e}}{n_e}\right)
  \frac{1}{\pi^{1/2} u_{e}}\frac{1}{q}
  \exp\left(-\frac{(z_q^L/q)^2}{u_{e}^2}\right)
  +\frac{n_{\kappa e}}{n_e}
  \frac{1}{\pi^{1/2} \kappa_e^{1/2} u_{e,\kappa}}
  \frac{\Gamma(\kappa_e)}{\Gamma(\kappa_e-1/2)}
  \frac{1}{q}\left(1+\frac{(z_q^L/q)^2}{\kappa_e u_{e,\kappa}^2}
  \right)^{-(\kappa_e)}
  +\frac{1}{\mu_{\bf q}^L g}\frac{q^2}{\pi}
  P_q^{\sigma L}.
\end{eqnarray*}

Proceeding in the same way, the expression at the denominator
of the expression for the asymptotic wave spectrum becomes
\begin{equation*}
  \begin{split}
   \left(1-\frac{n_{\kappa e}}{n_e}\right)
  &\frac{1}{\pi^{1/2} u_{e}}\frac{1}{q}
  \exp\left(-\frac{(z_q^L/q)^2}{u_{e}^2}\right)
  +\frac{u_e^2}{u_{e,\kappa}^2}
  \frac{n_{\kappa e}}{n_e}
  \frac{1}{\pi^{1/2} \kappa_e^{1/2} u_{e,\kappa}}\\
  &\times\frac{\Gamma(\kappa_e)}{\Gamma(\kappa_e-1/2)}
  \frac{1}{q}\left(1+\frac{(z_q^L/q)^2}{\kappa_e u_{e,\kappa}^2}
  \right)^{-(\kappa_e+1)}
  -\frac{1}{\mu_{\bf q}^L}\frac{q^2}{\pi}
  \frac{T_e}{T_*}\frac{1}{(\sigma z_q^L)^2}
  \gamma_{\bf q}^{\sigma L(coll)}.
 \end{split}
\end{equation*}

Therefore,
\begin{eqnarray}
\label{L,asymp}
{\cal E}_{\bf q}^{\sigma L}&=& 
\frac{g}{2(z_{\bf q}^L)^2}
\biggl[\left(1-\frac{n_{\kappa e}}{n_e}\right)
\exp\left(-\frac{(z_q^L/q)^2}{u_{e}^2}\right)\nonumber\\
&&+\frac{n_{\kappa e}}{n_e}
\frac{1}{(\kappa_e-3/2)^{1/2}}
\frac{\Gamma(\kappa_e)}{\Gamma(\kappa_e-1/2)}
\left(1+\frac{(z_q^L/q)^2}{\kappa_e-3/2}
\right)^{-\kappa_e}+\hat{P}_q^{\sigma L}\biggr]\nonumber\\
&&\times \biggl[\left(1-\frac{n_{\kappa e}}{n_e}\right)
\exp\left(-\frac{(z_q^L/q)^2}{u_{e}^2}\right)\\
&&+\frac{n_{\kappa e}}{n_e}
\frac{1}{(\kappa_e-3/2)^{3/2}}
\frac{\Gamma(\kappa_e+1)}{\Gamma(\kappa_e-1/2)}
\left(1+\frac{(z_q^L/q)^2}{\kappa_e-3/2}
   \right)^{-(\kappa_e+1)}-2\hat{\gamma}_{\bf q}^{\sigma L(coll)}\biggr]^{-1},
   \nonumber
\end{eqnarray}
where
\begin{equation}
  \hat{P}_q^{\sigma L}= \frac{u_e}{\mu_{\bf q}^L g}\frac{q^3}{\pi^{1/2}}
  P_q^{\sigma L},
\end{equation}
\begin{equation}
  \hat{\gamma}_{\bf q}^{\sigma L(coll)}= \frac{u_e}{\mu_{\bf q}^L}
  \frac{q^3}{\pi^{1/2}}\frac{1}{2(\sigma z_q^L)^2}
  \gamma_{\bf q}^{\sigma L(coll)}.
\end{equation}

\autoref{fig5} shows the normalized value of the asymptotic spectrum of
$L$ waves, obtained with the use of Eq. \eqref{L,asymp}, considering a
plasma in which the ion population is described by a Maxwellian velocity
distribution, and the electron population is described by a distribution
as defined in equation \eqref{fbeta}, with $n_{\kappa e}/n_e= 0.05$. That
is, the electron distribution is a core-halo distribution, with $5\%$
of the particles in the halo population. For the evaluation of the
collisional damping and electrostatic bremsstrahlung terms, appearing
in Eq. \eqref{L,asymp}, we used Eqs. \eqref{GqL} and \eqref{PqL}, taking
into account only the Maxwellian distribution, which is a reasonable
approximation  due to the smallness of the halo population. 
\autoref{fig5}(a) shows the spectra obtained considering several values
of the index $\kappa_e$, from $\kappa_e=2.5$ to $\kappa_e=40$. It is seen
that the wave amplitude increases at the region of small values of $q$,
with the increase of $\kappa_e$. It is also seen that in the case of
fairly large value of $\kappa_e$, as $\kappa_e=40$, the spectrum obtained
in the case of a core-halo distribution is very close to the spectrum
obtained in the case of a purely Maxwellian electron distribution, which
can be obtained from equation \eqref{L,asymp} by taking $n_{\kappa e}=0$.
It is also seen that in the case of small values of $\kappa_e$ the
asymptotic spectrum is qualitatively very similar to the spectrum
obtained after the time evolution of the system, taking into account
the new effects of electrostatic bremsstrahlung and collisional damping,
shown in Figure 1 of Ref. \cite{Tigik2017a}. For comparison, we
show in figure \autoref{fig5}(b) the asymptotic spectrum of $L$ waves
which would be obtained by neglecting the new effects, of collisional
bremsstrahlung and collisional damping.
% \begin{figure}[h]
%   \begin{center}
%     %% \hspace{-0.42cm}
%     \includegraphics[scale=0.5,angle=270]{IL1D_005kvar.eps}
%     \includegraphics[scale=0.5,angle=270]{IL1D_005kvarno-brem.eps}
%     \caption{Asymptotic spectrum of Langmuir waves for several values
%       of $\kappa$ index and Maxwellian distribution. (a) With electrostatic
%     bremsstrahlung emission and collisional damping.
%    (b) Without bremsstrahlung emission and collisional damping.}
%     \label{fig5}
%   \end{center}
% \end{figure}

The equations presented in this appendix and, more important, the
ideas about the asymptotic state of the eigenmodes of an unmagnetized
plasma considering several values of kappa coefficient, were developed
in parallel with another work, which slightly deviates from the
main subject of this PhD research, but had a big contribution on the
development of the work presented in Ref. \cite{Tigik2017a}. 
The work in question, whose title
is ``Weakly turbulent plasma processes in the presence of inverse
power-law velocity tail population'' \cite{Tigik2017b}, investigates
the modifications on the spectra of the Langmuir, ion-sound and
transverse waves caused by different kappa indexes in a core-halo
velocity distribution function. The full article can be seen in
\Cref{appC}.

\chapter{Extra publication}
\label{appC}
This publication is mainly related with the results results presented in
Ref. \cite{Tigik2017a}.
We can say that most of the ideas about the physical processes occurring
in \cite{Tigik2017a}, regarding the formation of the core-halo velocity
distribution and the fact that the electrostatic bremsstrahlung could be
the underlying process behind the ubiquity of such velocity distribution
in the space environment, came from the analysis of the results presented
in \cite{Tigik2017b}.

\includepdf[pages=-]{Tigik2017b.pdf}
\end{appendix}

\bibliographystyle{unsrturl}
\bibliography{papers,books}
\end{document}

### 2019-05-12 pagtit.tex
Add files via upload

\begin{titlepage}
  \begin{center}
  \centering{
    \textsc{\Large \sffamily {Universidade Federal do Rio Grande do Sul}}\\
    \textsc{\Large \sffamily {Programa de Pós-Graduação em Física}}\\
    \vspace{0.2cm}
    {\large  Qualifying Exam}}\\
\end{center}

\vspace{6cm}

\vfill
\begin{center}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\setcounter{footnote}{2}
{\Large \sffamily \textbf{Time evolution of weakly turbulent processes in
    the presence of collisional interactions in astrophysical plasmas}\footnote[1]{
    Project financed by the by the Conselho Nacional de
    Desenvolvimento Científico e Tecnológico (CNPq) and the
    Coordenação de Aperfeiçoamento Pessoal de Nível Superior (CAPES).}}\\
{\large \sffamily (Evolução temporal de processos fracamente turbulentos
  na presença de efeitos colisionais em plasmas astrofísicos)}\\
\vspace{1.5cm}
\Large Sabrina Tigik Ferrão\\
\end{center}
\vspace{3cm}
\vfill
\hfill
\parbox{.5\textwidth}{Doctoral Thesis prepared under the supervision of
  Professor Luiz Fernando Ziebell, presented to the Physics Graduation
  Program of the Instituto de F\'{\i}sica at UFRGS, in partial fullfillment
  of the requirements for obtaining the title of Doctor in Sciences.}\\
\vfill
\vspace{1cm}
\begin{center}
  { Porto Alegre\\ \today}
\vspace{0.5cm}
\renewcommand{\thefootnote}{\arabic{footnote}}
\end{center}

\end{titlepage}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "quali"
%%% End:

### 2019-05-12 thesis.tex
Add files via upload

--- 2019-05-12 draft.tex
@@
 \definecolor{lilac}{rgb}{0.78, 0.64, 0.78}
-
 \begin{document}
+
 \frenchspacing 
@@
 \setcounter{page}{0}
-
-% LFZ180216: O título não está aqui, mas pode ser discutido um pouco.
-% A questão é que parece dar ênfase demais a processos colisionais. A gente
-% estuda a evolução temporal do sistema, incluindo processos colisionais. Parece
-% meio forte dizer que se estuda a evolução de processos colisionais, apenas.
-% Por outro lado, se ficar assim, acho que deve ser "collisional processes"
-% em lugar de "colisional process"
-% Sabrina: Eu mudei um pouco o título pra incluir a teoria de turbulência
-% fraca. Ficou meio grande, mas fazer o quê? Não tirei "plasmas
-% astrofísicos" porque acho que dá uma vaga ideia de com que tipo de plasma
-% estamos lidando. Eu acho melhor do que escrever "low density and fully
-% ionized plasmas", o que deixaria o título maior ainda. Mas, se achares
-% necessário, posso tirar a menção a plasmas astrofísicos e deixar sem nada
-% que caracterize o plasma, ou colocar "low density and fully ionized plasmas".
-% O que achares melhor.
-% Sabrina 20/02: Sem comentários a respeito do título?
 \chapter{Introduction}
@@
 be neglected, what happens when the studied phenomenon evolves
-in a much shorter 
-% LFZ180216: "much shorter" ?
-% Sabrina: OK
-time-scale than the collisional relaxation time
+in a much shorter time-scale than the collisional relaxation time
 of the plasma in question \cite{akhi1967}. In such cases, the
 plasma dynamics may be described by the Vlasov-Maxwell system, 
-% LFZ180216: Acho que vai vírgula depois de "system"
-% Sabrina: OK
 a complex set of coupled equations whose solution invariably will
@@
 
-With the lowest order of this chain of perturbative approximations,
-the linear theory, it is possible to obtain the dispersion relations,
-mathematical expressions that not only help us on identifying the
+With the lowest order of this chain of perturbative approximations, the
+linear theory, it is possible to obtain the dispersion relations, which
+are mathematical expressions that not only help us on identifying the
 different oscillatory modes that may be excited in plasmas, but also
@@
 $t$ \cite{klimo,klimon}.
-% LFZ180216: Acho que deve ser "instant $t$" (ou seja, $t$ em itálico).
-% Sabrina: OK
 
@@
 \bibliography{papers,books}
+
 \end{document}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: t
+%%% End:

### 2019-05-13 thesis.tex
Rewriting the introduction
Started with de definition of plasma (still to be finished);

Next, talk about why studying plasma is important.

@@
   work [P. H. Yoon et al., Phys. Rev. E 93:033203 (2016)], collisional
-% LFZ180220: Coloquei espaço entre a vírgula e "Phys. Rev. E". E coloquei
-% vírgula após "incorporated", na linha que segue.
   effects and collective processes were systematically incorporated,
@@
   considering electrostatic oscillations. The outcome of this innovative
-% LFZ180220: Mudei "outcomes" para "outcome", uma vez que o verbo está como
-% "was".
-% Sabrina: não seria melhor manter o "outcomes" e trocar "was" por "were"?
-% É que tem mais de um resultado... Ou será que dá pra considerar esses
-% dois itens como um resultado global?
   approach was a formal mathematical expression for the collisional
-  damping rate for Langmuir and ion-sound waves, and the discovery of a
-  new fundamental  process of emission of electrostatic fluctuations, in
-  the ion-sound and Langmuir frequency range, caused by binary interactions
-  of particles,
-% LFZ180220: Não fica melhor "caused by binary interactions of particles",
-% em lugar de "caused by particle scattering"? Se não achares adequado tens
-% que voltar à forma anterior.
-% Sabrina: Acho que pode ser. Na verdade meio que copiei parte dessa frase
-% do artigo. Acho que o Peter quis dar ênfase ao fato de a mudança na forma
-% da função de distribuição ser causada por espalhamento. Mas concordo que
-% aqui pode causar certa confusão por causa do efeito de espalhamento das
-% ondas. Então concordo, já fiz a mudança.
-  named \emph{electrostatic bremsstrahlung}. In the present study we
-  introduce the first numerical analysis of these two new equations and
+  damping rate for Langmuir and ion-sound waves, and the discovery of a new
+  fundamental  process of emission of electrostatic fluctuations, in the
+  ion-sound and Langmuir frequency range, caused by binary interactions of
+  particles, named \emph{electrostatic bremsstrahlung}. In the present study
+  we introduce the first numerical analysis of these two new equations and
   discuss the relevance of these numerical results in the solar physics scope.
-  %The first work concerns the collisional damping equation, where we compare
   The first work to be discussed concerns the collisional damping equation, 
-  and in it we compare
-% LFZ180220: Fiz uma proposta de mmudança na frase. OK?
-% Sabrina: OK
-  the results of numerical integration of the rigorous expression with the
-  damping rate calculated with the widely applied \emph{Spitzer formula}.
-  % Besides that, the insignificance of the collisional damping rate gets
-  % LFZ180220: Aqui também, proposta de mudança na frase. Entre outras coisas,
-% estou propondo inversão das frases. OK?
-% (verifiquei que essa nova ordem está de acordo com o que estava no resumo,
-% abaixo)
-% Sabrina: ah sim, a ideia de inserir essa frase veio quando eu estava
-% escrevendo o resumo já, aí só acrescentei aqui, mas no lugar errado,
-% pelo visto
-  We show that the Spitzer approximation highly over-estimates the intensity
-  of collisional attenuation of plasma waves. 
+  and in it we compare the results of numerical integration of the rigorous
+  expression with the damping rate calculated with the widely applied
+  \emph{Spitzer formula}. We show that the Spitzer approximation highly
+  over-estimates the intensity of collisional attenuation of plasma waves. 
   The lack of relevance of the collisional damping rate gets further 
-  % proven 
-  demonstrated when we compare it with the collisionless (Landau) damping rate. 
-  In the second work to be discussed, we analyze
-  the so-far ignored electrostatic bremsstrahlung effect. We show that the
-  presence of electrostatic bremsstrahlung emission modifies the Langmuir
-  %spectrum, which in turn alters the shape of the initial Maxwellian electron
-  %velocity distribution. 
-  % LFZ180220: Proposta de mudança aqui. OK?
-  % Sabrina: OK
-  spectrum, which in turn alters the shape of the initial electron
-  velocity distribution, assumed to be Maxwellian. 
-  After a long time-evolution period (numerical
-  integration), the system seems to arrive to a new quasi-steady state, in
-  which the shape of the electron velocity distribution resembles the shape
-  of a core-halo distribution function, i.e., composed by a Maxwellian core
-  and a suprathermal tail. The outcomes of both analyses are unprecedented;
-  the prospects and possibilities for further studies on this subject are
-  promising.
-  % Sabrina: não sei se preciso mencionar este trabalho aqui, mas coloquei
-  % mesmo assim. Se achares denecessário, é só comentar o trecho a seguir:
-  % LFZ180220: Acho que cabe sim mencionar esse trabalho. Mas proponho uma
-  % mudança na frase. Acho exagerado dizer que "não tem nenhuma relação",
-  % uma vez que o bremsstrahlung é um efeito colisional.
-  % Sabrina: é, eu sei que alguma relação tem, só não sabia muito como
-  % expressar isso sem me enrolar. Enfim, ficou muito boa a tua sugestão. 
-  In the end, we also present an extra result, indirectly related to the
-  main subject of this doctoral project, regarding the analysis of the
-  complete set of electromagnetic weak turbulence equations, in the presence
-  of a core-halo velocity distribution function. 
-  %This work, however, was a
-  %parallel research and does not have any relation with the main subject of
-  %this doctoral working proposal.
-
-  % Sabrina: o trecho abaixo foi removido do abstract para dar uma
-  % "enxugada" no texto. Se achares necessário, recoloco.
-  % To do so, we assume Maxwellian
-  % velocity distribution for ions and electrons, and consider static ions
-  % while the electrons evolve in time under the quasilinear velocity diffusion
-  % process, which also includes spontaneous emission, collisional damping
-  % and, of course, electrostatic bremsstrahlung in the wave kinetic equation.
-  % For the particles we consider the quasilinear particle kinetic equation
-  % added by the linearized Landau collision operator.
+  demonstrated when we compare it with the collisionless (Landau) damping
+  rate. In the second work to be discussed, we analyze the so-far ignored
+  electrostatic bremsstrahlung effect. We show that the presence of
+  electrostatic bremsstrahlung emission modifies the Langmuir spectrum,
+  which in turn alters the shape of the initial electron velocity
+  distribution, assumed to be Maxwellian. After a long time-evolution period
+  (numerical integration), the system seems to arrive to a new quasi-steady
+  state, in which the shape of the electron velocity distribution resembles
+  the shape of a core-halo distribution function, i.e., composed by a
+  Maxwellian core and a suprathermal tail. The outcomes of both analyses are
+  unprecedented; the prospects and possibilities for further studies on this
+  subject are promising. In the end, we also present an extra result,
+  indirectly related to the main subject of this doctoral project, regarding
+  the analysis of the complete set of electromagnetic weak turbulence equations,
+  in the presence of a core-halo velocity distribution function. 
 \end{abstract}
@@
     [P. H. Yoon et al., Phys. Rev. E 93:033203 (2016)], efeitos colisionais
-% LFZ180220: Coloquei espaço entre a vírgula e "Phys. Rev. E"
-% Sabrina: OK
     e processos coletivos foram sistematicamente incorporados, partindo
@@
     considerando oscilações eletrostáticas. O resultado dessa abordagem
-% LFZ180220: Mudei para "O resultado", para combinar com "foi"
-% Sabrina: Nossa, sério que eu errei isso aqui também? Geeente...
-% Traduzi sem nem pensar a respeito, que vergonha.
     inovadora foi uma expressão matemática formal para a taxa de amortecimento
@@
     faixa de frequência das ondas de Langmuir e das ondas íon-acústicas,
-    %causado pelo espalhamento das partículas do plasma, nomeado como
-% LFZ180220: Proponho mudança, compatível com a proposta no "abstract"
-% Sabrina: OK
      causado por interações binárias entre partículas do plasma, nomeado como
@@
     discutimos a relevância desses resultados numéricos no contexto da física
-    %solar. O primeiro trabalho se refere à nova equação para o amortecimento
-    %colisional, no qual comparamos o resultado da integração numérica dessa
-% LFZ180220: Proponho mudança similar àquela proposta no "abstract".
-% Sabrina: OK
     solar. O primeiro trabalho a ser discutido se refere à nova equação para o 
     amortecimento colisional, e nele comparamos o resultado da integração
-    numérica dessa
-    expressão, com a largamente usada \emph{fórmula de Spitzer}. Com isso
-    conseguimos mostrar que a aproximação de Spitzer super-estima em muito
-    a intensidade da atenuação colisional das ondas de plasma. Além disso,
-% LFZ180220: Aqui o ordenamento das frase já estava adequado, e de acordo com
-% a mudança proposta no "abstract". So faço uma pequena mudança no texto. OK?
-    %a insignificância da taxa de amortecimento colisional se comprova quando
-% Sabrina: OK
-    a falta de relevância da taxa de amortecimento colisional fica
-    demonstrada quando
-    a comparamos com a taxa de amortecimento não colisional (de Landau).
-    No segundo trabalho, nós analizamos o até então ignorado efeito de
-    \emph{bremsstrahlung} eletrostático. Nó mostramos que a presença da
-    emissão de \emph{bremsstrahlung} eletrostático modifica o espectro
-    das ondas de Langmuir que, por sua vez, altera a forma da função de
-    %distribuição inicial dos elétrons, que é Maxwelliana. Após um longo
-% LFZ180220: Mudança compatível com a mudança proposta no "abstract".
-% Sabrina: OK
-    distribuição inicial dos elétrons, suposta Maxwelliana. Após um longo
-    tempo de evolução temporal (integração numérica), o sistema parece
-    chegar a um novo estado quase-estacionário, no qual a forma da função
-    de distribuição de velocidades dos elétrons lembra a forma de uma função
-    de distribuição núcleo-halo, ou seja, composta por um núcleo Maxwelliano e
-    uma cauda supratérmica. Os resultados de ambas análises são sem precedentes;
-    as perspectivas e as possibilidades para novos estudos neste assunto são
-    promissoras.
-    % Sabrina: não sei se preciso mencionar este trabalho aqui, mas coloquei
-    % mesmo assim. Se achares denecessário, é só comentar o trecho a seguir:
-% LFZ180220: Mudança proposta similar à que foi proposta no "abstract":
-    %No final é também apresentado um resultado extra, relativo à
-% Sabrina: OK
-    No final é também apresentado um resultado extra, indiretamente relacionado
-    ao assunto principal desse projeto de trabalho de doutorado, relativo à
-    análise do conjunto completo de equações eletromagnéticas da teoria de
-    turbulência fraca, na presença de uma função de distribuição de velocidades
-    núcleo-halo. 
-    %Este trabalho, no entanto, não tem relação com o assunto
-    %principal dessa proposta de trabalho de doutorado.
+    numérica dessa expressão, com a largamente usada \emph{fórmula de Spitzer}.
+    Com isso conseguimos mostrar que a aproximação de Spitzer super-estima
+    em muito a intensidade da atenuação colisional das ondas de plasma. Além
+    disso, a falta de relevância da taxa de amortecimento colisional fica
+    demonstrada quando a comparamos com a taxa de amortecimento não colisional
+    (de Landau). No segundo trabalho, nós analizamos o até então ignorado efeito
+    de \emph{bremsstrahlung} eletrostático. Nó mostramos que a presença da
+    emissão de \emph{bremsstrahlung} eletrostático modifica o espectro das ondas
+    de Langmuir que, por sua vez, altera a forma da função de distribuição
+    inicial dos elétrons, suposta Maxwelliana. Após um longo tempo de evolução
+    temporal (integração numérica), o sistema parece chegar a um novo estado
+    quase-estacionário, no qual a forma da função de distribuição de velocidades
+    dos elétrons lembra a forma de uma função de distribuição núcleo-halo, ou
+    seja, composta por um núcleo Maxwelliano e uma cauda supratérmica. Os
+    resultados de ambas análises são sem precedentes; as perspectivas e as
+    possibilidades para novos estudos neste assunto são promissoras. No final é
+    também apresentado um resultado extra, indiretamente relacionado ao assunto
+    principal desse projeto de trabalho de doutorado, relativo à análise do
+    conjunto completo de equações eletromagnéticas da teoria de turbulência
+    fraca, na presença de uma função de distribuição de velocidades núcleo-halo. 
    \end{abstract}
@@
 \label{cha:intro}
-In the context of the plasma kinetic theory, processes
-involving waves and kinetic instabilities, the so-called\emph{
-  collective processes}, are almost exclusively associated with
-situations in which the effects of collisional dissipation can
-be neglected, what happens when the studied phenomenon evolves
-in a much shorter time-scale than the collisional relaxation time
-of the plasma in question \cite{akhi1967}. In such cases, the
-plasma dynamics may be described by the Vlasov-Maxwell system, 
-a complex set of coupled equations whose solution invariably will
+% In the context of physics, the word ``plasma'' is used to designate a gas whose degree
+% of ionization is such that the interaction between its components is dominated by the electric
+% and magnetic forces generated by the presence and movement of the negatively and positively
+% charged particles.
+%
+% In the context of physics, the word ``plasma'' is used to designate a gas whose
+% degree of ionization is such that its dynamics is dominated by the forces of
+% electric and magnetic nature of the charged particles, overcoming the influence
+% of the collisions between neutral particles.
+%
+In the context of physics, the word ``plasma'' is used to designate a gas whose
+degree of ionization is such that the forces of electric and magnetic nature of
+the charged particles overcome the influence of the collisions between neutral
+particles, in the overall dynamics of the gas. Besides that, the
+
+When it comes to the plasma kinetic theory, processes involving waves
+and kinetic instabilities, the so-called \emph{collective processes},
+are almost exclusively associated with situations in which the effects
+of collisional dissipation can be neglected, what happens when the
+studied phenomenon evolves in a much shorter time-scale than the
+collisional relaxation time of the plasma in question \cite{akhi1967}.
+In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
+system, a complex set of coupled equations whose solution invariably will
 depend on some degree of approximation. In the presence of small
@@
 different oscillatory modes that may be excited in plasmas, but also
-wholly characterizes these oscillations. 
-% LFZ180216: Como está no plural, "dispersion relations", acho que a frase
-% deve seguir como:
-% "mathematical expressions that not only help us on identifying the
-% different oscillatory modes that may be excited in plasmas, but also
-% wholly characterize these oscillations."
-% Sabrina: OK
-Valuable information like
+wholly characterizes these oscillations. Valuable information like
 how these waves propagate and the frequencies that will resonate with
 the plasma particles, resulting in damping or amplification of these
-% LFZ180216: "of these"?
-% Sabrina: OK
 oscillations \cite{bitt,chen,gurnett2017}, are given by the dispersion
-relations. This information, however, is static. 
-% LFZ180216: "is static", ao invés de "it is static"? Acho que o sujeiro já
-% é "This information", não precisa do "it".
-% Sabrina: OK
-There is no way to
+relations. This information, however, is static. There is no way to
 know, based solely on the linear formulation, any further development
@@
 purpose of the quasilinear approximation.
-% LFZ180216: Sugestão:
-% "Thus, to clarify if these oscillations will grow
-% until their amplitudes become too large to be treated by a perturbative
-% method, or if they will rapidly increase and saturate, 
-% or if they will be completely damped,
-% or if they will decrease a little and then saturate, 
-% a certain degree of nonlinearity must be taken
-% into account. That is the purpose of the quasilinear approximation."
-% Sabrina: OK
 
@@
 the equation for the time evolution of the velocity distribution
-function. The velocity distribution will then evolve in time
-through a process of diffusion in velocity space,
-% LFZ180216: Acho que não está errado, mas me parece melhor "through a
-% process of diffusion in velocity space,"
-% Sabrina: OK
- in which the diffusion
+function. The velocity distribution will then evolve in time through
+a process of diffusion in velocity space, in which the diffusion
 coefficient depends on the spectral energy density of the waves.
 The dispersion relation is formally given by the same expression
-obtained under the linear theory, except that now it 
-depends on a time-dependent velocity distribution function, 
-% LFZ180216: Suggestion: depends on a time-dependent velocity
-% distribution function,
-% Sabrina: OK
-which must vary in a much slower
-time-scale than the period of the plasma oscillations. Under such
-condition, the gradual changing on the velocity space shape slowly
-modifies the wave spectrum, whose new form will then alter the
-velocity distribution function and so on, until a new quasi-stationary
-equilibrium state is attained \cite{gurnett2017}. However, depending
-on the phenomenon being described this saturation state reached
-under the quasilinear approximation might keep on evolving if higher
-order nonlinearities are taken into account \cite{akhi2}. This kind
-of nonlinear analysis is given by the \emph{weak turbulence theory},
-which is the next step in this chain of perturbative approximations.
+obtained under the linear theory, except that now it depends on a
+time-dependent velocity distribution function, which must vary in a
+much slower time-scale than the period of the plasma oscillations.
+Under such condition, the gradual changing on the velocity space
+shape slowly modifies the wave spectrum, whose new form will then
+alter the velocity distribution function and so on, until a new
+quasi-stationary equilibrium state is attained \cite{gurnett2017}.
+However, depending on the phenomenon being described this saturation
+state reached under the quasilinear approximation might keep on
+evolving if higher order nonlinearities are taken into account
+\cite{akhi2}. This kind of nonlinear analysis is given by the
+\emph{weak turbulence theory}, which is the next step in this chain
+of perturbative approximations.
 
@@
 order to include new effects. In the initial work, it was considered
-only the propagation of electrostatic oscillations, 
-% LFZ180216: Em lugar do trecho acima, acho melhor dizer "it was considered
-% only the propagation of electrostatic oscillations,"
-% Isso porque a frase anterior falava que novos efeitos tinham sido
-% incluidos ao formalismo, e dessa forma o "added" parece indicar que as
-% oscilações eletrostáticas foram adicionadas, como novos efeitos, e não 
-% é o caso.
-% Sabrina: OK
-taking into account the
-effects of both wave-wave and wave-particle interactions \cite{Yoon00}.
+only the propagation of electrostatic oscillations, taking into account
+the effects of both wave-wave and wave-particle interactions \cite{Yoon00}.
 Later, the formalism was expanded, and the effects of discrete particle,
-% LFZ180216: "discrete particle effects"?
-% Sabrina 20/02: acho que passei batido por esse antes...
 related to spontaneous emission and spontaneous scattering processes
@@
 other studies that also include the emission of electromagnetic waves
-\cite{ZYSGP14c,ZYPGP15,ZPYGP16}. Some studies
-using a one-dimensional approach have also been made 
-\cite{ZiebellGY01,GaelzerZY02,GZVYR08}.
-% LFZ180216: Nessa parte final da frase a ideia não era dizer "other studies
-% that also include the emission of electromagnetic waves"?
-%
-% Sabrina: Pode ser. Acho, traduzi mal o texto do plano de pesquisa
-% para o PDSE.
-% LFZ180220: No plano para o PDSE havia uma frase mais ambígua do que essa que
-% propus aqui. Dizia "estudo de processos de emissão envolvendo ondas de
-% Langmuir". Nota que se diz "processos de emissão", sem especificar o tipo.
-% E depois "envolvendo ondas de Langmuir". Não era apenas "emissão de ondas
-% de Langmuir", como tinhas escrito na primeira versão. Poderíamos colocar
-% a mesma frase do PDSE, mas acho que esta que diz "also include the emission
-% of electromagnetic waves" também serve. A frase anterior fala em turbulência
-% de Langmuir", e essa fala em "also include" outros efeitos. OK?
-% Sabrina: OK
-%
-% LFZ180216: Outra coisa: Poderia haver aqui uma frase como "Some studies
-% using a one-dimensional approach have also been made 
-% \cite{ZiebellGY01,GaelzerZY02,GZVYR08}."
-% Na verdade, essa referência GZVYR08, se aparecer aqui assim como sugiro, deve
-% sair da frase anterior onde estão mmencionadas análises bi-dimensionais.
-% Sabrina: Desculpa, mas não entendi bem como escrever essa parte, até porque
-% tenho pouca familiaridade com esses trabalhos em 1D. Na verdade não tenho eles
-% nem em  bibtex, nem em pdf. Mas se quiseres editar o texto para colocar eles
-% e adicionar o bibtex no papers.bib, ficarei muito agradecida. Se eu for fazer
-% isso, vai me tomar um tempo que infelizmente não tenho...
-% LFZ180220: OK, vou fazer a mudança conforme estava proposto, e adicionar as
-% referências.
-% Sabrina: Obrigada!
-The Langmuir turbulence is a by-product 
-% LFZ180216: "by-product"?
-% Sabrina: OK
-of the instability generated when an energetic electron beam interacts with
-a background plasma. The electron beam alters the electron velocity
-distribution triggering the so-called \emph{bump-in-tail instability}.
-Besides being recurrently used in textbooks as an illustrative example
-of the quasilinear diffusion process \cite{akhi2,chen,gurnett2017}, the
-bump-in-tail instability also has an essential role in the study of type
-II and type III radio bursts \cite{Emslie1984,Hannah2009,ZVST11,Hannah2011,
-  KK12,RR14,BNKR14}. In this context, the relevance of a more accurate
-description of nonlinear kinetic instabilities in plasmas, represented
-here by the beam-plasma interaction, becomes clear.
+\cite{ZYSGP14c,ZYPGP15,ZPYGP16}. Some studies using a one-dimensional
+approach have also been made \cite{ZiebellGY01,GaelzerZY02,GZVYR08}.
+The Langmuir turbulence is a by-product  of the instability generated
+when an energetic electron beam interacts with a background plasma. The
+electron beam alters the electron velocity distribution triggering the
+so-called \emph{bump-in-tail instability}. Besides being recurrently used
+in textbooks as an illustrative example of the quasilinear diffusion process
+\cite{akhi2,chen,gurnett2017}, the bump-in-tail instability also has an
+essential role in the study of type II and type III radio bursts
+\cite{Emslie1984,Hannah2009,ZVST11,Hannah2011,KK12,RR14,BNKR14}. In this
+context, the relevance of a more accurate description of nonlinear kinetic
+instabilities in plasmas, represented here by the beam-plasma interaction,
+becomes clear.
 
@@
 effects into the already well established weak turbulence formalism.
-The authors used 
-% LFZ180216: Acho que podes escrever "The authors used ..." e mais abaixo na
-% frase "they also kept ...", ou então "The authors use ..., they also keep".
-% Como está misturas dois tempos verbais na mesma frase.
-% Sabrina: OK, corrigi para "used"
-the same standard weak turbulence perturbative method
+The authors used the same standard weak turbulence perturbative method
 but, instead of keeping only the collective eigenmodes in the linear
@@
 eigenmode frequency range, which is caused by particle scattering. 
-Since this is a form of braking radiation, 
-% LFZ180216: "braking radiation"?
-% Sabrina: OK
-the authors named it as
+Since this is a form of braking radiation, the authors named it as
 \emph{electrostatic bremsstrahlung}.
@@
 published in this subject. In \Cref{cha:final}, we summarize the
-results and discuss the perspectives of the present research.
-Then, we propose a schedule for the remaining period 
-% LFZ180216: "for the remaining period"?
-% Sabrina: OK
-until the thesis
+results and discuss the perspectives of the present research. Then,
+we propose a schedule for the remaining period until the thesis
 defense. In the end we have three appendices. \Cref{appA} shows
@@
 presence and in the absence of the electrostatic bremsstrahlung.
-% LFZ180216: Tenho a impressão que essa última frase dá uma impressão errada.
-% Se bem me lembro, é suposta a presença de uma distribuição do tipo
-% "inverse power-law", mas na hora de calcular o bremsstrahlung se usa uma
-% Maxwelliana. Sugiro uma frase mais ambígua, que não entra em detalhes, mas
-% não diz que o bremsstrahlung foi calculado com a "Kappa". Por exemplo,
-% "presents a discussion about the asymptotic equilibrium state of the
-% Langmuir waves spectrum, considering a combination of a inverse power-law 
-% kappa distribution and a Maxwellian distribution, in the presence and in the
-% absence of the electrostatic bremsstrahlung."
-% Sabrina: OK
-The discussion in \Cref{appB} is
-related with the article appended in \Cref{appC}, which is a
-parallel research and is only slightly related with the main
-subject of this work, that is the study of the combined action
-of collective and collisional processes in weakly turbulent
-plasmas, in the presence of electrostatic oscillations.
+The discussion in \Cref{appB} is related with the article appended
+in \Cref{appC}, which is a parallel research and is only slightly
+related with the main subject of this work, that is the study of the
+combined action of collective and collisional processes in weakly
+turbulent plasmas, in the presence of electrostatic oscillations.
 
@@
     {\bf \nabla \times E}&=& -\frac{1}{c}
-   \frac{\partial \bf B}{\partial t}\\
+   \frac{\partial {\bf B}}{\partial t}\\
   \label{max4}

### 2019-05-16 thesis.tex
Still editing the introduction

@@
 %
-In the context of physics, the word ``plasma'' is used to designate a gas whose
-degree of ionization is such that the forces of electric and magnetic nature of
-the charged particles overcome the influence of the collisions between neutral
-particles, in the overall dynamics of the gas. Besides that, the
+% In the context of physics, the word ``plasma'' is used to designate a gas whose
+% degree of ionization is such that the interactions involving forces of electric
+% and magnetic nature of the charged particles, overcome the influence of the
+% collisions between neutral particles, in the overall dynamics of the gas.
+%
+In the context of physics, the word "plasma" designates a gas whose degree of
+ionization is such that the interactions involving forces of electric and magnetic
+nature, of the charged particles, overcome the influence of the binary collisions
+between neutral particles on the overall dynamics of the gas. The charged particles
+might also interact with the neutral components of the gas
 

### 2019-05-16 thesis.tex
* thesis.tex: Summary: Still editing the introduction

@@
 ionization is such that the interactions involving forces of electric and magnetic
-nature, of the charged particles, overcome the influence of the binary collisions
-between neutral particles on the overall dynamics of the gas. The charged particles
-might also interact with the neutral components of the gas
+nature, of the charged particles, overcome the influence of the neutral-neutral
+and neutral-charged binary collisions, on the overall dynamics of the gas. As a
+consequence of the long-range feature of the electric and magnetic fields, one
+charged particle may interact with several other particles, that interface with
+other charges, and so on; characterizing the so-called ``collective behavior''.
+Such behavior gives rise to a variety of plasma waves and instabilities, whose
+intensities will depend on another essential collective property of the plasma:
+the Debye shielding. The Debye shielding is defined as the resulting net charge
+inside a given volume element of the plasma. When the number of negative and
+positive particles are the same, the plasma waves and instabilities arise from
+the small fluctuations driven by the constant movement and interactions among the
+charges. These small fluctuations on the Debye shielding establish a fundamental
+characteristic of neutral plasmas, the ``quasineutrality''. On the other hand,
+plasmas that do not have overall charge neutrality might also have some degree
+of Debye shielding. In such case, however, the electric and magnetic fields are
+more intense and have a longer range due to the absence of quasineutrality.
+These characteristics make nonneutral plasmas a whole new subject, with distinct
+properties regarding its behavior and stability.
 

### 2019-05-17 thesis.tex
Rewriting the definition of plasma
Writing a more understandable version of the definition of plasma.

--- 2019-05-16 thesis.tex
@@
 %\usepackage[portuguese,brazil,brazilian]{babel}
-%\usepackage[utf8]{inputenc} %comentar para luatex
-\usepackage[utf8]{luainputenc} %comentar para pdftex
+%\usepackage[utf8]{inputenc} %comment when using luatex
+\usepackage[utf8]{luainputenc} %comment when using pdftex
 \usepackage{lmodern}
@@
 %
-In the context of physics, the word "plasma" designates a gas whose degree of
-ionization is such that the interactions involving forces of electric and magnetic
-nature, of the charged particles, overcome the influence of the binary collisions
-between neutral particles on the overall dynamics of the gas. The charged particles
-might also interact with the neutral components of the gas
+% In the context of physics, the word "plasma" designates a gas whose degree of
+% ionization is such that the interactions involving forces of electric and magnetic
+% nature, of the charged particles, overcome the influence of the neutral-neutral
+% and neutral-charged binary collisions, on the overall dynamics of the gas. As a
+% consequence of the long-range feature of the electric and magnetic fields, one
+% charged particle may interact with several other particles, that interface with
+% other charges, and so on; characterizing the so-called ``collective behavior''.
+% Such behavior gives rise to a variety of plasma waves and instabilities, whose
+% intensities will depend on another essential collective property of the plasma:
+% the Debye shielding. The Debye shielding is defined as the resulting net charge
+% inside a given volume element of the plasma. When the number of negative and
+% positive particles are the same, the plasma waves and instabilities arise from
+% the small fluctuations driven by the constant movement and interactions among the
+% charges. These small fluctuations on the Debye shielding establish a fundamental
+% characteristic of neutral plasmas, the ``quasineutrality''. On the other hand,
+% plasmas that do not have overall charge neutrality might also have some degree
+% of Debye shielding. In such case, however, the electric and magnetic fields are
+% more intense and have a longer range due to the absence of quasineutrality.
+% These characteristics make nonneutral plasmas a whole new subject, with distinct
+% properties regarding its behavior and stability.
 

### 2019-05-19 thesis.tex
minor modifications

@@
 
+A plasma is an ionized gas in which the charged particle population is sufficiently
+large so the forces of electric and magnetic nature, generated by the charges and
+their movement, overcome the influence of the collisions between neutral particles,
+that dominate the kinetics of neutral gases, on the overall dynamics of the system.
+
 When it comes to the plasma kinetic theory, processes involving waves
@@
 and explore its applications in the solar physics scope. In
-\Cref{cha:kin-theo} and \Cref{cha:weak-turb}, we make a brief review
+\Cref{cha:theo-fram} and \Cref{cha:weak-turb}, we make a brief review
 of the basic plasma kinetic theory equations and the weak turbulence
@@
 
-\chapter{Kinetic theory}
-\label{cha:kin-theo}
+\chapter{Theoretical framework}
+\label{cha:theo-fram}
+
+\section{Kinetic theory}
+\label{sec:kin-theo}
 The kinetic theory is the most fundamental description of the

### 2019-05-21 thesis.tex
plasma definition
Not ready yet.

@@
 % properties regarding its behavior and stability.
-
-A plasma is an ionized gas in which the charged particle population is sufficiently
-large so the forces of electric and magnetic nature, generated by the charges and
-their movement, overcome the influence of the collisions between neutral particles,
-that dominate the kinetics of neutral gases, on the overall dynamics of the system.
-
-When it comes to the plasma kinetic theory, processes involving waves
+%
+% A plasma is an ionized gas in which the charged particle population is sufficiently
+% large so the forces of electric and magnetic nature, generated by the charges and
+% their movement, overcome the influence of the collisions between neutral particles,
+% that dominate the kinetics of neutral gases, on the overall dynamics of the system.
+%
+Plasma physics is the area
+
+In the context of plasma kinetic theory, processes involving waves
 and kinetic instabilities, the so-called \emph{collective processes},
@@
 \label{cha:theo-fram}
+Let us consider a given set of atoms or molecules, which is composed of
+positively and negatively charged particles, and also neutral components.
+One can say, correctly, that such a system is an ionized gas, because of
+the presence of charged particles in its composition. However, what can
+be said about the dominant dynamics of the ionized gas, since neutral and
+charged particles have quite a distinct behavior? Assuming the gravitational
+force is negligible, the neutral particles will move freely in the medium
+until one collides with another \cite{chen}. Thus, the interaction between
+the neutral components is characterized as short-ranged, since it relies
+only on binary collisions.
 

### 2019-05-22 thesis.tex
Minor additions

@@
 be said about the dominant dynamics of the ionized gas, since neutral and
-charged particles have quite a distinct behavior? Assuming the gravitational
-force is negligible, the neutral particles will move freely in the medium
-until one collides with another \cite{chen}. Thus, the interaction between
-the neutral components is characterized as short-ranged, since it relies
-only on binary collisions.
+charged particles have quite a distinct behavior? Assuming that the
+gravitational force is negligible, the neutral particles will move freely
+in the medium until one collides with another \cite{klimon}. Therefore, the
+interaction between the neutral components is characterized as short-ranged,
+since it relies only on collisions between two particles. Charged particles,
+on the other hand, are sources of electric fields. Besides that, their
+motion generates currents that will induce magnetic fields. The
 

### 2019-05-25 draft.tex
added some text I won't use, but would like to keep
Added some text I won't use, but would like to keep. The text is after \end{document}.

@@
 \end{document}
+
+% In the context of physics, the word ``plasma'' is used to designate a gas whose degree
+% of ionization is such that the interaction between its components is dominated by the electric
+% and magnetic forces generated by the presence and movement of the negatively and positively
+% charged particles.
+%
+% In the context of physics, the word ``plasma'' is used to designate a gas whose
+% degree of ionization is such that its dynamics is dominated by the forces of
+% electric and magnetic nature of the charged particles, overcoming the influence
+% of the collisions between neutral particles.
+%
+% In the context of physics, the word ``plasma'' is used to designate a gas whose
+% degree of ionization is such that the interactions involving forces of electric
+% and magnetic nature of the charged particles, overcome the influence of the
+% collisions between neutral particles, in the overall dynamics of the gas.
+%
+% In the context of physics, the word "plasma" designates a gas whose degree of
+% ionization is such that the interactions involving forces of electric and magnetic
+% nature, of the charged particles, overcome the influence of the neutral-neutral
+% and neutral-charged binary collisions, on the overall dynamics of the gas. As a
+% consequence of the long-range feature of the electric and magnetic fields, one
+% charged particle may interact with several other particles, that interface with
+% other charges, and so on; characterizing the so-called ``collective behavior''.
+% Such behavior gives rise to a variety of plasma waves and instabilities, whose
+% intensities will depend on another essential collective property of the plasma:
+% the Debye shielding. The Debye shielding is defined as the resulting net charge
+% inside a given volume element of the plasma. When the number of negative and
+% positive particles are the same, the plasma waves and instabilities arise from
+% the small fluctuations driven by the constant movement and interactions among the
+% charges. These small fluctuations on the Debye shielding establish a fundamental
+% characteristic of neutral plasmas, the ``quasineutrality''. On the other hand,
+% plasmas that do not have overall charge neutrality might also have some degree
+% of Debye shielding. In such case, however, the electric and magnetic fields are
+% more intense and have a longer range due to the absence of quasineutrality.
+% These characteristics make nonneutral plasmas a whole new subject, with distinct
+% properties regarding its behavior and stability.
+%
+% A plasma is an ionized gas in which the charged particle population is sufficiently
+% large so the forces of electric and magnetic nature, generated by the charges and
+% their movement, overcome the influence of the collisions between neutral particles,
+% that dominate the kinetics of neutral gases, on the overall dynamics of the system.
+%
+
+Let us consider a given set of atoms or molecules, which is composed of
+positively and negatively charged particles, and also neutral components.
+One can say, correctly, that such a system is an ionized gas, because of
+the presence of charged particles in its composition. However, what can
+be said about the dominant dynamics of the ionized gas, since neutral and
+charged particles have quite a distinct behavior? The neutral particles,
+assuming that the gravitational force is negligible, will move freely
+in the medium until one collides with another \cite{klimon}. Therefore,
+the interaction between the neutral components is characterized as
+short-ranged, since it relies only on collisions between two particles.
+Charged particles, on the other hand, are sources of electric fields.
+Besides that, their motion generates currents that will induce magnetic
+fields. The charged particles dynamics is dominated by the presence
+of these fields that can act at distance, interacting and  the
+fields of several particles at the same time.

### 2019-05-26 thesis.tex
New section
Started writing the section about astrophysical plasmas

--- 2019-05-21 thesis.tex
@@
 \label{cha:intro}
-% In the context of physics, the word ``plasma'' is used to designate a gas whose degree
-% of ionization is such that the interaction between its components is dominated by the electric
-% and magnetic forces generated by the presence and movement of the negatively and positively
-% charged particles.
-%
-% In the context of physics, the word ``plasma'' is used to designate a gas whose
-% degree of ionization is such that its dynamics is dominated by the forces of
-% electric and magnetic nature of the charged particles, overcoming the influence
-% of the collisions between neutral particles.
-%
-% In the context of physics, the word ``plasma'' is used to designate a gas whose
-% degree of ionization is such that the interactions involving forces of electric
-% and magnetic nature of the charged particles, overcome the influence of the
-% collisions between neutral particles, in the overall dynamics of the gas.
-%
-% In the context of physics, the word "plasma" designates a gas whose degree of
-% ionization is such that the interactions involving forces of electric and magnetic
-% nature, of the charged particles, overcome the influence of the neutral-neutral
-% and neutral-charged binary collisions, on the overall dynamics of the gas. As a
-% consequence of the long-range feature of the electric and magnetic fields, one
-% charged particle may interact with several other particles, that interface with
-% other charges, and so on; characterizing the so-called ``collective behavior''.
-% Such behavior gives rise to a variety of plasma waves and instabilities, whose
-% intensities will depend on another essential collective property of the plasma:
-% the Debye shielding. The Debye shielding is defined as the resulting net charge
-% inside a given volume element of the plasma. When the number of negative and
-% positive particles are the same, the plasma waves and instabilities arise from
-% the small fluctuations driven by the constant movement and interactions among the
-% charges. These small fluctuations on the Debye shielding establish a fundamental
-% characteristic of neutral plasmas, the ``quasineutrality''. On the other hand,
-% plasmas that do not have overall charge neutrality might also have some degree
-% of Debye shielding. In such case, however, the electric and magnetic fields are
-% more intense and have a longer range due to the absence of quasineutrality.
-% These characteristics make nonneutral plasmas a whole new subject, with distinct
-% properties regarding its behavior and stability.
-%
-% A plasma is an ionized gas in which the charged particle population is sufficiently
-% large so the forces of electric and magnetic nature, generated by the charges and
-% their movement, overcome the influence of the collisions between neutral particles,
-% that dominate the kinetics of neutral gases, on the overall dynamics of the system.
-%
-Plasma physics is the area
 
@@
 
+\section{Astrophysical plasmas}
+\label{sec:astro-plasmas}
+The plasma physics branch of Physics is broad. From life-changing
+industrial applications like the plasma processing of integrated
+circuits - an essential step of the manufacturing process of tiny
+integrated circuits -, passing through the development of the
+telecommunications via radio-frequency, to day-to-day devices
+like fluorescent lamps \cite{bell,gurnett2017,chen}. Another
+important application of plasmas on Earth
+
 Considering the context presented above, the working proposal of
@@
 \label{cha:theo-fram}
-Let us consider a given set of atoms or molecules, which is composed of
-positively and negatively charged particles, and also neutral components.
-One can say, correctly, that such a system is an ionized gas, because of
-the presence of charged particles in its composition. However, what can
-be said about the dominant dynamics of the ionized gas, since neutral and
-charged particles have quite a distinct behavior? Assuming the gravitational
-force is negligible, the neutral particles will move freely in the medium
-until one collides with another \cite{chen}. Thus, the interaction between
-the neutral components is characterized as short-ranged, since it relies
-only on binary collisions.
 

### 2019-05-27 thesis.tex
Did some writing
Astrophysical plasmas and definition of plasma (again).

@@
 \label{sec:astro-plasmas}
-The plasma physics branch of Physics is broad. From life-changing
-industrial applications like the plasma processing of integrated
-circuits - an essential step of the manufacturing process of tiny
-integrated circuits -, passing through the development of the
-telecommunications via radio-frequency, to day-to-day devices
-like fluorescent lamps \cite{bell,gurnett2017,chen}. Another
-important application of plasmas on Earth
+The first fact that a plasma physics student learns, before even
+understanding the definition of plasma, is that most of the baryonic
+matter in the universe is in the plasma state. This \emph{most} is
+usually estimated to be around $99\%$ \cite{bitt,gurnett2017}. If this
+high estimate has something to do with the fact that our probes and
+telescopes can only directly detect ionized matter, because it emits
+radiation, \cite{chen} it is still a case to be studied.
+
+In order to understand what is a plasma, one must have to be aware of
+the differences between the dynamics of neutral and fully ionized gases.
+In a neutral gas, assuming that the influence of gravity can be neglected,
+the dynamics is dictated by collisions between two components that are
+very close to each other. A fully ionized gas, on the other hand, is only
+composed of charged particles, that are sources of electric fields. Besides
+that, the motion of charged particles generates electric currents, that
+will induce magnetic fields. This means that one charge can interact with
+several other charges at a considerable distance, through these fields.
+Therefore, a partially ionized gas is considered a plasma when its dynamics
+is dominated by the electric and magnetic forces of the charged particles,
+consequently, a fully ionized gas is also a plasma.
+
+Astrophysical plasmas are observed in a myriad of configurations,
+regarding composition, density, temperature, and degree of ionization.
 

### 2019-06-04 thesis.tex
Added section about collective processes

--- 2019-05-26 thesis.tex
@@
 
-\section{Astrophysical plasmas}
-\label{sec:astro-plasmas}
-The plasma physics branch of Physics is broad. From life-changing
-industrial applications like the plasma processing of integrated
-circuits - an essential step of the manufacturing process of tiny
-integrated circuits -, passing through the development of the
-telecommunications via radio-frequency, to day-to-day devices
-like fluorescent lamps \cite{bell,gurnett2017,chen}. Another
-important application of plasmas on Earth
-
 Considering the context presented above, the working proposal of
@@
 
-\chapter{Theoretical framework}
-\label{cha:theo-fram}
+\section{Collective and collisional processes in plasmas}
+\label{sec:collec-coll-proc}
+In order to understand what collective processes are, one has to
+have in mind that a plasma is a many-body system composed mostly
+- or completely - of charged particles, that interact with each
+other through electromagnetic forces. Due to the long range nature
+of the electromagnetic forces, one charge can interact with several
+charges at the same time, that will interact with others, and so
+on. In such arrangement, the particle motion, at a certain volume
+element of the plasma, will be affected not only by the surrounding
+environment, but it will also be influenced by the conditions at
+distant regions of the system. This nonlocal feature of the plasma
+dynamics is called \emph{collective behavior} \cite{chen}.
+
+Collective behavior is a necessary condition for an ionized to be
+considered a plasma. As a fundamental characteristic, it occurs in
+plasmas that exhibit overall neutrality, the so-called neutral
+plasmas, and also in nonneutral plasmas.
 

### 2019-06-04 thesis.tex
Added one more paragraph to the section
* thesis.tex: Summary: Added section about collective processes

@@
 
-Collective behavior is a necessary condition for an ionized to be
-considered a plasma. As a fundamental characteristic, it occurs in
-plasmas that exhibit overall neutrality, the so-called neutral
-plasmas, and also in nonneutral plasmas.
+Collective processes are the outcome of collective behavior, i.e.,
+are processes that occur as a response of the collective behavior
+of the plasma. Such phenomena exists in both neutral (same number of
+negative and positive components), and nonneutral (different quantities
+of negative and positive charges, or have only one charge species)
+plasmas. The dynamics in both cases, however, is dramatically different.
+In this work we are interested only in the first case and, once we
 

### 2019-06-04 thesis.tex
changes...

--- 2019-06-04 thesis.tex
@@
 
-Considering the context presented above, the working proposal of
-this PhD Thesis is to put forward the first numerical analysis of
-the new weak turbulence theory for collisional plasmas \cite{YZKS16}
-and explore its applications in the solar physics scope. In
-\Cref{cha:theo-fram} and \Cref{cha:weak-turb}, we make a brief review
-of the basic plasma kinetic theory equations and the weak turbulence
-theory, respectively. In \Cref{noneigenmode}, we introduce the
-new generalization of the weak turbulence theory, which takes into
-account the contribution of noneigenmode fluctuations during the
-derivation of the particle and wave kinetic equations, resulting
-in three new terms. In \Cref{main}, we contextualize the present
-work regarding the theory discussed in the previous chapter and
-present the results obtained so far by appending the two papers
-published in this subject. In \Cref{cha:final}, we summarize the
-results and discuss the perspectives of the present research. Then,
-we propose a schedule for the remaining period until the thesis
-defense. In the end we have three appendices. \Cref{appA} shows
-an improved approximation for the second order susceptibility of
-the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
-presents a discussion about the asymptotic equilibrium state of the
-Langmuir waves spectrum, considering a combination of a inverse
-power-law kappa distribution and a Maxwellian distribution, in the
-presence and in the absence of the electrostatic bremsstrahlung.
-The discussion in \Cref{appB} is related with the article appended
-in \Cref{appC}, which is a parallel research and is only slightly
-related with the main subject of this work, that is the study of the
-combined action of collective and collisional processes in weakly
-turbulent plasmas, in the presence of electrostatic oscillations.
-
-\section{Collective and collisional processes in plasmas}
-\label{sec:collec-coll-proc}
-In order to understand what collective processes are, one has to
-have in mind that a plasma is a many-body system composed mostly
-- or completely - of charged particles, that interact with each
-other through electromagnetic forces. Due to the long range nature
-of the electromagnetic forces, one charge can interact with several
-charges at the same time, that will interact with others, and so
-on. In such arrangement, the particle motion, at a certain volume
-element of the plasma, will be affected not only by the surrounding
-environment, but it will also be influenced by the conditions at
-distant regions of the system. This nonlocal feature of the plasma
-dynamics is called \emph{collective behavior} \cite{chen}.
-
-Collective behavior is a necessary condition for an ionized to be
-considered a plasma. As a fundamental characteristic, it occurs in
-plasmas that exhibit overall neutrality, the so-called neutral
-plasmas, and also in nonneutral plasmas.
-
-\section{Kinetic theory}
+% Considering the context presented above, the working proposal of
+% this PhD Thesis is to put forward the first numerical analysis of
+% the new weak turbulence theory for collisional plasmas \cite{YZKS16}
+% and explore its applications in the solar physics scope. In
+% \Cref{cha:theo-fram} and \Cref{cha:weak-turb}, we make a brief review
+% of the basic plasma kinetic theory equations and the weak turbulence
+% theory, respectively. In \Cref{noneigenmode}, we introduce the
+% new generalization of the weak turbulence theory, which takes into
+% account the contribution of noneigenmode fluctuations during the
+% derivation of the particle and wave kinetic equations, resulting
+% in three new terms. In \Cref{main}, we contextualize the present
+% work regarding the theory discussed in the previous chapter and
+% present the results obtained so far by appending the two papers
+% published in this subject. In \Cref{cha:final}, we summarize the
+% results and discuss the perspectives of the present research. Then,
+% we propose a schedule for the remaining period until the thesis
+% defense. In the end we have three appendices. \Cref{appA} shows
+% an improved approximation for the second order susceptibility of
+% the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
+% presents a discussion about the asymptotic equilibrium state of the
+% Langmuir waves spectrum, considering a combination of a inverse
+% power-law kappa distribution and a Maxwellian distribution, in the
+% presence and in the absence of the electrostatic bremsstrahlung.
+% The discussion in \Cref{appB} is related with the article appended
+% in \Cref{appC}, which is a parallel research and is only slightly
+% related with the main subject of this work, that is the study of the
+% combined action of collective and collisional processes in weakly
+% turbulent plasmas, in the presence of electrostatic oscillations.
+
+\section{Astrophysical plasmas}
+\label{sec:astro-plasma}
+At a first glance, the study of plasmas seems completely unrelated
+with
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.5\textwidth]{corona2017.png}
+%    \includegraphics[0.4\textwidth]{}
+    \caption{Solar corona captured during the total solar eclipse of 2017. Credit:
+      \href{https://hdr-astrophotography.com/a-propos/}{Nicolas Lefaudeux}.}
+    \label{fig1}
+  \end{center}
+\end{figure}
+
+% In order to understand what collective processes are, one has to
+% have in mind that a plasma is a many-body system composed mostly
+% - or completely - of charged particles, that interact with each
+% other through electromagnetic forces. Due to the long range nature
+% of the electromagnetic forces, one charge can interact with several
+% charges at the same time, that will interact with others, and so
+% on. In such arrangement, the particle motion, at a certain volume
+% element of the plasma, will be affected not only by the surrounding
+% environment, but it will also be influenced by the conditions at
+% distant regions of the system. This nonlocal characteristic  of the plasma
+% dynamics is called \emph{collective behavior} \cite{chen}.
+
+\chapter{Kinetic theory}
 \label{sec:kin-theo}

### 2019-06-17 thesis.tex
edited astophysical plasmas

@@
 \label{sec:astro-plasma}
-At a first glance, the study of plasmas seems completely unrelated
-with
+On Earth, the plasma is considered an exotic state of matter, associated to the
+glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
+laboratories, and the promise of cleaner and technically infinite energy source
+when scientists and engineers manage to succeed at obtaining a controlled, and
+energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
+everyday life are rare, restricted to the occurrence of lightning during storms
+and beautiful auroras that are spotted at high latitudes. In the interplanetary
+and interstellar space, however, the situation is the opposite. Starting in the
+outer layers of Earth's atmosphere, passing through the solar wind in the
+interplanetary space, to the stellar interiors and atmospheres, accretion disks,
+and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
+the observable matter is in the plasma state \cite{may}.
+
+% Astrophysics is a millennial observational science, that started with bare eyes
+% observation of the sky, describing the constellations, and solar, lunar and
+% planetary cycles. These first observations of the relative motion of planetary
+% bodies led to solar clocks, calendars, and navigation charts. Nowadays, we have
+% extremely sophisticated equipment of observation, both on Earth and in space,
+% that can reach
 
@@
   \begin{center}
-    \includegraphics[width=0.5\textwidth]{corona2017.png}
-%    \includegraphics[0.4\textwidth]{}
-    \caption{Solar corona captured during the total solar eclipse of 2017. Credit:
-      \href{https://hdr-astrophotography.com/a-propos/}{Nicolas Lefaudeux}.}
+    \includegraphics[width=0.48\textwidth]{corona2017.png}
+    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
+    \caption{Solar corona captured during the total solar eclipse of 2017.
+      {\footnotesize Credit:}
+      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
+      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
     \label{fig1}
@@
 
-\subsection{Low amplitude electrostatic oscillations}
+\section{Low amplitude electrostatic oscillations}
 We are interested in the presence of high-frequency electrostatic
@@
 bremsstrahlung and collisional damping.
-% \begin{figure}[h]
-%   \begin{center}
-%     %% \hspace{-0.42cm}
-%     \includegraphics[scale=0.5,angle=270]{IL1D_005kvar.eps}
-%     \includegraphics[scale=0.5,angle=270]{IL1D_005kvarno-brem.eps}
-%     \caption{Asymptotic spectrum of Langmuir waves for several values
-%       of $\kappa$ index and Maxwellian distribution. (a) With electrostatic
-%     bremsstrahlung emission and collisional damping.
-%    (b) Without bremsstrahlung emission and collisional damping.}
-%     \label{fig5}
-%   \end{center}
-% \end{figure}
+\begin{figure}[h]
+  \begin{center}
+    %% \hspace{-0.42cm}
+    \includegraphics[scale=0.5,angle=270]{IL1D_005kvar.eps}
+    \includegraphics[scale=0.5,angle=270]{IL1D_005kvarno-brem.eps}
+    \caption{Asymptotic spectrum of Langmuir waves for several values
+      of $\kappa$ index and Maxwellian distribution. (a) With electrostatic
+    bremsstrahlung emission and collisional damping.
+   (b) Without bremsstrahlung emission and collisional damping.}
+    \label{fig5}
+  \end{center}
+\end{figure}
 

### 2019-06-28 thesis.tex
New version of section 1

@@
 
-\section{Astrophysical plasmas}
+\section{Kinetic processes in astrophysical plasmas}
 \label{sec:astro-plasma}
-On Earth, the plasma is considered an exotic state of matter, associated to the
-glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
-laboratories, and the promise of cleaner and technically infinite energy source
-when scientists and engineers manage to succeed at obtaining a controlled, and
-energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
-everyday life are rare, restricted to the occurrence of lightning during storms
-and beautiful auroras that are spotted at high latitudes. In the interplanetary
-and interstellar space, however, the situation is the opposite. Starting in the
-outer layers of Earth's atmosphere, passing through the solar wind in the
-interplanetary space, to the stellar interiors and atmospheres, accretion disks,
-and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
-the observable matter is in the plasma state \cite{may}.
-
-% Astrophysics is a millennial observational science, that started with bare eyes
-% observation of the sky, describing the constellations, and solar, lunar and
-% planetary cycles. These first observations of the relative motion of planetary
-% bodies led to solar clocks, calendars, and navigation charts. Nowadays, we have
-% extremely sophisticated equipment of observation, both on Earth and in space,
-% that can reach
+The plasma, as a collection of ions and electrons, has its dynamics
+dominated by the electric and magnetic fields generated by the presence
+of charged particles, and electric currents that arise from their
+movement. Due to the long-range nature of these self-generated fields,
+one particle affects the movement of several other particles, which
+will interact with other particles, and so on. This \emph{collective
+  behavior}\footnote{A more detailed description on all the processes
+  and conditions that characterize the collective behavior in neutral
+  plasmas can be seen in Refs. \cite{bitt,gurnett2017,chen}. For
+  nonneutral plasmas, see Ref. \cite{DavidsonNonNeutral}.} is what
+characterizes an ionized gas as a plasma, and also is the reason behind
+the complexity of the plasma dynamics.
 

### 2019-06-29 thesis.tex
changes

@@
 
-\section{Kinetic processes in astrophysical plasmas}
-\label{sec:astro-plasma}
-The plasma, as a collection of ions and electrons, has its dynamics
-dominated by the electric and magnetic fields generated by the presence
-of charged particles, and electric currents that arise from their
-movement. Due to the long-range nature of these self-generated fields,
-one particle affects the movement of several other particles, which
-will interact with other particles, and so on. This \emph{collective
-  behavior}\footnote{A more detailed description on all the processes
-  and conditions that characterize the collective behavior in neutral
-  plasmas can be seen in Refs. \cite{bitt,gurnett2017,chen}. For
-  nonneutral plasmas, see Ref. \cite{DavidsonNonNeutral}.} is what
-characterizes an ionized gas as a plasma, and also is the reason behind
-the complexity of the plasma dynamics.
-
-\begin{figure}[h]
-  \begin{center}
-    \includegraphics[width=0.48\textwidth]{corona2017.png}
-    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
-    \caption{Solar corona captured during the total solar eclipse of 2017.
-      {\footnotesize Credit:}
-      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
-      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
-    \label{fig1}
-  \end{center}
-\end{figure}
-
-% In order to understand what collective processes are, one has to
-% have in mind that a plasma is a many-body system composed mostly
-% - or completely - of charged particles, that interact with each
-% other through electromagnetic forces. Due to the long range nature
-% of the electromagnetic forces, one charge can interact with several
-% charges at the same time, that will interact with others, and so
-% on. In such arrangement, the particle motion, at a certain volume
-% element of the plasma, will be affected not only by the surrounding
-% environment, but it will also be influenced by the conditions at
-% distant regions of the system. This nonlocal characteristic  of the plasma
-% dynamics is called \emph{collective behavior} \cite{chen}.
-
-\chapter{Kinetic theory}
+\chapter{Kinetic theory and astrophysical plasmas}
 \label{sec:kin-theo}
+
+The plasma is a collection of ions, electrons and neutral particles that has
+its dynamics dominated by the electric and magnetic fields, generated by the
+electrically charged particles and the electric currents related to their
+motion, respectively. Due to the long-range nature of these self-generated
+fields, one particle affects the movement of several other particles, which
+will interact with other particles, and so on. This \emph{collective behavior}
+\footnote{A detailed description of all the processes and conditions that
+  characterize the collective behavior in plasmas, can be accessed in the
+  following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
+is what characterizes an ionized gas as a plasma, and is also the reason
+behind the complexity of the plasma dynamics. This complexity comes in the
+form of a myriad of self-consistent oscillatory processes, where the electric
+and magnetic fields affect - and are affected by - the position and motion of
+the charges, and how they vary in time \cite{chen}.
+
+Describing such complicated dynamics it is not an easy task.
+
 The kinetic theory is the most fundamental description of the
@@
 \cite{klimo}.
+
+\section{Kinetic processes in astrophysical plasmas}
+\label{sec:astro-plasma}
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{corona2017.png}
+    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
+    \caption{Solar corona captured during the total solar eclipse of 2017.
+      {\footnotesize Credit:}
+      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
+      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
+    \label{fig1}
+  \end{center}
+\end{figure}
 

### 2019-06-30 thesis.tex
more text

@@
 
-Describing such complicated dynamics it is not an easy task.
+A complete description of such a complicated dynamics would depend on determining
+the position and momentum of each particle, and their respective microscopic
+electric and magnetic fields, in a time instant. This strategy is not practical
+and in most of the cases not feasible for many-body systems, like the plasma.  
+However, this microscopic description can be dealt through a hierarchy of
+approximations, leading to the three main theories of plasma physics: kinetic,
+multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
+formulations will depend on the phenomenon that needs to be described,
 

### 2019-06-30 draft.tex
more dummy text

@@
 fields of several particles at the same time.
+
+The plasma physics branch of Physics is broad. From life-changing
+industrial applications like the plasma processing of integrated
+circuits - an essential step of the manufacturing process of the
+tiny integrated circuits -, passing through the development of the
+telecommunications via radio-frequency, to day-to-day devices
+like fluorescent lamps \cite{bell,gurnett2017,chen}. Another
+important application of plasmas on Earth
+
+% The first fact that a plasma physics student learns, before even
+% understanding the definition of plasma, is that most of the baryonic
+% matter in the universe is in the plasma state. This \emph{most} is
+% usually estimated to be around $99\%$ \cite{bitt,gurnett2017}. If this
+% high estimate has something to do with the fact that our probes and
+% telescopes can only directly detect ionized matter, because it emits
+% radiation, \cite{chen} it is still a case to be studied.
+
+% In order to understand what is a plasma, one must have to be aware of
+% the differences between the dynamics of neutral and fully ionized gases.
+% In a neutral gas, assuming that the influence of gravity can be neglected,
+% the dynamics is dictated by collisions between two components that are
+% very close to each other \cite{klimon}. A fully ionized gas, on the other
+% hand, is only composed of charged particles, which are sources of electric
+% fields. Besides that, the motion of charged particles generates electric
+% currents, that will induce magnetic fields. In such arrangement, one charge
+% can interact with several other charges at a considerable distance trough
+% the action of the self-generated electric and magnetic fields. Therefore, a
+% partially ionized gas is considered a plasma when its degree of ionization
+% is such that its dynamics is dominated by the electric and magnetic forces
+% of the charged particles. Under such definition, a fully ionized gas is, of
+% course, also considered a plasma.
+
+% Plasmas can be classified according with their overall neutrality as
+% \emph{neutral} when the density of electrons and ions are the same, and
+% \emph{non-neutral} when the densities of the negatively and positively
+% charged particles are different, which includes the case of one component
+% plasma.
+
+% In the beginning of this chapter it was mentioned a fundamental
+% characteristic of a plasma: the \emph{collective processes}.
+% Indeed, an ionized gas cannot be called a plasma if its dynamics
+% is not predominantly collective.
+
+% In order to define collective processes, one should have in mind that
+% a plasma is a gas that has most of its components in an ionized state.
+% For instance, let us consider a hydrogen gas that was heated to the
+% point where the electrons were separated from their respective ions.
+% What we have now is gas that is composed of charged particles that
+% are source of electric fields. Also, the motion of the electrons
+% generates electric currents that induce magnetic fields.
+
+On Earth, the plasma is considered an exotic state of matter, associated to the
+glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
+laboratories, and the promise of cleaner and technically infinite energy source
+when scientists and engineers manage to succeed at obtaining a controlled, and
+energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
+everyday life are rare, restricted to the occurrence of lightning during storms
+and beautiful auroras that are spotted at high latitudes. In the interplanetary
+and interstellar space, however, the situation is the opposite. Starting in the
+outer layers of Earth's atmosphere, passing through the solar wind in the
+interplanetary space, to the stellar interiors and atmospheres, accretion disks,
+and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
+the observable matter is in the plasma state \cite{may}.
+
+What defines the plasma state in an ionized gas, is the presence of collective
+behavior, which is a consequence of the long-range action of the electric and
+magnetic forces that are generated by the charged particles and their movement.
+There are other important properties, like Debye shielding and quasineutrality,
+that are well described in introductory books \cite{chen,bitt,gurnett2017} and
+will not be addressed here. Beyond these fundamental properties, plasmas can
+be found in an immense variety of configurations, and this is notably true for
+the plasma in space.

### 2019-07-07 thesis.tex
Version before serious modification in subsection 4.1.3
Version before adding a more deep explanation on the contribution of the noneigenmode term to the wave kinetic equation.

@@
 of the non-collective fluctuations emitted by thermal particles. The
-outcome is a complete first principles nonlinear description of the
-propagation of electrostatic oscillations in the presence of both wave
-and particle collisional dissipation, and a hitherto unknown process.
-This new effect depicts the emission of electrostatic radiation in the
-eigenmode frequency range, which is caused by particle scattering. 
-Since this is a form of braking radiation, the authors named it as
-\emph{electrostatic bremsstrahlung}.
+outcome is a complete nonlinear description, from first principles, of
+the propagation of electrostatic oscillations in the presence of both
+wave and particle collisional dissipation and a new equation describing
+a hitherto unknown process. This new effect depicts the emission of
+electrostatic radiation, in the eigenmode frequency range, caused by
+particle scattering. Since this is a form of braking radiation, the
+authors named it as \emph{electrostatic bremsstrahlung}.
 
@@
 will interact with other particles, and so on. This \emph{collective behavior}
-\footnote{A detailed description of all the processes and conditions that
+\footnote{A detailed exposition of all the processes and conditions that
   characterize the collective behavior in plasmas, can be accessed in the
@@
 the position and momentum of each particle, and their respective microscopic
-electric and magnetic fields, in a time instant. This strategy is not practical
-and in most of the cases not feasible for many-body systems, like the plasma.  
-However, this microscopic description can be dealt through a hierarchy of
+electric and magnetic fields, in a given instant in time. This strategy is not
+practical and in most of the cases not feasible for many-body systems, like the
+plasma. However, this microscopic description can be dealt through a hierarchy of
 approximations, leading to the three main theories of plasma physics: kinetic,
 multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
-formulations will depend on the phenomenon that needs to be described,
+formulations will depend on the phenomenon that needs to be described.
+
+\section{Kinetic processes in astrophysical plasmas}
+\label{sec:astro-plasma}
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{corona2017.png}
+    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
+    \caption{Solar corona captured during the total solar eclipse of 2017.
+      {\footnotesize Credit:}
+      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
+      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
+    \label{fig1}
+  \end{center}
+\end{figure}
 
@@
 
-\section{Kinetic processes in astrophysical plasmas}
-\label{sec:astro-plasma}
-
-\begin{figure}[h]
-  \begin{center}
-    \includegraphics[width=0.48\textwidth]{corona2017.png}
-    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
-    \caption{Solar corona captured during the total solar eclipse of 2017.
-      {\footnotesize Credit:}
-      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
-      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
-    \label{fig1}
-  \end{center}
-\end{figure}
-
 \section{Low amplitude electrostatic oscillations}
@@
 where the zero-order electric field is assumed to be zero and
-$F_a$ is the equilibrium velocity distribution.
+$F_a$ is the equilibrium velocity distribution function.
 
@@
 Thus, at this point, one must choose whether the quasilinear approach
-is enough or if a nonlinear formulation is necessary. In the first case
+is enough, or if a nonlinear formulation is necessary. In the first case
 all terms proportional to $\delta {\bf E} \delta f_a$ are neglected in
@@
 
-Now we assume the fluctuations may be decomposed in terms of the
+Now, we assume the fluctuations may be decomposed in terms of the
 Fourier-Laplace transformation over the fast time-scale of the

### 2019-07-08 thesis.tex
changes

@@
 
-\chapter{Kinetic theory and astrophysical plasmas}
+\chapter{Kinetic theory of plasmas}
 \label{sec:kin-theo}
 
-The plasma is a collection of ions, electrons and neutral particles that has
-its dynamics dominated by the electric and magnetic fields, generated by the
-electrically charged particles and the electric currents related to their
-motion, respectively. Due to the long-range nature of these self-generated
-fields, one particle affects the movement of several other particles, which
-will interact with other particles, and so on. This \emph{collective behavior}
-\footnote{A detailed exposition of all the processes and conditions that
-  characterize the collective behavior in plasmas, can be accessed in the
-  following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
-is what characterizes an ionized gas as a plasma, and is also the reason
-behind the complexity of the plasma dynamics. This complexity comes in the
-form of a myriad of self-consistent oscillatory processes, where the electric
-and magnetic fields affect - and are affected by - the position and motion of
-the charges, and how they vary in time \cite{chen}.
-
-A complete description of such a complicated dynamics would depend on determining
-the position and momentum of each particle, and their respective microscopic
-electric and magnetic fields, in a given instant in time. This strategy is not
-practical and in most of the cases not feasible for many-body systems, like the
-plasma. However, this microscopic description can be dealt through a hierarchy of
-approximations, leading to the three main theories of plasma physics: kinetic,
-multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
-formulations will depend on the phenomenon that needs to be described.
-
-\section{Kinetic processes in astrophysical plasmas}
-\label{sec:astro-plasma}
-
-\begin{figure}[h]
-  \begin{center}
-    \includegraphics[width=0.48\textwidth]{corona2017.png}
-    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
-    \caption{Solar corona captured during the total solar eclipse of 2017.
-      {\footnotesize Credit:}
-      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
-      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
-    \label{fig1}
-  \end{center}
-\end{figure}
+% The plasma is a collection of ions, electrons and neutral particles that has
+% its dynamics dominated by the electric and magnetic fields, generated by the
+% electrically charged particles and the electric currents related to their
+% motion, respectively. Due to the long-range nature of these self-generated
+% fields, one particle affects the movement of several other particles, which
+% will interact with other particles, and so on. This \emph{collective behavior}
+% \footnote{A detailed exposition of all the processes and conditions that
+%   characterize the collective behavior in plasmas, can be accessed in the
+%   following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
+% is what characterizes an ionized gas as a plasma, and is also the reason
+% behind the complexity of the plasma dynamics. This complexity comes in the
+% form of a myriad of self-consistent oscillatory processes, where the electric
+% and magnetic fields affect - and are affected by - the position and motion of
+% the charges, and how they vary in time \cite{chen}.
+
+% A complete description of such a complicated dynamics would depend on determining
+% the position and momentum of each particle, and their respective microscopic
+% electric and magnetic fields, in a given instant in time. This strategy is not
+% practical and in most of the cases not feasible for many-body systems, like the
+% plasma. However, this microscopic description can be dealt through a hierarchy of
+% approximations, leading to the three main theories of plasma physics: kinetic,
+% multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
+% formulations will depend on the phenomenon that needs to be described.
 
@@
 
-\subsection{Noneigenmode contribution to nonlinear wave
-  kinetic equation}
-For the nonlinear wave kinetic equation, the implementation
-is far more extensive and complicated than the two previous
-cases. Such complex series of steps is not well suited to a
-Qualifying Exam text but to a PhD Thesis, where they can be
-properly explained and then, well comprehended by the reader.
+\subsection{Noneigenmode contribution to nonlinear wave kinetic equation}
+For the nonlinear wave kinetic equation, the implementation is far more
+extensive and complicated than the two previous cases. 
 In this text, we provide a brief explanation of the method,
@@
 After an extensive algebraic manipulation that involves making explicit
-use of definition \cref{field-fluc} in the noneigenmode field fluctuations,
+use of definition \eqref{field-fluc} in the noneigenmode field fluctuations,
 carrying out the $\omega '$ integrations, then using Eq. \eqref{principal}
@@
 \label{appC}
-This publication is mainly related with the results results presented in
+This publication is mainly related with the results presented in
 Ref. \cite{Tigik2017a}.
@@
 \includepdf[pages=-]{Tigik2017b.pdf}
+
+\chapter{Applications to astrophysical plasmas}
+\label{appD}
+On Earth, the plasma is considered an exotic state of matter, associated to the
+glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
+laboratories, and the promise of cleaner and technically infinite energy source
+when scientists and engineers manage to succeed at obtaining a controlled, and
+energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
+everyday life are rare, restricted to the occurrence of lightning during storms,
+flames, and the beautiful auroras that take place at high latitudes. In the
+interplanetary and interstellar space, however, the situation is the opposite.
+Starting in the outer layers of Earth's atmosphere, passing through the solar
+wind in the interplanetary space, to the stellar interiors and atmospheres,
+accretion disks, and molecular clouds it is estimated that something around
+$99 \sim 99.9\%$ of the observable matter is in the plasma state \cite{may}. 
+Therefore, the study and comprehension of the physics of plasma processes is a
+fundamental branch of astrophysics.
+
+The
+
+% \section{Kinetic processes in astrophysical plasmas}
+% \label{sec:astro-plasma}
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{corona2017.png}
+    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
+    \caption{Solar corona captured during the total solar eclipse of 2017.
+      {\footnotesize Credit:}
+      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
+      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
+    \label{figD1}
+  \end{center}
+\end{figure}
+
 \end{appendix}

### 2019-07-10 thesis.tex
*** empty log message ***

@@
 \label{appD}
-On Earth, the plasma is considered an exotic state of matter, associated to the
-glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
-laboratories, and the promise of cleaner and technically infinite energy source
-when scientists and engineers manage to succeed at obtaining a controlled, and
-energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
-everyday life are rare, restricted to the occurrence of lightning during storms,
-flames, and the beautiful auroras that take place at high latitudes. In the
-interplanetary and interstellar space, however, the situation is the opposite.
-Starting in the outer layers of Earth's atmosphere, passing through the solar
-wind in the interplanetary space, to the stellar interiors and atmospheres,
-accretion disks, and molecular clouds it is estimated that something around
-$99 \sim 99.9\%$ of the observable matter is in the plasma state \cite{may}. 
-Therefore, the study and comprehension of the physics of plasma processes is a
-fundamental branch of astrophysics.
-
-The
+On Earth, the plasma is considered an exotic state of matter, associated to
+the glowing gas inside fluorescent and neon lamps, microchip manufacturing,
+research laboratories, and the promise of cleaner and technically infinite
+energy source when scientists and engineers manage to succeed at obtaining
+a controlled, and energetically efficient, thermonuclear fusion \cite{bell}.
+Naturally occurring plasmas in our everyday life are rare, restricted to the
+occurrence of lightning during storms, flames, and the beautiful auroras that
+take place at high latitudes. In the interplanetary and interstellar space,
+however, the situation is the opposite. Starting in the outer layers of
+Earth's atmosphere, passing through the solar wind in the interplanetary space,
+to the stellar interiors and atmospheres, accretion disks, and molecular clouds
+it is estimated that something around $99 \sim 99.9\%$ of the observable matter
+is in the plasma state \cite{may}. Therefore, the study and comprehension of
+the physics of plasma processes is a fundamental branch of astrophysics.
+
+Plasma is a gas in which the atoms -or molecules- are in an ionized state.
+In such condition, long-range electric and magnetic forces determine the
+interactions of the charged particles. This coupling between the variations
+in the electric and magnetic fields and the motion of ions and electrons
+gives rise to the myriad of collective processes that characterize a
+plasma\cite{tsytotp}.
 

### 2019-07-13 thesis.tex
agora vai

@@
 
-Plasma is a gas in which the atoms -or molecules- are in an ionized state.
-In such condition, long-range electric and magnetic forces determine the
-interactions of the charged particles. This coupling between the variations
-in the electric and magnetic fields and the motion of ions and electrons
-gives rise to the myriad of collective processes that characterize a
-plasma\cite{tsytotp}.
+In this thesis, we present a theoretical model for the inclusion of single
+particle fluctuations and collisional processes related to electrostatic
+oscillation in rarefied, unmagnetized, non-relativistic and fully ionized
+plasmas.
+
+% Plasma is a gas in which the atoms -or molecules- are in an ionized state.
+% In such condition, long-range electric and magnetic forces determine the
+% interactions of the charged particles. This coupling between the variations
+% in the electric and magnetic fields and the motion of ions and electrons
+% is behind the collective behavior that characterizes the plasma dynamics
+% \cite{tsytotp}. The complex processes
 

### 2019-07-14 pagtit.tex
minor modification
Changed "Qalifying Exam" for "Doctoral Thesis" in the header.
Aesthetical modifications
* pagtit.tex: Summary: minor modification
changed the title

@@
     \textsc{\Large \sffamily {Programa de Pós-Graduação em Física}}\\
-    \vspace{0.2cm}
-    {\large  Qualifying Exam}}\\
+    \vspace{0.15cm}
+    \textsc{\large  Doctoral Thesis}}\\
 \end{center}
@@
 {\Large \sffamily \textbf{Time evolution of weakly turbulent processes in
-    the presence of collisional interactions in astrophysical plasmas}\footnote[1]{
+    the presence of collisional interactions in solar plasmas}\footnote[1]{
     Project financed by the by the Conselho Nacional de
@@
 %%% mode: latex
-%%% TeX-master: "quali"
+%%% TeX-master: "thesis"
 %%% End:

### 2019-07-14 thesis.tex
*** empty log message ***

@@
 
-\chapter{Applications to astrophysical plasmas}
+\chapter{Applications to solar plasmas}
 \label{appD}
@@
 it is estimated that something around $99 \sim 99.9\%$ of the observable matter
-is in the plasma state \cite{may}. Therefore, the study and comprehension of
-the physics of plasma processes is a fundamental branch of astrophysics.
+in the universe is in the plasma state \cite{may,}. Therefore, the study and
+comprehension of the physics of plasma processes is a fundamental branch of
+astrophysics.
+
+Space plasmas are observed in a broad variety of
 

### 2019-07-18 draft.tex
*** empty log message ***

@@
 energetically efficient, thermonuclear fusion. Naturally occurring plasmas in our
-everyday life are rare, restricted to the occurrence of lightning during storms
-and beautiful auroras that are spotted at high latitudes. In the interplanetary
-and interstellar space, however, the situation is the opposite. Starting in the
-outer layers of Earth's atmosphere, passing through the solar wind in the
-interplanetary space, to the stellar interiors and atmospheres, accretion disks,
-and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
-the observable matter is in the plasma state \cite{may}.
+everyday life are rare, restricted to the occurrence of lightning during storms,
+flames and beautiful auroras that are spotted at high latitudes. In the
+interplanetary and interstellar space, however, the situation is the opposite.
+Starting in the outer layers of Earth's atmosphere, passing through the solar
+wind in the interplanetary space, to the stellar interiors and atmospheres,
+accretion disks, and molecular clouds it is estimated that something around
+$99 \sim 99.9\%$ of the observable matter is in the plasma state \cite{may}.
 
@@
 the plasma in space.
+
+%The plasma that permeates the near Earth environment, and our solar system
+% has its source in the plasma ejections
+
+% During the development of this doctoral research, there was always a
+% concern about not being restricted to purely theoretical modeling of
+% the plasma phenomena.
+
+% Describing nonlinear processes in plasmas, in
+% the kinetic theory level, requires a series of approximations and
+% idealized assumptions that, at first glance, it might look like one
+% is losing the connection with the real-world physics.
+
+% On Earth, the plasma is considered an exotic state of matter, associated to
+% the glowing gas inside fluorescent and neon lamps, microchip manufacturing,
+% research laboratories, and the promise of cleaner and technically infinite
+% energy source when scientists and engineers manage to succeed at obtaining
+% a controlled, and energetically efficient, thermonuclear fusion \cite{bell}.
+% Naturally occurring plasmas in our everyday life are rare, restricted to the
+% occurrence of lightning during storms, flames, and the beautiful auroras that
+% take place at high latitudes. In the interplanetary and interstellar space,
+% however, the situation is the opposite. Starting in the outer layers of
+% Earth's atmosphere, passing through the solar wind in the interplanetary space,
+% to the stellar interiors and atmospheres, accretion disks, and molecular clouds
+% it is estimated that something around $99 \sim 99.9\%$ of the observable matter
+% in the universe is in the plasma state \cite{may}. Therefore, the study and
+% comprehension of the physics of plasma processes is a fundamental branch of
+% astrophysics.
+
+% Plasma is a gas in which the atoms -or molecules- are in an ionized state.
+% In such condition, long-range electric and magnetic forces determine the
+% interactions of the charged particles. This coupling between the variations
+% in the electric and magnetic fields and the motion of ions and electrons
+% is behind the collective behavior that characterizes the plasma dynamics
+% \cite{tsytotp}. The complex processes

### 2019-07-18 thesis.tex
*** empty log message ***

--- 2019-07-10 thesis.tex
@@
 \label{appD}
-On Earth, the plasma is considered an exotic state of matter, associated to
-the glowing gas inside fluorescent and neon lamps, microchip manufacturing,
-research laboratories, and the promise of cleaner and technically infinite
-energy source when scientists and engineers manage to succeed at obtaining
-a controlled, and energetically efficient, thermonuclear fusion \cite{bell}.
-Naturally occurring plasmas in our everyday life are rare, restricted to the
-occurrence of lightning during storms, flames, and the beautiful auroras that
-take place at high latitudes. In the interplanetary and interstellar space,
-however, the situation is the opposite. Starting in the outer layers of
-Earth's atmosphere, passing through the solar wind in the interplanetary space,
-to the stellar interiors and atmospheres, accretion disks, and molecular clouds
-it is estimated that something around $99 \sim 99.9\%$ of the observable matter
-is in the plasma state \cite{may}. Therefore, the study and comprehension of
-the physics of plasma processes is a fundamental branch of astrophysics.
+On Earth, the plasma is considered an exotic state of matter, associated to the
+glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
+laboratories, and the promise of cleaner and practically inexhaustible energy
+source once we have controlled and energetically efficient thermonuclear fusion
+\cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
+to the occurrence of lightning during storms, flames, and the beautiful auroras
+that take place at high latitudes. In the space, however, the situation is the
+opposite. Starting in the outer layers of Earth's atmosphere, passing through the
+solar wind in the interplanetary space, to the stellar interiors and atmospheres,
+accretion disks, and molecular clouds it is estimated that something around
+$99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
+\cite{may}.
 
@@
 in the electric and magnetic fields and the motion of ions and electrons
-gives rise to the myriad of collective processes that characterize a
-plasma\cite{tsytotp}.
+is the cause of the wide variety of oscillatory processes that characterize
+the plasma dynamics\cite{tsytotp}.
+
+Understanding the complex physics of
+the plasma state is a fundamental
+
+% In this thesis, we present a theoretical model for the inclusion of single
+% particle fluctuations and collisional processes related to electrostatic
+% oscillation in rarefied, unmagnetized, non-relativistic and fully ionized
+% plasmas.
 

### 2019-07-19 thesis.tex
*** empty log message ***

@@
 $99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
-\cite{may}.
-
-Plasma is a gas in which the atoms -or molecules- are in an ionized state.
-In such condition, long-range electric and magnetic forces determine the
-interactions of the charged particles. This coupling between the variations
-in the electric and magnetic fields and the motion of ions and electrons
-is the cause of the wide variety of oscillatory processes that characterize
-the plasma dynamics\cite{tsytotp}.
-
-Understanding the complex physics of
-the plasma state is a fundamental
+\cite{may}. Therefore, the study of the physics of plasma processes is a
+fundamental branch of astrophysics\cite{tsypa}.
+
+Space plasmas are observed in a vast range of temperature, density, magnetic
+field strengths and scale lengths. However, in most of the cases, models used
+to describe processes
+
+%Plasma is a gas in which the atoms -or molecules- are in an ionized state.
+% In such condition, long-range electric and magnetic forces determine the
+% interactions of the charged particles. This coupling between the variations
+% in the electric and magnetic fields and the motion of ions and electrons
+% is the cause of the wide variety of oscillatory processes that characterize
+% the plasma dynamics\cite{tsytotp}.
 

### 2019-07-23 thesis.tex
*** empty log message ***

@@
 
-Space plasmas are observed in a vast range of temperature, density, magnetic
-field strengths and scale lengths. However, in most of the cases, models used
-to describe processes
+The theory developed during this graduate research has relevant contributions in
+the study of the combined action of nonlinear kinetic plasma instabilities and
+collisional processes in plasmas. This new approach might help us to elucidate
+the fundamental physics behind critical features observed in the solar plasma.
+Besides solar physics, the present formalism, due to its underlying character,
+can be extended to the plasma of different astrophysical environments and even
+laboratory plasmas. In this appendix, we will make a brief revision on solar
+physics, pointing out the phenomena that are associated with our model.
 

### 2019-07-24 thesis.tex
new paragraph

--- 2019-07-19 thesis.tex
@@
 
-Space plasmas are observed in a vast range of temperature, density, magnetic
-field strengths and scale lengths. However, in most of the cases, models used
-to describe processes
+The analysis presented in this doctoral thesis has relevant contributions in the
+study of the combined action of nonlinear kinetic instabilities and collisional
+processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
+profile under consideration might be considered quite idealized, the physical
+processes that are being addressed have fundamental character - the plasma waves
+under consideration and the particle interactions are inherent to any plasma.
+The underlying nature of these processes means that they might impact the plasma
+dynamics at different astrophysical environments and also in laboratory plasmas.
+Laboratory plasmas, however, are usually constrained by very specific conditions
+that are unique to each experiment. This specificity makes the analysis in the
+experimental context counter productive. A more broad approach is to compare our
+theoretical results with plasma phenomena that are independent of imposed laboratory
+conditions: astrophysical plasmas.
+
+ In this appendix, we will make a brief revision on solar
+physics, pointing out the phenomena that are associated with our model.
 

### 2019-07-24 thesis.tex
* thesis.tex: Summary: new paragraph

@@
 that are unique to each experiment. This specificity makes the analysis in the
-experimental context counter productive. A more broad approach is to compare our
-theoretical results with plasma phenomena that are independent of imposed laboratory
-conditions: astrophysical plasmas.
-
+experimental context counter productive. A more broad approach was then to compare
+our theoretical results with phenomena observed in the naturally occurring space
+plasma.
+
+Astrophysical plasmas are observed in a vast range of densities, temperatures,
+magnetic fields, and scale lengths\footnote{The description of such an extensive list is
+out of the scope of this text. On that matter, Ref.~\cite{peratt2014} offers a
+quite complete description of space plasma and space plasma phenomena occurring
+in all cosmic scales.}.  
  In this appendix, we will make a brief revision on solar

### 2019-07-25 thesis.tex
*** empty log message ***

--- 2019-07-24 thesis.tex
@@
 that are unique to each experiment. This specificity makes the analysis in the
-experimental context counter productive. A more broad approach is to compare our
-theoretical results with plasma phenomena that are independent of imposed laboratory
-conditions: astrophysical plasmas.
+experimental context counter productive. A more broad approach was then to compare
+our theoretical results with phenomena observed in a naturally occurring space
+plasma, that is also accessible to direct measurements. In that sense, the solar
+plasma was the logical choice.
+
+It is well known that the plasma in our solar system is considered as a natural
+laboratory for the study of space plasma. The wide variety of plasma phenomena
+accessible to direct, in situ measurements and highly resolved remote sensing,
+might be scaled to other astrophysical environments. Besides that, theoretical
+models developed to explain phenomena observed in the solar system plasma might
+be extrapolated to describe plasma process occurring in more extreme astrophysical
+systems.
+
+% Astrophysical plasmas are observed in a vast range of densities, temperatures,
+% magnetic fields, and scale lengths\footnote{The description of such an extensive
+%   list is out of the scope of this text. On that matter, Ref.~\cite{peratt2014}
+%   offers a quite complete exposure of space plasma, and space plasma phenomena
+%   occurring in all cosmic scales.}.
+
+% \footnote{In the literature, the term ``astrophysical plasma'' is sometimes
+%   used to refer to the plasma observed outside the solar system, while ``space
+%   plasma'' is used to account for the plasma in our interplanetary space. In this
+%   text, however, both terms are being used as synonyms.}
+
+% With some exotic exceptions, like the super
+% dense and degenerate plasma of white dwarfs (which is beyond the applicability
+% of our theory), the solar system hosts a large variety of plasma whose properties
+
+accessible
+to both in situ measurements and highly resolved remote sensing.
 

### 2019-07-26 thesis.tex
*** empty log message ***

--- 2019-07-24 thesis.tex
@@
 \label{appD}
-On Earth, the plasma is considered an exotic state of matter, associated to the
-glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
-laboratories, and the promise of cleaner and practically inexhaustible energy
-source once we have controlled and energetically efficient thermonuclear fusion
-\cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
-to the occurrence of lightning during storms, flames, and the beautiful auroras
-that take place at high latitudes. In the space, however, the situation is the
-opposite. Starting in the outer layers of Earth's atmosphere, passing through the
-solar wind in the interplanetary space, to the stellar interiors and atmospheres,
-accretion disks, and molecular clouds it is estimated that something around
-$99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
-\cite{may}. Therefore, the study of the physics of plasma processes is a
-fundamental branch of astrophysics\cite{tsypa}.
+% On Earth, the plasma is considered an exotic state of matter, associated to the
+% glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
+% laboratories, and the promise of cleaner and practically inexhaustible energy
+% source once we have controlled and energetically efficient thermonuclear fusion
+% \cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
+% to the occurrence of lightning during storms, flames, and the beautiful auroras
+% that take place at high latitudes. In the space, however, the situation is the
+% opposite. Starting in the outer layers of Earth's atmosphere, passing through the
+% solar wind in the interplanetary space, to the stellar interiors and atmospheres,
+% accretion disks, and molecular clouds it is estimated that something around
+% $99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
+% \cite{may}. Therefore, the study of the physics of plasma processes is a
+% fundamental branch of astrophysics\cite{tsypa}.
 
@@
 that are unique to each experiment. This specificity makes the analysis in the
-experimental context counter productive. A more broad approach is to compare our
-theoretical results with plasma phenomena that are independent of imposed laboratory
-conditions: astrophysical plasmas.
-
- In this appendix, we will make a brief revision on solar
-physics, pointing out the phenomena that are associated with our model.
-
-%Plasma is a gas in which the atoms -or molecules- are in an ionized state.
-% In such condition, long-range electric and magnetic forces determine the
-% interactions of the charged particles. This coupling between the variations
-% in the electric and magnetic fields and the motion of ions and electrons
-% is the cause of the wide variety of oscillatory processes that characterize
-% the plasma dynamics\cite{tsytotp}.
-
-% In this thesis, we present a theoretical model for the inclusion of single
-% particle fluctuations and collisional processes related to electrostatic
-% oscillation in rarefied, unmagnetized, non-relativistic and fully ionized
-% plasmas.
-
-% \section{Kinetic processes in astrophysical plasmas}
-% \label{sec:astro-plasma}
+experimental context counter productive. A more broad approach was then to compare
+our theoretical results with phenomena observed in the naturally occurring space
+plasma\footnote{In the literature, the term ``astrophysical plasma'' is sometimes
+  used to refer to the plasma observed outside the solar system, while ``space
+  plasma'' is used to account for the plasma in our interplanetary space. In this
+  text, however, both terms are being used as synonyms.}. The accessibility to
+direct, in situ measurements, highly resolved remote sensing and high-resolution
+spectroscopy make of the solar plasma the right choice for our analysis.
+
+% In order to offer a deeper insight on the solar phenomena 
+% In this appendix, we make a brief description of the solar processes that are
+% being addressed by our theory.
+
+\section{}
+\label{sec:solar-physics}
+The Sun is a G2 main-sequence star. From the stellar astrophysics point
+of view, it is considered ordinary, without any unique property that could
+differentiate it from other main-sequence stars; except for the fact that
+it is remarkably close to us. These two facts make the Sun a perfect model
+of study, not only for stellar evolution theorists but also for plasma
+physicists.
 

### 2019-07-29 thesis.tex
*** empty log message ***

@@
 % $99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
-% \cite{may}. Therefore, the study of the physics of plasma processes is a
-% fundamental branch of astrophysics\cite{tsypa}.
+% \cite{may}. So understanding the basic physics of plasma processes might help on
+% interpreting and describing
 
@@
   plasma'' is used to account for the plasma in our interplanetary space. In this
-  text, however, both terms are being used as synonyms.}. The accessibility to
-direct, in situ measurements, highly resolved remote sensing and high-resolution
-spectroscopy make of the solar plasma the right choice for our analysis.
-
-% In order to offer a deeper insight on the solar phenomena 
-% In this appendix, we make a brief description of the solar processes that are
-% being addressed by our theory.
-
-\section{}
+  text, however, both terms are being used as synonyms.}.
+
+Astrophysical plasmas are observed in a vast range of densities, temperatures,
+magnetic fields, and scale lengths\footnote{For a relatively brief, but
+  comprehensive, description of the scales and characteristics of cosmic plasmas,
+  see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
+Earth's atmosphere, passing through the solar wind in the interplanetary space,
+to the stellar interiors and atmospheres, accretion disks, and molecular clouds
+it is estimated that something around $99 \sim 99.9\%$ of the observable matter
+in the universe is in the plasma state\cite{may}. Most of these plasmas are quite
+far from our measurement instruments, being accessible only through analysis of
+the electromagnetic spectrum emitted from their remote location.
+
+% The accessibility to
+% direct, in situ measurements, highly resolved remote sensing and high-resolution
+% spectroscopy make of the solar plasma the right choice for our analysis.
+
+\section{Solar physics}
 \label{sec:solar-physics}
-The Sun is a G2 main-sequence star. From the stellar astrophysics point
-of view, it is considered ordinary, without any unique property that could
-differentiate it from other main-sequence stars; except for the fact that
-it is remarkably close to us. These two facts make the Sun a perfect model
-of study, not only for stellar evolution theorists but also for plasma
-physicists.
+
+The solar system is permeated with a constant plasma flow of solar origin.
+This tenuous and rapid flowing plasma, know as \emph{solar wind}, is
+expelled
+
+% The Sun is a G2 main-sequence star. From the stellar astrophysics point
+% of view, it is considered ordinary, without any unique property that could
+% differentiate it from other main-sequence stars; except for the fact that
+% it is remarkably close to us. These two facts make the Sun a perfect model
+% of study not only for several areas of astrophysics, like stellar structure
+% and evolution, but also for plasma physics.
 

### 2019-07-30 thesis.tex
another day writing the thesis...

@@
 it is estimated that something around $99 \sim 99.9\%$ of the observable matter
-in the universe is in the plasma state\cite{may}. Most of these plasmas are quite
-far from our measurement instruments, being accessible only through analysis of
-the electromagnetic spectrum emitted from their remote location.
+in the universe is in the plasma state\cite{may}. The absolute majority of space
+plasmas are unreachable to in situ observation, being accessible only through
+analysis of the electromagnetic spectrum emitted from their remote location.
 

### 2019-07-30 thesis.tex
* thesis.tex: Summary: another day writing the thesis...

--- 2019-07-29 thesis.tex
@@
 Astrophysical plasmas are observed in a vast range of densities, temperatures,
-magnetic fields, and scale lengths\footnote{For a relatively brief, but
-  comprehensive, description of the scales and characteristics of cosmic plasmas,
-  see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
-Earth's atmosphere, passing through the solar wind in the interplanetary space,
-to the stellar interiors and atmospheres, accretion disks, and molecular clouds
-it is estimated that something around $99 \sim 99.9\%$ of the observable matter
-in the universe is in the plasma state\cite{may}. Most of these plasmas are quite
-far from our measurement instruments, being accessible only through analysis of
-the electromagnetic spectrum emitted from their remote location.
+magnetic fields, ionization degree, and scale lengths\footnote{For a relatively
+  brief, but comprehensive, description of the scales and characteristics of
+  cosmic plasmas, see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the
+outer layers of Earth's atmosphere, passing through the solar wind in the
+interplanetary space, to the stellar interiors and atmospheres, accretion disks,
+and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
+the observable matter in the universe is in the plasma state\cite{may}. Under
+cosmic conditions, even the weakly ionized gas of the neutral hydrogen regions
+around galaxies or in the atmosphere of cold stars have a strong reaction to
+electromagnetic fields, exhibiting the characteristic collective behavior of
+plasmas\cite{tsypa,peratt2014}.
+Since this ubiquity of plasmas in space came as a fact, astrophysicists and
+plasma physicists have been increasingly exchanging knowledge, with plasma
+physics providing theoretical background and laboratory models that might help
+with the interpretation and physical explanation of astrophysical observations,
+and astrophysics confirming theoretical predictions of plasma physics with
+observations of phenomena that are unique to space plasma\cite{tsypa,Kulsrud2005}.
+
+The absolute majority of the plasma observed in space is far away from us,
+being accessible only through analysis of the electromagnetic spectrum
+emitted from their quite remote location. A fortunate exception to this
+fact is the plasma in our solar system.
 

### 2019-07-31 thesis.tex
* thesis.tex: Summary: another day writing the thesis...
got tired for today

@@
 plasma physicists have been increasingly exchanging knowledge, with plasma
-physics providing theoretical background and laboratory models that might help
-with the interpretation and physical explanation of astrophysical observations,
-and astrophysics confirming theoretical predictions of plasma physics with
-observations of phenomena that are unique to space plasma\cite{tsypa,Kulsrud2005}.
-
-The absolute majority of the plasma observed in space is far away from us,
-being accessible only through analysis of the electromagnetic spectrum
-emitted from their quite remote location. A fortunate exception to this
-fact is the plasma in our solar system.
-
-% The accessibility to
-% direct, in situ measurements, highly resolved remote sensing and high-resolution
-% spectroscopy make of the solar plasma the right choice for our analysis.
+physics providing theoretical background, computational and laboratory models
+that might help with the interpretation and physical explanation of astrophysical
+observations, and astrophysics confirming theoretical and computational
+predictions on plasma physics with observations of phenomena that are unique
+to space plasma\cite{tsypa,Kulsrud2005}.
+
+On that regard, the results obtained during this graduate research can be
+found on both sides of this mutual contribution. In \cite{Tigik2016a},
+\cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
+numerical evidence of plasma processes that might aid in the interpretation
+and accurate modeling  of phenomena observed in the solar plasma. While in
+\cite{Tigik2017a}, we introduce a new equation depicting an unknown process
+and numerically analyze it in the context of solar physics; its existence
+outside theory, however, will depend on the development of more advanced
+space probes to be confirmed. The choice for applying our theory to
+phenomena observed in the solar plasma, and not in some remote space plasma,
+now became evident. The accessibility to direct, in situ measurements,
+highly resolved remote sensing and high-resolution spectroscopy made the
+solar plasma the right choice for our analysis.
+
+% The absolute majority of the plasma observed in space is far away from us,
+% being accessible only through analysis of the electromagnetic spectrum
+% emitted from their quite remote location. A fortunate exception to this
+% fact is the plasma in our solar system.
 

### 2019-07-31 thesis.tex
removed the schedule that was part of the qualifying exam - now can sleep tight
* thesis.tex: Summary: got tired for today

@@
 
-The prospects of this research are promising. Besides including the
-new effects on the time evolution of nonlinear beam-plasma interaction,
-we are planning the inclusion of effects due to non-homogeneous
-medium on the beam-plasma dynamics, and its implementation in the numerical
-code. Furthermore, the results regarding
-the electrostatic bremsstrahlung term deserve further research in order
-to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
-the electrostatic bremsstrahlung being the underlying effect behind the
-generation of suprathermal velocity distributions, which are pervasively
-observed in space plasmas. The objectives above are in accordance with
-the research project approved for the ``Sandwich Doctorate Program'',
-that is proposed to occur under the supervision of Dr. Peter Yoon in the
-University of Maryland.
-
-\section{Schedule}
-\label{sec:schedule}
-The expected schedule for the remaining period of this doctoral
-research is detailed below:
-\begin{itemize}
-\item \textbf{March to July 2018:} inclusion the new effects on
-  the time evolution of nonlinear beam-plasma interaction, and of
-  implementation the code for the inclusion of non-homogeneous
-  medium on the beam-plasma dynamics;
-\item \textbf{August 2018 to February 2019:} internship period in
-  the University of Maryland, working on the further development
-  of the electrostatic bremsstrahlung hypothesis;
-\item \textbf{March to August of 2019:} Thesis elaboration.
-\end{itemize}
+% The prospects of this research are promising. Besides including the
+% new effects on the time evolution of nonlinear beam-plasma interaction,
+% we are planning the inclusion of effects due to non-homogeneous
+% medium on the beam-plasma dynamics, and its implementation in the numerical
+% code. Furthermore, the results regarding
+% the electrostatic bremsstrahlung term deserve further research in order
+% to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
+% the electrostatic bremsstrahlung being the underlying effect behind the
+% generation of suprathermal velocity distributions, which are pervasively
+% observed in space plasmas. The objectives above are in accordance with
+% the research project approved for the ``Sandwich Doctorate Program'',
+% that is proposed to occur under the supervision of Dr. Peter Yoon in the
+% University of Maryland.
+
+% \section{Schedule}
+% \label{sec:schedule}
+% The expected schedule for the remaining period of this doctoral
+% research is detailed below:
+% \begin{itemize}
+% \item \textbf{March to July 2018:} inclusion the new effects on
+%   the time evolution of nonlinear beam-plasma interaction, and of
+%   implementation the code for the inclusion of non-homogeneous
+%   medium on the beam-plasma dynamics;
+% \item \textbf{August 2018 to February 2019:} internship period in
+%   the University of Maryland, working on the further development
+%   of the electrostatic bremsstrahlung hypothesis;
+% \item \textbf{March to August of 2019:} Thesis elaboration.
+% \end{itemize}
 

### 2019-07-31 thesis.tex
better days will come

@@
 plasmas\cite{tsypa,peratt2014}.
-Since this ubiquity of plasmas in space came as a fact, astrophysicists and
-plasma physicists have been increasingly exchanging knowledge, with plasma
-physics providing theoretical background, computational and laboratory models
-that might help with the interpretation and physical explanation of astrophysical
-observations, and astrophysics confirming theoretical and computational
-predictions on plasma physics with observations of phenomena that are unique
-to space plasma\cite{tsypa,Kulsrud2005}.
-
-On that regard, the results obtained during this graduate research can be
-found on both sides of this mutual contribution. In \cite{Tigik2016a},
-\cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
-numerical evidence of plasma processes that might aid in the interpretation
-and accurate modeling  of phenomena observed in the solar plasma. While in
-\cite{Tigik2017a}, we introduce a new equation depicting an unknown process
-and numerically analyze it in the context of solar physics; its existence
-outside theory, however, will depend on the development of more advanced
-space probes to be confirmed. The choice for applying our theory to
-phenomena observed in the solar plasma, and not in some remote space plasma,
-now became evident. The accessibility to direct, in situ measurements,
-highly resolved remote sensing and high-resolution spectroscopy made the
-solar plasma the right choice for our analysis.
+
+Since the ubiquity of plasmas in space came as a fact, astrophysicists and
+plasma physicists have been noticing an increasing necessity for exchanging
+knowledge and mutually collaborating with their results. In this arrangement,
+plasma physics provides theoretical, computational, and laboratory models
+that might help with the interpretation and propose a physical explanation
+for astrophysical observations. Astrophysics, on the other hand, contributes
+with data from observations of phenomena that are unique to cosmic plasma and
+might be used to confirm theoretical and computational predictions on plasma
+physics, and also to compare with experimental results\cite{tsypa,Kulsrud2005}.
+A particular field of research that has been acting for a long time as a bridge
+between these two areas is the solar physics.
 
@@
 
-\section{Solar physics}
+\section{Solar and space physics}
 \label{sec:solar-physics}
+Solar physics can be thought of as a combination of plasma and space physics.
+The wide variety of plasmas and the accessibility to direct, in situ measurements,
+highly resolved remote sensing and high-resolution spectroscopy turned the solar
+system into Earth's plasma physics laboratory in space.
+%% falar sobre como física sola pode contribuir para fśica de plasmas em geral
 
@@
 
+% The theory developed during this graduate research makes use of solar physics
+% results to contribute on both sides. In \cite{Tigik2016a},
+% \cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
+% numerical evidence of plasma processes that might aid in the interpretation
+% and accurate modeling  of phenomena observed in the solar plasma. While in
+% \cite{Tigik2017a}, we introduce a new equation depicting an unknown process
+% and numerically analyze it in the context of solar physics; its existence
+% outside theory, however, will depend on the development of more advanced
+% space probes to be confirmed.
+
 \end{appendix}

### 2019-08-01 thesis.tex
not sure

@@
 plasma physicists have been noticing an increasing necessity for exchanging
-knowledge and mutually collaborating with their results. In this arrangement,
-plasma physics provides theoretical, computational, and laboratory models
-that might help with the interpretation and propose a physical explanation
-for astrophysical observations. Astrophysics, on the other hand, contributes
-with data from observations of phenomena that are unique to cosmic plasma and
-might be used to confirm theoretical and computational predictions on plasma
-physics, and also to compare with experimental results\cite{tsypa,Kulsrud2005}.
-A particular field of research that has been acting for a long time as a bridge
-between these two areas is the solar physics.
+knowledge and mutually collaborating with their results. A particular field
+of research that has been acting for a long time as a bridge between these two
+areas is the solar physics. The accessibility of the solar plasma to direct,
+in situ measurements, highly resolved remote sensing and high-resolution
+spectroscopy turned the solar system into Earth's space physics laboratory.
+
+A recent example of this complementarity is
+presented in Ref. \cite{Peterson2019}, where the authors reproduced in the
+laboratory a magnetic structure called, \emph{Parker spiral}, which is
+related to the acceleration process of solar -and stellar- winds. The
+authors also compare their results with numerical simulation of the same
+structure. Astrophysics, on the other hand, contributes with data from
+observations of space plasma phenomena that might be useful for testing
+theoretical predictions, and comparing with numerical and experimental
+results. In Ref. \cite{Chen2019}, for instance,
 

### 2019-08-02 thesis.tex
*** empty log message ***

--- 2019-07-31 thesis.tex
@@
 
-Since the ubiquity of plasmas in space came as a fact, astrophysicists and
-plasma physicists have been noticing an increasing necessity for exchanging
-knowledge and mutually collaborating with their results. In this arrangement,
-plasma physics provides theoretical, computational, and laboratory models
-that might help with the interpretation and propose a physical explanation
-for astrophysical observations. Astrophysics, on the other hand, contributes
-with data from observations of phenomena that are unique to cosmic plasma and
-might be used to confirm theoretical and computational predictions on plasma
-physics, and also to compare with experimental results\cite{tsypa,Kulsrud2005}.
-A particular field of research that has been acting for a long time as a bridge
-between these two areas is the solar physics.
+Due to the pervasiveness of the plasma state in space, plasma physics became
+an essential component in the multidisciplinary framework of astrophysics.
+At the same time, observations of space plasma phenomena have been gaining
+increasing relevance in theoretical, computational, and experimental areas
+of plasma physics research \cite{Kulsrud2005}. This mutual contribution is
+driven by solar physics.
+
+% Since the ubiquity of plasmas in space came as a fact, astrophysicists and
+% plasma physicists have been noticing an increasing necessity for exchanging
+% knowledge and mutually collaborating with their results. A particular field
+% of research that has been acting for a long time as a bridge between these two
+% areas is the solar physics. The accessibility of the solar plasma to direct,
+% in situ measurements, highly resolved remote sensing and high-resolution
+% spectroscopy turned the solar system into Earth's space physics laboratory.
+
+A recent example of this complementarity is
+presented in Ref. \cite{Peterson2019}, where the authors reproduced in the
+laboratory a magnetic structure called \emph{Parker spiral}, which is
+related to the acceleration process of solar - and stellar - winds. The
+authors compare their results with numerical simulation of the same
+structure, since in situ observations of this particular phenomena are not
+available yet. In Ref. \cite{Chen2019}, we have the opposite situation.
 

### 2019-08-02 thesis.tex
*** empty log message ***

@@
 dynamics at different astrophysical environments and also in laboratory plasmas.
-Laboratory plasmas, however, are usually constrained by very specific conditions
-that are unique to each experiment. This specificity makes the analysis in the
-experimental context counter productive. A more broad approach was then to compare
-our theoretical results with phenomena observed in the naturally occurring space
-plasma\footnote{In the literature, the term ``astrophysical plasma'' is sometimes
-  used to refer to the plasma observed outside the solar system, while ``space
-  plasma'' is used to account for the plasma in our interplanetary space. In this
-  text, however, both terms are being used as synonyms.}.
+Laboratory plasmas, however, are usually constrained by specific experimental
+set-up. This specificity would require deep knowledge, and maybe access, to one
+experiment, which makes the analysis in the experimental context restrictive and
+counter productive. A more broad approach was then to compare our theoretical
+results with phenomena observed in the naturally occurring space plasma.
+
+% \footnote{In the literature, the term ``astrophysical plasma'' is sometimes used
+%   to refer to the plasma observed outside the solar system, while ``space plasma''
+%   is used to account for the plasma in our interplanetary space. In this text,
+%   however, both terms are being used as synonyms.}
 
 Astrophysical plasmas are observed in a vast range of densities, temperatures,
-magnetic fields, ionization degree, and scale lengths\footnote{For a relatively
-  brief, but comprehensive, description of the scales and characteristics of
-  cosmic plasmas, see Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the
-outer layers of Earth's atmosphere, passing through the solar wind in the
-interplanetary space, to the stellar interiors and atmospheres, accretion disks,
-and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of
-the observable matter in the universe is in the plasma state\cite{may}. Under
-cosmic conditions, even the weakly ionized gas of the neutral hydrogen regions
-around galaxies or in the atmosphere of cold stars have a strong reaction to
-electromagnetic fields, exhibiting the characteristic collective behavior of
-plasmas\cite{tsypa,peratt2014}.
-
-Due to the pervasiveness of the plasma state in space, plasma physics became
-an essential component in the multidisciplinary framework of astrophysics.
-At the same time, observations of space plasma phenomena have been gaining
-increasing relevance in theoretical, computational, and experimental areas
-of plasma physics research \cite{Kulsrud2005}. This mutual contribution is
+magnetic fields, ionization degree, and scale lengths\footnote{A comprehensive
+  description of the scales and characteristics of cosmic plasmas can be seen
+  in Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
+Earth's atmosphere, passing through the solar wind in the interplanetary space,
+to the stellar interiors and atmospheres, accretion disks, and molecular clouds
+it is estimated that something around $99 \sim 99.9\%$ of the observable matter
+in the universe is in the plasma state. Under cosmic conditions, even the weakly
+ionized gas of the neutral hydrogen regions around galaxies or in the atmosphere
+of cold stars have a strong reaction to electromagnetic fields, exhibiting the
+characteristic collective behavior of plasmas and, therefore, are also considered
+plasmas\cite{tsypa,may,peratt2014}.
+
+Since the pervasiveness of the plasma state in space came as a fact, plasma
+physics became an essential component in the multidisciplinary framework of
+astrophysics. At the same time, observations of space plasma phenomena have
+been gaining increasing relevance in the advance of theoretical, computational,
+and experimental plasma physics research \cite{Kulsrud2005}. This mutual contribution is
 driven by solar physics.

### 2019-08-03 thesis.tex
*** empty log message ***

@@
 
-The analysis presented in this doctoral thesis has relevant contributions in the
-study of the combined action of nonlinear kinetic instabilities and collisional
-processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
-profile under consideration might be considered quite idealized, the physical
-processes that are being addressed have fundamental character - the plasma waves
-under consideration and the particle interactions are inherent to any plasma.
-The underlying nature of these processes means that they might impact the plasma
-dynamics at different astrophysical environments and also in laboratory plasmas.
-Laboratory plasmas, however, are usually constrained by specific experimental
-set-up. This specificity would require deep knowledge, and maybe access, to one
-experiment, which makes the analysis in the experimental context restrictive and
-counter productive. A more broad approach was then to compare our theoretical
-results with phenomena observed in the naturally occurring space plasma.
-
-% \footnote{In the literature, the term ``astrophysical plasma'' is sometimes used
-%   to refer to the plasma observed outside the solar system, while ``space plasma''
-%   is used to account for the plasma in our interplanetary space. In this text,
-%   however, both terms are being used as synonyms.}
-
-Astrophysical plasmas are observed in a vast range of densities, temperatures,
-magnetic fields, ionization degree, and scale lengths\footnote{A comprehensive
+% The analysis presented in this doctoral thesis has relevant contributions in the
+% study of the combined action of nonlinear kinetic instabilities and collisional
+% processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
+% profile under consideration might be considered quite idealized, the physical
+% processes that are being addressed have fundamental character - the plasma waves
+% under consideration and the particle interactions are inherent to any plasma.
+% The underlying nature of these processes means that they might impact the plasma
+% dynamics at different astrophysical environments and also in laboratory plasmas.
+% Laboratory plasmas, however, are usually constrained by specific experimental
+% set-up. This specificity would require in-depth knowledge and maybe access to
+% one experiment, which makes the analysis in the experimental context restrictive
+% and counterproductive. A more broad approach was then to compare our theoretical
+% results with phenomena observed in the naturally occurring space plasma.
+
+Astrophysical plasmas\footnote{In the literature, the term ``astrophysical
+  plasma'' is sometimes used to refer to the plasma observed outside the solar
+  system, while ``space plasma'' is used to account for the plasma in our
+  interplanetary space. In this text, however, both terms are being used as
+  synonyms.} are observed in a vast range of densities, temperatures, magnetic
+fields, ionization degree, and scale lengths\footnote{A comprehensive
   description of the scales and characteristics of cosmic plasmas can be seen

### 2019-08-04 thesis.tex
*** empty log message ***

@@
 and interpretation of several solar phenomena observed by space-probes \cite{
-  VWK2000,Hannah2009,ZVST11,KRB12,KF13,RR14,Reid2015}, a fact that emphasizes
+  Vinas2000,Hannah2009,ZVST11,KRB12,KF13,RR14,Reid2015}, a fact that emphasizes
 the necessity of the development of a mathematically rigorous theory able to
@@
 astrophysics. At the same time, observations of space plasma phenomena have
-been gaining increasing relevance in the advance of theoretical, computational,
-and experimental plasma physics research \cite{Kulsrud2005}. This mutual contribution is
-driven by solar physics.
+been gaining increasing relevance in the advance of theoretical\cite{YZKS16,
+  Tigik2017b}, computational\cite{Donnert2014,Pezzi2018}, and experimental
+\cite{Howes2018,Peterson2019} plasma physics research.
+
+A recent example
+of this complementarity is presented in Ref. \cite{Peterson2019}, where the
+authors reproduced in the laboratory a magnetic structure called \emph{Parker spiral}, which is
+related to the acceleration process of solar - and stellar - winds. The
+authors compare their results with numerical simulation of the same
+structure, since in situ observations of this particular phenomena are not
+available yet. In Ref. \cite{Chen2019}, we have the opposite situation.
 
@@
 % spectroscopy turned the solar system into Earth's space physics laboratory.
-
-A recent example of this complementarity is
-presented in Ref. \cite{Peterson2019}, where the authors reproduced in the
-laboratory a magnetic structure called \emph{Parker spiral}, which is
-related to the acceleration process of solar - and stellar - winds. The
-authors compare their results with numerical simulation of the same
-structure, since in situ observations of this particular phenomena are not
-available yet. In Ref. \cite{Chen2019}, we have the opposite situation.
 

### 2019-08-04 thesis.tex
*** empty log message ***

@@
 physics became an essential component in the multidisciplinary framework of
-astrophysics. At the same time, observations of space plasma phenomena have
-been gaining increasing relevance in the advance of theoretical\cite{YZKS16,
-  Tigik2017b}, computational\cite{Donnert2014,Pezzi2018}, and experimental
-\cite{Howes2018,Peterson2019} plasma physics research.
+astrophysics \cite{Parker1958a,Alfven1961,Gailitis1964}. At the same time,
+observations of space plasma phenomena have been gaining increasing relevance
+in the progress of theoretical, computational, and experimental plasma physics
+research. The quality and quantity of space observations led to the development
+of new theoretical models, and more advanced numerical schemes and experimental
+set-ups in the area of plasma physics \cite{YZKS16,Donnert2014,Pezzi2018,
+  Howes2018,Peterson2019}.
 

### 2019-08-05 thesis.tex
*** empty log message ***

--- 2019-08-04 thesis.tex
@@
 physics became an essential component in the multidisciplinary framework of
-astrophysics. At the same time, observations of space plasma phenomena have
-been gaining increasing relevance in the advance of theoretical\cite{YZKS16,
-  Tigik2017b}, computational\cite{Donnert2014,Pezzi2018}, and experimental
-\cite{Howes2018,Peterson2019} plasma physics research.
-
-A recent example
-of this complementarity is presented in Ref. \cite{Peterson2019}, where the
-authors reproduced in the laboratory a magnetic structure called \emph{Parker spiral}, which is
-related to the acceleration process of solar - and stellar - winds. The
-authors compare their results with numerical simulation of the same
-structure, since in situ observations of this particular phenomena are not
-available yet. In Ref. \cite{Chen2019}, we have the opposite situation.
+astrophysics \cite{Alfven1950,Parker1956,Alfven1961,Gailitis1964}. At the
+same time, the analysis and interpretation of observational data have been
+gaining increasing relevance in the progress of theoretical, computational,
+and experimental plasma physics research \cite{YZKS16,Donnert2014,Pezzi2018,
+  Howes2018,Peterson2019}. This interconnection between plasma physics and
+astrophysics was scrutinized by Hannes Alfvén, 1970's Nobel prize winner
+plasma physicist, in a Physics Today's article \cite{Alfven1971} in 1971.
 
@@
 % areas is the solar physics. The accessibility of the solar plasma to direct,
-% in situ measurements, highly resolved remote sensing and high-resolution
+% in siztu measurements, highly resolved remote sensing and high-resolution
 % spectroscopy turned the solar system into Earth's space physics laboratory.

### 2019-08-06 thesis.tex
*** empty log message ***

@@
 
-Since the pervasiveness of the plasma state in space came as a fact, plasma
-physics became an essential component in the multidisciplinary framework of
-astrophysics \cite{Alfven1950,Parker1956,Alfven1961,Gailitis1964}. At the
-same time, the analysis and interpretation of observational data have been
-gaining increasing relevance in the progress of theoretical, computational,
-and experimental plasma physics research \cite{YZKS16,Donnert2014,Pezzi2018,
-  Howes2018,Peterson2019}. This interconnection between plasma physics and
-astrophysics was scrutinized by Hannes Alfvén, 1970's Nobel prize winner
-plasma physicist, in a Physics Today's article \cite{Alfven1971} in 1971.
-
-% Since the ubiquity of plasmas in space came as a fact, astrophysicists and
-% plasma physicists have been noticing an increasing necessity for exchanging
-% knowledge and mutually collaborating with their results. A particular field
-% of research that has been acting for a long time as a bridge between these two
-% areas is the solar physics. The accessibility of the solar plasma to direct,
-% in siztu measurements, highly resolved remote sensing and high-resolution
-% spectroscopy turned the solar system into Earth's space physics laboratory.
-
-% The absolute majority of the plasma observed in space is far away from us,
-% being accessible only through analysis of the electromagnetic spectrum
-% emitted from their quite remote location. A fortunate exception to this
-% fact is the plasma in our solar system.
+As soon as the pervasiveness of the plasma state in space came as a fact,
+plasma physics began to be recognized as an essential component in the
+multidisciplinary framework of astrophysics \cite{Alfven1950,Parker1956,
+  Alfven1961,Gailitis1964,Alfven1971}. At the same time, the analysis and
+interpretation of observational data started to have increasing relevance
+in the progress of theoretical, computational, and experimental plasma
+physics research \cite{YZKS16,Donnert2014,Pezzi2018,Howes2018,Peterson2019}.
+In this context of mutual collaboration, the solar and interplanetary
+plasma research has a pivotal contribution. The accessibility to direct,
+in situ measurements, highly resolved remote sensing and high-resolution
+spectroscopy, turned the solar system into a space plasma laboratory.
+Processes like magnetic reconnection, particle acceleration, shocks, and
+turbulence can be "closely" observed by space probes, and the understanding
+acquired may be extended or adapted to address similar phenomena observed
+in remote astrophysical environments \cite{NAP10477}.
+
+The analysis presented in this doctoral thesis was analyzed in the context
+of solar physics. 
+% In this appendix we present a brief discussion on the current state-of-art
+% solar physics and
 

### 2019-08-07 thesis.tex
*** empty log message ***

@@
 
-Astrophysical plasmas\footnote{In the literature, the term ``astrophysical
-  plasma'' is sometimes used to refer to the plasma observed outside the solar
-  system, while ``space plasma'' is used to account for the plasma in our
-  interplanetary space. In this text, however, both terms are being used as
-  synonyms.} are observed in a vast range of densities, temperatures, magnetic
-fields, ionization degree, and scale lengths\footnote{A comprehensive
-  description of the scales and characteristics of cosmic plasmas can be seen
-  in Section 1.2 of Ref. \cite{peratt2014}.}. Starting in the outer layers of
-Earth's atmosphere, passing through the solar wind in the interplanetary space,
-to the stellar interiors and atmospheres, accretion disks, and molecular clouds
-it is estimated that something around $99 \sim 99.9\%$ of the observable matter
-in the universe is in the plasma state. Under cosmic conditions, even the weakly
-ionized gas of the neutral hydrogen regions around galaxies or in the atmosphere
-of cold stars have a strong reaction to electromagnetic fields, exhibiting the
-characteristic collective behavior of plasmas and, therefore, are also considered
-plasmas\cite{tsypa,may,peratt2014}.
+% \footnote{In the literature, the term ``astrophysical
+%   plasma'' is sometimes used to refer to the plasma observed outside the solar
+%   system, while ``space plasma'' is used to account for the plasma in our
+%   interplanetary space. In this text, however, both terms are being used as
+%   synonyms.}
+
+% \footnote{A comprehensive description of the scales and characteristics of
+%   cosmic plasmas can be seen in Section 1.2 of Ref. \cite{peratt2014}.}
+
+Astrophysical plasmas are observed in a vast range of densities, temperatures,
+magnetic fields, ionization degree, and scale lengths\cite{peratt2014}. Starting
+in the outer layers of Earth's atmosphere, passing through the solar wind in the
+interplanetary space, to the stellar interiors and atmospheres, accretion disks,
+and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of the
+observable matter in the universe is in the plasma state. Under cosmic conditions,
+even the weakly ionized gas of the neutral hydrogen regions around galaxies or in
+the atmosphere of cold stars have a strong reaction to electromagnetic fields,
+exhibiting the characteristic collective behavior of plasmas and, therefore, are
+also considered plasmas\cite{tsypa,may,peratt2014}.
 
@@
 
-The analysis presented in this doctoral thesis was analyzed in the context
-of solar physics. 
-% In this appendix we present a brief discussion on the current state-of-art
-% solar physics and
+The theory developed during this graduate research analyses the combined
+action of nonlinear kinetic instabilities and collisional processes in
+the context of solar physics. To contextualize our work within the solar
+plasma research, in this appendix, we present a brief review of the
+current state-of-art of solar physics, followed by a discussion on the
+plasma phenomena related to our study.
 
@@
 \label{sec:solar-physics}
+The solar system is permeated with a constant plasma flow of solar origin.
+This tenuous and rapid flowing plasma is the solar wind. It enfolds the Earth
+as it travels outward the solar system, creating a region around the Sun that
+extends to approximately $140\unit{AU}$ in the surrounding galactic space.
+This region, called heliosphere, is the domain of solar and space physics. In
+the boundaries of the heliosphere, the outward pressure of the solar plasma
+balances the inward pressure from the interstellar medium. This interface
+region, the heliopause, limits the volume in the galactic environment that is
+under the influence of the solar wind \cite{NAP13060}. A general depiction of
+the heliosphere and its main boundaries is depicted in \autoref{figD1}, where
+the termination shock separates the inner and outer regions of the heliosphere.
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{Heliosphere_main_Boundaries}
+    \caption{Main boundaries of the heliosphere.
+      {\footnotesize Credit:}
+      \href{https://science.nasa.gov/heliophysics/focus-areas/heliosphere}
+      {\footnotesize NASA}{\footnotesize , accessed at 07/08/2019}.}
+    \label{figD1}
+  \end{center}
+\end{figure}
+
 Solar physics can be thought of as a combination of plasma and space physics.
-The wide variety of plasmas and the accessibility to direct, in situ measurements,
-highly resolved remote sensing and high-resolution spectroscopy turned the solar
-system into Earth's plasma physics laboratory in space.
-%% falar sobre como física sola pode contribuir para fśica de plasmas em geral
-
-The solar system is permeated with a constant plasma flow of solar origin.
-This tenuous and rapid flowing plasma, know as \emph{solar wind}, is
-expelled
-
-% The Sun is a G2 main-sequence star. From the stellar astrophysics point
-% of view, it is considered ordinary, without any unique property that could
-% differentiate it from other main-sequence stars; except for the fact that
-% it is remarkably close to us. These two facts make the Sun a perfect model
-% of study not only for several areas of astrophysics, like stellar structure
-% and evolution, but also for plasma physics.
 
@@
       {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
-    \label{figD1}
+    \label{figD2}
   \end{center}
 \end{figure}
-
-% The theory developed during this graduate research makes use of solar physics
-% results to contribute on both sides. In \cite{Tigik2016a},
-% \cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
-% numerical evidence of plasma processes that might aid in the interpretation
-% and accurate modeling  of phenomena observed in the solar plasma. While in
-% \cite{Tigik2017a}, we introduce a new equation depicting an unknown process
-% and numerically analyze it in the context of solar physics; its existence
-% outside theory, however, will depend on the development of more advanced
-% space probes to be confirmed.
 

### 2019-08-08 thesis.tex
new text

@@
 \label{sec:solar-physics}
-The solar system is permeated with a constant plasma flow of solar origin.
-This tenuous and rapid flowing plasma is the solar wind. It enfolds the Earth
-as it travels outward the solar system, creating a region around the Sun that
-extends to approximately $140\unit{AU}$ in the surrounding galactic space.
-This region, called heliosphere, is the domain of solar and space physics. In
-the boundaries of the heliosphere, the outward pressure of the solar plasma
-balances the inward pressure from the interstellar medium. This interface
-region, the heliopause, limits the volume in the galactic environment that is
-under the influence of the solar wind \cite{NAP13060}. A general depiction of
-the heliosphere and its main boundaries is depicted in \autoref{figD1}, where
-the termination shock separates the inner and outer regions of the heliosphere.
-
+The domain of solar and space physics is the \emph{heliosphere}, a cavity in
+the interstellar medium, created by the constant supersonic flow of solar
+plasma that permeates the interplanetary space. This region encloses the solar
+system and extends for approximately $140\unit{AU}$ in the surrounding galactic
+space. Its outer limit is the \emph{heliopause}, an interface zone where the
+outgoing pressure of the solar plasma balances the incoming pressure from the
+interstellar medium. This comet-shaped plasma bubble, has an inner boundary, the
+\emph{termination shock}, which delimits the sphere of absolute influence of the
+solar plasma. Outside the termination shock, the solar wind particles start to
+be subjected to increasing external pressure, transitioning to a subsonic flow
+that blends with the interstellar medium at roughly $100\unit{AU}$ from the Sun.
+Beyond the termination shock, lies the heliosheath, a so-far-unexplored zone
+that extends out to the heliopause, separating the solar domain from the nearby
+galactic region \cite{NAP13060}. In \autoref{figD1}, we have a depiction of the
+regions and boundaries described above, and the current location of both Voyager
+missions, that are already outside the heliosphere, in the interstellar space.
 \begin{figure}[h]
   \begin{center}
-    \includegraphics[width=0.48\textwidth]{Heliosphere_main_Boundaries}
-    \caption{Main boundaries of the heliosphere.
+    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
+    \caption{Main boundaries of the heliosphere and the location of both
+      Voyager missions.}
       {\footnotesize Credit:}
-      \href{https://science.nasa.gov/heliophysics/focus-areas/heliosphere}
-      {\footnotesize NASA}{\footnotesize , accessed at 07/08/2019}.}
+      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
+      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
     \label{figD1}

### 2019-08-08 thesis.tex
* thesis.tex: Summary: new text

@@
 outgoing pressure of the solar plasma balances the incoming pressure from the
-interstellar medium. This comet-shaped plasma bubble, has an inner boundary, the
-\emph{termination shock}, which delimits the sphere of absolute influence of the
-solar plasma. Outside the termination shock, the solar wind particles start to
-be subjected to increasing external pressure, transitioning to a subsonic flow
-that blends with the interstellar medium at roughly $100\unit{AU}$ from the Sun.
-Beyond the termination shock, lies the heliosheath, a so-far-unexplored zone
-that extends out to the heliopause, separating the solar domain from the nearby
-galactic region \cite{NAP13060}. In \autoref{figD1}, we have a depiction of the
-regions and boundaries described above, and the current location of both Voyager
-missions, that are already outside the heliosphere, in the interstellar space.
+interstellar medium. This comet-shaped plasma bubble \cite{Dialynas2017}, has
+an inner boundary, the \emph{termination shock}, which delimits the sphere
+of absolute influence of the solar plasma. Beyond the termination shock, at
+roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
+heliosheath. In this region, the solar wind particles start being subjected to
+increasing external pressure, transitioning to a subsonic, turbulent flow that
+blends and interacts directly with the matter in the local interstellar medium
+\cite{NAP13060}. In \autoref{figD1}, we have a depiction of the regions and
+boundaries described above, and the current location of both Voyager missions,
+that are already outside the heliosphere, in the interstellar space.
 \begin{figure}[h]
@@
 
-Solar physics can be thought of as a combination of plasma and space physics.
+Inside the heliosphere, the solar and space physics research aims to understand
+the history, evolution and dynamics of the Sun and its effects on Earth's space
+environment. Besides that, the interplanetary system provide an accessible
+
+subjected to direct and relatively close action of
+the solar wind and radiation, lies our planet, Earth.
+
+The energy the Sun
+dumps over the Earth, in the form of visible light, ultraviolet and X-ray
+radiation, not only determines the temperature, shape of the terrestrial
+upper atmosphere and ionosphere, but also is responsible for the life as
+we know it.
 

### 2019-08-09 thesis.tex
*** empty log message ***

--- 2019-08-08 thesis.tex
@@
 Processes like magnetic reconnection, particle acceleration, shocks, and
-turbulence can be "closely" observed by space probes, and the understanding
+turbulence can be closely observed by space probes, and the understanding
 acquired may be extended or adapted to address similar phenomena observed
@@
 plasma that permeates the interplanetary space. This region encloses the solar
-system and extends for approximately $140\unit{AU}$ in the surrounding galactic
-space. Its outer limit is the \emph{heliopause}, an interface zone where the
-outgoing pressure of the solar plasma balances the incoming pressure from the
-interstellar medium. This comet-shaped plasma bubble, has an inner boundary, the
-\emph{termination shock}, which delimits the sphere of absolute influence of the
-solar plasma. Outside the termination shock, the solar wind particles start to
-be subjected to increasing external pressure, transitioning to a subsonic flow
-that blends with the interstellar medium at roughly $100\unit{AU}$ from the Sun.
-Beyond the termination shock, lies the heliosheath, a so-far-unexplored zone
-that extends out to the heliopause, separating the solar domain from the nearby
-galactic region \cite{NAP13060}. In \autoref{figD1}, we have a depiction of the
-regions and boundaries described above, and the current location of both Voyager
-missions, that are already outside the heliosphere, in the interstellar space.
+system and extends for approximately $140\unit{AU}$\footnote{$1\unit{AU}=150
+  \times 10^6\unit{km}$, where AU means \emph{astronomical unit}, which is
+  defined as the mean distance between the Sun and the Earth.} in the
+surrounding galactic space. Its outer limit is the \emph{heliopause}, an
+interface zone where the outgoing pressure of the solar plasma balances the
+incoming pressure from the interstellar medium. This comet-shaped plasma bubble
+\cite{Dialynas2017}, has an inner boundary, the \emph{termination shock}, which
+delimits the sphere of absolute influence of the solar plasma. Beyond the
+termination shock, at roughly $100\unit{AU}$ from the Sun, extending out to the
+heliopause, is the heliosheath. In this region, the solar wind particles start
+being subjected to increasing external pressure, transitioning to a subsonic,
+turbulent flow that blends and interacts directly with the matter in the local
+interstellar medium \cite{NAP13060}. In \autoref{figD1}, we have a depiction of
+the regions and boundaries described above, and the current location of both
+Voyager missions, that are already outside the heliosphere, in the interstellar
+space.
 \begin{figure}[h]
@@
 
-Solar physics can be thought of as a combination of plasma and space physics.
+As described above, particles ejected by the Sun determine the overall
+dynamics of the interplanetary space until the termination shock boundary.
+Beyond this boundary, the solar wind still has a significant influence on
+the nature of the local interstellar space for a long distance up to the
+heliopause. As a well established scientific discipline, solar and space
+physics aims to understand the history, evolution, and physical behavior
+of the most influential object in - and its impact on the dynamics of -
+the space environment around our home planet.
+
+% is not only
+% a matter of scientific curiosity.
+% Therefore, as a well established scientific discipline,
+% solar and space physics aims to understand the history, evolution, and
+% physical behavior of the most influential object in the space environment
+% around our home planet.
 

### 2019-08-10 thesis.tex
*** empty log message ***

@@
 dynamics of the interplanetary space until the termination shock boundary.
-Beyond this boundary, the solar wind still has a significant influence on
+Beyond this limit, the solar wind still has a significant influence on
 the nature of the local interstellar space for a long distance up to the
 heliopause. As a well established scientific discipline, solar and space
-physics aims to understand the history, evolution, and physical behavior
-of the most influential object in - and its impact on the dynamics of -
-the space environment around our home planet.
-
-% is not only
-% a matter of scientific curiosity.
-% Therefore, as a well established scientific discipline,
-% solar and space physics aims to understand the history, evolution, and
-% physical behavior of the most influential object in the space environment
-% around our home planet.
+physics can be summarized as to understand the history, evolution, and
+physical processes of the most influential object in the space environment
+around our home planet and its interaction with the solar system and the
+interstellar medium.
 
@@
   \begin{center}
-    \includegraphics[width=0.48\textwidth]{corona2017.png}
-    \includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
+    \includegraphics[width=0.9\textwidth]{corona2017.png}
+    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
     \caption{Solar corona captured during the total solar eclipse of 2017.

### 2019-08-10 thesis.tex
saving this version for any reason

@@
 plasma research, in this appendix, we present a brief review of the
-current state-of-art of solar physics, followed by a discussion on the
-plasma phenomena related to our study.
+current state-of-art of solar and space physics research, followed by a
+discussion on the solar plasma phenomena related to our study.
 
@@
 the interstellar medium, created by the constant supersonic flow of solar
-plasma that permeates the interplanetary space. This region encloses the solar
-system and extends for approximately $140\unit{AU}$\footnote{$1\unit{AU}=150
-  \times 10^6\unit{km}$, where AU means \emph{astronomical unit}, which is
-  defined as the mean distance between the Sun and the Earth.} in the
-surrounding galactic space. Its outer limit is the \emph{heliopause}, an
-interface zone where the outgoing pressure of the solar plasma balances the
-incoming pressure from the interstellar medium. This comet-shaped plasma bubble
-\cite{Dialynas2017}, has an inner boundary, the \emph{termination shock}, which
-delimits the sphere of absolute influence of the solar plasma. Beyond the
-termination shock, at roughly $100\unit{AU}$ from the Sun, extending out to the
-heliopause, is the heliosheath. In this region, the solar wind particles start
-being subjected to increasing external pressure, transitioning to a subsonic,
-turbulent flow that blends and interacts directly with the matter in the local
-interstellar medium \cite{NAP13060}. In \autoref{figD1}, we have a depiction of
-the regions and boundaries described above, and the current location of both
-Voyager missions, that are already outside the heliosphere, in the interstellar
-space.
+plasma that permeates the interplanetary space. This region encloses the
+solar system and extends for approximately $140\unit{AU}$\footnote{An AU
+  (astronomical unit) is defined as the mean distance between the Sun and
+  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
+galactic space. Its outer limit is the \emph{heliopause}, an interface zone
+where the outgoing pressure of the solar plasma balances the incoming pressure
+from the interstellar medium. This comet-shaped plasma bubble \cite{Dialynas2017},
+has an inner boundary, the \emph{termination shock}, which delimits the sphere
+of absolute influence of the solar plasma. Beyond the termination shock, at
+roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
+heliosheath. In this region, the solar wind particles start being subjected to
+increasing external pressure, transitioning to a subsonic, turbulent flow that
+blends and interacts directly with the matter in the local interstellar medium
+\cite{NAP13060}. In \autoref{figD1}, we have a depiction of the regions and
+boundaries described above, and the current location of both Voyager missions,
+that are already outside the heliosphere, in the interstellar space.
 \begin{figure}[h]
@@
 heliopause. As a well established scientific discipline, solar and space
-physics can be summarized as to understand the history, evolution, and
-physical processes of the most influential object in the space environment
-around our home planet and its interaction with the solar system and the
-interstellar medium.
+physics work towards developing a better understanding of this vast and
+complex dynamic system called heliosphere; where, within, very close to
+its most influential object, lies our home planet - Earth.
+
+\subsection{Main topics of solar and space physics research}
+\label{topics}
 

### 2019-08-10 thesis.tex
included figures
* thesis.tex: Summary: saving this version for any reason

@@
 heliopause. As a well established scientific discipline, solar and space
-physics work towards developing a better understanding of this vast and
-complex dynamic system called heliosphere; where, within, very close to
-its most influential object, lies our home planet - Earth.
-
-\subsection{Main topics of solar and space physics research}
+physics work towards developing a better understanding of the Sun and
+the solar processes molding this vast and complex dynamic system called
+heliosphere; where, within, very close to its most influential object,
+lies our home planet - Earth.
+
+\subsection{Solar and space physics research}
 \label{topics}
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
+    \caption{ESA's past, present, and future science missions for studying the solar system.}
+      {\footnotesize Credit:}
+      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
+      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
+    \label{figD1}
+  \end{center}
+\end{figure}
+
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
+    \caption{NASA's present and future heliophysics system observatory. The number
+      between parenthesis under the probe's name is the total number of spacecrafts
+      that compose the mission.}
+      {\footnotesize Credit:}
+      \href{https://science.nasa.gov/heliophysics}
+      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
+    \label{figD1}
+  \end{center}
+\end{figure}
 

### 2019-08-11 thesis.tex
*** empty log message ***

@@
 
+Inside the heliosphere, objectives of solar and space physics are
+understanding the evolution and dynamics of the Sun,
+
+\subsection{Solar and space physics research}
+\label{sec:topics}
+
 As described above, particles ejected by the Sun determine the overall
-dynamics of the interplanetary space until the termination shock boundary.
+dynamics of the interplanetary medium until the termination shock boundary.
 Beyond this limit, the solar wind still has a significant influence on
@@
 heliopause. As a well established scientific discipline, solar and space
-physics work towards developing a better understanding of the Sun and
+physics work towards developing a better comprehension of the Sun and
 the solar processes molding this vast and complex dynamic system called
-heliosphere; where, within, very close to its most influential object,
-lies our home planet - Earth.
-
-\subsection{Solar and space physics research}
-\label{topics}
+heliosphere.
+
+% ; where, within, very close to its most influential object,
+% lies our home planet - Earth.
 
@@
       {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
-    \label{figD1}
+    \label{esa}
   \end{center}
@@
       {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
-    \label{figD1}
+    \label{nasa}
   \end{center}
 \end{figure}
+
+\subsection{The Sun and its effects on the near-Earth environment}
+\label{sec:sun}
 
@@
       {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
-    \label{figD2}
+    \label{corona}
   \end{center}

### 2019-08-12 thesis.tex
last night!
* thesis.tex: Summary: last night, she said...

@@
 
-Inside the heliosphere, objectives of solar and space physics are
-understanding the evolution and dynamics of the Sun,
-
-\subsection{Solar and space physics research}
-\label{sec:topics}
-
-As described above, particles ejected by the Sun determine the overall
-dynamics of the interplanetary medium until the termination shock boundary.
-Beyond this limit, the solar wind still has a significant influence on
-the nature of the local interstellar space for a long distance up to the
-heliopause. As a well established scientific discipline, solar and space
-physics work towards developing a better comprehension of the Sun and
-the solar processes molding this vast and complex dynamic system called
-heliosphere.
-
-% ; where, within, very close to its most influential object,
-% lies our home planet - Earth.
-
-\begin{figure}[h]
-  \begin{center}
-    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
-    \caption{ESA's past, present, and future science missions for studying the solar system.}
-      {\footnotesize Credit:}
-      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
-      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
-    \label{esa}
-  \end{center}
-\end{figure}
-
+The extension of the influence that the plasma ejected from the Sun has, puts
+in perspective the fundamental role played by plasma physics in the solar and
+space physics research. %% talk about some key processes
+
+Inside the heliosphere, the Sun, the space environment around Earth and the
+interplanetary medium are extensively explored by space probes.
+%% say something about it
+
+Figures
+\ref{nasa} and \ref{esa} illustrate the current space missions of NASA and the
+European Space Agency (ESA), respectively. Describing the processes assessed by
+each one of the illustrated probes it is out of the scope of this work\footnote{
+  For a complete description, of the NASA missions is available at
+\url{https://science.nasa.gov/missions-page?field_division_tid=5&field_phase_tid=All}.
+For the ESA missions, go to \url{http://sci.esa.int/home/51459-missions/}.
+  Both sites were accessed at 11/08/2019.}.
 \begin{figure}[h]
@@
 \end{figure}
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
+    \caption{ESA's past, present, and future science missions for studying the solar system.}
+      {\footnotesize Credit:}
+      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
+      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
+    \label{esa}
+  \end{center}
+\end{figure}
+% As described above, ionized particles ejected by the Sun determine the
+% overall dynamics of the interplanetary medium until the termination shock
+% boundary. Beyond this limit, the solar wind still has a significant
+% influence on the nature of the local interstellar space for a long distance
+% up to the heliopause.
+% As a well established scientific discipline, solar and space physics work
+% towards developing a better comprehension of the Sun and
+% the solar processes molding this vast and complex dynamic system called
+% heliosphere.
+
+% ; where, within, very close to its most influential object,
+% lies our home planet - Earth.
 

### 2019-08-12 thesis.tex
*** empty log message ***

@@
 \tableofcontents{\thispagestyle{empty}}
-%\listoffigures{\thispagestyle{empty}}
+\listoffigures{\thispagestyle{empty}}
 \pagestyle{fancy}
@@
 roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
-heliosheath. In this region, the solar wind particles start being subjected to
-increasing external pressure, transitioning to a subsonic, turbulent flow that
+\emph{heliosheath}. In this region, the solar wind particles start being subjected
+to increasing external pressure, transitioning to a subsonic, turbulent flow that
 blends and interacts directly with the matter in the local interstellar medium
@@
 
-The extension of the influence that the plasma ejected from the Sun has, puts
-in perspective the fundamental role played by plasma physics in the solar and
-space physics research. %% talk about some key processes
+The fundamental questions of heliophysics start right in the Sun and the
+magnetic dynamo processes involved in the generation and variability of
+magnetic fields in the Sun, and how it determines the dynamics of the
+11-year solar cycle of sunspots. The appearance of sunspots is a sign of
+solar activity, characterized by solar flares and coronal mass ejections.
+
+This enhanced flux of energetic particles and radiation have direct impact
+in the \emph{space weather} around Earth, triggering geomagnetic storms
+that
 

### 2019-08-13 thesis.tex
*** empty log message ***

@@
 
-The fundamental questions of heliophysics start right in the Sun and the
-magnetic dynamo processes involved in the generation and variability of
-magnetic fields in the Sun, and how it determines the dynamics of the
-11-year solar cycle of sunspots. The appearance of sunspots is a sign of
-solar activity, characterized by solar flares and coronal mass ejections.
-
-This enhanced flux of energetic particles and radiation have direct impact
-in the \emph{space weather} around Earth, triggering geomagnetic storms
-that
-
-Inside the heliosphere, the Sun, the space environment around Earth and the
-interplanetary medium are extensively explored by space probes.
+% Investigations of the origin and behavior of the solar wind, energetic
+% particles, and magnetic fields in the heliosphere and their interaction
+% with Earth and other planets, as well as with the interstellar medium.
+% Investigations of the physics of magnetospheres, including fundamental
+% interactions of plasmas and particles with fields and waves, and coupling
+% to the solar wind and ionospheres.
+% Investigations of the physics of the terrestrial mesosphere, thermosphere,
+% ionosphere, including the coupling of these phenomena to the lower atmosphere
+% and magnetosphere.
+The major questions being studied by the international heliophysics community
+involve the solar dynamics, the origin and evolution of the solar wind,
+energetic particles and magnetic fields, and how they interact with Earth,
+other planetary bodies and the interstellar medium. % In the list below we
+% highlight the most Ref. \cite{schrijver2009}. 
+% are listed below:
+\begin{itemize}
+\item The magnetic dynamo processes involved in the generation and variability
+  of magnetic fields in the Sun, and how it determines the dynamics of the
+  11-year solar cycle of solar activity \cite{Charbonneau2005};
+\item The role of magnetic reconnection in the coronal mass ejection process
+  \cite{Qiu2005};
+\item The coronal heating problem \cite{Vinas2000,PP14,Pezzi2017};
+\item   
+\end{itemize}
+
+The heliophysics research, as expected by the very definition of the heliosphere,
+involves the study of a rich diversity of plasma phenomena. 
+% % The appearance of sunspots is a sign of
+% % solar activity, characterized by solar flares and coronal mass ejections.
+
+% This enhanced flux of energetic particles and radiation have direct impact
+% in the \emph{space weather} around Earth, triggering geomagnetic storms
+% that
+
+% Inside the heliosphere, the Sun, the space environment around Earth and the
+% interplanetary medium are extensively explored by space probes.
 %% say something about it

### 2019-08-13 thesis.tex
*** empty log message ***

--- 2019-08-12 thesis.tex
@@
 
-The fundamental questions of heliophysics start right in the Sun and the
-magnetic dynamo processes involved in the generation and variability of
-magnetic fields in the Sun, and how it determines the dynamics of the
-11-year solar cycle of sunspots. The appearance of sunspots is a sign of
-solar activity, characterized by solar flares and coronal mass ejections.
-
-This enhanced flux of energetic particles and radiation have direct impact
-in the \emph{space weather} around Earth, triggering geomagnetic storms
-that
-
-Inside the heliosphere, the Sun, the space environment around Earth and the
-interplanetary medium are extensively explored by space probes.
-%% say something about it
+The ultimate goal of heliophysics can be summarized as the search for a
+better understanding of the solar dynamics and how it affects the Earth,
+other planetary bodies, and the interstellar medium. The heliosphere is
+a coupled system, where different interacting elements that might look
+unrelated at first sight are connected by underlying plasma processes
+\cite{NAP13060}. A great example of this interconnection is the relation
+between the appearance of sunspots and the occurrence of non-recurrent
+geomagnetic storms, which are the most intense space weather disturbances.
+Evidence of such relationship started to appear at the end of the $19$th
+century. The correct hypothesis (coronal mass ejections associated with
+solar flares), however, which depended on advances in plasma physics
+theory, came along only in $1929$ \cite{chapman1929cosmical,Koskinen2011}.
+
+A better comprehension of the Sun and the dynamic space around our planet
+goes beyond the pure scientific curiosity. It is true that this accessible
+space physics laboratory can lead to discoveries that can be applied and
+extended to remote cosmic systems. But the primary reason behind the
+international effort (see Figures \ref{nasa} and \ref{esa}) on understanding
+the complex physics of the Sun and the interplanetary space, is to enable
+means to predict the occurrence and intensity of solar activity. This may
+open the possibility of developing reliable space-weather forecasts that
+may help us to protect satellites, humans
+
+\begin{itemize}
+\item The magnetic dynamo processes involved in the generation and variability
+  of magnetic fields in the Sun, and how it determines the dynamics of the
+  11-year solar cycle of solar activity \cite{Charbonneau2005};
+\item The role of magnetic reconnection in the coronal mass ejection process
+  \cite{Qiu2005};
+\item The coronal heating problem \cite{Vinas2000,PP14,Pezzi2017};
+\item   
+\end{itemize}
 

### 2019-08-14 thesis.tex
very close to the end

@@
 plasma research, in this appendix, we present a brief review of the
-current state-of-art of solar and space physics research, followed by a
-discussion on the solar plasma phenomena related to our study.
+current state-of-the-art of solar and space physics research, followed
+by a discussion on the solar plasma phenomena related to our study.
 
@@
 \label{sec:solar-physics}
-The domain of solar and space physics is the \emph{heliosphere}, a cavity in
-the interstellar medium, created by the constant supersonic flow of solar
+The domain of solar and space physics is the \emph{heliosphere}, a cavity
+in the interstellar medium, created by the constant supersonic flow of solar
 plasma that permeates the interplanetary space. This region encloses the
@@
   Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
-galactic space. Its outer limit is the \emph{heliopause}, an interface zone
-where the outgoing pressure of the solar plasma balances the incoming pressure
-from the interstellar medium. This comet-shaped plasma bubble \cite{Dialynas2017},
-has an inner boundary, the \emph{termination shock}, which delimits the sphere
-of absolute influence of the solar plasma. Beyond the termination shock, at
-roughly $100\unit{AU}$ from the Sun, extending out to the heliopause, is the
-\emph{heliosheath}. In this region, the solar wind particles start being subjected
-to increasing external pressure, transitioning to a subsonic, turbulent flow that
-blends and interacts directly with the matter in the local interstellar medium
-\cite{NAP13060}. In \autoref{figD1}, we have a depiction of the regions and
-boundaries described above, and the current location of both Voyager missions,
-that are already outside the heliosphere, in the interstellar space.
+galactic space. Its outer limit is the \emph{heliopause}, an interface
+zone where the outgoing pressure of the solar plasma balances the incoming
+pressure from the interstellar medium. This comet-shaped plasma bubble
+\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
+which delimits the sphere of absolute influence of the solar plasma. Beyond
+the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
+out to the heliopause, lies the \emph{heliosheath}. In this region, the
+solar wind particles start being subjected to increasing external pressure,
+transitioning to a subsonic, turbulent flow that blends and interacts
+directly with the matter in the local interstellar medium \cite{NAP13060}.
+In \autoref{figD1}, we have a depiction of the regions and boundaries
+described above, and the current location of both Voyager missions, that
+are already outside the heliosphere, in the interstellar space.
 \begin{figure}[h]
   \begin{center}
-    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
+    \includegraphics[width=0.89\textwidth]{solar_system_env.png}
     \caption{Main boundaries of the heliosphere and the location of both
@@
 Evidence of such relationship started to appear at the end of the $19$th
-century. The correct hypothesis (coronal mass ejections associated with
-solar flares), however, which depended on advances in plasma physics
-theory, came along only in $1929$ \cite{chapman1929cosmical,Koskinen2011}.
-
+century. However, the correct hypothesis supporting this correlation
+(coronal mass ejections associated with solar flares), which depended
+on advances in plasma physics theory, came along only in $1929$
+\cite{chapman1929cosmical,Koskinen2011}.
+
+\subsection{The Sun and the near-Earth environment}
+\label{sec:sun}
 A better comprehension of the Sun and the dynamic space around our planet
-goes beyond the pure scientific curiosity. It is true that this accessible
-space physics laboratory can lead to discoveries that can be applied and
-extended to remote cosmic systems. But the primary reason behind the
-international effort (see Figures \ref{nasa} and \ref{esa}) on understanding
-the complex physics of the Sun and the interplanetary space, is to enable
-means to predict the occurrence and intensity of solar activity. This may
-open the possibility of developing reliable space-weather forecasts that
-may help us to protect satellites, humans
-
-\begin{itemize}
-\item The magnetic dynamo processes involved in the generation and variability
-  of magnetic fields in the Sun, and how it determines the dynamics of the
-  11-year solar cycle of solar activity \cite{Charbonneau2005};
-\item The role of magnetic reconnection in the coronal mass ejection process
-  \cite{Qiu2005};
-\item The coronal heating problem \cite{Vinas2000,PP14,Pezzi2017};
-\item   
-\end{itemize}
-
-Figures
-\ref{nasa} and \ref{esa} illustrate the current space missions of NASA and the
-European Space Agency (ESA), respectively. Describing the processes assessed by
-each one of the illustrated probes it is out of the scope of this work\footnote{
-  For a complete description, of the NASA missions is available at
+goes beyond the pure scientific curiosity. This accessible space physics
+laboratory can indeed lead to discoveries that can be applied and extended
+to remote cosmic systems. However, the primary reason behind the international
+effort\footnote{A complete description, of NASA's missions is available at
 \url{https://science.nasa.gov/missions-page?field_division_tid=5&field_phase_tid=All}.
-For the ESA missions, go to \url{http://sci.esa.int/home/51459-missions/}.
-  Both sites were accessed at 11/08/2019.}.
+For ESA's missions, go to \url{http://sci.esa.int/home/51459-missions/}.
+Both websites were accessed at 11/08/2019.} (see Figures \ref{nasa} and \ref{esa}
+) on understanding the complex physics of the Sun and interplanetary space
+is to unlock means of predicting the occurrence and intensity of solar activity,
+and anticipate how the near-Earth environment will be affected.  On that regard,
+a critical aspect being addressed is the response of Earth’s magnetosphere,
+ionosphere, and atmosphere to solar inputs. The objective is to open the
+possibility of developing reliable models for the space weather forecast.
+Forecasting space weather may help us to protect humans and electronic equipment
+in space from the incoming flux of energetic ionized matter and radiation coming
+from the Sun, and ground-based technological infrastructure from the geomagnetic
+storms they cause \cite{NAP13060}.
 \begin{figure}[h]
   \begin{center}
-    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
+    \includegraphics[width=0.89\textwidth]{hso_fleet_chart_april_2019.pdf}
     \caption{NASA's present and future heliophysics system observatory. The number
@@
 \end{figure}
+
 \begin{figure}[h]
   \begin{center}
-    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
+    \includegraphics[width=0.89\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
     \caption{ESA's past, present, and future science missions for studying the solar system.}
@@
 \end{figure}
-% As described above, ionized particles ejected by the Sun determine the
-% overall dynamics of the interplanetary medium until the termination shock
-% boundary. Beyond this limit, the solar wind still has a significant
-% influence on the nature of the local interstellar space for a long distance
-% up to the heliopause.
-% As a well established scientific discipline, solar and space physics work
-% towards developing a better comprehension of the Sun and
-% the solar processes molding this vast and complex dynamic system called
-% heliosphere.
-
-% ; where, within, very close to its most influential object,
-% lies our home planet - Earth.
-
-\subsection{The Sun and its effects on the near-Earth environment}
-\label{sec:sun}
+
+Another important aspect... blah blah blah whiskas sachet... solar corona.
+Talk about my work then corro pra galera
 
@@
   \begin{center}
-    \includegraphics[width=0.9\textwidth]{corona2017.png}
+    \includegraphics[width=0.89\textwidth]{corona2017.png}
     %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}

### 2019-08-14 thesis.tex
*** empty log message ***

@@
   \begin{center}
-    \includegraphics[width=0.89\textwidth]{solar_system_env.png}
+    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
     \caption{Main boundaries of the heliosphere and the location of both
@@
 For ESA's missions, go to \url{http://sci.esa.int/home/51459-missions/}.
-Both websites were accessed at 11/08/2019.} (see Figures \ref{nasa} and \ref{esa}
-) on understanding the complex physics of the Sun and interplanetary space
-is to unlock means of predicting the occurrence and intensity of solar activity,
-and anticipate how the near-Earth environment will be affected.  On that regard,
-a critical aspect being addressed is the response of Earth’s magnetosphere,
-ionosphere, and atmosphere to solar inputs. The objective is to open the
-possibility of developing reliable models for the space weather forecast.
-Forecasting space weather may help us to protect humans and electronic equipment
-in space from the incoming flux of energetic ionized matter and radiation coming
-from the Sun, and ground-based technological infrastructure from the geomagnetic
-storms they cause \cite{NAP13060}.
+Both websites were accessed at 11/08/2019.} (see Figures \ref{nasa} and
+\ref{esa}) on understanding the complex physics of the Sun and interplanetary
+space is to unlock means of predicting the occurrence and intensity of solar
+activity, and anticipate how the near-Earth environment will be affected.
+Reliable forecasting of the space weather is essential for protecting
+electronic equipment, radio communications, GPS signal and humans in space
+from the effects of the interaction between the dense, magnetized plasma of
+coronal mass ejections with the geomagnetic field, and also from the
+energetic radiation emitted by solar flares \cite{NAP13060}.
 \begin{figure}[h]
   \begin{center}
-    \includegraphics[width=0.89\textwidth]{hso_fleet_chart_april_2019.pdf}
+    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
     \caption{NASA's present and future heliophysics system observatory. The number
@@
   \begin{center}
-    \includegraphics[width=0.89\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
+    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
     \caption{ESA's past, present, and future science missions for studying the solar system.}
@@
 
-Another important aspect... blah blah blah whiskas sachet... solar corona.
-Talk about my work then corro pra galera
-
 \begin{figure}[h]
   \begin{center}
-    \includegraphics[width=0.89\textwidth]{corona2017.png}
+    \includegraphics[width=0.9\textwidth]{corona2017.png}
     %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}

### 2019-08-15 thesis.tex
* thesis.tex: Summary: very close to the end

@@
   \begin{center}
-    \includegraphics[width=0.9\textwidth]{solar_system_env.png}
+    \includegraphics[width=0.892\textwidth]{solar_system_env.png}
     \caption{Main boundaries of the heliosphere and the location of both
@@
 coronal mass ejections with the geomagnetic field, and also from the
-energetic radiation emitted by solar flares \cite{NAP13060}.
-\begin{figure}[h]
+energetic radiation emitted by solar flares. Extreme coronal mass ejections
+can also cause stronger geomagnetic disturbances that may affect terrestrial
+infrastructure such as electric power grids \cite{NAP13060}.
+\begin{figure}[hb]
   \begin{center}
-    \includegraphics[width=0.9\textwidth]{hso_fleet_chart_april_2019.pdf}
+    \includegraphics[width=0.892\textwidth]{hso_fleet_chart_april_2019.pdf}
     \caption{NASA's present and future heliophysics system observatory. The number
@@
 \end{figure}
-
-\begin{figure}[h]
+\begin{figure}[ht]
   \begin{center}
-    \includegraphics[width=0.9\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
+    \includegraphics[width=0.892\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
     \caption{ESA's past, present, and future science missions for studying the solar system.}
@@
 
-\begin{figure}[h]
+\section{How all of this is related to this work?}
+\label{sec:corona}
+The source of the tenuous magnetized plasma permeating the heliosphere,
+and also the origin of the dangerous solar output disturbing the near-Earth
+environment, is the outermost layer of the Sun: the solar corona. The solar
+corona can be easily recognized as the bright halo that appears around the
+hidden Sun during solar eclipses. \autoref{corona} shows a beautiful
+photograph of the corona, taken in the $2017$’s solar eclipse. In the picture,
+one can see the moon covering the bright chromosphere, allowing us to have
+a glimpse of the thin, but ultra-hot coronal plasma.
+
+\begin{figure}[hb]
   \begin{center}
-    \includegraphics[width=0.9\textwidth]{corona2017.png}
+    \includegraphics[width=0.892\textwidth]{corona2017.png}
     %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}

### 2019-08-15 thesis.tex
*** empty log message ***

@@
 
-\section{How all of this is related to this work?}
+\subsection{The solar corona}
 \label{sec:corona}
-The source of the tenuous magnetized plasma permeating the heliosphere,
-and also the origin of the dangerous solar output disturbing the near-Earth
-environment, is the outermost layer of the Sun: the solar corona. The solar
-corona can be easily recognized as the bright halo that appears around the
-hidden Sun during solar eclipses. \autoref{corona} shows a beautiful
-photograph of the corona, taken in the $2017$’s solar eclipse. In the picture,
-one can see the moon covering the bright chromosphere, allowing us to have
-a glimpse of the thin, but ultra-hot coronal plasma.
+The source of the tenuous magnetized plasma permeating the heliosphere, and
+also the origin of solar particles and radiation that may cause disruptive
+space weather around Earth, is the outermost layer of the Sun: the solar
+corona \cite{Cranmer2017,Klein2017}. The solar corona can be easily recognized
+as the bright halo that appears around the hidden Sun during solar eclipses.
+\autoref{corona} shows two beautiful photographs of the corona, taken in two
+different solar eclipses, August 21 $2017$ and $2019$. In both pictures, one
+can see the moon covering the bright photosphere, allowing us to have a
+glimpse of the thin, but ultra-hot coronal plasma. Non-intuitively, the solar
+corona is, at the same time, the thinnest and the hottest outer layer of
+the Sun, where the temperature is of the order of $10^6\unit{K}$.
 
@@
     \includegraphics[width=0.892\textwidth]{corona2017.png}
-    %\includegraphics[width=0.4305\textwidth]{high-contrast-corona.png}
-    \caption{Solar corona captured during the total solar eclipse of 2017.
+    \includegraphics[width=0.892\textwidth]{corona2019.png}
+    \caption{Solar corona captured during the total solar eclipse of 2017 (top panel)
+      and 2019 (lower panel). The reddish contour at some regions is the chromosphere,
+      and the reddish arcs are solar prominences, chromospheric plasma structures that
+      penetrate the coronal region \cite{BenzA2002,Habbal2010,JeanVlaude2015}.
       {\footnotesize Credit:}
-      \href{https://hdr-astrophotography.com/high-resolution-2017-total-solar-eclipse/}
-      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 05/06/2019}.}
+      \href{https://hdr-astrophotography.com}
+      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 15/08/2019}.}
     \label{corona}

### 2019-08-16 thesis.tex
*** empty log message ***

@@
 \autoref{corona} shows two beautiful photographs of the corona, taken in two
-different solar eclipses, August 21 $2017$ and $2019$. In both pictures, one
-can see the moon covering the bright photosphere, allowing us to have a
-glimpse of the thin, but ultra-hot coronal plasma. Non-intuitively, the solar
-corona is, at the same time, the thinnest and the hottest outer layer of
-the Sun, where the temperature is of the order of $10^6\unit{K}$.
+different solar eclipses, August 21 $2017$ and July 2 $2019$. In both pictures,
+one can see the moon covering the bright photosphere, allowing us to have a
+glimpse of the thin, but ultra-hot coronal plasma.
+
+Counter-intuitively, the solar corona is, at the same time, the most tenuous
+and the hottest outer layer of the Sun. At the top of the chromosphere, where
+the temperature might reach $20,000\,\unit{K}$, in a relatively narrow interface,
+the \emph{solar transition region}, the plasma temperature rises abruptly to
+$\sim 10^6\,\unit{K}$ \cite{BenzA2002}. It has been almost eighty years since
+the extreme coronal temperature came as the only reasonable explanation for the
+origin of the spectral lines observed in the solar corona \cite{Hunter1942},
+in a classical case of an answer that brings a more troublesome question. 
+Since then, several mechanisms have been proposed \cite{Parker1988,Scudder92b,
+  Vinas2000,PP14}, not only to comprehend the heating of the solar corona,
+but also the acceleration of the solar wind. Another unsolved problem that is
+directly connected to the inverted temperature profile of the solar corona, is
+regarding where and how the non-Maxwellian velocity distribution functions with
+suprathermal tails, observed in the solar wind, are formed.
+
+In \cite{Tigik2017a} ...
+present a new fundamental mechanism that is capable
+the formation of suprathermal tails in the electron velocity distribution function
+
+proposing a fundamental mechanism,
+the electrostatic bremsstrahlung, that might take electrons out of the thermal
+equilibrium
 
@@
       and the reddish arcs are solar prominences, chromospheric plasma structures that
-      penetrate the coronal region \cite{BenzA2002,Habbal2010,JeanVlaude2015}.
+      penetrate the coronal region.
       {\footnotesize Credit:}

### 2019-08-16 thesis.tex
*** empty log message ***

@@
 \usepackage{enumerate}
+\usepackage[inline]{enumitem}
 %\usepackage{chngcntr}
@@
 essential role in the study of type II and type III radio bursts
-\cite{Emslie1984,Hannah2009,ZVST11,Hannah2011,KK12,RR14,BNKR14}. In this
-context, the relevance of a more accurate description of nonlinear kinetic
-instabilities in plasmas, represented here by the beam-plasma interaction,
-becomes clear.
+\cite{Emslie1984,Hannah2009,ZVST11,Hannah2011,KK12,Reid2014,BNKR14}. In
+this context, the relevance of a more accurate description of nonlinear
+kinetic instabilities in plasmas, represented here by the beam-plasma
+interaction, becomes clear.
 
@@
 and interpretation of several solar phenomena observed by space-probes \cite{
-  Vinas2000,Hannah2009,ZVST11,KRB12,KF13,RR14,Reid2015}, a fact that emphasizes
-the necessity of the development of a mathematically rigorous theory able to
-describe hybrid situations involving collective oscillations and collisional
-interactions.
+  Vinas2000,Hannah2009,ZVST11,KRB12,KF13,Reid2014,Reid2015}, a fact that
+emphasizes the necessity of the development of a mathematically rigorous
+theory able to describe hybrid situations involving collective oscillations
+and collisional interactions.
 
@@
 the context of solar physics. To contextualize our work within the solar
-plasma research, in this appendix, we present a brief review of the
-current state-of-the-art of solar and space physics research, followed
-by a discussion on the solar plasma phenomena related to our study.
+plasma research, in \autoref{sec:solar-physics} we present a brief review
+of the current research in solar and space physics, and in \autoref{res}
+we discuss how our work is related to what is pointed in the previous
+section.
 
@@
 but also the acceleration of the solar wind. Another unsolved problem that is
-directly connected to the inverted temperature profile of the solar corona, is
-regarding where and how the non-Maxwellian velocity distribution functions with
-suprathermal tails, observed in the solar wind, are formed.
-
-In \cite{Tigik2017a} ...
-present a new fundamental mechanism that is capable
-the formation of suprathermal tails in the electron velocity distribution function
-
-proposing a fundamental mechanism,
-the electrostatic bremsstrahlung, that might take electrons out of the thermal
-equilibrium
-
-\begin{figure}[hb]
+directly connected to the inverted temperature profile of the solar corona and
+particle acceleration in the Sun, is regarding where and how the non-Maxwellian
+velocity distribution functions with suprathermal tails, observed in the solar
+wind, are formed.
+\begin{figure}
   \begin{center}
@@
 
+\section{How all of this is related to our research?}
+\label{res}
+The work
+
+In \cite{Tigik2017a} ...
+present a new fundamental mechanism that is capable
+the formation of suprathermal tails in the electron velocity distribution function
+
+proposing a fundamental mechanism,
+the electrostatic bremsstrahlung, that might take electrons out of the thermal
+equilibrium
+
+In \cite{Tigik2016a} we show for the first time that binary collisions
+impacts the dynamics of the plasma-beam instability in the same timescale
+of nonlinear processes associated to the emission and amplification of
+electrostatic, high-frequency plasma waves associated to electrons, also
+called .
+
+% As pointed in the introduction, the kinetic theory of plasmas is mostly
+% concerned with processes that involve waves and oscillatory instabilities.
+% Kinetic instabilities depend on the inter-particle displacement and the
+% electrostatic and electromagnetic oscillatory modes that arise as a response.
+% This kind of physics cannot be described using a macroscopic approach like
+% magnetohydrodynamics (MHD), that treat the plasma as magnetized, incompressible
+% fluid. A single-particle description is also out of the question because it
+% is both mathematically and computationally prohibitive. Statistical mechanics,
+% however, suits very well for the problem. But, as the reader could have noticed,
+% the kinetic description of plasmas is quite cumbersome and requires a lot of
+% approximations to get to any result. This does not mean that kinetic theory is
+% incapable to provide a reliable description of kinetic oscillatory instabilities
+% and micro-turbulent processes in real-world plasmas.
+
 \end{appendix}

### 2019-08-17 thesis.tex
the end?

--- 2019-08-16 thesis.tex
@@
 
-% Considering the context presented above, the working proposal of
-% this PhD Thesis is to put forward the first numerical analysis of
-% the new weak turbulence theory for collisional plasmas \cite{YZKS16}
-% and explore its applications in the solar physics scope. In
-% \Cref{cha:theo-fram} and \Cref{cha:weak-turb}, we make a brief review
-% of the basic plasma kinetic theory equations and the weak turbulence
-% theory, respectively. In \Cref{noneigenmode}, we introduce the
-% new generalization of the weak turbulence theory, which takes into
-% account the contribution of noneigenmode fluctuations during the
-% derivation of the particle and wave kinetic equations, resulting
-% in three new terms. In \Cref{main}, we contextualize the present
-% work regarding the theory discussed in the previous chapter and
-% present the results obtained so far by appending the two papers
-% published in this subject. In \Cref{cha:final}, we summarize the
-% results and discuss the perspectives of the present research. Then,
-% we propose a schedule for the remaining period until the thesis
-% defense. In the end we have three appendices. \Cref{appA} shows
-% an improved approximation for the second order susceptibility of
-% the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
-% presents a discussion about the asymptotic equilibrium state of the
-% Langmuir waves spectrum, considering a combination of a inverse
-% power-law kappa distribution and a Maxwellian distribution, in the
-% presence and in the absence of the electrostatic bremsstrahlung.
-% The discussion in \Cref{appB} is related with the article appended
-% in \Cref{appC}, which is a parallel research and is only slightly
-% related with the main subject of this work, that is the study of the
-% combined action of collective and collisional processes in weakly
-% turbulent plasmas, in the presence of electrostatic oscillations.
+Considering the context presented above, the working proposal of
+this PhD Thesis is to put forward the first numerical analysis of
+the new weak turbulence theory for collisional plasmas \cite{YZKS16}
+and explore its applications in the solar physics scope. In
+\Cref{cha:theo-fram} and \Cref{cha:weak-turb}, we make a brief review
+of the basic plasma kinetic theory equations and the weak turbulence
+theory, respectively. In \Cref{noneigenmode}, we introduce the
+new generalization of the weak turbulence theory, which takes into
+account the contribution of noneigenmode fluctuations during the
+derivation of the particle and wave kinetic equations, resulting
+in three new terms. In \Cref{main}, we contextualize the present
+work regarding the theory discussed in the previous chapter and
+present the results obtained so far by appending the two papers
+published in this subject. In \Cref{cha:final}, we summarize the
+results and discuss the perspectives of the present research. Then,
+we propose a schedule for the remaining period until the thesis
+defense. In the end we have three appendices. \Cref{appA} shows
+an improved approximation for the second order susceptibility of
+the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
+presents a discussion about the asymptotic equilibrium state of the
+Langmuir waves spectrum, considering a combination of a inverse
+power-law kappa distribution and a Maxwellian distribution, in the
+presence and in the absence of the electrostatic bremsstrahlung.
+The discussion in \Cref{appB} is related with the article appended
+in \Cref{appC}, which is a parallel research and is only slightly
+related with the main subject of this work, that is the study of the
+combined action of collective and collisional processes in weakly
+turbulent plasmas, in the presence of electrostatic oscillations.
+%%% I still have to list the last two appendixes in introduction
 
@@
 \label{sec:kin-theo}
-
-% The plasma is a collection of ions, electrons and neutral particles that has
-% its dynamics dominated by the electric and magnetic fields, generated by the
-% electrically charged particles and the electric currents related to their
-% motion, respectively. Due to the long-range nature of these self-generated
-% fields, one particle affects the movement of several other particles, which
-% will interact with other particles, and so on. This \emph{collective behavior}
-% \footnote{A detailed exposition of all the processes and conditions that
-%   characterize the collective behavior in plasmas, can be accessed in the
-%   following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
-% is what characterizes an ionized gas as a plasma, and is also the reason
-% behind the complexity of the plasma dynamics. This complexity comes in the
-% form of a myriad of self-consistent oscillatory processes, where the electric
-% and magnetic fields affect - and are affected by - the position and motion of
-% the charges, and how they vary in time \cite{chen}.
-
-% A complete description of such a complicated dynamics would depend on determining
-% the position and momentum of each particle, and their respective microscopic
-% electric and magnetic fields, in a given instant in time. This strategy is not
-% practical and in most of the cases not feasible for many-body systems, like the
-% plasma. However, this microscopic description can be dealt through a hierarchy of
-% approximations, leading to the three main theories of plasma physics: kinetic,
-% multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
-% formulations will depend on the phenomenon that needs to be described.
-
 The kinetic theory is the most fundamental description of the
@@
 
+\chapter{Two-dimensional time evolution of beam-plasma instability in the
+  presence of binary collisions}
+\label{master}
+Results of the Master's dissertation that led to the current doctoral
+research.
+\includepdf[pages=-]{Tigik2016a.pdf}
+
 \chapter{Applications to astrophysical plasmas}
 \label{appD}
-% On Earth, the plasma is considered an exotic state of matter, associated to the
-% glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
-% laboratories, and the promise of cleaner and practically inexhaustible energy
-% source once we have controlled and energetically efficient thermonuclear fusion
-% \cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
-% to the occurrence of lightning during storms, flames, and the beautiful auroras
-% that take place at high latitudes. In the space, however, the situation is the
-% opposite. Starting in the outer layers of Earth's atmosphere, passing through the
-% solar wind in the interplanetary space, to the stellar interiors and atmospheres,
-% accretion disks, and molecular clouds it is estimated that something around
-% $99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
-% \cite{may}. So understanding the basic physics of plasma processes might help on
-% interpreting and describing
-
-% The analysis presented in this doctoral thesis has relevant contributions in the
-% study of the combined action of nonlinear kinetic instabilities and collisional
-% processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
-% profile under consideration might be considered quite idealized, the physical
-% processes that are being addressed have fundamental character - the plasma waves
-% under consideration and the particle interactions are inherent to any plasma.
-% The underlying nature of these processes means that they might impact the plasma
-% dynamics at different astrophysical environments and also in laboratory plasmas.
-% Laboratory plasmas, however, are usually constrained by specific experimental
-% set-up. This specificity would require in-depth knowledge and maybe access to
-% one experiment, which makes the analysis in the experimental context restrictive
-% and counterproductive. A more broad approach was then to compare our theoretical
-% results with phenomena observed in the naturally occurring space plasma.
-
-% \footnote{In the literature, the term ``astrophysical
-%   plasma'' is sometimes used to refer to the plasma observed outside the solar
-%   system, while ``space plasma'' is used to account for the plasma in our
-%   interplanetary space. In this text, however, both terms are being used as
-%   synonyms.}
-
-% \footnote{A comprehensive description of the scales and characteristics of
-%   cosmic plasmas can be seen in Section 1.2 of Ref. \cite{peratt2014}.}
-
 Astrophysical plasmas are observed in a vast range of densities, temperatures,
@@
 the context of solar physics. To contextualize our work within the solar
-plasma research, in this appendix, we present a brief review of the
-current state-of-the-art of solar and space physics research, followed
-by a discussion on the solar plasma phenomena related to our study.
+plasma research, in \autoref{sec:solar-physics} we present a brief review
+of the current research in solar and space physics and the phenomena
+related to this work. The corresponding paper is pointed in a footnote.
 
@@
 directly with the matter in the local interstellar medium \cite{NAP13060}.
-In \autoref{figD1}, we have a depiction of the regions and boundaries
+In \autoref{figE1}, we have a depiction of the regions and boundaries
 described above, and the current location of both Voyager missions, that
@@
       {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
-    \label{figD1}
+    \label{figE1}
   \end{center}
@@
 to remote cosmic systems. However, the primary reason behind the international
-effort\footnote{A complete description, of NASA's missions is available at
-\url{https://science.nasa.gov/missions-page?field_division_tid=5&field_phase_tid=All}.
-For ESA's missions, go to \url{http://sci.esa.int/home/51459-missions/}.
-Both websites were accessed at 11/08/2019.} (see Figures \ref{nasa} and
+effort (see Figures \ref{nasa} and
 \ref{esa}) on understanding the complex physics of the Sun and interplanetary
@@
 coronal mass ejections with the geomagnetic field, and also from the
-energetic radiation emitted by solar flares. Extreme coronal mass ejections
+energetic radiation emitted by solar flares\footnote{The emission of hard X-rays
+  and type III radio bursts, both generated during solar flares, are addressed in
+  \cite{Tigik2016a} (see \autoref{master}).}. Extreme coronal mass ejections
 can also cause stronger geomagnetic disturbances that may affect terrestrial
@@
 but also the acceleration of the solar wind. Another unsolved problem that is
-directly connected to the inverted temperature profile of the solar corona, is
-regarding where and how the non-Maxwellian velocity distribution functions with
-suprathermal tails, observed in the solar wind, are formed.
-
-In \cite{Tigik2017a} ...
-present a new fundamental mechanism that is capable
-the formation of suprathermal tails in the electron velocity distribution function
-
-proposing a fundamental mechanism,
-the electrostatic bremsstrahlung, that might take electrons out of the thermal
-equilibrium
-
-\begin{figure}[hb]
+directly connected to the inverted temperature profile of the solar corona and
+particle acceleration in the Sun, is regarding where and how the non-Maxwellian
+velocity distribution functions with suprathermal tails, observed in the solar
+wind, are formed\footnote{The generation of suprathermal electrons in the lower
+  corona and its consequences to the coronal heating problem are tackled in
+  \cite{Tigik2017a} (see \autoref{sec:gen-supr}).}.
+\begin{figure}
   \begin{center}
@@
 
+%% Eu acho que ainda tenho que escrever algo aqui. Vou pensar ainda a respeito.
+
 \end{appendix}

### 2019-08-19 thesis.tex
first corrections

@@
     do plasma. Entretanto, a escala de tempo de longa duração dos
-    processos não lineares, sugere que processos colisionais podem ter
+    processos não lineares sugere que processos colisionais podem ter
     algum efeito na dinâmica do plasma, atuando em conjunto com os
@@
     numérica dessa expressão, com a largamente usada \emph{fórmula de Spitzer}.
-    Com isso conseguimos mostrar que a aproximação de Spitzer super-estima
+    Com isso conseguimos mostrar que a aproximação de Spitzer superestima
     em muito a intensidade da atenuação colisional das ondas de plasma. Além
@@
     demonstrada quando a comparamos com a taxa de amortecimento não colisional
-    (de Landau). No segundo trabalho, nós analizamos o até então ignorado efeito
-    de \emph{bremsstrahlung} eletrostático. Nó mostramos que a presença da
+    (de Landau). No segundo trabalho, analizamos o até então ignorado efeito
+    de \emph{bremsstrahlung} eletrostático. Mostramos que a presença da
     emissão de \emph{bremsstrahlung} eletrostático modifica o espectro das ondas
@@
 show that nonlinear effects keep acting in the system in a time-scale that
-goes far beyond than the saturation time of the quasilinear instability,
+goes far beyond the saturation time of the quasilinear instability,
 to the extent that an asymptotic analysis of the new quasi-equilibrium
@@
 
-The hypothesis about the probable relevance of binary
-collisions in the nonlinear dynamics of the beam-plasma
-interaction was numerically tested in \cite{Tigik2016a}.
-In this work a linearized form of the Landau collision
-integral was added into the particle kinetic equation
-and the complete self-consistent set of electrostatic
-weak turbulence equations was numerically integrated in
-two-dimensions. It was shown that collisions indeed do
-affect the plasma dynamics in a time-scale that is very
-close to the time-scale of action of nonlinear effects.
-Beyond the purely theoretical conjecture, combining
-collective processes and collisional effects have some
-important applications in solar physics. In the solar
-hard X-ray analysis, for instance, the interpretation
-models that employ quasilinear/nonlinear oscillatory
-instabilities with some kind of collisional dissipation
-(collisional damping for the waves, binary collisions for
-the particles) are usually empirically adapted merely by
-adding an \emph{ad hoc} expression into the particles and wave
-kinetic equations to fit the observed data \cite{PK95,
-  Kohl1998,Veronig05,Brown2006,Kontar2011,KKDSSK11}, yet,
-there is no rigorous theory to compare or support such
-models. Moreover, though the formalism in \cite{Tigik2016a}
-makes use of the full Landau collision integral in the
-particle kinetic equation, it does not take into account
-collisional damping effects in the wave equation, which is
-widely used in these empirical models. The point is: until
-that moment, there was not a proper theoretical tool to deal
-with the combination of collective processes and collisional
-interaction.
+The hypothesis about the probable relevance of binary collisions in the
+nonlinear dynamics of the beam-plasma interaction was numerically tested
+in \cite{Tigik2016a} (see \autoref{master}). In this work, a linearized
+form of the Landau collision integral was added into the particle kinetic
+equation, and the weak turbulence theory's complete set of self-consistent,
+electrostatic equations was numerically integrated in two-dimensions.
+It was shown that collisions indeed do affect the plasma dynamics in a
+time-scale that is very close to the time-scale of action of nonlinear
+effects. Beyond the purely theoretical conjecture, combining collective
+processes and collisional effects have some important applications in
+solar physics. In the solar hard X-ray emission analysis, for instance, the
+models used for interpreting the spectra measured by the Reuven Ramaty High
+Energy Solar Spectroscopic Imager (RHESSI)\footnote{For more information
+ about the mission see: \url{https://hesperia.gsfc.nasa.gov/rhessi3/}.}
+that employ quasilinear/nonlinear wave instabilities with some kind of
+collisional dissipation (collisional damping for the waves, binary
+collisions for the particles) are usually empirically adapted merely by
+adding an \emph{ad hoc} expression into the particles and wave kinetic
+equations to fit the observed data \cite{PK95,Kohl1998,Veronig05,Brown2006,
+  Kontar2011,KKDSSK11}. However, there is no rigorous theory to compare
+and support such models. Moreover, though the formalism in \cite{Tigik2016a}
+makes use of the full Landau collision integral in the particle kinetic
+equation, it does not take into account collisional damping effects in the
+wave equation, which is widely used in these empirical models. The point
+is: until that moment, there was not a proper theoretical tool to deal
+with the combination of collective processes and collisional interaction.
 
@@
 and explore its applications in the solar physics scope. In
-\Cref{cha:theo-fram} and \Cref{cha:weak-turb}, we make a brief review
+\Cref{cha:kin-theo} and \Cref{cha:weak-turb}, we make a brief review
 of the basic plasma kinetic theory equations and the weak turbulence
@@
 \chapter{Kinetic theory of plasmas}
-\label{sec:kin-theo}
+\label{cha:kin-theo}
 The kinetic theory is the most fundamental description of the
@@
 % Sabrina: OK
-the ions and the electrons is the same $\hat n = \hat n_e = \hat n_i$.
+the ions and the electrons is the same, $\hat n = \hat n_e = \hat n_i$.
 
@@
 \begin{equation} 
-  \frac{\partial F_a}{\partial t}-\frac{e_a}{m_a}\
+  \frac{\partial F_a}{\partial t}+\frac{e_a}{m_a}\
   \delta {\bf E \cdot} \frac{\partial F_a}{\partial \bf v}
@@
 \frac{\partial\ \delta f_a}{\partial t}+{\bf v \cdot \nabla} \delta f_a
-+\frac{e_a}{m_a}\ \delta {\bf E \cdot} \frac{\partial F_a}{\partial t}
++\frac{e_a}{m_a}\ \delta {\bf E \cdot} \frac{\partial F_a}{\partial \bf v}
 +\frac{e_a}{m_a}\left[\delta {\bf E \cdot} \frac{\partial\ \delta f_a}{\partial \bf v}
@@
 the fluctuations, we take the appropriated ensembles averages. This
-procedure results in the nonlinear spectral balance equation.
-And is at this point, according to the two-time approximation, the
-slow time derivative is reintroduced \cite{YZKS16}. This procedure
-results in the nonlinear spectral balance equation\footnote{Equation
-  \eqref{nlebe} is not in the same form that appears in Refs.
-  \cite{Yoon00,Tigik2015}. The reason for this choice (see Eq. 2.59
-  of Ref. \cite{YZKS16}), will become clear in the next chapter.}
+procedure results in the nonlinear spectral balance equation. At this
+point, according to the two-time approximation, the slow time derivative
+is reintroduced \cite{YZKS16}. This procedure results in the nonlinear
+spectral balance equation\footnote{Equation \eqref{nlebe} is not in the
+  same form that appears in Refs. \cite{Yoon00,Tigik2015}. The reason
+  for this choice (see Eq. 2.59 of Ref. \cite{YZKS16}), will become
+  clear in the next chapter.}
 \begin{eqnarray}
@@
 
-The following definitions were used to write the above equations
+The following approximations and definitions were used to write
+the above equations
 \begin{displaymath}
@@
 \mu_{\bf k}^S=|k|^3\lambda_{De}^3\biggl(\frac{m_e}{m_i}\biggr)^{1/2}
-\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2}.
+\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},
 \end{displaymath}
@@
 contribution, is the central factor of this new kinetic turbulence theory
-for collisional plasmas. When
-% LFZ180216: Será que precisa essa vírgula depois de "When"?
-% Sabrina: definitivamente não. 
- it is substituted in the nonlinear terms of
-the nonlinear spectral balance equation, two new terms appear in the wave
-kinetic equation. The first term is a rigorous expression for the collisional
-damping rate of plasma waves. The second term is a hitherto unknown process
-of electrostatic radiation emission, in the eigenmode frequency range, due to
-particle scattering. This underlying electrostatic form of braking radiation
-% LFZ180216: "braking radiation" ?
-% Sabrina: OK
-was then called \emph{electrostatic bremsstrahlung} \cite{YZKS16}. For the
-particle kinetic equation, the application of this generalized expression is
-responsible for the arising of the Balescu-Lenard collision integral, without
-any \emph{ad hoc} addition.
+for collisional plasmas. When it is substituted in the nonlinear terms of
+the nonlinear spectral balance equation, three new terms appear in the wave
+kinetic equation. The first expression is an extension for the spontaneous
+scattering equation. The second term is a new, rigorous expression for the
+collisional damping rate of plasma waves. The third equation depicts a
+hitherto unknown process of electrostatic radiation emission, in the eigenmode
+frequency range, due to particle scattering. This underlying electrostatic
+form of braking radiation was then called \emph{electrostatic bremsstrahlung}
+\cite{YZKS16}. For the particle kinetic equation, the application of this
+generalized expression is responsible for the arising of the Balescu-Lenard
+collision integral, without any \emph{ad hoc} addition.
 
@@
 \end{equation}
-where dielectric constant is given by
+where the dielectric constant is given by
 \begin{equation}
@@
 $v_{Te}= \sqrt{2T_e/m_e}$ is the electron thermal velocity, and $T_e$
-and $T_i$ are the electron and ion temperature, respectively. This
-leads to
+and $T_i$ are, respectively, the electron and ion temperature expressed
+in units of energy. This leads to
 \begin{equation}
@@
 For the nonlinear wave kinetic equation, the implementation is far more
-extensive and complicated than the two previous cases. 
-In this text, we provide a brief explanation of the method,
-which is not very different from the quasilinear case, though
-it is way more complex, and present some important remarks
-regarding the inclusion of noneigenmodes in the nonlinear wave
-equation. It is worth to mention again that the process of
-inclusion of the noneigenmode contribution in the wave and the
-particle kinetic equations can be seen in Ref. \cite{YZKS16}.
+extensive and complicated than the two previous cases. In this text, we
+provide a brief explanation of the method, which is not very different
+from the quasilinear case, though it is way more complex, and present some
+critical remarks regarding the inclusion of noneigenmodes in the nonlinear
+wave equation. It is worth to mention again, that a more detailed procedure
+of the inclusion of the noneigenmode contribution in the weak turbulence's
+equations can be seen in \cite{YZKS16}.
 
@@
 
-Above, looking at the first noneigenmode term,
-(blue), one may notice the extreme similarity with its previous
-term, which describes the spontaneous scattering process. In fact, this
-term is nothing but a correction due to the noneigenmode fluctuations,
-to the spontaneous scattering process. Such effect, though, it is not
-relevant for this work and will not be analyzed here. However, we are
-interested in the last two corrections, the \emph{collisional damping}
-(in dark-green), and \emph{electrostatic bremsstrahlung} (in pink),
-respectively. The final expressions for the three new contributions
-to the wave kinetic equation are right below.
+Above, looking at the first noneigenmode term, in blue, one may notice
+the extreme similarity with its previous expression, which describes the
+spontaneous scattering process. In fact, this term is nothing but a
+\emph{correction} to the spontaneous scattering process. Colored in
+dark-green is the new, rigorous expression for the \emph{collisional
+  damping}. The pink equation in the end, depicts the so-far unknown
+\emph{electrostatic bremsstrahlung} process. The final expressions for
+the three new contributions to the wave kinetic equation are right below.
 

### 2019-08-20 thesis.tex
*** empty log message ***

@@
 \emph{electrostatic bremsstrahlung} process. The final expressions for
-the three new contributions to the wave kinetic equation are right below.
+the three new contributions to the wave kinetic equation are given below.
 
@@
 \label{main}
-The generalization introduced in \cite{YZKS16} and summarized
-in \Cref{noneigenmode}, is an innovative approach, in
-which the contribution of the usually neglected noneigenmode
-fluctuations is taken into account along with the well-known
-eigenmodes contribution. The outcome of this new formulation
-is a first principles theory that combines both collective
-and non-collective processes, assuming the propagation of
-electrostatic oscillations in unmagnetized plasmas, without
-any \emph{ad hoc} addition. Such theory is the basis of the
-present research, whose primary objective is performing
-numerical analysis of the generalized weak turbulence
-equations, and then investigate its applications on the
-description and interpretation of space plasma phenomena.
-More specifically, the solar plasma, where the results of
-the first two analysis \cite{Tigik2016b,Tigik2017a} have
-shown a promising perspective. In this chapter, we discuss
-some important aspects regarding the work that has been
-done until the moment and the employed methodology. Then,
-we present the results in the form of appended papers, in
-chronological order, in \Cref{coll-damp,sec:gen-supr}.
+The generalization introduced in \cite{YZKS16} and summarized in
+\Cref{noneigenmode}, is an innovative approach, in which the contribution
+of the usually neglected noneigenmode fluctuations is taken into account
+along with the well-known eigenmodes contribution. The outcome of this new
+formulation is a first principles theory that combines both collective
+and non-collective processes, assuming the propagation of electrostatic
+oscillations in unmagnetized plasmas, without any \emph{ad hoc} addition.
+Such theory is the basis of the present research, whose primary objective
+is performing numerical analysis of the generalized weak turbulence equations,
+and then investigate its applications on the description and interpretation
+of space plasma phenomena. More specifically, the solar plasma, where the
+results of the first two studies \cite{Tigik2016b,Tigik2017a} have shown a
+promising perspective.
+
+From the three new terms presented in the last chapter, we analyzed two:
+the collisional damping \cite{Tigik2016b} and electrostatic bremsstrahlung
+\cite{Tigik2017a}. The third term is a correction for the spontaneous
+scattering effect, which is a nonlinear process. The first study, however,
+analyses only the intensity of the collisional damping spectrum for $L$ and
+$S$ waves by numerically integrating Eqs. \eqref{gammaL} and \eqref{gammaS},
+respectively. Regarding the second study, the time evolution analysis was
+made using quasilinear approximation, which does not involve nonlinear
+wave-particle interaction, like the scattering effect. Besides that, a
+small correction to a nonlinear term does not seem to justify a whole study
+dedicated only to it.
+
+In this chapter, we discuss some essential aspects regarding the results
+obtained in both studies mentioned above. The results are presented in the
+form of appended papers, using chronological order, in \Cref{coll-damp,sec:gen-supr}.
 
@@
 
-The following paper is fairly self-sustained regarding the theory
-and methods applied. All important equations are there, including
-their normalized form and the normalization constants. Any doubt
-related to the origin of the new equations are filled by
-\Cref{noneigenmode}.
+The following paper is fairly self-sustained regarding the theory and
+methods applied. All important equations are there, including their
+normalized form and the normalization constants. 
+% Any doubt regarding the origin of the new equations is filled by \Cref{noneigenmode}.
 
@@
 plasma parameter, $\lambda_{De}=T_e/(4\pi\hat{n}e^2)=v_e^2/(2\omega_{pe}^2)$,
-$v_e=(2T_e/m_e)^{1/2}$ is the electron thermal velocity and $T_e$ is
-electrons temperature.
+$v_e=(2T_e/m_e)^{1/2}$ is the electron thermal velocity and $T_e$ is the
+electron temperature.
 
@@
 parameter, $\ln \Lambda$ is Coulomb logarithm, and $Z_{b=e,i}$ is
-the ion and electrons charge number, with $Z_e=1$.
+the charge number of ions and electrons, with $Z_e=1$.
 The dispersion relations for $L$ and $S$ waves in dimensionless
@@
 \label{cha:final}
-In this text, we have summarized the early results of the analysis of a new first
-principles theory, depicted in \Cref{noneigenmode}, which combines collective
-processes (eigenmodes) and collisional interactions (noneigenmodes), for Langmuir
-and ion-sound waves, without any \emph{ad hoc} addition. The importance of this
+In this thesis, we have presented the results of the first analysis of a new
+theory, depicted in \Cref{noneigenmode}, which combines collective processes
+(eigenmodes) and collisional interactions (noneigenmodes), for Langmuir and
+ion-sound waves, without any \emph{ad hoc} addition. The importance of this
 formalism, became clear right in the first study, presented in \Cref{coll-damp},
-where it was shown the collisional damping rate calculated with the heuristic
+where it was shown that the collisional damping rate calculated with the heuristic
 Spitzer formula, that is independent of the wave-number, is highly overestimated
@@
 
-The second study, discussed in \Cref{sec:gen-supr}, was focused on the
-consequences of taking into account the hitherto unknown effect of
-electrostatic bremsstrahlung. The outcome of such analysis revealed an
-underlying process, which takes the electron velocity distribution
-out of its initial equilibrium state and transforms it into a new
-quasi-equilibrium state that resembles a velocity distribution composed
-by a Maxwellian core with a suprathermal tail. Such velocity distributions
-are pervasively observed in space plasmas \cite{Parker1958a,Vasyliunas68,
-  Coroniti1974,FABMG75,Lin1998,Horne2005,Clark2015,Padovani2015,deSoria2016,
-  Padovani2017,Deca2017}. However, until these
-days, despite several attempts of explanations based on different models,
-no existing first principles approach is capable to self-consistently
-describe its origin and evolution. Again, the relevance of this research
-becomes evident. The ubiquity of inverse power-law velocity distribution
-in space plasmas indicates the action of a fundamental physical process on
-the plasma particles; this process may be the electrostatic bremsstrahlung.
-For instance, the possibility of the formation of a suprathermal electron
-distribution in a mildly collisional environment, as demonstrated in
-\cite{Tigik2017a}, is in accordance with the velocity filtration model,
-which rely on the existence of a high energy electron population in the
-transition region, located between the chromosphere and the solar corona,
-to explain the temperature inversion observed in the solar corona \cite{
-  Scudder92a,Scudder92b,Anderson94,Scudder94,Scudder96,DS99,DS03,Teles15}.
-Howsoever, the generality of the results of Ref. \cite{Tigik2017a} suggests
-that collisional interactions involving charged particles enfold physical
-processes that go beyond the Coulomb collisions effects, which might be
-connected to some unexplained phenomena in plasma. Therefore, it is in
-this context that the present doctoral working proposal is inserted.
-
+The second study, discussed in \Cref{sec:gen-supr}, focused on the
+consequences of including the hitherto unknown effect of electrostatic
+bremsstrahlung, in the time evolution of a Maxwellian electron velocity
+distribution, under the quasilinear regime. The unexpected outcome of this
+analysis revealed an underlying process responsible for taking the electron
+velocity distribution out of its initial equilibrium state, leading it to
+a new quasi-equilibrium state that is satisfied by a velocity distribution
+composed by a Maxwellian core with a suprathermal tail. Such velocity
+distributions are pervasively observed in space plasmas \cite{Parker1958a,
+  Vasyliunas68,Coroniti1974,FABMG75,Lin1998,Horne2005,Clark2015,Padovani2015,
+  deSoria2016,Padovani2017,Deca2017}. However, until these days, despite
+several attempts of explaining how they form and why space plasmas are
+particularly prone to develop a suprathermal tail while retaining the
+thermal core, no existing theory is capable of describing self-consistently
+its origin and evolution. Again, the relevance of this research becomes
+evident.
+
+The ubiquity of inverse power-law velocity distribution in space plasmas
+indicates the action of a fundamental physical process; this process may
+be the electrostatic bremsstrahlung. For instance, the possibility of the
+formation of suprathermal electron velocity distributions in a mildly
+collisional environment, as demonstrated in \cite{Tigik2017a}, has a positive
+correlation with the velocity filtration model, which rely on the existence
+of a high energy electron population in the transition region, located between
+the chromosphere and the solar corona, to explain the temperature inversion
+observed in the solar corona \cite{Scudder92a,Scudder92b,Anderson94,Scudder94,
+  Scudder96,DS99,DS03,Teles15}.
+
+As a final remark, we would like to emphasize the fundamental aspect of the
+theory presented in Ref. \cite{YZKS16}. The rigorous analysis performed during
+this doctoral research, suggest that collisional interactions involving charged
+particles enfold physical processes that go beyond the Coulomb collisions
+effects. An enthralling prospect of this study lies in the possibility of these
+underlying kinetic processes being connected to unexplained phenomena observed
+in space plasmas. On that regard...
+
+% It is time for new advances in the kinetic description of plasmas. For
+% a long time, space observations could only resolve physical phenomena occurring
+% in macroscopic scales, described by the magnetohydrodynamic (MHD) theory.
+
+% A better understanding of the combined action of collective and collisional
+% plasma processes has some important impact on how observational data from
+% denser regions of the solar corona are analyzed. Now that the Parker solar
+% probe 
 % The prospects of this research are promising. Besides including the

### 2019-08-21 thesis.tex
almost there

@@
 \end{equation}
-where, $\gamma_{\bf q}^{\sigma L}$ and $\gamma_{\bf q}^{\sigma S}$ describe
+where $\gamma_{\bf q}^{\sigma L}$ and $\gamma_{\bf q}^{\sigma S}$ describe
 the collisional damping rate for $L$ and $S$ waves, respectively
@@
 The ubiquity of inverse power-law velocity distribution in space plasmas
-indicates the action of a fundamental physical process; this process may
-be the electrostatic bremsstrahlung. For instance, the possibility of the
-formation of suprathermal electron velocity distributions in a mildly
+indicates the action of a fundamental physical process that might -or
+might not- be the electrostatic bremsstrahlung. For instance, the possibility
+of the formation of suprathermal electron velocity distributions in a mildly
 collisional environment, as demonstrated in \cite{Tigik2017a}, has a positive
-correlation with the velocity filtration model, which rely on the existence
-of a high energy electron population in the transition region, located between
-the chromosphere and the solar corona, to explain the temperature inversion
-observed in the solar corona \cite{Scudder92a,Scudder92b,Anderson94,Scudder94,
-  Scudder96,DS99,DS03,Teles15}.
-
-As a final remark, we would like to emphasize the fundamental aspect of the
+correlation with the velocity filtration model, which relies on the existence
+of a high energy electron population in the solar transition region, located
+between the chromosphere and the solar corona, to explain the temperature
+inversion observed in the solar corona \cite{Scudder92a,Scudder92b,Anderson94,
+  Scudder94,Scudder96,DS99,DS03,Teles15}.
+
+% As a final remark, i
+It is important to emphasize the fundamental aspect of the
 theory presented in Ref. \cite{YZKS16}. The rigorous analysis performed during
-this doctoral research, suggest that collisional interactions involving charged
+this doctoral research, suggests that collisional interactions involving charged
 particles enfold physical processes that go beyond the Coulomb collisions
@@
 underlying kinetic processes being connected to unexplained phenomena observed
-in space plasmas. On that regard...
-
-% It is time for new advances in the kinetic description of plasmas. For
-% a long time, space observations could only resolve physical phenomena occurring
-% in macroscopic scales, described by the magnetohydrodynamic (MHD) theory.
-
-% A better understanding of the combined action of collective and collisional
-% plasma processes has some important impact on how observational data from
-% denser regions of the solar corona are analyzed. Now that the Parker solar
-% probe 
-% The prospects of this research are promising. Besides including the
-% new effects on the time evolution of nonlinear beam-plasma interaction,
-% we are planning the inclusion of effects due to non-homogeneous
-% medium on the beam-plasma dynamics, and its implementation in the numerical
-% code. Furthermore, the results regarding
-% the electrostatic bremsstrahlung term deserve further research in order
-% to confirm or discard the hypothesis made in Ref. \cite{Tigik2017a}, about
-% the electrostatic bremsstrahlung being the underlying effect behind the
-% generation of suprathermal velocity distributions, which are pervasively
-% observed in space plasmas. The objectives above are in accordance with
-% the research project approved for the ``Sandwich Doctorate Program'',
-% that is proposed to occur under the supervision of Dr. Peter Yoon in the
-% University of Maryland.
-
-% \section{Schedule}
-% \label{sec:schedule}
-% The expected schedule for the remaining period of this doctoral
-% research is detailed below:
-% \begin{itemize}
-% \item \textbf{March to July 2018:} inclusion the new effects on
-%   the time evolution of nonlinear beam-plasma interaction, and of
-%   implementation the code for the inclusion of non-homogeneous
-%   medium on the beam-plasma dynamics;
-% \item \textbf{August 2018 to February 2019:} internship period in
-%   the University of Maryland, working on the further development
-%   of the electrostatic bremsstrahlung hypothesis;
-% \item \textbf{March to August of 2019:} Thesis elaboration.
-% \end{itemize}
+in space plasmas. On that regard, the electrostatic weak turbulence theory for
+collisional plasmas is a first step towards a more accurate description of the
+microscopic physics of plasmas. Further development should extend this formalism
+to include electromagnetic waves and, in the long term, the influence of ambient
+magnetic field.
+
+These efforts on improving the theoretical description of kinetic processes in
+plasmas and numerically analyzing the equations are just in time with current
+technological progress in the resolution capability of spacecraft measurement
+equipment. A great example of this new trend is the Magneto-spheric Multiscale
+(MMS) mission that investigates the physics of magnetic reconnection in the
+Earth's magnetosphere. Equipped with high-precision instruments \cite{Pollock2016,
+  Torbert2016}, MMS was capable of directly measure wave-particle energy
+exchange process in the ion kinetic scale \cite{Gershman2017}, for the first
+time. Therefore, it is becoming evident that the kinetic scale is the next
+frontier in observational plasma physics, and this will require a more accurate
+and comprehensive theory.
 
@@
 
-Since this approximation assumes the dominant frequency range on the
-denominators is given by the dispersion relation of Langmuir waves
+Since this approximation assumes that the dominant frequency range on
+the denominators is given by the dispersion relation of Langmuir waves
 (see Eq. \eqref{dom-freq}), which are high frequency oscillations
@@
 in the outer layers of Earth's atmosphere, passing through the solar wind in the
-interplanetary space, to the stellar interiors and atmospheres, accretion disks,
-and molecular clouds it is estimated that something around $99 \sim 99.9\%$ of the
+interplanetary space, to the stellar interiors and atmospheres, accretion disks
+and molecular clouds, it is estimated that something around $99 \sim 99.9\%$ of the
 observable matter in the universe is in the plasma state. Under cosmic conditions,

### 2019-08-21 thesis.tex
final?

@@
 
-Considering the context presented above, the working proposal of
-this PhD Thesis is to put forward the first numerical analysis of
-the new weak turbulence theory for collisional plasmas \cite{YZKS16}
-and explore its applications in the solar physics scope. In
-\Cref{cha:kin-theo} and \Cref{cha:weak-turb}, we make a brief review
-of the basic plasma kinetic theory equations and the weak turbulence
-theory, respectively. In \Cref{noneigenmode}, we introduce the
-new generalization of the weak turbulence theory, which takes into
-account the contribution of noneigenmode fluctuations during the
-derivation of the particle and wave kinetic equations, resulting
-in three new terms. In \Cref{main}, we contextualize the present
-work regarding the theory discussed in the previous chapter and
-present the results obtained so far by appending the two papers
-published in this subject. In \Cref{cha:final}, we summarize the
-results and discuss the perspectives of the present research. Then,
-we propose a schedule for the remaining period until the thesis
-defense. In the end we have three appendices. \Cref{appA} shows
-an improved approximation for the second order susceptibility of
-the electrostatic bremsstrahlung for Langmuir waves. \Cref{appB}
-presents a discussion about the asymptotic equilibrium state of the
-Langmuir waves spectrum, considering a combination of a inverse
-power-law kappa distribution and a Maxwellian distribution, in the
-presence and in the absence of the electrostatic bremsstrahlung.
-The discussion in \Cref{appB} is related with the article appended
-in \Cref{appC}, which is a parallel research and is only slightly
-related with the main subject of this work, that is the study of the
-combined action of collective and collisional processes in weakly
-turbulent plasmas, in the presence of electrostatic oscillations.
-%%% I still have to list the last two appendixes in introduction
+Considering the context presented above, the working proposal of this PhD
+Thesis is to put forward the first numerical analysis of the new weak
+turbulence theory for collisional plasmas \cite{YZKS16} and explore its
+applications in the solar physics scope. In \Cref{cha:kin-theo}, we make
+a brief review of the basic plasma kinetic theory for electrostatic
+oscillations. \Cref{cha:weak-turb} revises the procedure for obtaining
+the weak turbulence equations for Langmuir and ion-sound waves and
+the quasilinear equation for the particle dynamics.
+
+The main subject of this thesis is discussed in \Cref{noneigenmode}. In
+\Cref{sec:inc-non} we show the methodology used in the formulation of this
+new generalization and the outcome of its inclusion in the quasilinear
+wave equation, and in the particle kinetic equation. \Cref{sec:non-non}
+describes the inclusion of the noneigenmode fluctuations in the nonlinear
+wave equations and the resulting terms, which are the main concern of
+the present analysis. In \Cref{main}, we contextualize the present work
+regarding the theory discussed in the previous chapter and present the
+results obtained in appended papers. \Cref{cha:final}, summarizes the
+results and presents a brief discussion on the and perspectives of this
+new generalized formalism, and its relevance for the next generation of
+solar physics research.
+
+In the end, we have five appendices. \Cref{appA} depicts an improved
+approximation for the second order susceptibility of the electrostatic
+bremsstrahlung for Langmuir waves. In \Cref{appB} we discuss the
+similarities of the asymptotic equilibrium state of the Langmuir waves
+spectrum, considering a combination of an inverse power-law kappa
+distribution and a Maxwellian distribution, in the presence and the
+absence of the electrostatic bremsstrahlung effect. The discussion in
+\Cref{appB} is related with to article appended in \Cref{appC}, which
+is parallel research and is only slightly related to the main subject
+of this work. \Cref{master} shows the paper that summarizes the results
+of my Master’s dissertation, which may be considered the starting point
+of this doctoral research. \Cref{appE} explores relevant aspects of
+current solar physics research and how they are connected to this work.
+It was written to be more like a light, informative reading, than a
+deep academic digression.
 
@@
 \section{Inclusion of noneigenmodes}
+\label{sec:inc-non}
 Let us start considering the linear part of the spectral balance equation,
@@
 of noneigenmode fluctuations will appear in the wave dynamics, as will
-become clear in the next subsection.
-
-\subsection{Noneigenmode contribution to nonlinear wave kinetic equation}
+become clear in the next section.
+
+\section{Noneigenmode contribution to nonlinear wave
+  kinetic equation}
+\label{sec:non-non}
 For the nonlinear wave kinetic equation, the implementation is far more
@@
 
-\subsubsection{Generalized wave kinetic equation for $L$ and $S$ waves}
+\subsection{Generalized wave kinetic equation for $L$ and $S$ waves}
 Adding Eqs. \eqref{gammaL} and \eqref{PkL} to Eq. \eqref{L,1},
@@
 consequences of including the hitherto unknown effect of electrostatic
-bremsstrahlung, in the time evolution of a Maxwellian electron velocity
+bremsstrahlung in the time evolution of a Maxwellian electron velocity
 distribution, under the quasilinear regime. The unexpected outcome of this
@@
 technological progress in the resolution capability of spacecraft measurement
-equipment. A great example of this new trend is the Magneto-spheric Multiscale
+equipment. A great example of this new trend is NASA's Magnetospheric Multiscale
 (MMS) mission that investigates the physics of magnetic reconnection in the
@@
 \renewcommand{\theequation}{A\arabic{equation}}
-Let us start with an analysis of the approximation of the second order
-susceptibility used in \cite{YZKS16} for the bremsstrahlung equations.
-The expressions for $L$ and $S$ waves, in the above cited paper, are
-given by:
-\begin{eqnarray}
-\label{bremsst,L,1}
-P_{\bf k}^{\sigma L} &=& \frac{3e^2T_e}{16\pi^3m_e}
-\biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2\frac{1}{k^2\lambda_{De}^2}
-\int d{\bf k}'\left(1+\frac{T_e}{T_i}
-+{k'}^2\lambda_{De}^2\right)^{-2}\left(1+\frac{T_e}{T_i}
-+({\bf k}-{\bf k}')^2\lambda_{De}^2\right)^{-2}
-\nonumber\\
-&& \times\int d{\bf v}\int d{\bf v}'\,
-\delta[\sigma\omega_{\bf k}^L-{\bf k}\bm{\cdot}{\bf v}
-+{\bf k}'\bm{\cdot}({\bf v}-{\bf v}')]
-\sum_aF_a({\bf v})\sum_bF_b({\bf v}'),
-\\
-\label{bremsst,S,1}
-P_{\bf k}^{\sigma S} &=& \mu_{\bf k}\frac{3e^2T_e}{16\pi^3m_e}
-\biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2\frac{1}{k^2\lambda_{De}^2}
-\int d{\bf k}'\left(1+\frac{T_e}{T_i}
-+{k'}^2\lambda_{De}^2\right)^{-2}\left(1+\frac{T_e}{T_i}
-+({\bf k}-{\bf k}')^2\lambda_{De}^2\right)^{-2}
-\nonumber\\
-&& \times\int d{\bf v}\int d{\bf v}'\,
-\delta[\sigma\omega_{\bf k}^S-{\bf k}\bm{\cdot}{\bf v}
-+{\bf k}'\bm{\cdot}({\bf v}-{\bf v}')]
-\sum_aF_a({\bf v})\sum_bF_b({\bf v}').
-\end{eqnarray}
-
-Assuming that the most important contribution comes from the region
-where ${\bf k}\cdot {\bf v}\simeq 0$, ${\bf k'}\cdot{\bf v'}\simeq 0$,
-and ${\bf k'}\cdot {\bf v}\simeq 0$,
+In this appendix, we present two different approximations applied to the
+second-order susceptibility in the electrostatic bremsstrahlung equation
+for Langmuir waves. Initially, for comparison, we show the original
+simplification used in Ref.~\cite{YZKS16}. In the sequence, we introduce
+an improved approximation for the same expression, highlighting the main
+differences. This new version, though, is only suitable for fast-waves,
+which is the case of Langmuir oscillations, but the same does not apply
+to ion-sound waves. Moreover, the results for ion-sound waves are quite
+well behaved with the original approximation, which is the same that was
+initially used for  $L$ waves. Therefore, $S$ waves will take part only in
+\Cref{sec:orig-appr}, while \Cref{sec:alt-approx} will be directed solely
+the $L$ waves expression.
+
+\section{Original approximation}
+\label{sec:orig-appr}
+The initial expressions for $L$ and $S$ waves, still in terms of the
+second order susceptibility are given by:
+\begin{equation}
+\label{PkL-A}
+  \begin{split}
+    \frac{\partial I_{\bf k}^{\sigma L}}{\partial t}\biggr|_{\mbox{\tiny brem}}&=\sum_{a,b}
+\frac{12n_ee_a^2e_b^2\omega_{pe}^2}{\pi}\int d{\bf k}'\int d{\bf v}\int d{\bf v}'
+\,\frac{|\chi^{(2)}({\bf k}',0|{\bf k}-{\bf k}',0)|^2}{k'^2|{\bf k}-{\bf k}'|^2
+|\epsilon({\bf k}',0)|^2|\epsilon({\bf k}-{\bf k}',0)|^2}\\
+&\times\delta\left[\sigma\omega_{\bf k}^L-{\bf k}\cdot{\bf v}+{\bf k}'\cdot
+  ({\bf v}-{\bf v}')\right]F_a({\bf v})F({\bf v}'),
+\end{split}
+\end{equation}
+\begin{equation}
+     \label{PkS-A}
+  \begin{split}
+ \frac{\partial}{\partial t}
+\frac{I_{\bf k}^{\sigma S}}{\mu_{\bf k}}\biggr|_{\mbox{\tiny brem}}&=\sum_{a,b}
+\frac{12n_ee_a^2e_b^2\omega_{pe}^2}{\pi}
+\int d{\bf k}'\int d{\bf v}\int d{\bf v}'
+\,\frac{|\chi^{(2)}({\bf k}',0|{\bf k}-{\bf k}',0)|^2}{k'^2|{\bf k}-{\bf k}'|^2
+|\epsilon({\bf k}',0)|^2|\epsilon({\bf k}-{\bf k}',0)|^2}\\
+&\times\delta\left[\sigma\omega_{\bf k}^S-{\bf k}\cdot{\bf v}+{\bf k}'\cdot
+  ({\bf v}-{\bf v}')\right]F_a({\bf v})F({\bf v}').
+  \end{split}
+\end{equation}
+
+Assuming that the most important contribution comes from the region where
+${\bf k}\cdot {\bf v}\simeq 0$, ${\bf k'}\cdot{\bf v'}\simeq 0$, and
+${\bf k'}\cdot {\bf v}\simeq 0$,
 \begin{equation}
@@
   +\frac{1}{({\bf k'})\cdot{\bf v''}}\right]
-+ \frac{\bf k'\cdot v''}{\bf k\cdot v''} 
-+ \frac{({\bf k}-{\bf k'}){\bf \cdot v''}}{\bf k\cdot v''} 
++\underbrace{ \frac{\bf k'\cdot v''}{\bf k\cdot v''} 
++ \frac{({\bf k}-{\bf k'}){\bf \cdot v''}}{\bf k\cdot v''}}_{=1}
 \right\} F_a({\bf v''}) + i\,{\rm Im}\chi^{(2)}
@@
 
-\begin{equation}
-\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
-\int d{\bf v''}\,\left[\frac{T_a}{m_a}
-\frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
-\frac{{\bf k}\cdot {\bf v''}}{({\bf k-k'})\cdot{\bf v''}}+1
-\right] F_a({\bf v''}) 
-\end{equation}
+%%% Falta algo aqui, ver isso %%%
+% \begin{equation}
+% \chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
+% \simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
+% \int d{\bf v''}\,\left[\frac{T_a}{m_a}
+% \frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
+% \frac{{\bf k}\cdot {\bf v''}}{({\bf k-k'})\cdot{\bf v''}}+1
+% \right] F_a({\bf v''}) 
+% \end{equation}
 \begin{equation}
@@
 =i\frac{e}{2T_e}\frac{1}{k k'|{\bf k-k'}|\lambda_{De}^2}
-\left(1-\frac{T_e^2}{T_i^2}\right).
-\end{equation}
+\left(1-\frac{T_e^2}{T_i^2}\right),
+\end{equation}
+and the resulting equations
+\begin{eqnarray}
+\label{bremsstL-A}
+P_{\bf k}^{\sigma L} &=& \frac{3e^2T_e}{16\pi^3m_e}
+\biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2\frac{1}{k^2\lambda_{De}^2}
+\int d{\bf k}'\left(1+\frac{T_e}{T_i}
++{k'}^2\lambda_{De}^2\right)^{-2}\left(1+\frac{T_e}{T_i}
++({\bf k}-{\bf k}')^2\lambda_{De}^2\right)^{-2}
+\nonumber\\
+&& \times\int d{\bf v}\int d{\bf v}'\,
+\delta[\sigma\omega_{\bf k}^L-{\bf k}\bm{\cdot}{\bf v}
++{\bf k}'\bm{\cdot}({\bf v}-{\bf v}')]
+\sum_aF_a({\bf v})\sum_bF_b({\bf v}'),
+\\
+\label{bremsstS-A}
+P_{\bf k}^{\sigma S} &=& \mu_{\bf k}\frac{3e^2T_e}{16\pi^3m_e}
+\biggl(1-\frac{T_e^2}{T_i^2}\biggr)^2\frac{1}{k^2\lambda_{De}^2}
+\int d{\bf k}'\left(1+\frac{T_e}{T_i}
++{k'}^2\lambda_{De}^2\right)^{-2}\left(1+\frac{T_e}{T_i}
++({\bf k}-{\bf k}')^2\lambda_{De}^2\right)^{-2}
+\nonumber\\
+&& \times\int d{\bf v}\int d{\bf v}'\,
+\delta[\sigma\omega_{\bf k}^S-{\bf k}\bm{\cdot}{\bf v}
++{\bf k}'\bm{\cdot}({\bf v}-{\bf v}')]
+\sum_aF_a({\bf v})\sum_bF_b({\bf v}').
+\end{eqnarray}
 
 \section{Alternative approach}
-From Eq.(4.24) in \cite{YZKS16} we have
+\label{sec:alt-approx}
+From Eq.(4.24) in Ref. \cite{YZKS16} we have
 \begin{eqnarray}
@@
 \left(1-\frac{m_e}{m_i}\frac{T_e}{T_i}\right)
+\end{equation}
+
+Therefore, the resulting equation for the electrostatic bremsstrahlung
+of $L$ waves in the new approximation is
+\begin{equation}
+  \label{PkL-A}
+  \begin{split}
+      P_{\bf k}^{\sigma L}
+  &= \frac{3e^2}{4\pi^3}\frac{1}{(\omega_\bk^L)^2}
+    \left(1-\frac{m_e}{m_i}\frac{T_e}{T_i}\right)^2\frac{v_e^4}{k^2}
+    \int d{\bf k}'k'^2|{\bf k- k'}|^2\left(1+\frac{T_e}{T_i}
+    +({\bf k}-{\bf k}')^2\lambda_D^2\right)^{-2}\\
+  &\times\left(1+\frac{T_e}{T_i}
+    +{k'}^2\lambda_D^2\right)^{-2} \int d{\bf v}\int d{\bf v}'\,
+    \delta[\sigma \omega_{\bf k}^L-{\bf k \cdot v}
+    +{\bf k'\cdot}({\bf v}-{\bf v}')]
+    \sum_aF_a({\bf v})\sum_bF_b({\bf v}')
+  \end{split}
 \end{equation}
@@
 \chapter{Applications to astrophysical plasmas}
-\label{appD}
+\label{appE}
 Astrophysical plasmas are observed in a vast range of densities, temperatures,

### 2019-08-21 thesis.tex
final final?
* thesis.tex: Summary: final?

@@
 In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
-system, a complex set of coupled equations whose solution invariably will
+system, a complex set of coupled equations which solution invariably will
 depend on some degree of approximation. In the presence of small
@@
 Under such condition, the gradual changing on the velocity space
-shape slowly modifies the wave spectrum, whose new form will then
+shape slowly modifies the wave spectrum, which new form will then
 alter the velocity distribution function and so on, until a new
@@
 equation, while the real part leads to the wave dispersion equation,
-whose solutions are the wave dispersion relations.
+which solutions are the wave dispersion relations.
 
@@
 are characterized by all ${\bf k}$ and $\omega$. Therefore, the fluctuations
-whose $\omega \ne \omega_{\bf k}$, which characterize the noneigenmodes,
+which $\omega \ne \omega_{\bf k}$, which characterize the noneigenmodes,
 are ignored. In Ref. \cite{YZKS16} the authors present a generalization
@@
 oscillations in unmagnetized plasmas, without any \emph{ad hoc} addition.
-Such theory is the basis of the present research, whose primary objective
+Such theory is the basis of the present research, which primary objective
 is performing numerical analysis of the generalized weak turbulence equations,
@@
 development of the work presented in Ref. \cite{Tigik2017a}. 
-The work in question, whose title
+The work in question, which title
 is ``Weakly turbulent plasma processes in the presence of inverse

### 2019-08-23 thesis.tex
Final (I guess)

@@
 In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
-system, a complex set of coupled equations which solution invariably will
+system, a complex set of coupled equations whose
+%which 
+% LFZ190822: Posso estar enganado, mas me parece que aqui seria mesmo
+% "whose", como estava antes, e não "which".
+% Sabrina: resolvi colocar "whose" de novo depois de uma rápida, mas
+% controversa, pesquisa no google
+solution invariably will
 depend on some degree of approximation. In the presence of small
@@
 Under such condition, the gradual changing on the velocity space
-shape slowly modifies the wave spectrum, which new form will then
-alter the velocity distribution function and so on, until a new
-quasi-stationary equilibrium state is attained \cite{gurnett2017}.
-However, depending on the phenomenon being described this saturation
-state reached under the quasilinear approximation might keep on
-evolving if higher order nonlinearities are taken into account
+shape slowly modifies the shape of the wave spectrum, whose
+% LFZ190822: Não seria mesmo "whose"?
+% Sabrina: ok
+new form will alter the velocity distribution function and so
+on, until a new quasi-stationary equilibrium state is attained
+\cite{gurnett2017}. However, depending on the phenomenon being
+described this saturation state reached under the quasilinear
+approximation might keep on evolving if higher order nonlinearities are taken into account
 \cite{akhi2}. This kind of nonlinear analysis is given by the
@@
 results obtained in appended papers. \Cref{cha:final}, summarizes the
-results and presents a brief discussion on the and perspectives of this
-new generalized formalism, and its relevance for the next generation of
+results and discuss some remarking conclusions obtained in this analysis.
+At the end of this chapter, we also deliberate the perspectives for this
+new generalized formalism and its relevance for the next generation of
 solar physics research.
+% LFZ190822: Suponho que aqui devia ser "... a brief discussion on the
+% conclusions obtained and on the perspectives ..." ?
+% Sabrina: Melhorou?
+% and its relevance for the next generation of solar physics research are
+% also deliberated.
 
@@
 point, according to the two-time approximation, the slow time derivative
-is reintroduced \cite{YZKS16}. This procedure results in the nonlinear
+is reintroduced \cite{YZKS16}. We then obtain the nonlinear
+% LFZ190822: Seria melhor evitar a repetição de "This procedure results".
+% Quem sabe aqui se escreve algo como "We then obtain the nonlinear
+% spectral balance equation\footnote{..." ?
+% Sabrina: Sim! Eu nem tinha percebido isso
 spectral balance equation\footnote{Equation \eqref{nlebe} is not in the
@@
 equation, while the real part leads to the wave dispersion equation,
-which solutions are the wave dispersion relations.
+whose solutions 
+% LFZ190822: Não seria "whose solutions", como estava antes?
+%Sabrina: ok
+are the wave dispersion relations.
 
@@
 \mu_{\bf k}^S=|k|^3\lambda_{De}^3\biggl(\frac{m_e}{m_i}\biggr)^{1/2}
-\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},
+\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2}.
 \end{displaymath}
-
+% LFZ190822: Ao final da expressão acima havia um ponto "." e corrigistes
+% colocando uma vírgula. Mas acho que era para ser ponto mesmo, pois a frase
+% acaba ali.
+% Sabrina: ok
 \chapter{Weak turbulence for collisional plasmas}
@@
 are characterized by all ${\bf k}$ and $\omega$. Therefore, the fluctuations
-which $\omega \ne \omega_{\bf k}$, which characterize the noneigenmodes,
+with 
+% LFZ190822: Acho que aqui seria "with", não ''which" (i.e., "the fluctuations 
+% with $\omega\ne\omega_{\bf k}$, which characterize the ...")
+% Sabrina: de fato.
+$\omega \ne \omega_{\bf k}$, which characterize the noneigenmodes,
 are ignored. In Ref. \cite{YZKS16} the authors present a generalization
@@
 frequency range, due to particle scattering. This underlying electrostatic
-form of braking radiation was then called \emph{electrostatic bremsstrahlung}
+form of braking radiation was
+% LFZ190822: Esse "then" me parece desnecessário.
+% Sabrina: ok
+called \emph{electrostatic bremsstrahlung}
 \cite{YZKS16}. For the particle kinetic equation, the application of this
@@
 critical remarks regarding the inclusion of noneigenmodes in the nonlinear
-wave equation. It is worth to mention again, that a more detailed procedure
-of the inclusion of the noneigenmode contribution in the weak turbulence's
+wave equation. It is worth to mention again, that a more detailed description
+of the procedure
+% LFZ190822: Talvez fique melhor "... a more detailed description of the
+% procedures for inclusion of the ..."
+% Sabrina: ok
+for the inclusion of the noneigenmode contribution in the weak turbulence's
 equations can be seen in \cite{YZKS16}.
@@
 oscillations in unmagnetized plasmas, without any \emph{ad hoc} addition.
-Such theory is the basis of the present research, which primary objective
+Such theory is the basis of the present research, in which the
+% LFZ190822: Não seria "whose", como estava antes?
+% Sabrina: troquei para "in which"
+primary objective
 is performing numerical analysis of the generalized weak turbulence equations,
@@
 \label{coll-damp}
-In this first analysis, we have numerically integrated Eqs. \eqref{gammaL}
+In this first analysis, presented in Ref. \cite{Tigik2016b}, we have
+numerically integrated Eqs. \eqref{gammaL}
+% LFZ190822: O artigo está anexado, mas acho que mesmo assim vale dizer qual
+% é o artigo na lista de referências. Algo como
+% "In this first analysis, presented in Ref. \cite{Tigik...}, 
+% we have numerically integrated Eqs. \eqref{gammaL} for ..."
+% Sabrina: ok
 for $L$ waves, and \eqref{gammaS} for $S$ waves, considering Maxwellian
@@
 \label{cha:final}
-In this thesis, we have presented the results of the first analysis of a new
+In this thesis, we have presented the results of the first analyses 
+% LFZ190822: Talvez seja mais correto dizer "of the first analyses ...", que
+% é plural, enquanto que "analysis" é singular.
+% Sabrina: ok
+of a new
 theory, depicted in \Cref{noneigenmode}, which combines collective processes
@@
 differences. This new version, though, is only suitable for fast-waves,
-which is the case of Langmuir oscillations, but the same does not apply
-to ion-sound waves. Moreover, the results for ion-sound waves are quite
+which is the case of Langmuir oscillations, but does not apply to the case
+% LFZ190822: Aqui me parece que ficaria melhor dizer This new version, though,
+% is only suitable for fast waves, which is the case of Langmuir oscillations,
+% but does not apply to the case of ion-sound waves. does not apply
+% Sabrina: ok
+of ion-sound waves. Moreover, the results for ion-sound waves are quite
 well behaved with the original approximation, which is the same that was
-initially used for  $L$ waves. Therefore, $S$ waves will take part only in
+initially used for $L$ waves in Ref.~\cite{YZKS16}.
+% LFZ190822: Acho que aqui cabe continuar dizendo "... for $L$ waves in
+% Ref.~\cite{YZKS16}."
+% Sabrina: ok
+Therefore, $S$ waves will be considered only in
+% LFZ190822: Acho melhor "will be considered", em vez de "will take part"
 \Cref{sec:orig-appr}, while \Cref{sec:alt-approx} will be directed solely
-the $L$ waves expression.
+% LFZ190822: Sugiro "... will be directed solely to the use in expressions
+% related to $L$ waves.", em lugar de "the $L$ waves expression."
+% Sabrina: acho que se eu usar "expressions" vai dar a impressão de que
+% essa aproximação vai ser usada em outra equação que não seja a do
+% electrostatic bremsstrahlung. Não lembro se a gente chegou a usar essa
+% aproximação na expressão do amortecimento colisional. Mas acho que não.
+to the  expression for $L$ waves.
 
@@
 \begin{split}
-\chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
+\chi_a^{(2)}[{\bf k'},&{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
 \simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}\\
-&\times\int d{\bf v''}\,\left\{\frac{T_a}{m_a}
+&\times\int d{\bf v''}\,\biggl\{\frac{T_a}{m_a}
 \frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
 \left[\frac{1}{({\bf k-k'})\cdot{\bf v''}}
-  +\frac{1}{({\bf k'})\cdot{\bf v''}}\right]
-+\underbrace{ \frac{\bf k'\cdot v''}{\bf k\cdot v''} 
++\frac{1}{({\bf k'})\cdot{\bf v''}}\right]\\
+&+\underbrace{ \frac{\bf k'\cdot v''}{\bf k\cdot v''} 
 + \frac{({\bf k}-{\bf k'}){\bf \cdot v''}}{\bf k\cdot v''}}_{=1}
-\right\} F_a({\bf v''}) + i\,{\rm Im}\chi^{(2)}
-\end{split}
-\end{equation}
-where we have used $f_a= \hat{n} F_a$.
-
-%%% Falta algo aqui, ver isso %%%
-% \begin{equation}
-% \chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-% \simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
-% \int d{\bf v''}\,\left[\frac{T_a}{m_a}
-% \frac{{\bf k'}\cdot({\bf k-k'})}{{\bf k}\cdot{\bf v''}}
-% \frac{{\bf k}\cdot {\bf v''}}{({\bf k-k'})\cdot{\bf v''}}+1
-% \right] F_a({\bf v''}) 
-% \end{equation}
-\begin{equation}
-\chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}
-\int d{\bf v''}\,\left[\frac{T_a}{m_a}
+\biggr\} F_a({\bf v''}) + i\,{\rm Im}\chi^{(2)},
+\end{split}
+\end{equation}
+\begin{equation}
+  \begin{split}
+\chi_a^{(2)}[{\bf k'},&{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
+\simeq-i\frac{e_a}{T_a}\frac{\omega_{pa}^2}{k k'|{\bf k-k'}|}\frac{1}{v_{a}^2}\\
+&\times\int d{\bf v''}\,\left[\frac{T_a}{m_a}
 \frac{{\bf k'}\cdot({\bf k-k'})}{({\bf k-k'})\cdot{\bf v''}}+1
 \right] F_a({\bf v''})
-\end{equation}
+\end{split}
+\end{equation}
+where we have used $f_a= \hat{n} F_a$.
 
@@
 
-Due its asymmetry, the terms which are linear in ${\bf v''}$ will vanish
+Due its asymmetry, the terms, which are linear in ${\bf v''}$, will vanish
 when integrated, remaining
@@
 (see Eq. \eqref{dom-freq}), which are high frequency oscillations
-near the electron plasma frequency, it is not suitable for use on
+near the electron plasma frequency, it is not suitable for use in
+% LFZ190822: "on", ou "in"?
+% Sabrina: ok
 the bremsstrahlung expression for $S$ waves.
@@
 development of the work presented in Ref. \cite{Tigik2017a}. 
-The work in question, which title
+The work in question, whose title
+% LFZ190822: Como já comentado em outros lugares, não seria "whose", como 
+% estava antes?
+% Sabrina: ok
 is ``Weakly turbulent plasma processes in the presence of inverse
@@
 
-\chapter{Two-dimensional time evolution of beam-plasma instability in the
-  presence of binary collisions}
+\chapter{Two-dimensional time evolution of beam-plasma
+  instability in the presence of binary collisions}
 \label{master}
-Results of the Master's dissertation that led to the current doctoral
-research.
+The paper included in this appendix is the complete text of Ref.
+\cite{Tigik2016a}, which summarizes the outcomes of the Master's
+dissertation \cite{Tigik2015} that led to the current doctoral
+research. This text was included here with the intention to give
+the reader a complete view of the work developed during my graduate
+studies.
+
 \includepdf[pages=-]{Tigik2016a.pdf}

### 2019-08-24 ty.tex
*** empty log message ***

%\newpage
\pagestyle{empty}
\chapter*{Acknowledgements}
% \begin{center}
% {\centering{\chapter*{Acknowledgements}}}
% \end{center}
\begin{quote}
% Sou grata ao Prof. Luiz Fernando Ziebell pela excelente orientação.
% Sua grande dedicação em ensinar, sua disponibilidade para solucionar
% dúvidas e sua imensa paciência foram decisivos para a execução deste
% trabalho. Também sou grata aos colegas de Grupo pela agradável convivência
% e pela constante troca de conhecimento.

% Agradeço aos amigos da ``CG''. À Amanda, à Lais e à Nicole pelas
% diversas e divertidas conversas sobre ``a vida o universo e tudo mais''.
% Ao Demétrius e ao Vinícius pelas discussões sem sentido mais engraçadas
% e irritantes que já tive.

% Reservo um agradecimento especial à minha família, que tanto me apoiou.
% Ao meu marido pelo companheirismo e incentivo. Ao meu filho por nortear 
% a minha vida e enchê-la de emoções. À minha mãe pelo amor e pela dedicação
% à minha educação. Amo vocês.
\end{quote}

### 2019-11-11 thesis.tex
added acknowledgements and epigraph
first corrections

@@
 %\input{folhadeaprovacao}
-%\input{ty}
-%\input{epi}
+% \input{ty}
+% \input{epi}
 %\input{resumo}
@@
 \label{cha:kin-theo}
+
 The kinetic theory is the most fundamental description of the
@@
 dynamics is given by the Vlasov-Maxwell system, which is composed
-by the Vlasov movement equation
+of the Vlasov movement equation
 \begin{equation}
@@
 here given in cgs units, as commonly used in the
-plasma physics literature.
+;plasma physics literature.
 
@@
 
-In the above equation we have two possibilities to the wave-number
+In the above equation we have two possibilities for the wave-number
 frequency space. If one is interested in the region of $({\bf k},\omega)$
@@
   \,{\bf q}\cdot\frac{\partial \Phi_e}{\partial{\bf u}}\biggr)
-  +P_{\bf q}^{\sigma L}+2\gamma_{\bf q}^{\sigma L}\calE_{\bf q}^{\sigma L}\approx 0,
+  +P_{\bf q}^{\sigma L}+2\gamma_{\bf q}^{\sigma L}{\cal E}_{\bf q}^{\sigma L}\approx 0,
   \label{asymp}
@@
 
+\chapter{Microscopic equations for a fully ionized plasma}
+\label{appF}
+Plasmas are ionized gases that exhibit collective behavior. Usually composed
+of positive and negative charges and neutral particles, a plasma is said to
+be \emph{neutral} when the quantity of particles with opposite charges is the
+same~\cite{klimo}, and \emph{nonneutral} when it is constituted - or have a
+significant excess - of one kind of charge~\cite{DavidsonNonNeutral}. In this
+work, it will be considered a fully ionized hydrogen plasma, which is overall
+neutral, with the number of protons and electrons being the same.
+
+Electrons and ions are sources of electric and magnetic fields. Due to the
+long-range nature of these fields, particles can interact simultaneously, at
+distance, with several other particles in the system. The effective range of
+the interactions among charges is determined by the \emph{Debye length}
+\begin{equation}
+  \label{debye}
+  \lambda_{De}=\sqrt{\frac{T_a}{4\pi n_a e_a^2}},
+\end{equation}
+where $a=i$ for ions and $a=e$ for electrons. This means that a specific charge
+will interact effectively only with other charges that are inside of a virtual
+sphere with radius given by $\lambda_{De}$, being almost completely shielded
+from the influence of particles outside the \emph{Debye sphere}. I say almost
+because there are small fluctuations in the \emph{Debye shielding}; they are
+behind the complex self-consistent collective behavior of plasmas.
+
+Such characteristic ads a layer of complexity in the plasma dynamics, that does
+not exists in the description of neutral gases. For instance, the microscopic
+state of a plasma is not
+
 \end{appendix}

### 2019-11-12 thesis.tex
*** empty log message ***

@@
 \label{cha:kin-theo}
-
-The kinetic theory is the most fundamental description of the
-plasma dynamics. Based on the concepts and methods of statistical
-mechanics, together with the Maxwell equations, it provides a
-formal self-consistent evolution of the plasma processes. This
-formalism takes into account the variations of the velocity
-distribution function $f({\bf r},{\bf v},t)$ in the phase-space
-for each particle species. Statistically, this means that the
-product between the distribution function and the volume element
+Plasmas are ionized gases that exhibit collective behavior. Usually composed
+of positive and negative charges and neutral particles, a plasma is said to
+be \emph{neutral} when the quantity of particles with opposite charges is the
+same~\cite{klimo}, and \emph{nonneutral} when it is constituted - or have a
+significant excess - of one kind of charge~\cite{DavidsonNonNeutral}. In this
+work, it will be considered a fully ionized hydrogen plasma, which is overall
+neutral. In such case, the density of protons and electrons per volume unity
+is the same, therefore $n_e=n_i=n$.
+
+Electrons and ions are sources of electric and magnetic fields. Due to the
+long-range nature of these fields, particles can interact simultaneously, at
+distance, with several other particles in the system. The effective range of
+the interactions among charges is determined by the \emph{Debye length}
+\begin{equation}
+  \label{debye}
+  \lambda_{De}=\sqrt{\frac{k_BT_e}{4\pi n e^2}},
+\end{equation}
+where $T_e$ is the electron temperature, $k_B$ the Boltzmann constant, $n$
+the plasma density and $e$ the charge. This means that a specific charge
+will interact effectively only with other charges that are inside of a
+virtual sphere with radius given by $\lambda_{De}$, being almost completely
+shielded from the influence of particles outside the \emph{Debye sphere}.
+
+The kinetic theory is the most fundamental description of the plasma
+dynamics. Based on the concepts and methods of statistical mechanics,
+together with the Maxwell equations, it provides a formal self-consistent
+evolution of the plasma processes. This formalism takes into account the
+variations of the velocity distribution function $f({\bf r},{\bf v},t)$
+in the phase-space for each particle species. Statistically, this means
+that the product between the distribution function and the volume element
 in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
@@
 work, it will be considered a fully ionized hydrogen plasma, which is overall
-neutral, with the number of protons and electrons being the same.
+neutral, with the density of protons and electrons being the same, therefore
+$n_e=n_i=n$.
 
@@
   \label{debye}
-  \lambda_{De}=\sqrt{\frac{T_a}{4\pi n_a e_a^2}},
-\end{equation}
-where $a=i$ for ions and $a=e$ for electrons. This means that a specific charge
-will interact effectively only with other charges that are inside of a virtual
-sphere with radius given by $\lambda_{De}$, being almost completely shielded
-from the influence of particles outside the \emph{Debye sphere}. I say almost
-because there are small fluctuations in the \emph{Debye shielding}; they are
-behind the complex self-consistent collective behavior of plasmas.
-
-Such characteristic ads a layer of complexity in the plasma dynamics, that does
-not exists in the description of neutral gases. For instance, the microscopic
-state of a plasma is not
+  \lambda_{De}=\sqrt{\frac{k_BT_e}{4\pi n e^2}},
+\end{equation}
+where $T_e$ is the electron temperature, $k_B$ the Boltzmann constant, $n$
+the plasma density and $e$ the charge. This means that a specific charge
+will interact effectively only with other charges that are inside of a
+virtual sphere with radius given by $\lambda_{De}$, being almost completely
+shielded from the influence of particles outside the \emph{Debye sphere}.
 

### 2019-11-12 ty.tex
*** empty log message ***

@@
 % \end{center}
-\begin{quote}
-% Sou grata ao Prof. Luiz Fernando Ziebell pela excelente orientação.
-% Sua grande dedicação em ensinar, sua disponibilidade para solucionar
-% dúvidas e sua imensa paciência foram decisivos para a execução deste
-% trabalho. Também sou grata aos colegas de Grupo pela agradável convivência
-% e pela constante troca de conhecimento.
+%\begin{quote}
+To my supervisor Luiz Fernando Ziebell, whose guidance, encouragement,
+and patience (tons of) made this work possible. Particularly, I would
+like to state my sincere appreciation for the trusting he always
+demonstrated to have in my capabilities for developing high-quality
+research and for his availability to help me when I needed. Professor,
+I am grateful for all these years of learning and fruitful work that
+are culminating in this doctoral thesis.
 
-% Agradeço aos amigos da ``CG''. À Amanda, à Lais e à Nicole pelas
-% diversas e divertidas conversas sobre ``a vida o universo e tudo mais''.
-% Ao Demétrius e ao Vinícius pelas discussões sem sentido mais engraçadas
-% e irritantes que já tive.
+To Peter Yoon, for the all the collaboration and for receiving me in
+the University of Maryland. Peter, I also want to thank you for all
+the encouragement in this beginning of career. That meant a lot to me.
 
-% Reservo um agradecimento especial à minha família, que tanto me apoiou.
-% Ao meu marido pelo companheirismo e incentivo. Ao meu filho por nortear 
-% a minha vida e enchê-la de emoções. À minha mãe pelo amor e pela dedicação
-% à minha educação. Amo vocês.
-\end{quote}
+To Dr. Adolfo Viñas who dedicated a part of his time to teach me PIC
+simulation and discuss the subtleties of kinetic theory of plasmas.
+Dr. Viñas, thank you very much for your time and your availability.
+
+To my friends that never let me down. Nicole for the companionship, life
+
+To my family for the patience, support and for always stand by me even
+when I just needed to be alone to do my work. Gabriel,
+
+%\end{quote}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "thesis"
+%%% End:

### 2019-11-12 draft.tex
*** empty log message ***

@@
 be said about the dominant dynamics of the ionized gas, since neutral and
-charged particles have quite a distinct behavior? The neutral particles,
+charged particles have quite a distinct behavior? Neutral particles,
 assuming that the gravitational force is negligible, will move freely
@@
 
-On Earth, the plasma is considered an exotic state of matter, associated to the
+On Earth, the plasma is considered an exotic state of matter, associated with the
 glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
@@
 % \cite{tsytotp}. The complex processes
+
+% It is well known that the plasma in our solar system is considered as a natural
+% laboratory for the study of space plasma. The wide variety of plasma phenomena
+% accessible to direct, in situ measurements and highly resolved remote sensing,
+% might be scaled to other astrophysical environments. Besides that, theoretical
+% models developed to explain phenomena observed in the solar system plasma might
+% be extrapolated to describe plasma process occurring in more extreme astrophysical
+% systems.
+
+% Astrophysical plasmas are observed in a vast range of densities, temperatures,
+% magnetic fields, and scale lengths\footnote{The description of such an extensive
+%   list is out of the scope of this text. On that matter, Ref.~\cite{peratt2014}
+%   offers a quite complete exposure of space plasma, and space plasma phenomena
+%   occurring in all cosmic scales.}.
+
+% With some exotic exceptions, like the super
+% dense and degenerate plasma of white dwarfs (which is beyond the applicability
+% of our theory), the solar system hosts a large variety of plasma whose properties
+
+%Plasma is a gas in which the atoms -or molecules- are in an ionized state.
+% In such condition, long-range electric and magnetic forces determine the
+% interactions of the charged particles. This coupling between the variations
+% in the electric and magnetic fields and the motion of ions and electrons
+% is the cause of the wide variety of oscillatory processes that characterize
+% the plasma dynamics\cite{tsytotp}.
+
+% In this thesis, we present a theoretical model for the inclusion of single
+% particle fluctuations and collisional processes related to electrostatic
+% oscillation in rarefied, unmagnetized, non-relativistic and fully ionized
+% plasmas.
+
+% The problems in solar physics addressed by our theory are related to three
+% specific regions of the wide range of action of the solar plasma: solar activity
+% regions \cite{Tigik2016a}, transition region between the chromosphere and solar
+% corona \cite{Tigik2017a} and the solar wind \cite{Tigik2017b}. The paper
+
+% In this appendix we provide a brief discussion about the space plasma phenomena
+% that are addressed by our theory.
+
+% In this text we presented three papers that were published during this Ph.D.
+% research, \cite{Tigik2016b,Tigik2017a,Tigik2017b}, and each one of them
+% address a different problem in solar physics. There is also another article,
+% \cite{Tigik2016a}, which corresponds to the results of the Master's
+% dissertation that served as basis for this project.
+
+% Each one of the four papers published during this graduate studies is 
+% different solar physics phenomena
+
+% In order to offer a deeper insight on the solar phenomena 
+% In this appendix, we make a brief description of the solar processes that are
+% being addressed by our theory.
+
+% The Sun is a G2 main-sequence star. From the stellar astrophysics point
+% of view, it is considered ordinary, without any unique property that could
+% differentiate it from other main-sequence stars; except for the fact that
+% it is remarkably close to us. These two facts make the Sun a perfect model
+% of study not only for several areas of astrophysics, like stellar structure
+% and evolution, but also for plasma physics.
+
+% The theory developed during this graduate research makes use of solar physics
+% results to contribute on both sides. In \cite{Tigik2016a},
+% \cite{Tigik2016b} and \cite{Tigik2017b}, we present theoretical and
+% numerical evidence of plasma processes that might aid in the interpretation
+% and accurate modeling  of phenomena observed in the solar plasma. While in
+% \cite{Tigik2017a}, we introduce a new equation depicting an unknown process
+% and numerically analyze it in the context of solar physics; its existence
+% outside theory, however, will depend on the development of more advanced
+% space probes to be confirmed.
+ ------------------------------------------------------------------------
+
+% Investigations of the origin and behavior of the solar wind, energetic
+% particles, and magnetic fields in the heliosphere and their interaction
+% with Earth and other planets, as well as with the interstellar medium.
+% Investigations of the physics of magnetospheres, including fundamental
+% interactions of plasmas and particles with fields and waves, and coupling
+% to the solar wind and ionospheres.
+% Investigations of the physics of the terrestrial mesosphere, thermosphere,
+% ionosphere, including the coupling of these phenomena to the lower atmosphere
+% and magnetosphere.
+
+% % The appearance of sunspots is a sign of
+% % solar activity, characterized by solar flares and coronal mass ejections.
+
+% This enhanced flux of energetic particles and radiation have direct impact
+% in the \emph{space weather} around Earth, triggering geomagnetic storms
+% that
+
+% Inside the heliosphere, the Sun, the space environment around Earth and the
+% interplanetary medium are extensively explored by space probes.
+%% say something about it
+
+% \begin{itemize}
+% \item The magnetic dynamo processes involved in the generation and variability
+%   of magnetic fields in the Sun, and how it determines the dynamics of the
+%   11-year solar cycle of solar activity \cite{Charbonneau2005};
+% \item The role of magnetic reconnection in the coronal mass ejection process
+%   \cite{Qiu2005};
+% \item The coronal heating problem \cite{Vinas2000,PP14,Pezzi2017};
+% \item   
+% \end{itemize}
+ % On that regard, a critical aspect being addressed is the response of Earth’s
+ % magnetosphere, ionosphere, and atmosphere to solar inputs.
+ % Ref. \cite{schrijver2009}
+
+% \usepackage[inline]{enumitem}
+% \begin{enumerate*}[label={\alph*)},font={\bfseries}]
+% \item very rarefied plasmas, where collisions can be completely neglected,
+%   and
+% \item extremely fast phenomena, where the quasi-steady state is attained before
+%   collisions can affect the dynamics.
+% \end{enumerate*}
+
+% , and have
+% been a successful approach for describing kinetic oscillatory instabilities
+% and micro-turbulent processes
+
+% As pointed in the introduction, the kinetic theory of plasmas is mostly
+% concerned with processes that involve waves and oscillatory instabilities.
+% Kinetic instabilities depend on the inter-particle displacement and the
+% electrostatic and electromagnetic oscillatory modes that arise as a response.
+% This kind of physics cannot be described using a macroscopic approach like
+% magnetohydrodynamics (MHD), that treat the plasma as magnetized, incompressible
+% fluid. A single-particle description is also out of the question because it
+% is both mathematically and computationally prohibitive. Statistical mechanics,
+% however, suits very well for the problem. But, as the reader could have noticed,
+% the kinetic description of plasmas is quite cumbersome and requires a lot of
+% approximations to get to any result. This does not mean that kinetic theory is
+% incapable to provide a reliable description of kinetic oscillatory instabilities
+% and micro-turbulent processes in real-world plasmas.
+
+ % On Earth, the plasma is considered an exotic state of matter, associated to the
+% glowing gas inside fluorescent and neon lamps, microchip manufacturing, research
+% laboratories, and the promise of cleaner and practically inexhaustible energy
+% source once we have controlled and energetically efficient thermonuclear fusion
+% \cite{bell}. Naturally occurring plasmas in our everyday life are rare, restricted
+% to the occurrence of lightning during storms, flames, and the beautiful auroras
+% that take place at high latitudes. In the space, however, the situation is the
+% opposite. Starting in the outer layers of Earth's atmosphere, passing through the
+% solar wind in the interplanetary space, to the stellar interiors and atmospheres,
+% accretion disks, and molecular clouds it is estimated that something around
+% $99 \sim 99.9\%$ of the observable matter in the universe is in the plasma state
+% \cite{may}. So understanding the basic physics of plasma processes might help on
+% interpreting and describing
+
+% The analysis presented in this doctoral thesis has relevant contributions in the
+% study of the combined action of nonlinear kinetic instabilities and collisional
+% processes in unmagnetized, fully ionized, hydrogen plasmas. Though the plasma's
+% profile under consideration might be considered quite idealized, the physical
+% processes that are being addressed have fundamental character - the plasma waves
+% under consideration and the particle interactions are inherent to any plasma.
+% The underlying nature of these processes means that they might impact the plasma
+% dynamics at different astrophysical environments and also in laboratory plasmas.
+% Laboratory plasmas, however, are usually constrained by specific experimental
+% set-up. This specificity would require in-depth knowledge and maybe access to
+% one experiment, which makes the analysis in the experimental context restrictive
+% and counterproductive. A more broad approach was then to compare our theoretical
+% results with phenomena observed in the naturally occurring space plasma.
+
+% \footnote{In the literature, the term ``astrophysical
+%   plasma'' is sometimes used to refer to the plasma observed outside the solar
+%   system, while ``space plasma'' is used to account for the plasma in our
+%   interplanetary space. In this text, however, both terms are being used as
+%   synonyms.}
+
+% \footnote{A comprehensive description of the scales and characteristics of
+% cosmic plasmas can be seen in Section 1.2 of Ref. \cite{peratt2014}.}
+
+% The plasma is a collection of ions, electrons and neutral particles that has
+% its dynamics dominated by the electric and magnetic fields, generated by the
+% electrically charged particles and the electric currents related to their
+% motion, respectively. Due to the long-range nature of these self-generated
+% fields, one particle affects the movement of several other particles, which
+% will interact with other particles, and so on. This \emph{collective behavior}
+% \footnote{A detailed exposition of all the processes and conditions that
+%   characterize the collective behavior in plasmas, can be accessed in the
+%   following introductory books \cite{bitt,gurnett2017,chen,DavidsonNonNeutral}.}
+% is what characterizes an ionized gas as a plasma, and is also the reason
+% behind the complexity of the plasma dynamics. This complexity comes in the
+% form of a myriad of self-consistent oscillatory processes, where the electric
+% and magnetic fields affect - and are affected by - the position and motion of
+% the charges, and how they vary in time \cite{chen}.
+
+% A complete description of such a complicated dynamics would depend on determining
+% the position and momentum of each particle, and their respective microscopic
+% electric and magnetic fields, in a given instant in time. This strategy is not
+% practical and in most of the cases not feasible for many-body systems, like the
+% plasma. However, this microscopic description can be dealt through a hierarchy of
+% approximations, leading to the three main theories of plasma physics: kinetic,
+% multi-fluid, and magnetohydrodynamics (MHD). The use of each one of these
+% formulations will depend on the phenomenon that needs to be described.
+
+Em \cite{klimo} somos apresentados a uma formulação microscópica que combina
+os métodos da mecânica clássica para a descrição da variação da posição e do 
+momentum das partículas, com as equações de Maxwell para a descrição dos campos 
+microscópicos gerados pela movimentação das partículas. Dessa forma, o
+estado de um plasma ficaria definido se conseguíssemos determinar as
+coordenadas e os momenta de todas as partículas, bem como os valores dos
+campos elétrico e magnético em cada ponto, em um determinado instante do
+tempo. Com isso, teoricamente, conseguiríamos montar um sistema de equações
+que descreveria a evolução temporal do sistema, bastando para isso que
+determinássemos as condições iniciais de posição e de momentum para as
+partículas e as condições iniciais para os campos.
+
+Contudo, como mencionado anteriormente, essa abordagem é impraticável, devido
+a imensa quantidade de partículas que compõem um plasma.
+Entretanto, essa formulação pode ser aproximada, permitindo que obtenhamos
+uma descrição macroscópica das propriedades do plasma. Existe uma hierarquia
+de aproximações que leva às três principais teorias da física de plasmas:
+cinética, multi-fluido e magnetoidrodinâmica (MHD). Essas teorias são 
+aplicáveis em diferentes contextos, dentro da gama de fenômenos e de condições
+que podem ocorrer em um plasma. Como o assunto deste trabalho envolve a
+evolução de processos físicos que dependem de detalhes da distribuição de
+velocidades das partículas, precisamos aplicar a mais fundamental das três
+formulações, a teoria cinética.
+
+A teoria cinética de plasmas consiste na aplicação dos métodos e conceitos da 
+mecânica estatística, em conjunto com as equações de Maxwell, para obter uma
+descrição macroscópica formal da evolução de um plasma. Este será nosso
+ponto de partida.
+
+% This means that a specific charge
+% will interact effectively only with other charges that are inside of a
+% virtual sphere with radius given by $\lambda_{De}$, being almost completely
+% shielded from the influence of particles outside the \emph{Debye sphere}.
+% These interactions 
+% It is almost because, in the presence of thermal motion, there are small
+% fluctuations , creating \emph{Debye shielding}; they are behind the complex
+% self-consistent collective behavior of plasmas.

### 2019-11-14 thesis.tex
kinetic theory

@@
 In such cases, the plasma dynamics may be described by the Vlasov-Maxwell
-system, a complex set of coupled equations whose
-%which 
-% LFZ190822: Posso estar enganado, mas me parece que aqui seria mesmo
-% "whose", como estava antes, e não "which".
-% Sabrina: resolvi colocar "whose" de novo depois de uma rápida, mas
-% controversa, pesquisa no google
-solution invariably will
-depend on some degree of approximation. In the presence of small
+system, a complex set of coupled equations whose solution invariably
+will depend on some degree of approximation. In the presence of small
 amplitude oscillations in a fully ionized plasma, we can make use
@@
 Under such condition, the gradual changing on the velocity space
-shape slowly modifies the shape of the wave spectrum, whose
-% LFZ190822: Não seria mesmo "whose"?
-% Sabrina: ok
-new form will alter the velocity distribution function and so
-on, until a new quasi-stationary equilibrium state is attained
-\cite{gurnett2017}. However, depending on the phenomenon being
-described this saturation state reached under the quasilinear
-approximation might keep on evolving if higher order nonlinearities are taken into account
-\cite{akhi2}. This kind of nonlinear analysis is given by the
+shape slowly modifies the shape of the wave spectrum, whose new form
+will alter the velocity distribution function and so on, until a new
+quasi-stationary equilibrium state is attained \cite{gurnett2017}.
+However, depending on the phenomenon being described this saturation
+state reached under the quasilinear approximation might keep on evolving
+if higher order nonlinearities are taken into account \cite{akhi2}.
+This kind of nonlinear analysis is given by the
 \emph{weak turbulence theory}, which is the next step in this chain
@@
 \label{cha:kin-theo}
-Plasmas are ionized gases that exhibit collective behavior. Usually composed
-of positive and negative charges and neutral particles, a plasma is said to
-be \emph{neutral} when the quantity of particles with opposite charges is the
-same~\cite{klimo}, and \emph{nonneutral} when it is constituted - or have a
-significant excess - of one kind of charge~\cite{DavidsonNonNeutral}. In this
-work, it will be considered a fully ionized hydrogen plasma, which is overall
-neutral. In such case, the density of protons and electrons per volume unity
-is the same, therefore $n_e=n_i=n$.
+Plasmas are ionized gases that exhibit collective behavior. Composed of
+positive and negative charges and neutral particles, a plasma is said to
+be \emph{neutral} when the quantity of particles with opposite charges is
+the same~\cite{klimon}, and \emph{nonneutral} when it is constituted - or
+have a significant excess - of one kind of charge~\cite{DavidsonNonNeutral}.
+For the present work, we assume a fully ionized hydrogen plasma, which is
+overall neutral and does not contain any neutral particle. In such a case,
+half the total number of particles is given by protons and the other half
+by electrons.
 
@@
 distance, with several other particles in the system. The effective range of
-the interactions among charges is determined by the \emph{Debye length}
+these interactions is determined by the \emph{Debye length}
 \begin{equation}
@@
 where $T_e$ is the electron temperature, $k_B$ the Boltzmann constant, $n$
-the plasma density and $e$ the charge. This means that a specific charge
-will interact effectively only with other charges that are inside of a
+the plasma density and $e$ the electron charge. This means that a specific
+charge will interact effectively only with other charges that are inside of a
 virtual sphere with radius given by $\lambda_{De}$, being almost completely
 shielded from the influence of particles outside the \emph{Debye sphere}.
+The self-consistent interaction between charged particles and electric and
+magnetic fields, creates fluctuations in the local neutrality of the plasma,
+giving rise to the series of oscillations and complex wave phenomena that
+characterize the plasma’s collective behavior~\cite{chen}.
+
+Describing the precise state of a plasma, in a given time, would require
+the knowledge of the $6N$ phase-space coordinates of each particle, and also
+the microscopic amplitudes of the electric and magnetic fields at each point
+in space. Such exact representation is clearly a non-practical approach for
+a many-body system like the plasma. However, this microscopic formulation
+can be approximated to a macroscopic description by taking the average of
+the microscopic quantities and making suitable assumptions to truncate the
+correlation functions at an appropriate point~\cite{klimon}. This will lead
+to the plasma kinetic equations, which is the first of a hierarchy of
+approximations that also includes the multi-fluid and magnetohydrodynamic
+theories. The application of each one of these formulations will depend on
+the context and the scale of the phenomena being described~\cite{chen}.
+In this work we are interested in small-scale processes that depend on
+velocity-space properties, requiring a kinetic description of the plasma.
 
@@
 in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
-represents the probability of finding a particle of species
-$\alpha$ in a volume element $d^3r$ around ${\bf r}$ and in a
-velocity volume element $d^3v$ around ${\bf v}$, at the instant
-$t$ \cite{klimo,klimon}.
+represents the probability of finding a particle of species $\alpha$ in a
+volume element $d^3r$ around ${\bf r}$ and in a velocity volume element
+$d^3v$ around ${\bf v}$, at the instant $t$ \cite{klimon}.
+
+In a first approximation, the plasma dynamics is described by the
+Boltzmann equation
+\begin{equation}
+\frac{\partial f_\alpha({\bf r},{\bf v},t)}{\partial t}
++{\bf v \cdot \nabla_r}f_\alpha({\bf r},{\bf v},t)
+ +\frac{{\bf F}}{m_\alpha} {\bf\cdot \nabla_v}f_\alpha({\bf r},{\bf v},t)
+=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{coll}.
+\label{boltz}
+\end{equation}
 
@@
 between the averaged kinetic energy of the particles per volume unity
-$\calE_{kin}=\bar n m<v^2>/2$, and the energy density $\calE_f$, which
+${\cal E}_{kin}=\bar n m<v^2>/2$, and the energy density ${\cal E}_f$, which
 is associated with the fluctuations of the perturbative electric field.
@@
   \label{eq:weak}
-  \calE_f \ll \calE_{kin},
+  {\cal E}_f \ll {\cal E}_{kin},
 \end{equation}
@@
 
-\chapter{Microscopic equations for a fully ionized plasma}
-\label{appF}
-Plasmas are ionized gases that exhibit collective behavior. Usually composed
-of positive and negative charges and neutral particles, a plasma is said to
-be \emph{neutral} when the quantity of particles with opposite charges is the
-same~\cite{klimo}, and \emph{nonneutral} when it is constituted - or have a
-significant excess - of one kind of charge~\cite{DavidsonNonNeutral}. In this
-work, it will be considered a fully ionized hydrogen plasma, which is overall
-neutral, with the density of protons and electrons being the same, therefore
-$n_e=n_i=n$.
-
-Electrons and ions are sources of electric and magnetic fields. Due to the
-long-range nature of these fields, particles can interact simultaneously, at
-distance, with several other particles in the system. The effective range of
-the interactions among charges is determined by the \emph{Debye length}
-\begin{equation}
-  \label{debye}
-  \lambda_{De}=\sqrt{\frac{k_BT_e}{4\pi n e^2}},
-\end{equation}
-where $T_e$ is the electron temperature, $k_B$ the Boltzmann constant, $n$
-the plasma density and $e$ the charge. This means that a specific charge
-will interact effectively only with other charges that are inside of a
-virtual sphere with radius given by $\lambda_{De}$, being almost completely
-shielded from the influence of particles outside the \emph{Debye sphere}.
-
 \end{appendix}

### 2019-11-15 thesis.tex
FTFY

@@
 
-The kinetic theory is the most fundamental description of the plasma
-dynamics. Based on the concepts and methods of statistical mechanics,
-together with the Maxwell equations, it provides a formal self-consistent
-evolution of the plasma processes. This formalism takes into account the
-variations of the velocity distribution function $f({\bf r},{\bf v},t)$
-in the phase-space for each particle species. Statistically, this means
+Based on the concepts and methods of statistical mechanics, together with the
+Maxwell equations, the kinetic theory is the most fundamental description of
+the plasma dynamics, providing a formal, self-consistent evolution of plasma
+processes. As in the case of neutral gases, the kinetic formalism of plasmas
+takes into account the variations of the velocity distribution function
+$f({\bf r},{\bf v},t)$ in the phase-space, for each particle species.
+Statistically, this means
 that the product between the distribution function and the volume element

### 2019-11-18 thesis.tex
untouched Vlasov approach
This is the last version before a big change in the previous version of the thesis

@@
 $f({\bf r},{\bf v},t)$ in the phase-space, for each particle species.
-Statistically, this means
-that the product between the distribution function and the volume element
-in the hexa-dimensional phase-space $f_\alpha({\bf r},{\bf v},t)d^3r d^3v$
-represents the probability of finding a particle of species $\alpha$ in a
-volume element $d^3r$ around ${\bf r}$ and in a velocity volume element
-$d^3v$ around ${\bf v}$, at the instant $t$ \cite{klimon}.
+Statistically, this means that the product between the distribution function
+and the volume element in the hexa-dimensional phase-space
+$f_\alpha({\bf r},{\bf v},t)d^3r d^3v$ represents the probability of finding
+a particle of species $\alpha$ in a volume element $d^3r$ around ${\bf r}$
+and in a velocity volume element $d^3v$ around ${\bf v}$, at the instant $t$
+\cite{klimon}.
 
@@
 \end{equation}
+
+Above, in the left-hand side, the differential vector operators $\nabla_{\bf r}$
+and $\nabla_{\bf v}$ represent, respectively, gradients in space ($x,y,z$) and
+velocity ($v_x, v_y,v_z$) coordinates. The quantity ${\bf F}$ is the acting
+force in the system, and  $m_{\alpha}$ is the mass of the particles of kind
+$\alpha$, which in a fully ionized plasma can assume two values: electrons
+$\alpha=e$  and ions  $\alpha=i$. The right-hand side depicts the temporal
+variation of the velocity distribution function due to collisional interactions
+between the system's particles.
+
+For plasmas, in the general case, the acting force in Eq. \eqref{boltz}, is
+given by the Lorentz force added by an external force, which, at kinetic scales,
+is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
+  use of cgs units will be consistent trough all this work.}, ${\bf F}$ has the
+following form
+\begin{equation}
+  {\bf F}=\sum_{\alpha}q_{\alpha}\left[{\bf E}({\bf r},t)
+    +\frac{1}{c}{\bf v \times B}({\bf r},t)\right]
+  +{\bf F_{ext}},
+  \label{florentz}
+\end{equation}
+where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, ${\bf E}$
+and ${\bf B}$ are the electric and magnetic fields, respectively, and $c$ is
+the speed of light.
+
+\section{The Vlasov approach}
+\label{vlasov-appr}
 

### 2019-11-19 thesis.tex
*** empty log message ***

@@
  +\frac{{\bf F}}{m_\alpha} {\bf\cdot \nabla_v}f_\alpha({\bf r},{\bf v},t)
-=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{coll}.
+=\left(\frac{\partial f_\alpha ({\bf r},{\bf v},t)}{\partial t}\right)_{\rm coll}.
 \label{boltz}
@@
 
-Above, in the left-hand side, the differential vector operators $\nabla_{\bf r}$
-and $\nabla_{\bf v}$ represent, respectively, gradients in space ($x,y,z$) and
-velocity ($v_x, v_y,v_z$) coordinates. The quantity ${\bf F}$ is the acting
+Above, on the left-hand side, the differential vector operators $\nabla_{\bf r}$
+and $\nabla_{\bf v}$ represent, respectively, the gradients in ($x,y,z$) space
+and ($v_x, v_y,v_z$) velocity coordinates. The quantity ${\bf F}$ is the acting
 force in the system, and  $m_{\alpha}$ is the mass of the particles of kind
-$\alpha$, which in a fully ionized plasma can assume two values: electrons
+$\alpha$, which, in a fully ionized plasma, can assume two values: electrons
 $\alpha=e$  and ions  $\alpha=i$. The right-hand side depicts the temporal
@@
 \end{equation}
-where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, ${\bf E}$
-and ${\bf B}$ are the electric and magnetic fields, respectively, and $c$ is
-the speed of light.
-
-\section{The Vlasov approach}
-\label{vlasov-appr}
-
-As mentioned before, in the absence of collisions, the plasma
-dynamics is given by the Vlasov-Maxwell system, which is composed
-of the Vlasov movement equation
+where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, $c$ is
+the speed of light, and ${\bf E}({\bf r},t)$ and ${\bf B}({\bf r},t)$ are
+the electric and magnetic fields, respectively.
+
+Collisional interactions can be neglected when the time necessary for
+the plasma to establish statistical equilibrium - the relaxation time
+$\tau_{\rm rel}$ - is much greater than the characteristic time $\tau$
+of the process being studied~\cite{klimon,Tigik2015}.
+% The relaxation time of a plasma is defined
+% as follows $\tau_{\rm rel}=\lambda_{De}/v_{th}g$, where $\lambda_{De}$ is
+% given by Eq. \eqref{debye}, $v_{th}$ is the thermal velocity, and $g$
+% is the plasma parameter.
+
+\section{Vlasov-Maxwell system of equations}
+\label{vlasov-maxwell}
+As mentioned before, in the absence of collisions, the plasma dynamics is given
+by the Vlasov-Maxwell system, which is composed of the Vlasov movement equation
 \begin{equation}
@@
     {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
-    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t},
+    +\frac{1}{c}\frac{\partial{\bf E}}{\partial t}.
 \end{eqnarray}
-here given in cgs units, as commonly used in the
-;plasma physics literature.
+% here given in cgs units, as commonly used in the plasma physics literature.
 

### 2019-11-20 thesis.tex
more discussion

@@
 $\alpha=e$  and ions  $\alpha=i$. The right-hand side depicts the temporal
-variation of the velocity distribution function due to collisional interactions
-between the system's particles.
-
-For plasmas, in the general case, the acting force in Eq. \eqref{boltz}, is
-given by the Lorentz force added by an external force, which, at kinetic scales,
+variation of the velocity distribution function due to collisions between the
+system's particles.
+
+Collisional interactions are the central point of the present thesis.
+However, the formalism presented in \Cref{noneigenmode}, departs from
+the weak turbulence equations, which are the nonlinear approximation of
+the kinetic equations for low-amplitude instabilities in a collisionless
+plasma. The contribution of the correlations between \emph{source}
+fluctuations, that account for collisional interactions  (see.~\cite{
+  klimon,Tigik2015}), are then retrieved by the inclusion of noneigenmode
+contribution in both wave and particle kinetic equations. The difference
+of this new approach is that
+
+%% ~\cite{klimon,Tigik2015}
+
+\section{The Vlasov approach}
+\label{vlasov-appro}
+Collisional interactions can be neglected when the time necessary for
+the plasma to establish statistical equilibrium is much greater than the
+characteristic time of the process being studied. In this section, we
+present a brief discussion about the necessary set of assumptions that
+allow us to disregard the effect of collisions in dilute plasmas. In the
+sequence we present the complete set of self-consistent equations for
+a collisionless plasma.
+
+% Let $\tau_{\rm rel}$ be the time necessary for the plasma to establish
+% statistical equilibrium, i.e, the relaxation time.
+
+the relaxation time $\tau_{\rm rel}$ 
+% The relaxation time of a plasma is defined
+% as follows $\tau_{\rm rel}=\lambda_{De}/v_{th}g$, where $\lambda_{De}$ is
+% given by Eq. \eqref{debye}, $v_{th}$ is the thermal velocity, and $g$
+% is the plasma parameter.
+
+As mentioned before, in the absence of collisions, the plasma dynamics is given
+by the Vlasov-Maxwell system, which is composed of the Vlasov movement equation
+\begin{equation}
+  \label{eq:vlasov}
+  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
+  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
+  +\frac{\bf F}{m_{\alpha}}
+  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0.
+\end{equation}
+
+In the general case, the acting force in Eqs. \eqref{boltz} and \eqref{eq:vlasov},
+is given by the Lorentz force added by an external force, which, at kinetic scales,
 is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
@@
 \end{equation}
-where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, $c$ is
-the speed of light, and ${\bf E}({\bf r},t)$ and ${\bf B}({\bf r},t)$ are
-the electric and magnetic fields, respectively.
-
-Collisional interactions can be neglected when the time necessary for
-the plasma to establish statistical equilibrium - the relaxation time
-$\tau_{\rm rel}$ - is much greater than the characteristic time $\tau$
-of the process being studied~\cite{klimon,Tigik2015}.
-% The relaxation time of a plasma is defined
-% as follows $\tau_{\rm rel}=\lambda_{De}/v_{th}g$, where $\lambda_{De}$ is
-% given by Eq. \eqref{debye}, $v_{th}$ is the thermal velocity, and $g$
-% is the plasma parameter.
-
-\section{Vlasov-Maxwell system of equations}
-\label{vlasov-maxwell}
-As mentioned before, in the absence of collisions, the plasma dynamics is given
-by the Vlasov-Maxwell system, which is composed of the Vlasov movement equation
-\begin{equation}
-  \label{eq:vlasov}
-  \frac{\partial f_{\alpha}({\bf r},{\bf v},t)}{\partial t}
-  +{\bf v \cdot \nabla_r}f_{\alpha}({\bf r},{\bf v},t)
-  +\frac{q_{\alpha}}{m_{\alpha}}
-  \left({\bf E}({\bf r},t)+\frac{1}{c}{\bf v}\times {\bf B}({\bf r},t) \right)
-  {\bf \cdot \nabla_v}f_{\alpha}({\bf r},{\bf v},t)=0,
-\end{equation}
-where the fields are described by the Maxwell equations
+where $q_{\alpha}$ is the charge of the particles of kind $\alpha$, and $c$ is
+the speed of light. The quantities ${\bf E}({\bf r},t)$ and ${\bf B}({\bf r},t)$
+are, respectively, the electric and magnetic fields, which are described by the
+Maxwell equations
 \begin{eqnarray}
@@
 \end{eqnarray}
-% here given in cgs units, as commonly used in the plasma physics literature.
-
-In a statistical description, the charge density $\rho$
-and the current density ${\bf J}$ depend on the velocity
-distribution function
+
+In a statistical description, the charge density $\rho$ and the current
+density ${\bf J}$ depend on the velocity distribution function
 \begin{eqnarray}
@@
   &=&\sum_{\alpha}q_{\alpha}\int_v{\bf v}
-  f_{\alpha}({\bf r},{\bf v},t) d^3v,
+  f_{\alpha}({\bf r},{\bf v},t) d^3v.
 \end{eqnarray}
-where $\alpha$ accounts for all charged species that constitute
-the plasma. In a fully ionized hydrogen plasma, $\alpha=i$ for
-ions and $\alpha=e$ for electrons.
+% where the fields are described by the Maxwell equations
+% \begin{eqnarray}
+%   \label{max1}
+%   {\bf \nabla \cdot E}&=& 4\pi\rho\\
+%   \label{max2}
+%   {\bf \nabla \cdot B}&=& 0\\
+%   \label{max3}
+%     {\bf \nabla \times E}&=& -\frac{1}{c}
+%    \frac{\partial {\bf B}}{\partial t}\\
+%   \label{max4}
+%     {\bf \nabla \times B}&=& \frac{4\pi}{c}{\bf J}
+%     +\frac{1}{c}\frac{\partial{\bf E}}{\partial t}.
+% \end{eqnarray}
+% here given in cgs units, as commonly used in the plasma physics literature.
+
+% In a statistical description, the charge density $\rho$
+% and the current density ${\bf J}$ depend on the velocity
+% distribution function
+% \begin{eqnarray}
+%   \label{qdensity}
+%     \rho({\bf r},t)
+%   &=&\sum_{\alpha}q_{\alpha}\int_v
+%     f_{\alpha}({\bf r},{\bf v},t)d^3v\\
+% \label{jdensity}
+%   {\bf J}({\bf r},t)
+%   &=&\sum_{\alpha}q_{\alpha}\int_v{\bf v}
+%   f_{\alpha}({\bf r},{\bf v},t) d^3v,
+% \end{eqnarray}
+% where $\alpha$ accounts for all charged species that constitute
+% the plasma. In a fully ionized hydrogen plasma, $\alpha=i$ for
+% ions and $\alpha=e$ for electrons.
 

### 2019-11-21 thesis.tex
another appendix (maybe)

@@
 Collisional interactions are the central point of the present thesis.
-However, the formalism presented in \Cref{noneigenmode}, departs from
-the weak turbulence equations, which are the nonlinear approximation of
-the kinetic equations for low-amplitude instabilities in a collisionless
-plasma. The contribution of the correlations between \emph{source}
-fluctuations, that account for collisional interactions  (see.~\cite{
-  klimon,Tigik2015}), are then retrieved by the inclusion of noneigenmode
-contribution in both wave and particle kinetic equations. The difference
+However, the formalism presented in \Cref{noneigenmode}, departs from the
+weak turbulence equations, which are the nonlinear approximation of the
+kinetic equations for low-amplitude instabilities in a collisionless plasma.
+The contribution of the correlations between \emph{source} fluctuations,
+which account for collisional interactions  (see.~\cite{klimon,Tigik2015}),
+are then retrieved with the inclusion of noneigenmode contribution.
+in both wave and particle kinetic equations. The difference
 of this new approach is that
@@
 
+\chapter{Klimontovich formalism}
+\label{app-klimo}
+% The Klimontovich formalism is the basis of 
+% This appendix has the objective to complement important concepts discussed in
+% \Cref{noneigenmode}. 
+% In this appendix I present the standard approach that leads to the well known
+% Balescu-Lenard collision integral. The objective here is to put the formalism
+% presented in this thesis in a context where it can be compared with the usual
+% text-book method that employs the Klimontovich statistical formulation. The
+% derivation shown here is basically a version of Chapter 4
+
+\section{Micorscopic equations for a fully ionized plasma}
+\label{mic-eq}
+Let us consider a fully ionized hydrogen plasma, where $e_a$ and $m_a$ are,
+respectively the charge and the mass of the particles of species $a$, that
+can be or electrons $e_e\equiv -e$ or protons (ions) $e_i\equiv e$. Denoting
+$N_a$ as the total number of particles of species $a$ in the plasma, the
+neutrality condition of a plasma is given by
+\begin{equation}
+  \sum_ae_aN_a=0.  
+\end{equation}
+
+The probability distribution function for a N-body system in phase-space,
+$x\equiv({\bf r, v})$, is given by the Klimontovich function
+\begin{equation}
+N_a(x,t)=N_a({\bf r, v}, t)=\sum_{i=1}^{N_a}
+\delta[{\bf r}-{\bf r}_{ia}(t)]
+\delta[{\bf v}-{\bf v}_{ia}(t)].
+\end{equation}
+
 \end{appendix}

### 2019-11-22 thesis.tex
before moving the solar physics appendix

--- 2019-11-20 thesis.tex
@@
 
-Collisional interactions are the central point of the present thesis.
-However, the formalism presented in \Cref{noneigenmode}, departs from
-the weak turbulence equations, which are the nonlinear approximation of
-the kinetic equations for low-amplitude instabilities in a collisionless
-plasma. The contribution of the correlations between \emph{source}
-fluctuations, that account for collisional interactions  (see.~\cite{
-  klimon,Tigik2015}), are then retrieved by the inclusion of noneigenmode
-contribution in both wave and particle kinetic equations. The difference
-of this new approach is that
+Collisional interactions are the central point of the present thesis. However,
+the formalism presented in \Cref{noneigenmode}, departs from the weak turbulence
+equations, which are the kinetic description of nonlinear, low-amplitude
+instabilities in a collisionless plasma. The contribution of the correlations
+between \emph{source} fluctuations, which account for collisional interactions
+(see.~\cite{klimon,Tigik2015}), are then retrieved with the inclusion of
+noneigenmode contributions in the wave and particle kinetic equations\footnote{
+  For instance, in \Cref{sec:inc-non}, it will be shown that including the
+  noneigenmode fluctuations in the weak turbulence's formal particle kinetic
+  equation leads to an expression that accounts for the collisional interactions
+  that appear on the right-hand side of equation~\eqref{boltz}.}. Therefore,
+at this point, it will be assumed that collisions can be neglected.
 
 %% ~\cite{klimon,Tigik2015}
-
-\section{The Vlasov approach}
-\label{vlasov-appro}
-Collisional interactions can be neglected when the time necessary for
-the plasma to establish statistical equilibrium is much greater than the
-characteristic time of the process being studied. In this section, we
-present a brief discussion about the necessary set of assumptions that
-allow us to disregard the effect of collisions in dilute plasmas. In the
-sequence we present the complete set of self-consistent equations for
-a collisionless plasma.
-
-% Let $\tau_{\rm rel}$ be the time necessary for the plasma to establish
-% statistical equilibrium, i.e, the relaxation time.
-
-the relaxation time $\tau_{\rm rel}$ 
+\section{The Vlasov-Maxwell system of equations}
+% \label{vlasov-appro}
+% When the time necessary for the plasma to establish statistical equilibrium
+% is much greater than the characteristic time of the process being studied,
+% collisions can be neglected. In this section, is presented a brief discussion
+% about the necessary set of assumptions that allow us to disregard the effect
+% of collisions in dilute plasmas. In the sequence we present the complete set
+% of self-consistent equations for a collisionless plasma.
+
+% \subsection{Plasma parameter and relaxation time}
+% \label{plasma-param-relax}
+% A plasma is considered diluted when the plasma parameter $g\ll 1$, which
+% has the following form
+% \begin{equation}
+%   \label{ppar}
+%   g=\frac{1}{n\lambda_{De}^3},
+% \end{equation}
+% where $n$ is the number of charges inside the Debye sphere, and $\lambda_{De}$
+% is the Debye length, given by Eq. \eqref{debye}. At priory, the inequality
+% $g\ll 1$ seems counter intuitive, since it means that you must have a large
+% number of charged particles in the Debye sphere. However, if one substitutes
+% $\lambda_{De}$ with its expression,
+% \begin{align}
+%   g&=\frac{4\pi n e^2}{n T_e}\sqrt{\frac{4\pi n e^2}{T_e}}\\
+%    &=\frac{4\pi e^2}{T_e}\sqrt{\frac{4\pi n e^2}{T_e}}
+% \end{align}
+
+% % Let $\tau_{\rm rel}$ be the time necessary for the plasma to establish
+% % statistical equilibrium, i.e, the relaxation time.
+
+% the relaxation time $\tau_{\rm rel}$ 
 % The relaxation time of a plasma is defined
@@
 
-As mentioned before, in the absence of collisions, the plasma dynamics is given
-by the Vlasov-Maxwell system, which is composed of the Vlasov movement equation
+In the absence of collisions, the plasma dynamics is given by the Vlasov-Maxwell
+system, which is composed of the Vlasov movement equation
 \begin{equation}
@@
 
+% \chapter{Klimontovich formalism}
+% \label{app-klimo}
+% % The Klimontovich formalism is the basis of 
+% % This appendix has the objective to complement important concepts discussed in
+% % \Cref{noneigenmode}. 
+% % In this appendix I present the standard approach that leads to the well known
+% % Balescu-Lenard collision integral. The objective here is to put the formalism
+% % presented in this thesis in a context where it can be compared with the usual
+% % text-book method that employs the Klimontovich statistical formulation. The
+% % derivation shown here is basically a version of Chapter 4
+
+% \chapter{Microscopic equations for a fully ionized plasma}
+% \label{mic-eq}
+% Let us consider a fully ionized hydrogen plasma, where $e_a$ and $m_a$ are,
+% respectively the charge and the mass of the particles of species $a$, that
+% can be or electrons $e_e\equiv -e$ or protons (ions) $e_i\equiv e$. Denoting
+% $N_a$ as the total number of particles of species $a$ in the plasma, the
+% neutrality condition of a plasma is given by
+% \begin{equation}
+%   \sum_ae_aN_a=0.  
+% \end{equation}
+
+% The probability distribution function for a N-body system in phase-space,
+% $({\bf r, v})$, is given by the Klimontovich function
+% \begin{equation}
+% N_a({\bf r, v}, t)=\sum_{i=1}^{N_a}
+% \delta[{\bf r}-{\bf r}_i^a(t)]
+% \delta[{\bf v}-{\bf v}_i^a(t)],
+% \end{equation}
+% where ${\bf r}_i^a$ is the exact position and ${\bf v}_i^a$ the exact velocity
+% of the $i\unit{th}$ particle of species $a$, in a given time $t$.
+
 \end{appendix}

### 2019-11-22 thesis.tex
after moving the solar physics appendix to introduction
* thesis.tex: Summary: before moving the solar physics appendix

@@
 
+\section{Applications to astrophysical plasmas}
+\label{appE}
+Astrophysical plasmas are observed in a vast range of densities, temperatures,
+magnetic fields, ionization degree, and scale lengths\cite{peratt2014}. Starting
+in the outer layers of Earth's atmosphere, passing through the solar wind in the
+interplanetary space, to the stellar interiors and atmospheres, accretion disks
+and molecular clouds, it is estimated that something around $99 \sim 99.9\%$ of the
+observable matter in the universe is in the plasma state. Under cosmic conditions,
+even the weakly ionized gas of the neutral hydrogen regions around galaxies or in
+the atmosphere of cold stars have a strong reaction to electromagnetic fields,
+exhibiting the characteristic collective behavior of plasmas and, therefore, are
+also considered plasmas\cite{tsypa,may,peratt2014}.
+
+As soon as the pervasiveness of the plasma state in space came as a fact,
+plasma physics began to be recognized as an essential component in the
+multidisciplinary framework of astrophysics \cite{Alfven1950,Parker1956,
+  Alfven1961,Gailitis1964,Alfven1971}. At the same time, the analysis and
+interpretation of observational data started to have increasing relevance
+in the progress of theoretical, computational, and experimental plasma
+physics research \cite{YZKS16,Donnert2014,Pezzi2018,Howes2018,Peterson2019}.
+In this context of mutual collaboration, the solar and interplanetary
+plasma research has a pivotal contribution. The accessibility to direct,
+in situ measurements, highly resolved remote sensing and high-resolution
+spectroscopy, turned the solar system into a space plasma laboratory.
+Processes like magnetic reconnection, particle acceleration, shocks, and
+turbulence can be closely observed by space probes, and the understanding
+acquired may be extended or adapted to address similar phenomena observed
+in remote astrophysical environments \cite{NAP10477}.
+
+The theory developed during this graduate research analyses the combined
+action of nonlinear kinetic instabilities and collisional processes in
+the context of solar physics. To contextualize our work within the solar
+plasma research, in \autoref{sec:solar-physics} we present a brief review
+of the current research in solar and space physics and the phenomena
+related to this work. The corresponding paper is pointed in a footnote.
+
+\subsection{Solar and space physics}
+\label{sec:solar-physics}
+The domain of solar and space physics is the \emph{heliosphere}, a cavity
+in the interstellar medium, created by the constant supersonic flow of solar
+plasma that permeates the interplanetary space. This region encloses the
+solar system and extends for approximately $140\unit{AU}$\footnote{An AU
+  (astronomical unit) is defined as the mean distance between the Sun and
+  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
+galactic space. Its outer limit is the \emph{heliopause}, an interface
+zone where the outgoing pressure of the solar plasma balances the incoming
+pressure from the interstellar medium. This comet-shaped plasma bubble
+\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
+which delimits the sphere of absolute influence of the solar plasma. Beyond
+the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
+out to the heliopause, lies the \emph{heliosheath}. In this region, the
+solar wind particles start being subjected to increasing external pressure,
+transitioning to a subsonic, turbulent flow that blends and interacts
+directly with the matter in the local interstellar medium \cite{NAP13060}.
+In \autoref{figE1}, we have a depiction of the regions and boundaries
+described above, and the current location of both Voyager missions, that
+are already outside the heliosphere, in the interstellar space.
+\begin{figure}[h]
+  \begin{center}
+    \includegraphics[width=0.892\textwidth]{solar_system_env.png}
+    \caption{Main boundaries of the heliosphere and the location of both
+      Voyager missions.}
+      {\footnotesize Credit:}
+      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
+      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
+    \label{figE1}
+  \end{center}
+\end{figure}
+
+The ultimate goal of heliophysics can be summarized as the search for a
+better understanding of the solar dynamics and how it affects the Earth,
+other planetary bodies, and the interstellar medium. The heliosphere is
+a coupled system, where different interacting elements that might look
+unrelated at first sight are connected by underlying plasma processes
+\cite{NAP13060}. A great example of this interconnection is the relation
+between the appearance of sunspots and the occurrence of non-recurrent
+geomagnetic storms, which are the most intense space weather disturbances.
+Evidence of such relationship started to appear at the end of the $19$th
+century. However, the correct hypothesis supporting this correlation
+(coronal mass ejections associated with solar flares), which depended
+on advances in plasma physics theory, came along only in $1929$
+\cite{chapman1929cosmical,Koskinen2011}.
+
+\subsection{The Sun and the near-Earth environment}
+\label{sec:sun}
+A better comprehension of the Sun and the dynamic space around our planet
+goes beyond the pure scientific curiosity. This accessible space physics
+laboratory can indeed lead to discoveries that can be applied and extended
+to remote cosmic systems. However, the primary reason behind the international
+effort (see Figures \ref{nasa} and
+\ref{esa}) on understanding the complex physics of the Sun and interplanetary
+space is to unlock means of predicting the occurrence and intensity of solar
+activity, and anticipate how the near-Earth environment will be affected.
+Reliable forecasting of the space weather is essential for protecting
+electronic equipment, radio communications, GPS signal and humans in space
+from the effects of the interaction between the dense, magnetized plasma of
+coronal mass ejections with the geomagnetic field, and also from the
+energetic radiation emitted by solar flares\footnote{The emission of hard X-rays
+  and type III radio bursts, both generated during solar flares, are addressed in
+  \cite{Tigik2016a} (see \autoref{master}).}. Extreme coronal mass ejections
+can also cause stronger geomagnetic disturbances that may affect terrestrial
+infrastructure such as electric power grids \cite{NAP13060}.
+\begin{figure}[hb]
+  \begin{center}
+    \includegraphics[width=0.892\textwidth]{hso_fleet_chart_april_2019.pdf}
+    \caption{NASA's present and future heliophysics system observatory. The number
+      between parenthesis under the probe's name is the total number of spacecrafts
+      that compose the mission.}
+      {\footnotesize Credit:}
+      \href{https://science.nasa.gov/heliophysics}
+      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
+    \label{nasa}
+  \end{center}
+\end{figure}
+\begin{figure}[ht]
+  \begin{center}
+    \includegraphics[width=0.892\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
+    \caption{ESA's past, present, and future science missions for studying the solar system.}
+      {\footnotesize Credit:}
+      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
+      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
+    \label{esa}
+  \end{center}
+\end{figure}
+
+\subsection{The solar corona}
+\label{sec:corona}
+The source of the tenuous magnetized plasma permeating the heliosphere, and
+also the origin of solar particles and radiation that may cause disruptive
+space weather around Earth, is the outermost layer of the Sun: the solar
+corona \cite{Cranmer2017,Klein2017}. The solar corona can be easily recognized
+as the bright halo that appears around the hidden Sun during solar eclipses.
+\autoref{corona} shows two beautiful photographs of the corona, taken in two
+different solar eclipses, August 21 $2017$ and July 2 $2019$. In both pictures,
+one can see the moon covering the bright photosphere, allowing us to have a
+glimpse of the thin, but ultra-hot coronal plasma.
+
+Counter-intuitively, the solar corona is, at the same time, the most tenuous
+and the hottest outer layer of the Sun. At the top of the chromosphere, where
+the temperature might reach $20,000\,\unit{K}$, in a relatively narrow interface,
+the \emph{solar transition region}, the plasma temperature rises abruptly to
+$\sim 10^6\,\unit{K}$ \cite{BenzA2002}. It has been almost eighty years since
+the extreme coronal temperature came as the only reasonable explanation for the
+origin of the spectral lines observed in the solar corona \cite{Hunter1942},
+in a classical case of an answer that brings a more troublesome question. 
+Since then, several mechanisms have been proposed \cite{Parker1988,Scudder92b,
+  Vinas2000,PP14}, not only to comprehend the heating of the solar corona,
+but also the acceleration of the solar wind. Another unsolved problem that is
+directly connected to the inverted temperature profile of the solar corona and
+particle acceleration in the Sun, is regarding where and how the non-Maxwellian
+velocity distribution functions with suprathermal tails, observed in the solar
+wind, are formed\footnote{The generation of suprathermal electrons in the lower
+  corona and its consequences to the coronal heating problem are tackled in
+  \cite{Tigik2017a} (see \autoref{sec:gen-supr}).}.
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.892\textwidth]{corona2017.png}
+    \includegraphics[width=0.892\textwidth]{corona2019.png}
+    \caption{Solar corona captured during the total solar eclipse of 2017 (top panel)
+      and 2019 (lower panel). The reddish contour at some regions is the chromosphere,
+      and the reddish arcs are solar prominences, chromospheric plasma structures that
+      penetrate the coronal region.
+      {\footnotesize Credit:}
+      \href{https://hdr-astrophotography.com}
+      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 15/08/2019}.}
+    \label{corona}
+  \end{center}
+\end{figure}
+
+\section{Thesis organization}
+\label{sec:thesis-organization}
 The main subject of this thesis is discussed in \Cref{noneigenmode}. In
@@
 
-In the end, we have five appendices. \Cref{appA} depicts an improved
+In the end, we have four appendices. \Cref{appA} depicts an improved
 approximation for the second order susceptibility of the electrostatic
@@
 of my Master’s dissertation, which may be considered the starting point
-of this doctoral research. \Cref{appE} explores relevant aspects of
-current solar physics research and how they are connected to this work.
-It was written to be more like a light, informative reading, than a
-deep academic digression.
+of this doctoral research. % \Cref{appE} explores relevant aspects of
+% current solar physics research and how they are connected to this work.
+% It was written to be more like a light, informative reading, than a
+% deep academic digression.
 
@@
 
-\chapter{Applications to astrophysical plasmas}
-\label{appE}
-Astrophysical plasmas are observed in a vast range of densities, temperatures,
-magnetic fields, ionization degree, and scale lengths\cite{peratt2014}. Starting
-in the outer layers of Earth's atmosphere, passing through the solar wind in the
-interplanetary space, to the stellar interiors and atmospheres, accretion disks
-and molecular clouds, it is estimated that something around $99 \sim 99.9\%$ of the
-observable matter in the universe is in the plasma state. Under cosmic conditions,
-even the weakly ionized gas of the neutral hydrogen regions around galaxies or in
-the atmosphere of cold stars have a strong reaction to electromagnetic fields,
-exhibiting the characteristic collective behavior of plasmas and, therefore, are
-also considered plasmas\cite{tsypa,may,peratt2014}.
-
-As soon as the pervasiveness of the plasma state in space came as a fact,
-plasma physics began to be recognized as an essential component in the
-multidisciplinary framework of astrophysics \cite{Alfven1950,Parker1956,
-  Alfven1961,Gailitis1964,Alfven1971}. At the same time, the analysis and
-interpretation of observational data started to have increasing relevance
-in the progress of theoretical, computational, and experimental plasma
-physics research \cite{YZKS16,Donnert2014,Pezzi2018,Howes2018,Peterson2019}.
-In this context of mutual collaboration, the solar and interplanetary
-plasma research has a pivotal contribution. The accessibility to direct,
-in situ measurements, highly resolved remote sensing and high-resolution
-spectroscopy, turned the solar system into a space plasma laboratory.
-Processes like magnetic reconnection, particle acceleration, shocks, and
-turbulence can be closely observed by space probes, and the understanding
-acquired may be extended or adapted to address similar phenomena observed
-in remote astrophysical environments \cite{NAP10477}.
-
-The theory developed during this graduate research analyses the combined
-action of nonlinear kinetic instabilities and collisional processes in
-the context of solar physics. To contextualize our work within the solar
-plasma research, in \autoref{sec:solar-physics} we present a brief review
-of the current research in solar and space physics and the phenomena
-related to this work. The corresponding paper is pointed in a footnote.
-
-\section{Solar and space physics}
-\label{sec:solar-physics}
-The domain of solar and space physics is the \emph{heliosphere}, a cavity
-in the interstellar medium, created by the constant supersonic flow of solar
-plasma that permeates the interplanetary space. This region encloses the
-solar system and extends for approximately $140\unit{AU}$\footnote{An AU
-  (astronomical unit) is defined as the mean distance between the Sun and
-  Earth, $1\unit{AU}\approx 150\times 10^6\unit{km}$.} in the surrounding
-galactic space. Its outer limit is the \emph{heliopause}, an interface
-zone where the outgoing pressure of the solar plasma balances the incoming
-pressure from the interstellar medium. This comet-shaped plasma bubble
-\cite{Dialynas2017}, also has an inner boundary, the \emph{termination shock},
-which delimits the sphere of absolute influence of the solar plasma. Beyond
-the termination shock, at roughly $100\unit{AU}$ from the Sun, extending
-out to the heliopause, lies the \emph{heliosheath}. In this region, the
-solar wind particles start being subjected to increasing external pressure,
-transitioning to a subsonic, turbulent flow that blends and interacts
-directly with the matter in the local interstellar medium \cite{NAP13060}.
-In \autoref{figE1}, we have a depiction of the regions and boundaries
-described above, and the current location of both Voyager missions, that
-are already outside the heliosphere, in the interstellar space.
-\begin{figure}[h]
-  \begin{center}
-    \includegraphics[width=0.892\textwidth]{solar_system_env.png}
-    \caption{Main boundaries of the heliosphere and the location of both
-      Voyager missions.}
-      {\footnotesize Credit:}
-      \href{https://voyager.jpl.nasa.gov/news/details.php?article_id=112}
-      {\footnotesize NASA/JPL-Caltech}{\footnotesize , accessed at 08/08/2019.}
-    \label{figE1}
-  \end{center}
-\end{figure}
-
-The ultimate goal of heliophysics can be summarized as the search for a
-better understanding of the solar dynamics and how it affects the Earth,
-other planetary bodies, and the interstellar medium. The heliosphere is
-a coupled system, where different interacting elements that might look
-unrelated at first sight are connected by underlying plasma processes
-\cite{NAP13060}. A great example of this interconnection is the relation
-between the appearance of sunspots and the occurrence of non-recurrent
-geomagnetic storms, which are the most intense space weather disturbances.
-Evidence of such relationship started to appear at the end of the $19$th
-century. However, the correct hypothesis supporting this correlation
-(coronal mass ejections associated with solar flares), which depended
-on advances in plasma physics theory, came along only in $1929$
-\cite{chapman1929cosmical,Koskinen2011}.
-
-\subsection{The Sun and the near-Earth environment}
-\label{sec:sun}
-A better comprehension of the Sun and the dynamic space around our planet
-goes beyond the pure scientific curiosity. This accessible space physics
-laboratory can indeed lead to discoveries that can be applied and extended
-to remote cosmic systems. However, the primary reason behind the international
-effort (see Figures \ref{nasa} and
-\ref{esa}) on understanding the complex physics of the Sun and interplanetary
-space is to unlock means of predicting the occurrence and intensity of solar
-activity, and anticipate how the near-Earth environment will be affected.
-Reliable forecasting of the space weather is essential for protecting
-electronic equipment, radio communications, GPS signal and humans in space
-from the effects of the interaction between the dense, magnetized plasma of
-coronal mass ejections with the geomagnetic field, and also from the
-energetic radiation emitted by solar flares\footnote{The emission of hard X-rays
-  and type III radio bursts, both generated during solar flares, are addressed in
-  \cite{Tigik2016a} (see \autoref{master}).}. Extreme coronal mass ejections
-can also cause stronger geomagnetic disturbances that may affect terrestrial
-infrastructure such as electric power grids \cite{NAP13060}.
-\begin{figure}[hb]
-  \begin{center}
-    \includegraphics[width=0.892\textwidth]{hso_fleet_chart_april_2019.pdf}
-    \caption{NASA's present and future heliophysics system observatory. The number
-      between parenthesis under the probe's name is the total number of spacecrafts
-      that compose the mission.}
-      {\footnotesize Credit:}
-      \href{https://science.nasa.gov/heliophysics}
-      {\footnotesize NASA}{\footnotesize , accessed at 10/08/2019.}
-    \label{nasa}
-  \end{center}
-\end{figure}
-\begin{figure}[ht]
-  \begin{center}
-    \includegraphics[width=0.892\textwidth]{ESA_s_fleet_of_Solar_System_explorers_2019.jpg}
-    \caption{ESA's past, present, and future science missions for studying the solar system.}
-      {\footnotesize Credit:}
-      \href{https://www.esa.int/spaceinimages/Images/2019/02/ESA_s_fleet_of_Solar_System_explorers}
-      {\footnotesize ESA}{\footnotesize , accessed at 10/08/2019.}
-    \label{esa}
-  \end{center}
-\end{figure}
-
-\subsection{The solar corona}
-\label{sec:corona}
-The source of the tenuous magnetized plasma permeating the heliosphere, and
-also the origin of solar particles and radiation that may cause disruptive
-space weather around Earth, is the outermost layer of the Sun: the solar
-corona \cite{Cranmer2017,Klein2017}. The solar corona can be easily recognized
-as the bright halo that appears around the hidden Sun during solar eclipses.
-\autoref{corona} shows two beautiful photographs of the corona, taken in two
-different solar eclipses, August 21 $2017$ and July 2 $2019$. In both pictures,
-one can see the moon covering the bright photosphere, allowing us to have a
-glimpse of the thin, but ultra-hot coronal plasma.
-
-Counter-intuitively, the solar corona is, at the same time, the most tenuous
-and the hottest outer layer of the Sun. At the top of the chromosphere, where
-the temperature might reach $20,000\,\unit{K}$, in a relatively narrow interface,
-the \emph{solar transition region}, the plasma temperature rises abruptly to
-$\sim 10^6\,\unit{K}$ \cite{BenzA2002}. It has been almost eighty years since
-the extreme coronal temperature came as the only reasonable explanation for the
-origin of the spectral lines observed in the solar corona \cite{Hunter1942},
-in a classical case of an answer that brings a more troublesome question. 
-Since then, several mechanisms have been proposed \cite{Parker1988,Scudder92b,
-  Vinas2000,PP14}, not only to comprehend the heating of the solar corona,
-but also the acceleration of the solar wind. Another unsolved problem that is
-directly connected to the inverted temperature profile of the solar corona and
-particle acceleration in the Sun, is regarding where and how the non-Maxwellian
-velocity distribution functions with suprathermal tails, observed in the solar
-wind, are formed\footnote{The generation of suprathermal electrons in the lower
-  corona and its consequences to the coronal heating problem are tackled in
-  \cite{Tigik2017a} (see \autoref{sec:gen-supr}).}.
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.892\textwidth]{corona2017.png}
-    \includegraphics[width=0.892\textwidth]{corona2019.png}
-    \caption{Solar corona captured during the total solar eclipse of 2017 (top panel)
-      and 2019 (lower panel). The reddish contour at some regions is the chromosphere,
-      and the reddish arcs are solar prominences, chromospheric plasma structures that
-      penetrate the coronal region.
-      {\footnotesize Credit:}
-      \href{https://hdr-astrophotography.com}
-      {\footnotesize Nicolas Lefaudeux}{\footnotesize , accessed at 15/08/2019}.}
-    \label{corona}
-  \end{center}
-\end{figure}
-
 %% Eu acho que ainda tenho que escrever algo aqui. Vou pensar ainda a respeito.

### 2019-11-23 thesis.tex
FTFY (Thesis organization)

@@
 
-Considering the context presented above, the working proposal of this PhD
-Thesis is to put forward the first numerical analysis of the new weak
-turbulence theory for collisional plasmas \cite{YZKS16} and explore its
-applications in the solar physics scope. In \Cref{cha:kin-theo}, we make
-a brief review of the basic plasma kinetic theory for electrostatic
-oscillations. \Cref{cha:weak-turb} revises the procedure for obtaining
-the weak turbulence equations for Langmuir and ion-sound waves and
-the quasilinear equation for the particle dynamics.
-
 \section{Applications to astrophysical plasmas}
@@
   \cite{Tigik2017a} (see \autoref{sec:gen-supr}).}.
-\begin{figure}
+
+\begin{figure}[h!]
   \begin{center}
@@
 
+\vspace{0.5cm}
+
 \section{Thesis organization}
 \label{sec:thesis-organization}
+Considering the context presented above, the working proposal of this PhD
+Thesis is to put forward the first numerical analysis of the new weak
+turbulence theory for collisional plasmas \cite{YZKS16} and explore its
+applications in the solar physics scope. In \Cref{cha:kin-theo}, we make
+a brief review of the basic plasma kinetic theory for electrostatic
+oscillations. \Cref{cha:weak-turb} revises the procedure for obtaining
+the weak turbulence equations for Langmuir and ion-sound waves and
+the quasilinear equation for the particle dynamics.
+
 The main subject of this thesis is discussed in \Cref{noneigenmode}. In

### 2019-11-25 thesis.tex
final (?)

@@
 %\input{folhadeaprovacao}
-% \input{ty}
-% \input{epi}
+\input{ty}
+\input{epi}
 %\input{resumo}
@@
 \end{equation}
-where $T_e$ is the electron temperature, $k_B$ the Boltzmann constant, $n$
-the plasma density and $e$ the electron charge. This means that a specific
-charge will interact effectively only with other charges that are inside of a
-virtual sphere with radius given by $\lambda_{De}$, being almost completely
-shielded from the influence of particles outside the \emph{Debye sphere}.
-The self-consistent interaction between charged particles and electric and
-magnetic fields, creates fluctuations in the local neutrality of the plasma,
-giving rise to the series of oscillations and complex wave phenomena that
-characterize the plasma’s collective behavior~\cite{chen}.
-
-Describing the precise state of a plasma, in a given time, would require
-the knowledge of the $6N$ phase-space coordinates of each particle, and also
-the microscopic amplitudes of the electric and magnetic fields at each point
-in space. Such exact representation is clearly a non-practical approach for
-a many-body system like the plasma. However, this microscopic formulation
-can be approximated to a macroscopic description by taking the average of
-the microscopic quantities and making suitable assumptions to truncate the
-correlation functions at an appropriate point~\cite{klimon}. This will lead
-to the plasma kinetic equations, which is the first of a hierarchy of
-approximations that also includes the multi-fluid and magnetohydrodynamic
-theories. The application of each one of these formulations will depend on
-the context and the scale of the phenomena being described~\cite{chen}.
-In this work we are interested in small-scale processes that depend on
-velocity-space properties, requiring a kinetic description of the plasma.
+where $T_e$ is the electron temperature\footnote{Due to the high mobility,
+  electrons are the main responsible for maintaining the Debye shielding.
+  There are specific situations where this is not true~\cite{chen}, but
+  they are outside of the scope of the current study.}, $k_B$ the Boltzmann
+constant, $n$ the plasma density and $e$ the electron charge. This means
+that a specific charge will interact effectively only with other charges
+that are inside of a virtual sphere with radius given by $\lambda_{De}$,
+being almost completely shielded from the influence of particles outside
+the \emph{Debye sphere}. The self-consistent interaction between charged
+particles and electric and magnetic fields, creates fluctuations in the
+local neutrality of the plasma, giving rise to the series of oscillations
+and complex wave phenomena that characterize the plasma’s collective
+behavior~\cite{chen}. Describing the precise state of a plasma, in a given
+time, requires the knowledge of the $6N$ phase-space coordinates of each
+particle, and also the microscopic amplitudes of the electric and magnetic
+fields at each point in space~\cite{klimon}. Such exact representation is
+clearly a non-practical approach for a many-body system like the plasma.
+However, this microscopic formulation can be approximated to a macroscopic
+description by taking the average of the microscopic quantities and making
+suitable assumptions to truncate the correlation functions at an appropriate
+point~\cite{klimon}. This will lead to the plasma kinetic equations, which is
+the first of a hierarchy of approximations that also includes the multi-fluid
+and magnetohydrodynamic theories. The application of each one of these
+formulations will depend on the context and the scale of the phenomena being
+described~\cite{chen}. In this work we are interested in small-scale processes
+that depend on velocity-space properties, requiring a kinetic description of
+the plasma.
 
@@
 
-In a first approximation, the plasma dynamics is described by the
-Boltzmann equation
+Like non-ionized gases, the statistical description of the plasma dynamics
+is given by the Boltzmann equation
 \begin{equation}
@@
 % Sabrina: OK
-Thus, at this point, one must choose whether the quasilinear approach
-is enough, or if a nonlinear formulation is necessary. In the first case
+Thus, at this point, one must choose if the quasilinear approach is
+enough, or if a nonlinear formulation is necessary. In the first case
 all terms proportional to $\delta {\bf E} \delta f_a$ are neglected in

### 2019-11-25 ty.tex
Acknowledgments

--- 2019-08-24 ty.tex
@@
-%\newpage
+\newpage
 \pagestyle{empty}
-\chapter*{Acknowledgements}
-% \begin{center}
-% {\centering{\chapter*{Acknowledgements}}}
-% \end{center}
-\begin{quote}
-% Sou grata ao Prof. Luiz Fernando Ziebell pela excelente orientação.
-% Sua grande dedicação em ensinar, sua disponibilidade para solucionar
-% dúvidas e sua imensa paciência foram decisivos para a execução deste
-% trabalho. Também sou grata aos colegas de Grupo pela agradável convivência
-% e pela constante troca de conhecimento.
+% {\centering{\textbf{\large Acknowledgments}}
+% \chapter*{Acknowledgements}
+\begin{center}
+  \textbf{\large Acknowledgments}
+% {\centering{\chapter*{Acknowledgments}}}
+\end{center}
+% \begin{quote}
 
-% Agradeço aos amigos da ``CG''. À Amanda, à Lais e à Nicole pelas
-% diversas e divertidas conversas sobre ``a vida o universo e tudo mais''.
-% Ao Demétrius e ao Vinícius pelas discussões sem sentido mais engraçadas
-% e irritantes que já tive.
+First of all, I acknowledge the dedication of my supervisor, Luiz Fernando
+Ziebell, whose guidance, encouragement, and patience (tons of) made this
+work possible. Further, I would like to state my sincere appreciation for
+the trusting he always demonstrated to have in my capabilities for developing
+high-quality research and for his availability to discuss my work, giving me
+insightful advice. % \emph{Professor, I am grateful for all these years of
+  % learning and fruitful work that culminated in this doctoral thesis.}
 
-% Reservo um agradecimento especial à minha família, que tanto me apoiou.
-% Ao meu marido pelo companheirismo e incentivo. Ao meu filho por nortear 
-% a minha vida e enchê-la de emoções. À minha mãe pelo amor e pela dedicação
-% à minha educação. Amo vocês.
-\end{quote}
+In the academic scope, I would like to thank Peter Yoon for the years of
+productive collaboration and for receiving me with great hospitality during
+my stay at the University of Maryland.
+% \emph{Peter, thank you very much for
+% all the encouragement you gave me. It meant a lot to me.}
+I also want to
+express my earnest appreciation to Dr.~Adolfo Viñas, who dedicated a part of
+his time to teach me PIC simulation and discuss the subtleties of the kinetic
+theory of plasmas during my time in the University of Maryland.
+% \emph{Dr.~Viñas, thank you very much for your time, availability, and guidance.}
+As special
+mentions, I would like to thank Jeferson Arenzon, Renato Pakter, and Rudi
+Gaelzer for their willingness to help me with my postdoc applications when I
+randomly appeared at their offices.
+
+From the Graduate Program in Physics, I am grateful to Liane Thier Ruschel for
+the kind and efficient assistance in dealing with bureaucratic procedures and
+the most diverse document requests. I also thank Mari Nunes for her patience
+and goodwill in dealing with everyday trouble of grad students.
+
+On the personal side, I thank Felipe for his comprehension, patience, support
+and encouragement during my undergrad and graduate years. I am also grateful
+to Gabriel for his love and refined sense of humor that cheers me up even in
+the saddest days.
+
+Agradeço especialmente à minha mãe, Diná, por ter me criado para ser uma
+mulher livre e a não aceitar qualquer papel na sociedade que não seja o
+que eu considere o melhor para mim. \emph{Mãe, essa tese é dedicada a ti.
+  Sem teu exemplo, eu não estaria onde estou. Obrigada por tudo!}
+
+From my friends and colleagues from UFRGS, I am grateful to Nicole for the
+companionship that ranges from hard-working weekends to life celebrations.
+\emph{Nicole, grad school would be terribly boring without you.} I also thank
+Amanda for showing me how to be prepared for life, Demétrius for the cheerful
+annoyance, and Vinícius for the light talks and for sharing his delicious
+bread. A special thanks to Thales, my example of plasma physicist, and to
+Fernanda, whose intelligence and dedication will always be my inspiration. 
+Special mentions to colleagues that were part of this journey and deserved
+to be remembered: Alexandre, Gustavo, João e Larissa.
+
+From Maryland, I am especially grateful to Jacek for the infinite talks, solid
+companionship and (mutual) support.\emph{ Jacek, you made my time in CP much
+  better. Dziękuję bardzo!}
+
+%\end{quote}
+
+%%% Local Variables:
+%%% mode: latex
+%%% TeX-master: "thesis"
+%%% End:

### 2019-11-28 thesis.tex
Made corrections until page 27. Next correction is in page 23

@@
 different oscillatory modes that may be excited in plasmas, but also
-wholly characterizes these oscillations. Valuable information like
+wholly characterize these oscillations. Valuable information like
 how these waves propagate and the frequencies that will resonate with
@@
 quasi-stationary equilibrium state is attained \cite{gurnett2017}.
-However, depending on the phenomenon being described this saturation
+However, depending on the phenomenon being described, this saturation
 state reached under the quasilinear approximation might keep on evolving
@@
 the effects of both wave-wave and wave-particle interactions \cite{Yoon00}.
-Later, the formalism was expanded, and the effects of discrete particle,
-related to spontaneous emission and spontaneous scattering processes
-were included \cite{Yoon05a}. In a further extension, the effects of
+Later, the formalism was expanded, and discrete particle effects,
+related to spontaneous emission and spontaneous scattering processes,
+were included~\cite{Yoon05a}. In a further extension, the effects of
 the propagation of electromagnetic waves were incorporated into the
@@
 in \cite{Tigik2016a} (see \autoref{master}). In this work, a linearized
-form of the Landau collision integral was added into the particle kinetic
+form of the Landau collision integral was added to the particle kinetic
 equation, and the weak turbulence theory's complete set of self-consistent,
@@
 the context of solar physics. To contextualize our work within the solar
-plasma research, in \autoref{sec:solar-physics} we present a brief review
-of the current research in solar and space physics and the phenomena
-related to this work. The corresponding paper is pointed in a footnote.
+plasma research, in Subsections~\ref{solar-physics},~\ref{sun} and
+\ref{solar-corona} we present a brief review of the current research in
+solar and space physics and the phenomena related to this work. The
+corresponding paper is pointed in a footnote.
 
 \subsection{Solar and space physics}
-\label{sec:solar-physics}
+\label{solar-physics}
 The domain of solar and space physics is the \emph{heliosphere}, a cavity
@@
 \cite{NAP13060}. A great example of this interconnection is the relation
-between the appearance of sunspots and the occurrence of non-recurrent
+between the appearing of sunspots and the occurrence of non-recurrent
 geomagnetic storms, which are the most intense space weather disturbances.
@@
 \subsection{The Sun and the near-Earth environment}
-\label{sec:sun}
+\label{sun}
 A better comprehension of the Sun and the dynamic space around our planet
@@
 \subsection{The solar corona}
-\label{sec:corona}
+\label{solar-corona}
 The source of the tenuous magnetized plasma permeating the heliosphere, and
@@
 results and discuss some remarking conclusions obtained in this analysis.
-At the end of this chapter, we also deliberate the perspectives for this
+At the end of this chapter, we also elaborate on the perspectives for this
 new generalized formalism and its relevance for the next generation of
@@
 absence of the electrostatic bremsstrahlung effect. The discussion in
-\Cref{appB} is related with to article appended in \Cref{appC}, which
-is parallel research and is only slightly related to the main subject
+\Cref{appB} is related to the article appended in \Cref{appC}, which
+is parallel research and is only slightly connected to the main subject
 of this work. \Cref{master} shows the paper that summarizes the results
@@
 
-Like non-ionized gases, the statistical description of the plasma dynamics
-is given by the Boltzmann equation
+Like in the case of non-ionized gases, the statistical description of the
+plasma dynamics is given by the Boltzmann equation
 \begin{equation}
@@
 equations, which are the kinetic description of nonlinear, low-amplitude
-instabilities in a collisionless plasma. The contribution of the correlations
+instabilities in a collisionless plasma. The contributions of the correlations
 between \emph{source} fluctuations, which account for collisional interactions
@@
 
-In the general case, the acting force in Eqs. \eqref{boltz} and \eqref{eq:vlasov},
+In the general case, the acting force in Eqs. \eqref{boltz} and \eqref{eq:vlasov}
 is given by the Lorentz force added by an external force, which, at kinetic scales,
 is also of electromagnetic nature. Therefore, in \emph{cgs} units\footnote{The
-  use of cgs units will be consistent trough all this work.}, ${\bf F}$ has the
+  use of cgs units will be consistent through all this work.}, ${\bf F}$ has the
 following form
@@
 instabilities, we must assure that these fluctuations are still inside
-the weak turbulence limit, i.e., if the turbulence is weak enough to be
+the weak turbulence limit, i.e., that the turbulence is weak enough to be
 treated by a perturbative method. Such boundary is defined by a comparison
@@
 where the subscript ``$a$'' is the kind of particle: $a=i$ for ions
-and $a=e$ for electrons. For an overall neutral plasma, the number
-density of
+and $a=e$ for electrons. For an overall neutral plasma, the average
+number density of
 % LFZ180216: Sugestão "the number density of"
@@
 
-Now, we assume the fluctuations may be decomposed in terms of the
-Fourier-Laplace transformation over the fast time-scale of the
+Now, we assume the that fluctuations may be decomposed in terms of
+the Fourier-Laplace transformation over the fast time-scale of the
 fluctuations, while amplitudes of the spectra vary in a slow
@@
 is given by the following expression\footnote{\Cref{part}
-  is not in the same form that it appears in Refs. \cite{Yoon00,Tigik2015}.
+  is not in the same form that appears in Refs. \cite{Yoon00,Tigik2015}.
   The reason for this choice, which is based in Ref. \cite{YZKS16},
@@
 waves is obtained\footnote{\Cref{wave-lin} is not in the same form
-  that it appears in Refs. \cite{Yoon00,Tigik2015}. The reason for this
+  that appears in Refs. \cite{Yoon00,Tigik2015}. The reason for this
   choice, which is based in Ref. \cite{YZKS16}, will become clear in

### 2019-11-29 thesis.tex
Corrections until page 37. Next corrections starting at page 44

@@
 the nonlinear spectral balance equation, three new terms appear in the wave
-kinetic equation. The first expression is an extension for the spontaneous
+kinetic equation. The first term is an extension for the spontaneous
 scattering equation. The second term is a new, rigorous expression for the
-collisional damping rate of plasma waves. The third equation depicts a
+collisional damping rate of plasma waves. The third term depicts a
 hitherto unknown process of electrostatic radiation emission, in the eigenmode
@@
 
-Therefore, we have two distinct situations. In the first case,
-when collective modes are not important, the electric field energy
-can be expressed by Eq. \eqref{balance} with the electric field fluctuation
-$\left< \delta E^2 \right>_{{\bf k},\omega}^0$ given by \eqref{field-fluc},
-and the standard situation, in which collective modes are important,
-then the wave electric field is determined by
+Therefore, we have two distinct situations. One is the situation in which
+collective modes are not important, and the electric field energy can be
+expressed by Eq. \eqref{balance} with the electric field fluctuation
+$\left< \delta E^2 \right>_{{\bf k},\omega}^0$ given by \eqref{field-fluc}.
+The other is standard situation, in which collective modes are important,
+and the wave electric field is determined by
 \begin{equation}
@@
 
-This procedure encompasses these two situations by taking into account
-the collective modes that satisfy the eigenmode condition, and the
-non eigenmode contribution by generalizing Eq. \eqref{wave-dens},
-as follows
+The procedure described above encompasses the two possibilities under
+analysis in this work by generalizing Eq.~\eqref{wave-dens} to take into
+account the noneigenmode contribution, given by Eq.~\eqref{field-fluc},
+along with Eq.~\eqref{Psi-eigen} for the collective modes that satisfy
+the eigenmode condition, resulting in the following expression
 \begin{equation}
@@
 \end{equation}
-that is equivalent to the first term of Eq. \eqref{wave-lin},
-plus the term of spontaneous emission, which is absent in
-\eqref{wave-lin}, but has the exact same form of the second
-right-hand term in Eq. \eqref{eigenmode-ql2} (see Eq. 3.8 of
- Ref. \cite{YZKS16}). These two processes are determined by
- linear wave-particle resonance conditions
+that is equivalent to the first two terms of Eq.~\eqref{wave-lin},
+which describe the effects of spontaneous and induced emissions,
+respectively. Both processes are determined by the linear
+ wave-particle resonance conditions
  $\sigma \omega_{\bf k}^\alpha-{\bf k\cdot v}=0$.
-So we may conclude that noneigenmodes do not alter the
+Therefore, we may conclude that noneigenmodes do not alter the
 quasilinear wave kinetic equation.
@@
 and Eqs. \eqref{gammaS} and \eqref{PkS} to Eq. \eqref{S,1}, and
-then substituting the spontaneous emission term of both equations
+then substituting the spontaneous scattering term of both equations
 with their respective corrected expressions, \eqref{corrL} and
@@
 new effects in the time evolution subroutine. The main objective here
-was to comprehend important aspects of this so-far unknown expression,
-how it relates to other equivalent plasma processes and with the
+was to comprehend important aspects of this so-far unknown expressions,
+how they relate to other equivalent plasma processes and with the
 heuristic Spitzer formula, for collisional damping. The main question
-was: ``Are they equivalent?'', more specifically, ``Are their intensities,
+was: ``Are they equivalent?'', more specifically, ``Are their magnitudes,
 at least, in the same order of magnitude?''. The answer was no. We found

### 2019-12-01 thesis.tex
correction of page 44

@@
 \end{equation}
-where $\gamma_{\bf q}^{\sigma L}$ and $\gamma_{\bf q}^{\sigma S}$ describe
-the collisional damping rate for $L$ and $S$ waves, respectively
+where $\gamma_{\bf q}^{\sigma L}$ and $\gamma_{\bf q}^{\sigma S}$ are the
+dimensionless form of Eqs. \eqref{gammaL} and \eqref{gammaS}, which
+describe the collisional damping rate for $L$ and $S$ waves,
+respectively
 \begin{equation}
@@
     \Phi_i({\bf u})\right)\delta(z_{\bf q}^S
-    -{\bf q'}\cdot{\bf u}),
-  \end{split}
-\end{equation}
-and $P_{\bf q}^{\sigma L}$ and $P_{\bf q}^{\sigma S}$ terms depict the
-normalized electrostatic bremsstrahlung equations, given by
+    -{\bf q'}\cdot{\bf u}).
+  \end{split}
+\end{equation}
+The terms $P_{\bf q}^{\sigma L}$ and $P_{\bf q}^{\sigma S}$ are the
+normalized versions of Eqs. \eqref{PkL} and \eqref{PkS}, that depict
+the electrostatic bremsstrahlung effect for $L$ and $S$ waves, and
+are respectively given by
 \begin{equation}
@@
 \chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-=&-\frac{4\pi ie_a}{k k'|{\bf k-k'}|}\frac{1}{2}\int d{\bf v''}\,\biggl[
+=&-\frac{4\pi i e_a}{k k'|{\bf k-k'}|}\frac{1}{2}\int d{\bf v''}\,\biggl[
 ({\bf k'}\cdot
@@
 \chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\int d{\bf v''}\\
+=-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\int d{\bf v''}\\
 &\times\left\{[\frac{{\bf k'}\cdot \partial_{\bf v''}}
@@
 \chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\int d{\bf v''}\\
+=-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\int d{\bf v''}\\
 &\times\left\{\frac{
@@
 \chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2} \int d{\bf v''}\\
+=-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2} \int d{\bf v''}\\
 &\times\left\{-\frac{T_a}{m_a}\frac{{\bf k'}\cdot({\bf k-k'})}
@@
 \chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\int d{\bf v''}\\
+=-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\int d{\bf v''}\\
 &\times \left\{-\frac{T_a}{m_a}\frac{{\bf k'}\cdot({\bf k-k'})}
@@
     \chi_a^{(2)}&[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-    =-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\int d{\bf v''}\\
+    =-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\int d{\bf v''}\\
     &\times\left[-\frac{T_a}{m_a}[{\bf k'}\cdot({\bf k-k'})]
@@
 \chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}
+=-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}
 \int d{\bf v''}\,\left[2\frac{({\bf k'}\cdot{\bf v''})
@@
 \chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-&=-\frac{2\pi ie_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}
+&=-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}
 2\frac{k'|{\bf k-k'}|}{(\sigma\omega_{\bf k}^L)^2} 
 \int d{\bf v''}\,|{\bf v''}|^2 f_a({\bf v''})\\
-&=-\frac{2\pi ie_a^3}{k m_a^2}\frac{m_a^2}{T_a^2}
+&=-\frac{2\pi i e_a^3}{k m_a^2}\frac{m_a^2}{T_a^2}
 \frac{2}{(\sigma\omega_{\bf k}^L)^2} \frac{2T_a}{m_a}\overline{n}\\
@@
 \simeq -i4\frac{e_a}{m_a}\frac{\omega_{pa}^2}{(\omega_{\bf k}^L)^2} 
-\frac{1}{kv_{a}^2}
+\frac{1}{k v_{a}^2}
 \end{equation}

### 2019-12-02 thesis.tex
Only the correction of page 45 was left

@@
 \end{equation}
-and the resulting equations
+and the resulting expressions
 \begin{eqnarray}
@@
 
-Due its asymmetry, the terms, which are linear in ${\bf v''}$, will vanish
-when integrated, remaining
+Due to their asymmetry, the terms which are linear in ${\bf v''}$ will vanish
+when integrated, leading to the following expression
 \begin{equation}
@@
 \chi_a^{(2)}[{\bf k'},{\bf k'\cdot v'}|{\bf k-k'},({\bf k-k'})\cdot{\bf v}]
-=-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}
-\int d{\bf v''}\,\left[2\frac{({\bf k'}\cdot{\bf v''})
+&=-\frac{2\pi i e_a^3}{k k'|{\bf k-k'}|m_a^2}\frac{m_a^2}{T_a^2}\\
+&\times \int d{\bf v''}\,\left[2\frac{({\bf k'}\cdot{\bf v''})
 (({\bf k-k'})\cdot{\bf v''})}
@@
 
-Therefore, the resulting equation for the electrostatic bremsstrahlung
+Therefore, the resulting expression for the electrostatic bremsstrahlung
 of $L$ waves in the new approximation is
@@
 
-For use in this asymptotic equation, let us assume isotropic distributions for
-ions and electrons, which are the summation of Maxwellian and $\kappa_\beta$
-distributions. In terms of dimensionless variables,
+For use in this asymptotic equation, let us assume isotropic distributions
+for ions and electrons, which are the summation of Maxwellian and kappa
+distributions. In terms of dimensionless variables, we have
 \begin{equation}
@@
 
-The equations presented in this appendix and, more important, the
-ideas about the asymptotic state of the eigenmodes of an unmagnetized
-plasma considering several values of kappa coefficient, were developed
-in parallel with another work, which slightly deviates from the
-main subject of this PhD research, but had a big contribution on the
+The equations presented in this appendix and, more important, the ideas
+about the asymptotic state of the eigenmodes of an unmagnetized plasma
+considering several values of the kappa coefficient, were developed in
+parallel with another work, which slightly deviates from the main
+subject of this PhD research, but had a big contribution on the
 development of the work presented in Ref. \cite{Tigik2017a}. 

### 2019-12-02 thesis.tex
Final correction (if everything goes well)
* thesis.tex: Summary: Only the correction of page 45 was left

@@
 where $\theta_{ab}(\Phi_a,\Phi_b)$ is the linearized Landau
-collision integral, given by
-\begin{equation}
-  \begin{split}
-     \theta_{ab}(\Phi_a,\Phi_b) &= \Gamma_{ab}\left\{
-     \frac{\partial}{\partial{\bf u}_a}\cdot
-     \left(2\frac{m_a}{m_b}\Psi(u_{ab})
-     \frac{{\bf u}_a}{u^3_a}\Phi_a\right)\right.\\
-  &+\frac{\partial}{\partial{\bf u}_a}\cdot
-     \left\{\left[\left(\Phi(u_{ab})
-     -\frac{1}{2 u_{ab}^2}\Psi(u_{ab})\right)
-     \frac{\partial^2u_a}{\partial{\bf u}_a
-     \partial{\bf u}_a}\right]\cdot
-     \frac{\partial \Phi_a}{\partial{\bf u}_a}\right\}
+collision integral, which, for $a=e$, is given by
+\begin{equation}
+  \begin{split}
+    \sum_b\theta_{eb}(\Phi_e,\Phi_b) &= \sum_b \Gamma_{eb}
+    \left\{\frac{\partial}{\partial{\bf u}}\cdot
+     \left(2\frac{m_e}{m_b}\Psi(u_{eb})
+     \frac{{\bf u}}{u^3}\Phi_e\right)\right.\\
+  &+\frac{\partial}{\partial{\bf u}}\cdot
+     \left\{\left[\left(\Phi(u_{eb})
+     -\frac{1}{2 u_{eb}^2}\Psi(u_{eb})\right)
+     \frac{\partial^2u}{\partial{\bf u}
+     \partial{\bf u}}\right]\cdot
+     \frac{\partial \Phi_e}{\partial{\bf u}}\right\}
     \label{eq:coll-lin} \\
-  &+\left. \frac{\partial}{\partial{\bf u}_a}\cdot
-     \left[\left(\frac{1}{u_{ab}^2}\Psi(u_{ab})
-     \frac{{\bf u}_a{\bf u}_a}{u_a^3}\right)\cdot
-   \frac{\partial \Phi_a}{\partial{\bf u}_a}\right]\right\},
-\end{split}
-\end{equation}
-where $u_{ab}\equiv u_a (v_{T_a}/v_{T_b})$, $u_a=v_a/v_{T_a}$,
-with $v_{T_a}$ and $v_{T_b}$ representing the thermal velocity of
-the particles of species $a$ and $b$, respectively. The quantity
-$\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an auxiliary function \cite{
-  Gaffey1976}, in which $\Phi(x) \equiv \frac{2}{\sqrt{\pi}}
+  &+\left. \frac{\partial}{\partial{\bf u}}\cdot
+     \left[\left(\frac{1}{u_{eb}^2}\Psi(u_{eb})
+     \frac{{\bf u}{\bf u}}{u^3}\right)\cdot
+   \frac{\partial \Phi_e}{\partial{\bf u}}\right]\right\},
+\end{split}
+\end{equation}
+where $u_{eb}\equiv u (v_{t_e}/v_{t_b})$, $u=v/v_{t_e}$,
+with $v_{t_e}$ and $v_{t_b}$ representing the thermal velocity of
+electrons and the particles of species $b$, with $b=e,i$. The
+quantity $\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an auxiliary function
+\cite{Gaffey1976}, in which $\Phi(x) \equiv \frac{2}{\sqrt{\pi}}
 \int_0^x e^{-t^2}dt$ is the error function and $\Phi'(x)=
 \frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative. The factor
-$\Gamma_{ab}$ is given by $\Gamma_{ab}=2\pi g Z_b^2 \ln\Lambda $,
+$\Gamma_{eb}$ is given by $\Gamma_{eb}=2\pi g Z_b^2 \ln\Lambda $,
 where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma

### 2019-12-02 thesis.tex
small correction
* thesis.tex: Summary: Only the correction of page 45 was left

* thesis.tex: Summary: Only the correction of page 45 was left

* thesis.tex: Summary: Final correction (if everything goes well)

@@
 with $v_{t_e}$ and $v_{t_b}$ representing the thermal velocity of
-electrons and the particles of species $b$, with $b=e,i$. The
-quantity $\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an auxiliary function
-\cite{Gaffey1976}, in which $\Phi(x) \equiv \frac{2}{\sqrt{\pi}}
-\int_0^x e^{-t^2}dt$ is the error function and $\Phi'(x)=
-\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative. The factor
-$\Gamma_{eb}$ is given by $\Gamma_{eb}=2\pi g Z_b^2 \ln\Lambda $,
+electrons and thermal velocity of the particles of species $b$,
+with $b=e,i$. The quantity $\Psi(x)\equiv\Phi(x)-x\Phi'(x)$ is an
+auxiliary function \cite{Gaffey1976}, in which
+$\Phi(x) \equiv \frac{2}{\sqrt{\pi}}\int_0^x e^{-t^2}dt$ is the error
+function and $\Phi'(x)=\frac{2}{\sqrt{\pi}}e^{-x^2}$ is its derivative.
+The factor $\Gamma_{eb}$ is given by $\Gamma_{eb}=2\pi g Z_b^2 \ln\Lambda $,
 where $g=1/[2^{3/2}(4\pi)^2\hat n \lambda_{De}^3]$ is the plasma

### 2019-12-03 thesis.tex
small correction

@@
 similarities of the asymptotic equilibrium state of the Langmuir waves
-spectrum, considering a combination of an inverse power-law kappa
+spectrum, considering a combination of an inverse power-law Kappa
 distribution and a Maxwellian distribution, in the presence and the
@@
 Therefore, we have two distinct situations. One is the situation in which
-collective modes are not important, and the electric field energy can be
+collective modes are not important, and the electric field energy may be
 expressed by Eq. \eqref{balance} with the electric field fluctuation
 $\left< \delta E^2 \right>_{{\bf k},\omega}^0$ given by \eqref{field-fluc}.
-The other is standard situation, in which collective modes are important,
+The other is the standard situation, in which collective modes are important,
 and the wave electric field is determined by
@@
 new effects in the time evolution subroutine. The main objective here
-was to comprehend important aspects of this so-far unknown expressions,
+was to comprehend important aspects of these so-far unknown expressions,
 how they relate to other equivalent plasma processes and with the
@@
 a theoretical core-halo distribution, composed $95\%$ by a Maxwellian
-core and $5\%$ by a kappa tail, in the presence and in the absence of
+core and $5\%$ by a Kappa tail, in the presence and in the absence of
 bremsstrahlung emission, for several values of the $\kappa$ index. It is
@@
 For use in this asymptotic equation, let us assume isotropic distributions
-for ions and electrons, which are the summation of Maxwellian and kappa
+for ions and electrons, which are the summation of Maxwellian and Kappa
 distributions. In terms of dimensionless variables, we have

### 2019-12-04 thesis.tex
Final (I promise)

@@
 form are given by
-\begin{eqnarray*}
+\begin{eqnarray}
   z_{\bf q}^L = \left(1+\frac{3}{2}q^2\right)^{1/2},
@@
      \left(1+3\frac{T_i}{T_e}\right)^{1/2}.
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 \setcounter{equation}{0}
-\renewcommand{\theequation}{A\arabic{equation}}
+\renewcommand{\theequation}{A.\arabic{equation}}
 In this appendix, we present two different approximations applied to the
@@
 \label{appB}
+\setcounter{equation}{0}
+\renewcommand{\theequation}{B.\arabic{equation}}
 The results presented in Ref. \cite{Tigik2017a} suggest that in the presence
@@
 
-Proceeding in the same way, the expression at the denominator
-of the expression for the asymptotic wave spectrum becomes
+Proceeding in the same way, the expression for the denominator
+of the asymptotic wave spectrum becomes
 \begin{equation*}

### 2019-12-05 thesis.tex
Now it's the final version! =D

@@
   ion-sound and Langmuir frequency range, caused by binary interactions of
-  particles, named \emph{electrostatic bremsstrahlung}. In the present study
+  particles, named \emph{electrostatic bremsstrahlung}. In the present study,
   we introduce the first numerical analysis of these two new equations and
@@
   The first work to be discussed concerns the collisional damping equation, 
-  and in it we compare the results of numerical integration of the rigorous
+  and in it, we compare the results of numerical integration of the rigorous
   expression with the damping rate calculated with the widely applied
@@
   distribution, assumed to be Maxwellian. After a long time-evolution period
-  (numerical integration), the system seems to arrive to a new quasi-steady
+  (numerical integration), the system seems to arrive at a new quasi-steady
   state, in which the shape of the electron velocity distribution resembles
@@
 of this work. \Cref{master} shows the paper that summarizes the results
-of my Master’s dissertation, which may be considered the starting point
+of my Masters dissertation, which may be considered the starting point
 of this doctoral research. % \Cref{appE} explores relevant aspects of
@@
 
-The following paper is fairly self-sustained regarding the theory and
-methods applied. All important equations are there, including their
-normalized form and the normalization constants. 
-% Any doubt regarding the origin of the new equations is filled by \Cref{noneigenmode}.
+The following paper\footnote{Credit: Reproduced from Physics of Plasmas 23,
+  064504 (2016);\url{https://doi.org/10.1063/1.4953802}, with the permission
+  of AIP Publishing.} is fairly self-sustained regarding the theory and methods
+applied. All important equations are there, including their normalized form
+and the normalization constants.
 
 \includepdf[pages=2-6]{Tigik2016b.pdf}
+
 \section{Generation of suprathermal electrons by collective processes
@@
   = 1,&\quad\mu_{\bf q}^S = \frac{q^3}{2^{3/2}}
-	\,\sqrt{\frac{m_e}{m_i}}\;\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},
-\end{align*}
-\begin{align*}
+	\,\sqrt{\frac{m_e}{m_i}}\;\biggl(1+\frac{3T_i}{T_e}\biggr)^{1/2},\\
+% \end{align*}
+% \begin{align*}
   \Phi_a({\bf u})=  v_e^3 F_a({\bf u}),& \quad
@@
 with velocity range $0<v_{\perp}/v_e<16$ and $-16<v_{\parallel}/v_e<16$.
+
+The outcome of this analysis, along with a detailed discussion about
+their importance in the context of solar and space physics can be seen
+in the following paper\footnote{Credit: S. F. Tigik \emph{et al} 2017
+  \emph{ApJL} {\bf 849} L30; \url{https://doi.org/10.3847/2041-8213/aa956f},
+  reproduced by permission of the AAS.}.
 
@@
 \label{appC}
-This publication is mainly related with the results presented in
-Ref. \cite{Tigik2017a}.
-We can say that most of the ideas about the physical processes occurring
-in \cite{Tigik2017a}, regarding the formation of the core-halo velocity
-distribution and the fact that the electrostatic bremsstrahlung could be
-the underlying process behind the ubiquity of such velocity distribution
-in the space environment, came from the analysis of the results presented
-in \cite{Tigik2017b}.
+This publication\footnote{Credit: Reproduced from Physics of Plasmas
+  24, 112902 (2017);\url{https://doi.org/10.1063/1.5009931}, with the
+  permission of AIP Publishing.} is mainly related with the results
+presented in Ref.~\cite{Tigik2017a}. It can be said can say that most
+of the ideas about the physical processes occurring in~\cite{Tigik2017a},
+regarding the formation of the core-halo velocity distribution and the
+fact that the electrostatic bremsstrahlung could be the underlying
+process behind the ubiquity of such velocity distribution in the space
+environment, came from the analysis of the results presented in
+\cite{Tigik2017b}.
 
@@
 \label{master}
-The paper included in this appendix is the complete text of Ref.
-\cite{Tigik2016a}, which summarizes the outcomes of the Master's
-dissertation \cite{Tigik2015} that led to the current doctoral
-research. This text was included here with the intention to give
-the reader a complete view of the work developed during my graduate
-studies.
+The paper\footnote{Credit: S. F. Tigik \emph{et al}, A\&A Volume 586,
+  February 2016, \url{https://doi.org/10.1051/0004-6361/201527271},
+  reproduced with permission, \textcopyright~ESO.} included in this
+appendix is the complete text of Ref. \cite{Tigik2016a}, which
+summarizes the outcomes of the Masters dissertation \cite{Tigik2015}
+that led to the current doctoral research. This text was included
+here with the intention to give the reader a complete view of the
+work developed during my graduate studies.
 
